### 2017-11-14 tex/bvp_paper.tex
initial repo commit

%\documentclass[iop]{emulateapj}
\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography]{revtex4-1}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{bm}
\usepackage{natbib}
\usepackage{longtable}
\LTcapwidth=0.87\textwidth

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}

\newcommand\mnras{{MNRAS}}%

\begin{document}
\author{Evan H. Anders}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Benjamin P. Brown}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\title{BVP Paper}

\begin{abstract}
WOW this is a really long sentence check out this abstract I'll just keep writing words to make this at least
one line long so we know what the formatting looks like, ok?
\end{abstract}
\maketitle

\section{Introduction}
\label{sec:intro}

\section{Experiment} 
\label{sec:experiment}

\section{Results \& Discussion}
\label{sec:results}

\begin{acknowledgments}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133.
\end{acknowledgments}

\appendix
\section{Process for setting enthalpy flux}

%\bibliography{../biblio.bib}
\end{document}

### 2017-11-17 tex/bvp_paper.tex
rough paper outline dumped in

@@
 \label{sec:intro}
+Here we introduce why the timescale problem is hard, and how the choice of initial conditions
+vastly effects the amount of time it takes for a solution to get to a meaningful solution
 
@@
 \label{sec:experiment}
+Here we talk about how to set up the RB problem that we're going to solve, and exactly what
+we're going to compare (how long the run is going to go from base and from bvp, how much time
+we're going to compare over after that, etc.)  We need to compare over a short enough timescale
+that the effects of BVPs don't get washed away, and we also need to compare over long enough
+timescales that we get the rare events we expect.  This is where we put a figure showing the
+time evolution of energy in IVP / BVP side-by-side.
 
@@
 \label{sec:results}
+Here we talk about how the solutions are different, or similar.  This includes:
+\begin{enumerate}
+\item Showing that the flow fields look similar
+\item Showing how the temperature / flux profiles look similar/different
+\item showing how Nu and Re scale with Ra in BVP / IVP.
+\item showing how the PDFs of $w$, $wT$, and $T$ change.
+\end{enumerate}
+
+Then we need to make some comments about whether this is good or bad
+
+Then we need to mention how the same thing can be done in stratified, just there you don't
+assume symmetrical boundary layers.
 

### 2017-11-21 notes/method_description/bvp_method.tex
starts adding notes on bvp writeup

%\documentclass[iop]{emulateapj}
\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography]{revtex4-1}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{bm}
\usepackage{natbib}
\usepackage{longtable}
\LTcapwidth=0.87\textwidth

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}

\newcommand\mnras{{MNRAS}}%

\begin{document}
\title{BVP Methods}

\maketitle

\section{Brief description of method}
In a really simple sense, this is the procedure that is being done when I do the
``BVP solve'' for getting a more converged atmosphere.
\begin{enumerate}
\item Start up IVP, and run it.
\item Once the flows hit Re = 1, wait some time, $t_{\text{transient}}$.
\item After $t_{\text{transient}}$, start taking horizontal and time averages of
specified profiles in the atmosphere.
\item Once the profiles are converged (the change in the profiles at the next timestep
change, on average, less than $f$, where $f$ is a fraction.  If $f=0.01$, the profiles
change no more than 1\% from the previous timestep.), feed them into a 1D problem. 
\item In the 1D problem, adjust the profiles from the atmosphere intelligently.  Feed
those profiles into a BVP that obeys the same thermal boundary conditions as the IVP,
then adjust the mean thermal profile of the IVP atmosphere with the result of the BVP.
\item Keep running the IVP.  If desired, wait some time, $t_{\text{equil}}$, and then restart
from step 3.

\section{More thorough write-up, Boussinesq convection}
In boussinesq convection, the time-steady energy equation can be written as
$$
\Div{ \bm{u} T - \kappa \grad T} = 0
$$
When we take horizontal averages and time averages, and assume constant $\kappa$,
this equation reduces to
$$
\partial_z \angles{(w T)} - \kappa \partial^2_z \angles{(T_0 + T_1)} = 0,
$$
where angles represent a time- and horizontal average.  Further, due to symmetry,
when we take a time- and horizontal average, we find that most of the terms in the 
Rayleigh-Benard momentum equation go away.  Even if they hadn't, the main thing we want
from the momentum equation is an update to the hydrostatic balance of the atmosphere, and
that means that we need to update
$$
\partial_z \angles{p} = \angles{T_1}.
$$

So, put simply, the BVP that we need to solve in RBC is 
\begin{equation}
\begin{split}
\frac{\partial T_1}{\partial z} - T_{1z} &= 0 \\
\kappa \frac{\partial T_{1z}}{\partial z} &= \frac{\partial}{\partial z} \angles{w T}  - \kappa \frac{\partial^2 T_0}{\partial z^2}\\
\frac{\partial p}{\partial z} - T_1 &= 0.
\end{split}
\end{equation}
These three equations, coupled with two properl thermal boundary conditions, retrieve the full
thermodynamic state of the atmosphere.  I've written the equations in their dedalus-like form,
for clarity.

In a real way, the profile of the enthalpy flux thus sets the profile of the thermal structure of
the atmosphere.

\end{enumerate}
\end{document}

### 2017-11-21 notes/method_description/bvp_method.tex
update

@@
 thermodynamic state of the atmosphere.  I've written the equations in their dedalus-like form,
-for clarity.
+for clarity.  I'll solve using fixed temp (top) and fixed flux (temp gradient, bottom) boundary
+conditions.  Dual fixed-flux boundary conditions will work as well, but then the integrated temperature
+profile's constant is actually not unique, so that system has degenerate answers that work for
+the BVP.
 
 In a real way, the profile of the enthalpy flux thus sets the profile of the thermal structure of
-the atmosphere.
+the atmosphere.  In order for this method to work, the profile of the enthalpy flux fed into the
+BVP must be the enthalpy flux profile that we expect in the fully evolved atmosphere.  Getting
+this profile properly is really the subtle part of this method, so let's talk about that.
 

### 2017-11-21 notes/method_description/bvp_method.tex
updates out BVP notes

@@
 \frac{\partial p}{\partial z} - T_1 &= 0.
+\label{eqn:RB_BVP_eqns}
 \end{split}
 \end{equation}
-These three equations, coupled with two properl thermal boundary conditions, retrieve the full
+These three equations, coupled with two proper thermal boundary conditions, retrieve the full
 thermodynamic state of the atmosphere.  I've written the equations in their dedalus-like form,
@@
 conditions.  Dual fixed-flux boundary conditions will work as well, but then the integrated temperature
-profile's constant is actually not unique, so that system has degenerate answers that work for
+profile's constant offset is actually not unique, so that system has degenerate answers that work for
 the BVP.
@@
 
+\subsection{Adjusting the enthalpy flux profile}
+One subtlety of the mixed flux (bot) / temperature (top) boundary conditions is that they are,
+by definition, asymmetrical (at least during the transient).  The non-adiabatic (large) temperature
+gradient in the system means that the system starts with too much energy, and it wants to relax
+to a constant temperature gradient.  To do that, flux needs to leave through the top, and this takes
+a long time when the diffusivities are small.
+
+To illustrate what's happening in our system, I've plotted some fluxes in Fig. \ref{fig:flux_fig}. 
+In the top panel of Fig.
+\ref{fig:flux_fig}, the fluxes of a rayleigh-benard system at Ra = $10^8$ are shown.  This
+plot shows the total flux in the IVP (blue), the convective flux (green), and the conductive flux
+(orange/yellow).  The dashed-dot black line is the flux being sent through the system at the
+bottom boundary.  The short red line is the profile that we get when we divide the enthalpy flux
+by the total flux, and then multiply that normalized profile by the flux entering the lower boundary.
+
+The bottom panel of Fig. \ref{fig:flux_fig} shows a zoom-in on the bottom part of the top panel.
+Here, we show the same "properly normalized" enthalpy flux that we just described in the top panel,
+but it is now shown in green.  This properly normalized profile is used as the enthalpy flux profile
+for the BVP, and this sets the temperature gradient (and thus the conductive flux) that we get
+out of the BVP, which is shown in yellow.  We then feed the temperature profile defined by
+the yellow line back into the IVP, and let the velocities in the IVP naturally react to the abrupt
+change in the background atmosphere.
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{./figs/bvp_fluxes.png}
+\caption{(top) The evolved fluxes from a 2-D rayleigh-benard convection experiment.  The upper
+(fixed temp) boundary is leaking out much more flux than the bottom boundary (fixed flux) supplies
+while the atmosphere equilibrates.  However, we know that the evolved solution should only carry
+the amount of flux supplied at the lower plate.  In the bottom panel, we show the enthalpy flux
+in the IVP, divided by the total flux, and then multiplied by the flux at the bottom boundary. This
+gives us an idea of what the enthalpy flux should be like in the evolved state, including the
+boundary layers.  The corresponding conductive flux that the temperature profile would have to
+carry is shown in yellow. \label{fig:flux_fig}}
+\end{figure}
+
+\subsection{The actual procedure, and open questions}
+So basically what we do is:
+\begin{enumerate}
+\item Run the IVP to get average fluxes, as in the top panel of Fig. \ref{fig:flux_fig}.
+\item Normalize the enthalpy flux profile properly to get the enthalpy flux profile as shown
+in the bottom panel of Fig. \ref{fig:flux_fig}
+\item Use that normalized enthalpy flux profile as a RHS constant forcing term in the BVP equations
+(Eqns. \ref{eqn:RB_BVP_eqns}), and solve for the consistent temperature profile that satisfies
+those equations under the proper boundary conditions
+\item Update the full fields in the IVP such that the mean pressure and temperature profiles are
+the pressure / temperature profiles that come out of the BVP.
+\item Run the IVP so that the velocity field relaxes in the presence of the new atmosphere.
+\end{enumerate}
+
+This seems to work well.  Open questions:
+\begin{enumerate}
+\item How long do we average over?  What's the right criterion for having a converged profile?
+\item How many times do we need to do the BVP to get to the right answer?  If we get the right
+converged profile, I think we're only going to need one BVP.
+\item How long does it take the velocity field to fully equilibrate post-BVP?
+\item How similar is the BVP final state to the IVP final state?
+\end{enumerate}
+
+Note: this is not hard to implement in fully compressible, too!
+
 \end{enumerate}

### 2017-11-21 notes/method_description/bvp_method.tex
writes up FC bvp

@@
 
+\section{Extension to Stratified convection and FC equation}
+This method is, fortunately, not hard to extend to the fully compressible equations. For
+a system whose full energy equation is of the form
+$$
+\frac{\partial E}{\partial t} + \Div{\bm{F}} = \kappa (\text{IH}),
+$$
+which is true of both polytropes and internally heated atmospheres, we find that the time
+stationary, vertically averaged profile is, once again,
+\begin{equation}
+\kappa\frac{\partial \angles{T_{1z}}}{\partial z} = 
+\frac{\partial}{\partial z}(\angles{\bm{F}_{\text{conv}} - \kappa T_{0z}} - \kappa (IH)
+\end{equation}
+And, for a properly constructed atmosphere where the initial profile carries the internal
+heating, the last two terms of this expression perfectly cancel each other out (at least,
+for constant $\kappa$, and for the atmospheres we're worried about right now).  So, with that,
+the full set of BVP equations for fully compressible atmospheres is
+\begin{equation}
+\begin{split}
+\frac{\partial T_1}{\partial z} - T_{1z} &= 0 \\
+\kappa \frac{\partial T_{1z}}{\partial z} &= \frac{\partial \bm{F}_{\text{conv}}}{\partial z} \\
+T_0 \partial_z \rho_1 + T_1 \partial_z \rho_0 + \rho_0 T_{1z} + \rho_1 T_{0z} &= - T_1 \partial_z \rho_1 - \rho_1 T_{1z} \\
+\frac{\partial M_1}{\partial z} - \rho_1 &= 0.
+\label{eqn:FC_BVP_eqns}
+\end{split}
+\end{equation}
+Here the first two equations are just the energy equation, the third equation is that the
+fluctuating components must be in hydrostatic equilibrium ($\grad P = \grad (\rho T) = 
+\rho \grad T + T \grad \rho = 0$, and assuming that the background is in hydrostatic equilibrium
+such that gravity drops out of the system), and the fourth equation is our mass conservation equation.
+This requires four boundary conditions: two thermal ones (fixed flux bot, fixed temp top), and
+two mass ones ($M_1 = 0$ at top and bottom).  Once again, by specifying the appropriate profile
+for the convective flux, the rest of the atmosphere follows.  This is also nice, because this
+formulation should also work with minor tweaks for more complicated forms of $\kappa$.
+
 \end{enumerate}

### 2017-11-27 tex/bvp_paper.tex
writes out ROUGH draft of introduction to BVP paper

@@
 \label{sec:intro}
-Here we introduce why the timescale problem is hard, and how the choice of initial conditions
-vastly effects the amount of time it takes for a solution to get to a meaningful solution
+In many simple studies of convection, the choice of boundary conditions greatly influences the dynamics
+of the evolved state.  In studies of incompressible, Boussinesq, \RB convection (RBC), many studies
+employ fixed temperature (Dirichlet) boundary conditions at the top and bottom, or fixed heat flux
+(Neumann) boundary conditions at both plates.  The former case represents plates of infinite conductivity,
+whereas the latter plates of finite conductivity.  In both cases, the choice of symmetric boundary
+conditions maintains overall system symettry, and both have been shown to transport heat in nearly the
+same manner \cite{johnston&doering2009}.
+
+Studies of convection in stratified systems which aim to model convection in natural, astrophysical systems,
+such as that in the outer envelope of low-to-moderate mass stars like the Sun, often employ a mixture of these
+two types of boundary conditions (references, references).  The flux at the lower boundary is fixed, modeling
+the constant energy generation of the stellar core, while the outer boundary condition is held at a fixed temperature,
+effectively allowing all heat generated to escape.
+
+While this setup is a useful model for understanding natural
+systems, simulations which employ this setup often suffer from a long convective transient as the thermodynamic structure
+of the atmosphere relaxes to the adiabatic profile specified by the fixed temperature upper boundary condition.
+This long evolution occurs on the ``Kelvin-Helmholtz,'' or thermal diffusion timescale of the atmosphere, 
+$t_{\text{KH}} \approx L_z^2 / \chi$, where $L_z$ is the domain depth and $\chi$ is the thermal diffusivity.
+Interesting convection happens as high values of the Rayleigh number, which scales like $\chi^{-1/2}$, such that
+in the astrophysically interesting regime of high-Ra, highly stratified convection, evolving a simulation for a
+KH time becomes numerically intractable.  As the Rayleigh number increases, the KH time increases while the average
+timestep required to resolve the more turbulent flows decreases.  The net result is that under standard initial conditions
+of hydrostatic- and thermal- equilibrium, the desired convective solution cannot be obtained and the dynamics of convection
+there cannot be studied.
+
+Here we present a method for using simple boundary value problems, along with information about the evolved flow fields,
+to fast-forward the slow thermal evolution of convecting simulations.  We present this method in the context of RBC, and
+then demonstrate that it applies to stratified, compressible convection under a simple modification.  These methods allow
+us to study the convective flows driven by the evolved thermal profile while only requiring initial value problems to run
+for long enough to resolve the fast dynamical timescales of convection.
 
@@
 
-%\bibliography{../biblio.bib}
+\bibliography{biblio.bib}
 \end{document}

### 2017-11-27 tex/bvp_paper.tex
placeholders Jeff as an author
work on experiment section

@@
 \affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
+\author{Jeffrey Oishi}
+\affiliation{Bates}
 \title{BVP Paper}
@@
 \label{sec:experiment}
-Here we talk about how to set up the RB problem that we're going to solve, and exactly what
-we're going to compare (how long the run is going to go from base and from bvp, how much time
-we're going to compare over after that, etc.)  We need to compare over a short enough timescale
-that the effects of BVPs don't get washed away, and we also need to compare over long enough
-timescales that we get the rare events we expect.  This is where we put a figure showing the
-time evolution of energy in IVP / BVP side-by-side.
+\subsection{Incompressible, Boussinesq \RB Convection}
+In studies of convection, it is natural to nondimensionalize the flows on the freefall velocity.
+Under the Boussinesq approximation, where $\rho = \rho_0 (1 - \alpha T_1)$ on the gravitational term in the momentum
+equation and $\rho = \rho_0$ on all other terms, the freefall velocity is $v_{\text{ff}} = \sqrt{\alpha g L^2 (dT/dz)_0}$.
+where $L$ is the depth of the domain, $g$ is the gravitational acceleration, and $(dT/dz)_0$ is the initial temperature
+gradient of the atmosphere, which controls the flux through the system.  The typical timescale and length scale
+then relate to each other according to $t_{\text{ff}} = L/v_{\text{ff}}$.
+Under this nondimensionalization, the Boussinsq, incompressible equations of motion are
+\begin{gather}
+\Div{\bm{u}} = 0, 
+	\label{eqn:incompressible}
+\\
+\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
+-\grad\varpi + T_1\hat{z} + \frac{\text{Pr}}{\text{Ra}}\grad^2\bm{u}, 
+	\label{eqn:bouss_momentum_eqn}
+\\
+\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \frac{1}{\text{Pr}\,\text{Ra}}\grad^2 T_1,
+	\label{eqn:bouss_energy_eqn}
+\end{gather}
+where
+\begin{equation}
+\text{Ra} = \frac{g \alpha L^4 \left(\frac{dT}{dz}\right)_0}{\nu\chi} = \frac{(L\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}
+\end{equation}
+are the nondimensional Rayleigh and Prandtl numbers, where $\nu$ is the viscous diffusivity and $\chi$ is
+the thermal diffusivity.
+
+One hallmark of Boussinesq convection is that upflows and downflows are symmetric, and thus the long time- and horizontal-
+average of the velocity field is exactly zero.  Assuming that the velocity field has perfect symmetry over a long time
+average, the horizontally-averaged, steady state momentum equation is just
+\begin{equation}
+\frac{\partial}{\partial z}\angles{\varpi} = \angles{T_1}\hat{z},
+	\label{eqn:simple_momentum}
+\end{equation}
+where $\angles{A}$ represent the horizontal- and time- average of the quantity $A$.  Thus, in the evolved solution, the
+vertical profile of the pressure perturbations are directly determined by the temperature field. 
+Under the Boussinesq approximation, $\bm{u}\cdot\grad(A) = \Div{\bm{u}A}$, and thus the steady state energy equation
+is just
+\begin{equation}
+\frac{\partial}{\partial z}\angles{w(T_0 + T_1)} = \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1}.
+	\label{eqn:simple_energy}
+\end{equation}
+Eqns (\ref{eqn:simple_momentum}) \& (\ref{eqn:simple_energy}) combine to form a second-order ODE which specifies the
+mean vertical profile of the temperature and pressure fields in the evolved solution.  These fields are completely specified
+by a set of two thermal boundary conditions and the evolved 
+profile of the convective flux, $F_{\text{conv}} = \angles{w(T_0 + T_1)}$.
+
+Under the choice of mixed thermal boundary conditions ($dT_1/dz = 0$ at $z = -1/2$, $T_1 = 0$ at $z = +1/2$), the initial
+atmosphere starts off with much more thermal energy ($\propto T$) than the evolved adiabatic solution pegged by the
+top temperature boundary condition.  This excess energy must leave the system through the upper (fixed $T$) boundary
+during the convective transient, and this results in an asymmetric flux profile during the slow thermal evolution of the
+atmosphere.  Furthermore, the convective flux (and the flux at the upper boundary layer) are O(1) during the convective
+transient, whereas the flux entering the atmosphere at the lower boundary is O(Ra$^{-1/2}$), so the asymmetry of the fluxes
+becomes increasingly pronounced as Ra is increased into the turbulent realm.
+
+In order to find the evolved temperature profile of the atmosphere, the evolved profile of the convective flux must
+be known.  We know that the evolved solution should be in flux equilibrium, and we know that the evolved flux through
+the atmosphere is the flux entering through the bottom.  Thus, the steady-state profile of the convective flux can be
+approximated as
+\begin{equation}
+F_{\text{conv, steady}} = F_{\text{bot}}\frac{\angles{w(T_0 + T_1)}}{\angles{w(T_0 + T_1) - \kappa \partial_z (T_0 + T_1)}}
+= F_{\text{bot}}\frac{\angles{F_{\text{conv, IVP}}}}{\angles{F_{\text{tot, IVP}}}}.
+\end{equation}
+Or, put simply, the steady state convective flux is what you get get rid of the asymmetry in the flux profile.
+This flux defined here is used in a 1D boundary value problem solve of 
+eqns (\ref{eqn:simple_momentum}) \& (\ref{eqn:simple_energy}) along with the appropriate boundary values.  The solution
+to that BVP is then used as new initial conditions, convection restarts, and so on.
 

### 2017-11-28 tex/bvp_paper.tex
adds FC equations

@@
 \newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
+\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
 \newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
@@
 \begin{gather}
-\Div{\bm{u}} = 0, 
+\DivU = 0, 
 	\label{eqn:incompressible}
@@
 
+\subsection{Fully Compressible Convection}
+We study stratified convection in an ideal gas whose adiabatic index is $\gamma = 5/3$.
+The initial atmospheric stratification is polytropic \cite{anders&brown2017}.
+We assume a Newtonian radiative conduction term \cite{lecoanet&all2014}, and solve the
+fully compressible Navier-Stokes equations of the form
+\begin{gather}
+\frac{\partial \ln \rho}{\partial t} + \bm{u}\cdot\grad\ln\rho + \DivU = 0
+	\label{eqn:FC_continuity}
+\\
+\frac{D \bm{u}}{Dt} = -T\grad\ln\rho - \grad T + \bm{g} - \Div{\stressT}
+	\label{eqn:FC_momentum}
+\\
+\frac{D T}{D t} + (\gamma-1)T\DivU = 
+\frac{1}{\rho c_V}\left(\kappa\grad^2 T - [\stressT\cdot\grad]\cdot\bm{u}\right),
+	\label{eqn:FC_energy}
+\end{gather}
+where $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$ and the viscous stress
+tensor is defined as
+\begin{equation}
+\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij
+}\DivU\right)
+\label{eqn:stress_tensor}
+\end{equation}
+and $\delta_{ij}$ is the Kronecker delta function.
+
 \section{Results \& Discussion}
@@
 \appendix
-\section{Process for setting enthalpy flux}
+\section{Table of Boussinesq Runs}
+
+\section{Table of stratified runs}
 

### 2017-11-30 tex/bvp_paper.tex
more small progress on paper.

@@
 there cannot be studied.
+
+Knowledge of Mixing Length theory and the nature of evolved convection has been used in some 
+previous studies (e.g., \cite{brandenburg&all2005}) to choose smarter initial conditions than
+the hydrostatic polytropic states.  However, these assumptions work best in convective regions
+which are bounded by stable layers.  In simple atmospheres where boundary layers form to meet
+boundary conditions at the upper and lower edge of the atmosphere, we cannot know 
+\emph{a priori} what the extent or shape of the boundary layer will be, as that must be chosen
+by the convective dynamics, and specification of the proper boundary layer is essential for
+placing the atmosphere along the proper adiabat.
 
@@
 
+\subsubsection{The Boundary Value Equations}
+In studies of fully compressible convection, the flux carried by the adiabatic temperature gradient
+is not available for convection.  Thus, only the flux \emph{in excess} of the adiabat will drive
+convection and be carried by convection.  As such, this is the only portion of the flux which
+must be examined to determine if the solution is in a converged state.  In a system with
+a fixed flux boundary condition, the available superadiabatic flux is
+\begin{equation}
+F_{\text{avail}} = -\kappa(\grad T_0 - \grad T_{\text{ad}}) = \kappa\frac{\epsilon}{c_P}\grad T_0,
+\end{equation}
+which is small when $\epsilon$ is small and only requires low Mach number convective flows
+to carry it.  In a perfectly evolved solution, there will be thin boundary layers in which
+conduction carries this flux in addition to the adiabatic flux, but in an efficient convective
+interior, convective fluxes must carry this full amount.
+
+The BVP equations are inspired by equations of stellar modeling  \cite{paxton&all2011} but adapted to these simulations
+of fully compressible convection.  Here, rather than parameterizing convection, we can get the
+convective fluxes directly from our simulation adn use them to solve for the appropriate structure
+of the atmosphere.  The FC BVP equations are
+\begin{gather}
+\frac{d M_1}{dz} = \rho_1 \\
+T_0 \grad \rho_1 + T_1 \grad \rho_0 + \rho_1 g = - T_0 \grad \rho_0 - T_1 \grad \rho_1 - \rho_0 g \\
+\kappa \frac{d^2 T_1}{d z^2} = -\frac{d}{dz}F_{\text{conv, z}},
+\end{gather}
+which ensure mass conservation, thermal equilibrium, and that the atmosphere is, on average,
+in hydrostatic equilibrium.  We couple these equations with four boundary conditions (mixed
+flux / temperature boundary conditions, as well as setting $M_1 = 0$ at the top and bottom
+of the atmosphere).
+
 \section{Results \& Discussion}

### 2017-12-07 tex/bvp_paper.tex
somes changes to paper & code

@@
 \label{sec:intro}
-In many simple studies of convection, the choice of boundary conditions greatly influences the dynamics
-of the evolved state.  In studies of incompressible, Boussinesq, \RB convection (RBC), many studies
-employ fixed temperature (Dirichlet) boundary conditions at the top and bottom, or fixed heat flux
-(Neumann) boundary conditions at both plates.  The former case represents plates of infinite conductivity,
-whereas the latter plates of finite conductivity.  In both cases, the choice of symmetric boundary
-conditions maintains overall system symettry, and both have been shown to transport heat in nearly the
-same manner \cite{johnston&doering2009}.
+In numerical studies of convection, the chosen boundary conditions at the upper and lower plates
+determines key quantities of the dynamics of the evolved state.
+Studies of incompressible, Boussinesq, \RB convection (RBC) often
+employ fixed temperature (Dirichlet) or fixed heat flux
+(Neumann) boundary conditions at both plates.  
+Dirichlet conditions represent plates of infinite conductivity,
+whereas Neumann condition model plates of finite conductivity.  
+In both cases, choosing symmetric boundary conditions maintains overall system symmetry, 
+and despite evolving towards quite different thermal structures, both types of conditions
+transport heat in the same manner \cite{johnston&doering2009}.
 
-Studies of convection in stratified systems which aim to model convection in natural, astrophysical systems,
-such as that in the outer envelope of low-to-moderate mass stars like the Sun, often employ a mixture of these
-two types of boundary conditions (references, references).  The flux at the lower boundary is fixed, modeling
-the constant energy generation of the stellar core, while the outer boundary condition is held at a fixed temperature,
-effectively allowing all heat generated to escape.
+Studies of convection in stratified systems which aim to model convection 
+in astrophysical systems, such as the outer envelopes of low-to-moderate mass stars 
+like the Sun, often employ a mixture of these
+two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991}.  
+The flux at the lower boundary is fixed, modeling
+the constant energy generation of the stellar core, 
+while the outer boundary condition is held at a fixed temperature,
+modeling the surface of a star which must output the energy generated internally.
 

### 2017-12-07 code/boussinesq_dynamics/equations.py

@@ -547,6 +547,23 @@ class BoussinesqEquations2D(BoussinesqEquations):
         snapshots.add_task("w")
         analysis_tasks.append(snapshots)
 
+        powers = solver.evaluator.add_file_handler(data_dir+'powers', sim_dt=output_dt, max_writes=max_slice_writes, mode=mode)
+        powers.add_task("interp(T1,         z={})".format(self.Lz/2),    name='T midplane', layout='c')
+        powers.add_task("interp(T1,         z={})".format(0.05*self.Lz), name='T near bot', layout='c')
+        powers.add_task("interp(T1,         z={})".format(0.95*self.Lz), name='T near top', layout='c')
+        powers.add_task("interp(u,         z={})".format(self.Lz/2),    name='u midplane' , layout='c')
+        powers.add_task("interp(u,         z={})".format(0.05*self.Lz), name='u near bot' , layout='c')
+        powers.add_task("interp(u,         z={})".format(0.95*self.Lz), name='u near top' , layout='c')
+        powers.add_task("interp(w,         z={})".format(self.Lz/2),    name='w midplane' , layout='c')
+        powers.add_task("interp(w,         z={})".format(0.05*self.Lz), name='w near bot' , layout='c')
+        powers.add_task("interp(w,         z={})".format(0.95*self.Lz), name='w near top' , layout='c')
+        for i in range(10):
+            fraction = 0.1*i
+            powers.add_task("interp(T1,     x={})".format(fraction*self.Lx), name='T at x=0.{}Lx'.format(i), layout='c')
+        analysis_tasks.append(powers)
+
+
+
         if coeff_output:
             coeffs = solver.evaluator.add_file_handler(data_dir+'coeffs', sim_dt=output_dt, max_writes=max_slice_writes, mode=mode)
             coeffs.add_task("T1+T0", name="T", layout='c')

### 2017-12-07 code/rayleigh_benard.py

@@ -156,12 +156,12 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
     checkpoint.set_checkpoint(solver, wall_dt=checkpoint_min*60, mode=mode)
         
     # Integration parameters
-    if not isinstance(run_time_therm, type(None)):
-        solver.stop_sim_time = run_time_therm*equations.thermal_time + solver.sim_time
-    elif not isinstance(run_time_buoyancy, type(None)):
-        solver.stop_sim_time  = run_time_buoyancy + solver.sim_time
-    else:
-        solver.stop_sim_time  = np.inf
+#    if not isinstance(run_time_therm, type(None)):
+#        solver.stop_sim_time = run_time_therm*equations.thermal_time + solver.sim_time
+#    elif not isinstance(run_time_buoyancy, type(None)):
+#        solver.stop_sim_time  = run_time_buoyancy + solver.sim_time
+#    else:
+    solver.stop_sim_time  = np.inf
     solver.stop_wall_time = run_time*3600.
     solver.stop_iteration = run_time_iter
 
@@ -203,6 +203,8 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
         logger.info('Starting loop')
         Re_avg = 0
         continue_bvps = True
+        not_corrected_times = True
+        init_time = solver.sim_time
         while (solver.ok and np.isfinite(Re_avg)) and continue_bvps:
             dt = CFL.compute_dt()
             solver.step(dt) #, trim=True)
@@ -211,6 +213,13 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
             log_string += 'Time: {:8.3e} ({:8.3e} therm), dt: {:8.3e}, '.format(solver.sim_time, solver.sim_time/equations.thermal_time,  dt)
             log_string += 'Re: {:8.3e}/{:8.3e}'.format(Re_avg, flow.max('Re'))
             logger.info(log_string)
+
+            if not_corrected_times and Re_avg > 1:
+                if not isinstance(run_time_therm, type(None)):
+                    solver.stop_sim_time = run_time_therm*equations.thermal_time + solver.sim_time
+                elif not isinstance(run_time_buoyancy, type(None)):
[…]

### 2017-12-08 tex/bvp_paper.tex
restructured paper

@@
 Knowledge of Mixing Length theory and the nature of evolved convection has been used in some 
-previous studies (e.g., \cite{brandenburg&all2005}) to choose smarter initial conditions than
+previous studies (e.g., \cite{brandenburg&all2005}) to choose initial conditions which are
+closer to the correct evolved adiabat than
 the hydrostatic polytropic states.  However, these assumptions work best in convective regions
@@
 
-Here we present a method for using simple boundary value problems, along with information about the evolved flow fields,
-to fast-forward the slow thermal evolution of convecting simulations.  We present this method in the context of RBC, and
-then demonstrate that it applies to stratified, compressible convection under a simple modification.  These methods allow
-us to study the convective flows driven by the evolved thermal profile while only requiring initial value problems to run
+Here we present a method for using simple boundary value problems, 
+along with information about the evolved flow fields,
+to fast-forward the slow thermal evolution of convecting simulations.  
+We present this method in the context of RBC, and
+then demonstrate that applying it to stratified, compressible convection 
+is simple.  These methods allow us to study the convective flows driven by 
+nearly the evolved thermal profile while only requiring initial value problems to run
 for long enough to resolve the fast dynamical timescales of convection.
 
-\section{Experiment} 
+\section{Incompressible, Boussinesq \RB Convection}
 \label{sec:experiment}
-\subsection{Incompressible, Boussinesq \RB Convection}
-In studies of convection, it is natural to nondimensionalize the flows on the freefall velocity.
-Under the Boussinesq approximation, where $\rho = \rho_0 (1 - \alpha T_1)$ on the gravitational term in the momentum
-equation and $\rho = \rho_0$ on all other terms, the freefall velocity is $v_{\text{ff}} = \sqrt{\alpha g L^2 (dT/dz)_0}$.
-where $L$ is the depth of the domain, $g$ is the gravitational acceleration, and $(dT/dz)_0$ is the initial temperature
-gradient of the atmosphere, which controls the flux through the system.  The typical timescale and length scale
-then relate to each other according to $t_{\text{ff}} = L/v_{\text{ff}}$.
-Under this nondimensionalization, the Boussinsq, incompressible equations of motion are
+In general, the method for fast-forwarding the atmospheric structure to the correct adiabat is
+simple and involves only a few steps.  At the start of convective simulations, a large transient
+occurs while the hydrostatic state gives way to the convective state.  After the peak of this
+transient, we begin to average the mean vertical profile of the convective flux and the conductive
+flux through the domain.  Once those flux profiles are converged, we solve a simple 
+boundary value problem using the information that those fluxes provide to determine what the
+evolved thermal structure of the atmosphere can be.  The stratification of the initial value
+problems is then adjusted to match the output of the BVP, and we run convection for dynamical
+timescales to let the flows adjust to the new, updated thermal structure.  We then measure
+quantities of the dynamics, and compare them to the dynamics of simulations which underwent a
+long thermal rundown, to determine if our simple BVPs effectively get our convective solution
+to the correct state.
+
+\subsection{Governing Equations, Nondimensionalization, and Domain setup}
+In our first set of experiments, we adopt the Oberbeck-Boussinesq approximation.  Here, the
+fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
+of thermal expansion ($\alpha$).  We non-dimensionalize length by the layer height ($L_z$) ,
+temperature by the (constant) initial temperature gradient across the layer ($\grad T_0$), and time
+by the freefall timescale ($L_z / v_{\text{ff}}$, with $v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$, where $g$ is 
+uniform gravitational acceleration in the $-\hat{z}$ direction). The dimensionless Boussinesq
+equations governing the velocity $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, temperature
+$T = T_0 + T_1$, and reduced pressure $\varpi$ are (cite Rayleigh, chandrasekar)
 \begin{gather}
@@
 \end{gather}
-where
+where the dimensionless control parameters are the Rayleigh and Prandtl numbers,
 \begin{equation}
-\text{Ra} = \frac{g \alpha L^4 \left(\frac{dT}{dz}\right)_0}{\nu\chi} = \frac{(L\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}
+\text{Ra} = \frac{g \alpha L^4 \left(\frac{dT}{dz}\right)_0}{\nu\chi} = \frac{(L\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
 \end{equation}
-are the nondimensional Rayleigh and Prandtl numbers, where $\nu$ is the viscous diffusivity and $\chi$ is
-the thermal diffusivity.
+The dimensionless vertical extent of the domain is $z = [-1/2, 1/2]$, and at the boundaries
+we impose no-slip, impenetrable boundary conditions such that $w = u = v = 0$ at $z = \pm 1/2$.
+At the lower boundary, we employ a fixed flux condition such that $\partial T_1 / \partial z = 0$
+at $z = -1/2$, and we impose a fixed temperature condition $T_1 = 0$ at $z = 1/2$. Both
+horizontal directions are periodic and have equal aspect ratio, $\gamma = 4$, such that
+the horizontal coordinates $x, y = [0, \Gamma]$.
 
-One hallmark of Boussinesq convection is that upflows and downflows are symmetric, and thus the long time- and horizontal-
-average of the velocity field is exactly zero.  Assuming that the velocity field has perfect symmetry over a long time
-average, the horizontally-averaged, steady state momentum equation is just
-\begin{equation}
+\subsection{The Boundary Value Problem}
+The Boussinesq BVP is simply the time-stationary, horizontally- and time- averaged equations
+of hydrostatic balance and energy conservation,
+\begin{gather}
 \frac{\partial}{\partial z}\angles{\varpi} = \angles{T_1}\hat{z},
-	\label{eqn:simple_momentum}
-\end{equation}
-where $\angles{A}$ represent the horizontal- and time- average of the quantity $A$.  Thus, in the evolved solution, the
-vertical profile of the pressure perturbations are directly determined by the temperature field. 
-Under the Boussinesq approximation, $\bm{u}\cdot\grad(A) = \Div{\bm{u}A}$, and thus the steady state energy equation
-is just
-\begin{equation}
-\frac{\partial}{\partial z}\angles{w(T_0 + T_1)} = \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1}.
-	\label{eqn:simple_energy}
-\end{equation}
-Eqns (\ref{eqn:simple_momentum}) \& (\ref{eqn:simple_energy}) combine to form a second-order ODE which specifies the
-mean vertical profile of the temperature and pressure fields in the evolved solution.  These fields are completely specified
-by a set of two thermal boundary conditions and the evolved 
-profile of the convective flux, $F_{\text{conv}} = \angles{w(T_0 + T_1)}$.
+	\label{eqn:bouss_BVP_momentum}
+\\
+\frac{\partial}{\partial z}\angles{wT_1} = \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1},
+	\label{eqn:bouss_BVP_energy}
+\end{gather}
+where $\angles{A}$ represents a time- and horizontally averaged profile of the quantity $A$.  These
+equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum_eqn}-\ref{eqn:bouss_energy_eqn})
+and neglecting terms that vanish due to symmetry in the evolved flows.  Convective flows
+are perturbations around a thermal profile defined by these equations in the proper evolved state.
 
-Under the choice of mixed thermal boundary conditions ($dT_1/dz = 0$ at $z = -1/2$, $T_1 = 0$ at $z = +1/2$), the initial
-atmosphere starts off with much more thermal energy ($\propto T$) than the evolved adiabatic solution pegged by the
-top temperature boundary condition.  This excess energy must leave the system through the upper (fixed $T$) boundary
-during the convective transient, and this results in an asymmetric flux profile during the slow thermal evolution of the
-atmosphere.  Furthermore, the convective flux (and the flux at the upper boundary layer) are O(1) during the convective
+In Boussinesq RBC, the thermal structure of the atmosphere is fully determined by the specification
+of the convective flux, $F_{conv} = \angles{w T_1}$.  If this profile is known, then $T_1$ and
+$\varpi$ can be found under the proper specifications of boundary conditions.  
+Under the choice of mixed thermal boundary conditions, the initial
+atmosphere contains more thermal energy ($\propto T$) than the 
+evolved adiabatic solution.  As the atmosphere adjusts to be nearly isothermal in the interior,
+it must evolve towards the (cold) temperature value specified at the upper boundary.
+The evolution of the atmosphere results in an asymmetric flux profile during 
+the slow thermal evolution of the atmosphere.  Furthermore, under our nondimensionalization,
+the convective flux (and the flux at the upper boundary layer) are O(1) during the convective
 transient, whereas the flux entering the atmosphere at the lower boundary is O(Ra$^{-1/2}$), so the asymmetry of the fluxes
@@
 
-In order to find the evolved temperature profile of the atmosphere, the evolved profile of the convective flux must
-be known.  We know that the evolved solution should be in flux equilibrium, and we know that the evolved flux through
-the atmosphere is the flux entering through the bottom.  Thus, the steady-state profile of the convective flux can be
-approximated as
+In order to find the evolved temperature profile of the atmosphere using the Boussinesq BVP equations, 
+the evolved profile of the convective flux must be properly specified.  In order to construct
+this profile, we acknowledge that the evolved solution will in flux equilibrium, 
+carrying the amount of the flux entering through the bottom.  
+Thus, the steady-state profile of the convective flux can be approximated as
 \begin{equation}
-F_{\text{conv, steady}} = F_{\text{bot}}\frac{\angles{w(T_0 + T_1)}}{\angles{w(T_0 + T_1) - \kappa \partial_z (T_0 + T_1)}}
+F_{\text{conv, steady}} = F_{\text{bot}}\frac{\angles{wT_1}}{\angles{wT_1 - \kappa \partial_z (T_0 + T_1)}}
 = F_{\text{bot}}\frac{\angles{F_{\text{conv, IVP}}}}{\angles{F_{\text{tot, IVP}}}}.
+\label{eqn:bouss_BVP_fconv}
 \end{equation}
-Or, put simply, the steady state convective flux is what you get get rid of the asymmetry in the flux profile.
-This flux defined here is used in a 1D boundary value problem solve of 
-eqns (\ref{eqn:simple_momentum}) \& (\ref{eqn:simple_energy}) along with the appropriate boundary values.  The solution
-to that BVP is then used as new initial conditions, convection restarts, and so on.
+Or, put simply, the steady state convective flux is retrieved by properly removing the asymmettry
+from the flux profile.
 
-\subsection{Fully Compressible Convection}
+In our Boussinesq BVPs, we solve Eqns. (\ref{eqn:bouss_BVP_momentum}-\ref{eqn:bouss_BVP_energy}),
+substituting $\angles{wT_1} = F_{\text{conv, steady}}$ as defined in eqn. (\ref{eqn:bouss_BVP_fconv})
+to retrieve the proper vertical profile of $T_1$ and $\varpi$.  We then update the mean horizontal value
+of $T_1$ and $\varpi$ in a corresponding IVP, and continue to timestep forward with the newly adjusted
+atmosphere.
+
+\subsection{Numerics}
+
+\subsection{Results}
+Here we talk about how the solutions are different, or similar.  This includes:
+\begin{enumerate}
+\item Showing that the flow fields look similar
+\item Showing how the temperature / flux profiles look similar/different
+\item showing how Nu and Re scale with Ra in BVP / IVP.
+\item showing how the PDFs of $w$, $wT$, and $T$ change.
+\end{enumerate}
+
+Then we need to make some comments about whether this is good or bad
+
+Then we need to mention how the same thing can be done in stratified, just there you don't
+assume symmetrical boundary layers.
+
+\section{Fully Compressible Convection}
+
+\subsection{Governing Equations}
 We study stratified convection in an ideal gas whose adiabatic index is $\gamma = 5/3$.
@@
 
-\subsubsection{The Boundary Value Equations}
+\subsection{The Boundary Value Equations}
 In studies of fully compressible convection, the flux carried by the adiabatic temperature gradient
@@
 
-\section{Results \& Discussion}
+\subsection{Results}
+
+\section{Discussion \& Conclusions}
 \label{sec:results}
-Here we talk about how the solutions are different, or similar.  This includes:
-\begin{enumerate}
-\item Showing that the flow fields look similar
-\item Showing how the temperature / flux profiles look similar/different
-\item showing how Nu and Re scale with Ra in BVP / IVP.
-\item showing how the PDFs of $w$, $wT$, and $T$ change.
-\end{enumerate}
-
-Then we need to make some comments about whether this is good or bad
-
-Then we need to mention how the same thing can be done in stratified, just there you don't
-assume symmetrical boundary layers.
 

### 2017-12-08 code/bvps/bvp_tools.py
fixes BVP to work with Oy

@@ -414,9 +414,8 @@ class BoussinesqBVPSolver(BVPSolverBase):
                         ])
     VEL_VARS = OrderedDict([
                 ('w_IVP',               'w'), 
-                ('wz_IVP',              'wz'), 
+                ('Oy_IVP',              'Oy'), 
                 ('u_IVP',               'u'), 
-                ('uz_IVP',              'uz'), 
                         ])
 
     def __init__(self, atmosphere_class, *args, **kwargs):
@@ -517,7 +516,7 @@ class BoussinesqBVPSolver(BVPSolverBase):
             atmosphere.problem = de.NLBVP(atmosphere.domain, variables=['T1', 'T1_z','p1'], ncc_cutoff=tolerance)
 
             #Zero out old varables to make atmospheric substitutions happy.
-            old_vars = ['u', 'w', 'dx(A)', 'uz', 'wz']
+            old_vars = ['u', 'w', 'dx(A)', 'Oy']
             for sub in old_vars:
                 atmosphere.problem.substitutions[sub] = '0'
 

### 2017-12-11 code/bvps/bvp_tools.py
lots of run script updates

@@ -275,6 +275,8 @@ class BVPSolverBase:
         """
         #Don't average if all BVPs are done
         if self.completed_bvps >= self.num_bvps:
+            if self.flow.grid_average('Re') < min_Re:
+               self.avg_time_start = self.solver.sim_time
             return
 
         if self.flow.grid_average('Re') > min_Re:

### 2017-12-11 code/rayleigh_benard.py

@@ -48,7 +48,7 @@ Options:
     --bvp_transient_time=<time>          How long to wait at beginning of run before starting to average for next one, in tbuoy [default: 20]
     --min_bvp_time=<time>                Minimum avg time for a bvp (in tbuoy) [default: 10]
     --bvp_resolution_factor=<mult>       an int, how many times larger than nz should the bvp nz be? [default: 1]
-    --bvp_convergence_factor=<fact>      How well converged time averages need to be for BVP [default: 3e-3]
+    --bvp_convergence_factor=<fact>      How well converged time averages need to be for BVP [default: 1e-3]
 """
 import logging
 logger = logging.getLogger(__name__)
@@ -228,6 +228,12 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
                                     'Lz'              : Lz
                                    }
                     diff_args = [Rayleigh, Prandtl]
+
+#                    u = solver.state['u']
+#                    w = solver.state['w']
+#                    u['g'] *= 0
+#                    w['g'] *= 0
+#                    equations.set_IC(solver, A0=1)
                     bvp_solver.solve_BVP(atmo_kwargs, diff_args, bc_dict)
                 if bvp_solver.terminate_IVP():
                     continue_bvps = False
@@ -369,7 +375,7 @@ if __name__ == "__main__":
     Rayleigh_Benard(Rayleigh=float(args['--Rayleigh']),
                     Prandtl=float(args['--Prandtl']),
                     restart=args['--restart'],
-                    aspect=int(args['--aspect']),
+                    aspect=float(args['--aspect']),
                     nz=int(args['--nz']),
                     nx=nx,
                     ny=ny,

### 2017-12-11 tex/bvp_paper.tex
updates paper and biblio a bit

@@
 modeling the surface of a star which must output the energy generated internally.
+This set of boundary conditions is also being studied more recently in Boussinesq convection
+\cite{korre&all2017}, and is displaying interesting characteristics such as internal layers which
+are stable to convection.
 
@@
 equations governing the velocity $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, temperature
-$T = T_0 + T_1$, and reduced pressure $\varpi$ are (cite Rayleigh, chandrasekar)
+$T = T_0 + T_1$, and reduced pressure $\varpi$ are \cite{spiegel&veronis1960}
 \begin{gather}
@@
 
+In essence, solving the BVP is equivalent to saying that even though the magnitude of flux through
+the system is not initially correct, the system appropriately picks out the ratios
+\begin{equation}
+f_{\text{conv}} = \frac{F_{\text{conv}}}{F_{\text{tot}}}\qquad
+f_{\text{cond}} = \frac{F_{\text{cond}}}{F_{\text{tot}}}.
+\end{equation}
+in the convective, transient state, but the total amount of flux is too large until the system
+reaches the proper isotherm.
+
 \subsection{Numerics}
+Copy+paste from last paper:
+
+We utilize the 
+Dedalus\footnote{\url{http://dedalus-project.org/}} 
+pseudospectral framework \cite{burns&all2016} to time-evolve  
+(\ref{eqn:continuity_eqn})-(\ref{eqn:energy_eqn}) 
+using an implicit-explicit (IMEX), third-order, four-step 
+Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
+Thermodynamic variables are decomposed such that $T = T_0 + T_1$ and
+$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
+and the velocity is $\bm{u} = w\bm{\hat{z}} + u\bm{\hat{x}} + v\bm{\hat{y}}$.
+In our 2D runs, $v = 0$.
+Subscript 0 variables, set by (\ref{eqn:polytrope}), 
+have no time derivative and vary only in $z$.
+Variables are time-evolved on a dealiased Chebyshev (vertical)
+and Fourier (horizontal, periodic) domain in which the
+physical grid dimensions are 3/2 the size of the coefficient grid.  
+Domain sizes range from
+64x256 coefficients at the lowest values of 
+Ra to 1024x4096 coefficients at Ra $> 10^{7}$ in 2D,
+and from 64x128$^2$ to  256x512$^2$ in 3D. 
+By using IMEX timestepping, we implicitly step the 
+stiff linear acoustic wave contribution and are able to
+efficiently study flows at high ($\sim 1$) 
+and low ($\sim 10^{-4}$) Ma.  Our equations take the form
+of the FC equations in \cite{lecoanet&all2014}, extended to include
+$\nu$ and $\chi$ which vary with depth, and we follow the approach there.
+This IMEX approach has been successfully 
+tested against a nonlinear benchmark  of the compressible 
+Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.
+
+We impose impenetrable, stress free, fixed temperature boundary conditions at
+the top and bottom of the domain, with 
+$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. 
+$T_1$ is initially filled with
+random white noise whose magnitude is infinitesimal
+compared to $\epsilon T_0$.
+We filter this noise spectrum in coefficient space, 
+such that only the lower 25\% of the coefficients
+have power. All reported results are taken from time averages
+over many $t_b$ beginning \{100, 40\}$t_b$
+after the start of our \{2D, 3D\} simulations to
+ensure our results are not biased by the convective transient.
 
@@
 assume symmetrical boundary layers.
-
-\section{Fully Compressible Convection}
-
-\subsection{Governing Equations}
-We study stratified convection in an ideal gas whose adiabatic index is $\gamma = 5/3$.
-The initial atmospheric stratification is polytropic \cite{anders&brown2017}.
-We assume a Newtonian radiative conduction term \cite{lecoanet&all2014}, and solve the
-fully compressible Navier-Stokes equations of the form
-\begin{gather}
-\frac{\partial \ln \rho}{\partial t} + \bm{u}\cdot\grad\ln\rho + \DivU = 0
-	\label{eqn:FC_continuity}
-\\
-\frac{D \bm{u}}{Dt} = -T\grad\ln\rho - \grad T + \bm{g} - \Div{\stressT}
-	\label{eqn:FC_momentum}
-\\
-\frac{D T}{D t} + (\gamma-1)T\DivU = 
-\frac{1}{\rho c_V}\left(\kappa\grad^2 T - [\stressT\cdot\grad]\cdot\bm{u}\right),
-	\label{eqn:FC_energy}
-\end{gather}
-where $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$ and the viscous stress
-tensor is defined as
-\begin{equation}
-\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij
-}\DivU\right)
-\label{eqn:stress_tensor}
-\end{equation}
-and $\delta_{ij}$ is the Kronecker delta function.
-
-\subsection{The Boundary Value Equations}
-In studies of fully compressible convection, the flux carried by the adiabatic temperature gradient
-is not available for convection.  Thus, only the flux \emph{in excess} of the adiabat will drive
-convection and be carried by convection.  As such, this is the only portion of the flux which
-must be examined to determine if the solution is in a converged state.  In a system with
-a fixed flux boundary condition, the available superadiabatic flux is
-\begin{equation}
-F_{\text{avail}} = -\kappa(\grad T_0 - \grad T_{\text{ad}}) = \kappa\frac{\epsilon}{c_P}\grad T_0,
-\end{equation}
-which is small when $\epsilon$ is small and only requires low Mach number convective flows
-to carry it.  In a perfectly evolved solution, there will be thin boundary layers in which
-conduction carries this flux in addition to the adiabatic flux, but in an efficient convective
-interior, convective fluxes must carry this full amount.
-
-The BVP equations are inspired by equations of stellar modeling  \cite{paxton&all2011} but adapted to these simulations
-of fully compressible convection.  Here, rather than parameterizing convection, we can get the
-convective fluxes directly from our simulation adn use them to solve for the appropriate structure
-of the atmosphere.  The FC BVP equations are
-\begin{gather}
-\frac{d M_1}{dz} = \rho_1 \\
-T_0 \grad \rho_1 + T_1 \grad \rho_0 + \rho_1 g = - T_0 \grad \rho_0 - T_1 \grad \rho_1 - \rho_0 g \\
-\kappa \frac{d^2 T_1}{d z^2} = -\frac{d}{dz}F_{\text{conv, z}},
-\end{gather}
-which ensure mass conservation, thermal equilibrium, and that the atmosphere is, on average,
-in hydrostatic equilibrium.  We couple these equations with four boundary conditions (mixed
-flux / temperature boundary conditions, as well as setting $M_1 = 0$ at the top and bottom
-of the atmosphere).
-
-\subsection{Results}
 

### 2017-12-13 code/rayleigh_benard.py
adds seed keyword to run script

@@ -30,6 +30,7 @@ Options:
     --run_time_iter=<run_time_iter>   Run time, number of iterations; if not set, n_iter=np.inf
 
     --restart=<restart_file>   Restart from checkpoint
+    --seed=<seed>              RNG seed for initial conditoins [default: 42]
 
     --max_writes=<max_writes>              Writes per file for files other than slices and coeffs [default: 20]
     --max_slice_writes=<max_slice_writes>  Writes per file for slices and coeffs [default: 20]
@@ -75,7 +76,7 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
                     data_dir='./', coeff_output=True, verbose=False, no_join=False,
                     do_bvp=False, num_bvps=10, bvp_convergence_factor=1e-2, bvp_equil_time=10, bvp_resolution_factor=1,
                     bvp_transient_time=30, bvp_final_equil_time=None, min_bvp_time=50,
-                    threeD=False):
+                    threeD=False, seed=42):
     import os
     from dedalus.tools.config import config
     
@@ -146,7 +147,7 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
 
     checkpoint = Checkpoint(data_dir)
     if isinstance(restart, type(None)):
-        equations.set_IC(solver)
+        equations.set_IC(solver, seed=seed)
         dt = None
         mode = 'overwrite'
     else:
@@ -401,6 +402,7 @@ if __name__ == "__main__":
                     bvp_transient_time=float(args['--bvp_transient_time']),
                     bvp_resolution_factor=int(args['--bvp_resolution_factor']),
                     min_bvp_time=float(args['--min_bvp_time']),
-                    threeD=args['--3D'])
+                    threeD=args['--3D'],
+                    seed=int(args['--seed']))
     
 

### 2017-12-13 tex/bvp_paper.tex
adds local run scripts and updates paper

@@
 -\grad\varpi + T_1\hat{z} + \frac{\text{Pr}}{\text{Ra}}\grad^2\bm{u}, 
-	\label{eqn:bouss_momentum_eqn}
+	\label{eqn:bouss_momentum}
 \\
 \frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \frac{1}{\text{Pr}\,\text{Ra}}\grad^2 T_1,
-	\label{eqn:bouss_energy_eqn}
+	\label{eqn:bouss_energy}
 \end{gather}
@@
 \subsection{Numerics}
-Copy+paste from last paper:
-
 We utilize the 
@@
 pseudospectral framework \cite{burns&all2016} to time-evolve  
-(\ref{eqn:continuity_eqn})-(\ref{eqn:energy_eqn}) 
+(\ref{eqn:incompressible})-(\ref{eqn:bouss_energy}) 
 using an implicit-explicit (IMEX), third-order, four-step 
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
-Thermodynamic variables are decomposed such that $T = T_0 + T_1$ and
-$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
+The temperature field is decomposed as $T = T_0(z) + T_1(x, y, z, t)$
 and the velocity is $\bm{u} = w\bm{\hat{z}} + u\bm{\hat{x}} + v\bm{\hat{y}}$.
 In our 2D runs, $v = 0$.
-Subscript 0 variables, set by (\ref{eqn:polytrope}), 
-have no time derivative and vary only in $z$.
 Variables are time-evolved on a dealiased Chebyshev (vertical)
@@
 Domain sizes range from
-64x256 coefficients at the lowest values of 
-Ra to 1024x4096 coefficients at Ra $> 10^{7}$ in 2D,
-and from 64x128$^2$ to  256x512$^2$ in 3D. 
-By using IMEX timestepping, we implicitly step the 
-stiff linear acoustic wave contribution and are able to
-efficiently study flows at high ($\sim 1$) 
-and low ($\sim 10^{-4}$) Ma.  Our equations take the form
-of the FC equations in \cite{lecoanet&all2014}, extended to include
-$\nu$ and $\chi$ which vary with depth, and we follow the approach there.
-This IMEX approach has been successfully 
-tested against a nonlinear benchmark  of the compressible 
-Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.
+32x128 coefficients at the lowest values of 
+Ra to 1024x4096 coefficients at Ra $> 10^{9}$ in 2D.
 
-We impose impenetrable, stress free, fixed temperature boundary conditions at
-the top and bottom of the domain, with 
-$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. 
-$T_1$ is initially filled with
-random white noise whose magnitude is infinitesimal
-compared to $\epsilon T_0$.
+As initial conditions, we fill $T_1$ with
+random white noise whose magnitude is $10^{-6}(\text{Ra Pr})^{-1/2}$.
+This ensures that the initial perturbations are much smaller than the
+evolved convective temperature perturbations, even at large Ra.
 We filter this noise spectrum in coefficient space, 
 such that only the lower 25\% of the coefficients
-have power. All reported results are taken from time averages
-over many $t_b$ beginning \{100, 40\}$t_b$
-after the start of our \{2D, 3D\} simulations to
-ensure our results are not biased by the convective transient.
+have power.
+
+In 2D, there are often multiple steady state solutions (e.g., 2-roll and 3-roll
+solutions) which have slightly different flow properties (heat transport, etc.).
+Even though the initial perturbations are very small, they shape the convective
+transient and thus determine the nature of the steady state convection, at least in
+the laminar regime.  In order to ensure that our results are not biased by differences
+in flow structure, we ran the simulations using distinct random temperature perturbations
+so as to compare statistics in comparable flow fields.  In 3D, rolls are nonstationary over
+convective timescales, and so these effects need not be considered there.
 
 \subsection{Results}
+We use the standard definition of the Nusselt number,
+\begin{equation}
+\text{Nu} = \frac{\angles{wT - P\grad T}}{\angles{- P \grad T}} =
+1 + \frac{\angles{wT}}{-P\Delta T},
+\end{equation}
+where $\Delta T = T(z = 1/2) - T(z = -1/2)$ is the evolved temperature difference
+between the top and bottom plates.  This form of the Nusselt number is valid even when
+the system is not yet in flux equilibrium, and reduces to the standard fixed flux definition
+of Nu  = $[1 - \angles{wT} / P]^{-1}$ \cite{johnston&doering2009}.
+
 Here we talk about how the solutions are different, or similar.  This includes:

### 2017-12-13 code/run_scripts/base_post/local_runs.sh

@@ -1,0 +1,6 @@
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e3 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e3_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e3 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e3_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=1.30e4 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra1.30e4_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e4 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e4_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e4 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e4_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+

### 2017-12-13 code/run_scripts/base_pre/local_runs.sh

@@ -1,0 +1,5 @@
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=2.79e3
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=6.01e3
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=1.30e4
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=2.79e4
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=6.01e4 --seed=150

### 2017-12-13 code/run_scripts/bvp_post/local_runs.sh

@@ -1,0 +1,6 @@
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e3 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e3_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e3 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e3_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=1.30e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra1.30e4_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e4_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e4_Pr1_a4.924/final_checkpoint/final_checkpoint_s1.h5
+

### 2017-12-13 code/run_scripts/bvp_pre/local_runs.sh

@@ -1,0 +1,5 @@
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e3   --do_bvp --bvp_final_equil_time=100 
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e3   --do_bvp --bvp_final_equil_time=100
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=1.30e4   --do_bvp --bvp_final_equil_time=100
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e4   --do_bvp --bvp_final_equil_time=100
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e4   --do_bvp --bvp_final_equil_time=100 --seed=150

### 2017-12-15 tex/bvp_paper.tex
first draft title of paper & first draft motivating paragraph

@@
 \affiliation{Bates}
-\title{BVP Paper}
+\title{Accelerated convergence of convective simulations using boundary value problems}
 
@@
 \label{sec:intro}
+Natural convection occurs in the presence of disparate scales. Granules on the
+solar surface have typical length scales of 1 Mm and overturn on the order of 10 minutes, whereas
+the full solar convection zone spans a depth of 200 Mm, and deep motions are expected to be at very
+low Mach number and constrained by the rotational timescale (1 month) of the Sun.  
+However, despite these relatively short dynamical times, the scale of energy transport on the
+Sun occurs on the Kelvin-Helmholtz timescale, which is nearly $3 \times 10^7$ years for the
+Sun (Michael stix 2003 Solar Physics). As simulations aim to model natural convection
+by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much
+longer than dynamical timescales \cite{Anders&Brown2017}, simulations will have to run for longer
+times to thermally converge.  Furthermore, as diffusivities decrease, finer grid meshes are required
+to resolve turbulent motions, and timestep sizes decrease.  The result is that high-Ra, interesting
+simulations which strive to model astrophysical convective processes are crippled by the combining effects
+of decreased timestep size due and increased convergence time. In order to study these systems, careful
+techniques must be developed to skip past the long thermal convergence in order to study the fast convective
+flows in the proper atmosphere.
+
 In numerical studies of convection, the chosen boundary conditions at the upper and lower plates
@@
 \begin{equation}
-\text{Nu} = \frac{\angles{wT - P\grad T}}{\angles{- P \grad T}} =
-1 + \frac{\angles{wT}}{-P\Delta T},
+\text{Nu} = \frac{\angles{wT - (\text{Ra Pr})^{-1/2}\grad T}}{\angles{- (\text{Ra Pr})^{-1/2} \grad T}} =
+1 + \frac{\angles{wT}}{-\Delta T}\sqrt{\text{Ra Pr}},
 \end{equation}

### 2017-12-15 tex/bvp_paper.tex
cite to stix

@@
 Sun occurs on the Kelvin-Helmholtz timescale, which is nearly $3 \times 10^7$ years for the
-Sun (Michael stix 2003 Solar Physics). As simulations aim to model natural convection
+Sun \cite{stix2003}. As simulations aim to model natural convection
 by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much

### 2017-12-15 tex/bvp_paper.tex
adds plot script for parameter space comparison plot to repo

--- 2017-12-13 tex/bvp_paper.tex
@@
 \label{sec:intro}
-In numerical studies of convection, the chosen boundary conditions at the upper and lower plates
-determines key quantities of the dynamics of the evolved state.
+Natural convection occurs in the presence of disparate timescales. Granules on the
+solar surface overturn on the order of 10 minutes, whereas deep motions in the Sun are likely at
+low Mach number and constrained by the solar rotation rate of \~1 month.  
+Despite these relatively short dynamical times, the scale of energy transport on the
+Sun occurs on the Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
+As simulations aim to model natural convection
+by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much
+longer than dynamical timescales \cite{Anders&Brown2017}, achieving converged simulations will 
+require runs which span a greater number of convective timescales in order to thermally converge.
+Furthermore, with increasing Ra and decreasing diffusivities, motions become more turbulent
+and require finer grid meshes and smaller timesteps to resolve turbulent motions, meaning that
+achieving even one overturn timescale becomes a harder problem.  
+These two effects combine to make thermally converging high-Ra, astrophysically interesting
+simulations intractable using modern numerical tools.
+
+In studies of stratified convection where a convective layer lies between stable layers, studies
+have used the knowledge of Mixing Length Theory (MLT) to adjust the initial thermal profile of
+atmospheres to a state which is closer to the adiabat chosen by convection \cite{brandenburg&all2005}.
+However, many studies of convection do not contain stable layers above and below the convection
+zone, and the presence of hard boundaries and the boundary layers that they form means
+that the proper adiabat cannot be known \emph{a priori} until the simulation evolves the
+structure of the boundary layers.
+
+The chosen boundary conditions at the upper and lower plates
+determine key quantities of the dynamics of the evolved state.
 Studies of incompressible, Boussinesq, \RB convection (RBC) often
@@
 Dirichlet conditions represent plates of infinite conductivity,
-whereas Neumann condition model plates of finite conductivity.  
+whereas Neumann conditions model plates of finite conductivity.  
 In both cases, choosing symmetric boundary conditions maintains overall system symmetry, 
-and despite evolving towards quite different thermal structures, both types of conditions
+and despite evolving towards different thermal structures, both types of conditions
 transport heat in the same manner \cite{johnston&doering2009}.
 
-Studies of convection in stratified systems which aim to model convection 
+Studies of convection which aim to model
 in astrophysical systems, such as the outer envelopes of low-to-moderate mass stars 
 like the Sun, often employ a mixture of these
-two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991}.  
+two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.  
 The flux at the lower boundary is fixed, modeling
@@
 modeling the surface of a star which must output the energy generated internally.
-This set of boundary conditions is also being studied more recently in Boussinesq convection
-\cite{korre&all2017}, and is displaying interesting characteristics such as internal layers which
-are stable to convection.
+While this setup is a useful model for understanding natural
+systems, simulations which employ this setup often suffer from a long 
+thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
+Dirichlet condition.
 
-While this setup is a useful model for understanding natural
-systems, simulations which employ this setup often suffer from a long convective transient as the thermodynamic structure
-of the atmosphere relaxes to the adiabatic profile specified by the fixed temperature upper boundary condition.
-This long evolution occurs on the ``Kelvin-Helmholtz,'' or thermal diffusion timescale of the atmosphere, 
-$t_{\text{KH}} \approx L_z^2 / \chi$, where $L_z$ is the domain depth and $\chi$ is the thermal diffusivity.
-Interesting convection happens as high values of the Rayleigh number, which scales like $\chi^{-1/2}$, such that
-in the astrophysically interesting regime of high-Ra, highly stratified convection, evolving a simulation for a
-KH time becomes numerically intractable.  As the Rayleigh number increases, the KH time increases while the average
-timestep required to resolve the more turbulent flows decreases.  The net result is that under standard initial conditions
-of hydrostatic- and thermal- equilibrium, the desired convective solution cannot be obtained and the dynamics of convection
-there cannot be studied.
-
-Knowledge of Mixing Length theory and the nature of evolved convection has been used in some 
-previous studies (e.g., \cite{brandenburg&all2005}) to choose initial conditions which are
-closer to the correct evolved adiabat than
-the hydrostatic polytropic states.  However, these assumptions work best in convective regions
-which are bounded by stable layers.  In simple atmospheres where boundary layers form to meet
-boundary conditions at the upper and lower edge of the atmosphere, we cannot know 
-\emph{a priori} what the extent or shape of the boundary layer will be, as that must be chosen
-by the convective dynamics, and specification of the proper boundary layer is essential for
-placing the atmosphere along the proper adiabat.
-
-Here we present a method for using simple boundary value problems, 
+Here we present a method for using simple boundary value problems (BVPs), 
 along with information about the evolved flow fields,
 to fast-forward the slow thermal evolution of convecting simulations.  
-We present this method in the context of RBC, and
-then demonstrate that applying it to stratified, compressible convection 
-is simple.  These methods allow us to study the convective flows driven by 
-nearly the evolved thermal profile while only requiring initial value problems to run
-for long enough to resolve the fast dynamical timescales of convection.
+We run two sets of experiments: one in which we allow convective simulations to evolve for a
+full thermal timescale before taking measurements, and another in which we employ a fast-forwarding,
+BVP technique which occurs on dynamical timescales. We compare these two sets of simulations to
+show the validity of the BVP technique.  Then, we use the BVP technique to run simulations
+at high Ra, in the regime where running for thermal timescales becomes computationally intractable.
 
-\section{Incompressible, Boussinesq \RB Convection}
+\section{Experiment}
 \label{sec:experiment}
-In general, the method for fast-forwarding the atmospheric structure to the correct adiabat is
-simple and involves only a few steps.  At the start of convective simulations, a large transient
-occurs while the hydrostatic state gives way to the convective state.  After the peak of this
-transient, we begin to average the mean vertical profile of the convective flux and the conductive
-flux through the domain.  Once those flux profiles are converged, we solve a simple 
-boundary value problem using the information that those fluxes provide to determine what the
-evolved thermal structure of the atmosphere can be.  The stratification of the initial value
-problems is then adjusted to match the output of the BVP, and we run convection for dynamical
-timescales to let the flows adjust to the new, updated thermal structure.  We then measure
-quantities of the dynamics, and compare them to the dynamics of simulations which underwent a
-long thermal rundown, to determine if our simple BVPs effectively get our convective solution
-to the correct state.
-
-\subsection{Governing Equations, Nondimensionalization, and Domain setup}
-In our first set of experiments, we adopt the Oberbeck-Boussinesq approximation.  Here, the
+In our study, we adopt the Oberbeck-Boussinesq approximation.  Here, the
 fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
@@
 where $\angles{A}$ represents a time- and horizontally averaged profile of the quantity $A$.  These
-equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum_eqn}-\ref{eqn:bouss_energy_eqn})
+equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum}-\ref{eqn:bouss_energy})
 and neglecting terms that vanish due to symmetry in the evolved flows.  Convective flows
@@
 \end{enumerate}
+
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
+\caption{\label{fig:parameter_space_comparison} }
+\end{figure}
 

### 2017-12-15 code/plotting/parameter_space_comparison.py

@@ -1,0 +1,105 @@
+"""
+Script for plotting a parameter space study of Nu v Ra.
+
+Usage:
+    parameter_space_plots.py --calculate
+    parameter_space_plots.py
+
+Options:
+    --calculate     If flagged, touch dedalus output files and do time averages.  If not, use post-processed data from before
+"""
+
+
+import matplotlib   
+matplotlib.rcParams.update({'font.size': 11})
+import matplotlib.pyplot as plt
+from matplotlib.colors import ColorConverter
+import os
+import numpy as np
+import glob
+from docopt import docopt
+from mpi4py import MPI
+comm_world = MPI.COMM_WORLD
+from collections import OrderedDict
+import h5py
+import matplotlib.gridspec as gridspec
+
+
+import dedalus.public as de
+
+EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
+FORCE_WRITE=False
+
+COLORS=['indigo', 'orange']
+MARKERS=['s', 'o', 'd', '*']
+MARKERSIZE=[5,4,5,7]
+
+MARKERS_2=['p', '^', '8']
+COLORS_2=['peru', 'gold', 'teal']
+MARKERSIZE_2=[5,5,5]
+
+fields = ['Re', 'Nu', 'IE']
+base_dirs = [
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+            ]
+
+info = OrderedDict()
+for a, base_dir in enumerate(base_dirs):
+
+    for i, d in enumerate(glob.glob('{:s}/*/'.format(base_dir))):
+        ra = d.split('_Ra')[-1].split('_')[0]
+        ra += '_{}'.format(a)
+
+        info[ra] = OrderedDict()
+        try:
+            with h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(d), 'r') as f:
+                for k in fields:
+                    info[ra][k] = f[k].value
+                info[ra]['sim_time'] = f['sim_time'].value
+        except:
+            print('cannot find file in {:s}'.format(d))
+
+print(info.keys())
+
+
+plt.figure(figsize=(8, 2.5))
+gs     = gridspec.GridSpec(*(1000,1000))
[…]

### 2017-12-15 code/boussinesq_dynamics/equations.py
nusselt number update, small other changes

@@ -277,7 +277,7 @@ class BoussinesqEquations(Equations):
         self.problem.substitutions['kappa_flux_z'] = '(-P*(T1_z+T0_z))'
         self.problem.substitutions['conv_flux_z']  = '(enth_flux_z + kappa_flux_z)'
         self.problem.substitutions['delta_T']      = '(right(T1 + T0) - left(T1 + T0))' 
-        self.problem.substitutions['Nu']           = '(conv_flux_z/(-P*delta_T))'
+        self.problem.substitutions['Nu']           = '(1 + enth_flux_z/(-P*delta_T))'
 
     def set_BC(self,
                fixed_flux=None, fixed_temperature=None, mixed_flux_temperature=None, mixed_temperature_flux=None,

### 2017-12-15 code/bvps/bvp_tools.py

@@ -468,9 +468,10 @@ class BoussinesqBVPSolver(BVPSolverBase):
 
         atmosphere.T0_z.set_scales(self.nz/atmosphere.nz, keep_data=True)
         flux_through_system = -atmosphere.P * atmosphere.T0_z['g']
+        flux_scaling = flux_through_system / self.profiles_dict['tot_flux_IVP']
 
         #Scale flux appropriately.
-        self.profiles_dict['enth_flux_IVP'] *= flux_through_system/self.profiles_dict['tot_flux_IVP']
+        self.profiles_dict['enth_flux_IVP'] *= flux_scaling #flux_through_system/self.profiles_dict['tot_flux_IVP']
 
         #Make some plots
         if not isinstance(self.plot_dir, type(None)):
@@ -493,6 +494,8 @@ class BoussinesqBVPSolver(BVPSolverBase):
                     plt.close()
         self.plot_count += 1
 
+        return flux_scaling
+
 
     def solve_BVP(self, atmosphere_kwargs, diffusivity_args, bc_kwargs, tolerance=1e-10):
         """
@@ -509,6 +512,7 @@ class BoussinesqBVPSolver(BVPSolverBase):
         return_dict = OrderedDict()
         for v in self.VARS.keys():
             return_dict[v] = np.zeros(self.nz, dtype=np.float64)
+        return_dict['flux_scaling'] = np.zeros(self.nz, dtype=np.float64)
 
 
         # No need to waste processor power on multiple bvps, only do it on one
@@ -526,7 +530,8 @@ class BoussinesqBVPSolver(BVPSolverBase):
             atmosphere._set_subs()
 
             # Create the appropriate enthalpy flux profile based on boundary conditions
-            self._update_profiles_dict(bc_kwargs, atmosphere, vel_adjust_factor)
+            return_dict['flux_scaling'] = self._update_profiles_dict(bc_kwargs, atmosphere, vel_adjust_factor)
+            vel_adjust_factor = np.sqrt(np.mean(return_dict['flux_scaling']))
 
             #Add time and horizontally averaged profiles from IVP to the problem as parameters
             for k in self.FIELDS.keys():
@@ -578,6 +583,11 @@ class BoussinesqBVPSolver(BVPSolverBase):
             self.comm.Allreduce(return_dict[v], glob, op=MPI.SUM)
             return_dict[v] = glob
 
+        v = 'flux_scaling'        
+        glob = np.zeros(self.nz)
[…]

### 2017-12-15 code/run_scripts/bvp_pre/local_runs.sh

@@ -1,5 +1,5 @@
-mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e3   --do_bvp --bvp_final_equil_time=100 
-mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e3   --do_bvp --bvp_final_equil_time=100
-mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=1.30e4   --do_bvp --bvp_final_equil_time=100
-mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e4   --do_bvp --bvp_final_equil_time=100
-mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e4   --do_bvp --bvp_final_equil_time=100 --seed=150
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e3   --do_bvp --bvp_final_equil_time=50  
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e3   --do_bvp --bvp_final_equil_time=50 
+mpirun -n 2 python3 rayleigh_benard.py --aspect=4.924 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=1.30e4   --do_bvp --bvp_final_equil_time=50 
[…]

### 2017-12-19 code/plotting/pdf_comparison.py
adds run scripts for last two figures

@@ -1,0 +1,121 @@
+"""
+Script for plotting a parameter space study of Nu v Ra.
+
+Usage:
+    parameter_space_plots.py --calculate
+    parameter_space_plots.py
+
+Options:
+    --calculate     If flagged, touch dedalus output files and do time averages.  If not, use post-processed data from before
+"""
+
+
+import matplotlib   
+matplotlib.rcParams.update({'font.size': 11})
+import matplotlib.pyplot as plt
+from matplotlib.colors import ColorConverter
+import os
+import numpy as np
+import glob
+from docopt import docopt
+from mpi4py import MPI
+comm_world = MPI.COMM_WORLD
+from collections import OrderedDict
+import h5py
+import matplotlib.gridspec as gridspec
+
+
+import dedalus.public as de
+
+EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
+FORCE_WRITE=False
+
+COLORS=['indigo', 'orange']
+MARKERS=['s', 'o', 'd', '*']
+MARKERSIZE=[5,4,5,7]
+
+MARKERS_2=['p', '^', '8']
+COLORS_2=['peru', 'gold', 'teal']
+MARKERSIZE_2=[5,5,5]
+
+base_dirs_post = [
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+            ]
+ra_runs = '6.01e4'
+
+info = OrderedDict()
+for a, base_dir in enumerate(base_dirs_post):
+    print(base_dir)
+
+    for i, d in enumerate(glob.glob('{:s}/*Ra{:s}*/'.format(base_dir, ra_runs))):
+        ra = d.split('_Ra')[-1].split('_')[0]
+        ra += '_{}'.format(a)
+
+        info[ra] = OrderedDict()
+
+        try:
+            with h5py.File('{:s}/profile_plots/profile_info.h5'.format(d), 'r') as f:
+                for k in f.keys():
+                    info[ra][k+'_profile'] = f[k].value
+        except:
+            print('cannot find profile file in {:s}'.format(d))
[…]

### 2017-12-19 code/plotting/temp_comparison.py

@@ -1,0 +1,117 @@
+"""
+Script for plotting a parameter space study of Nu v Ra.
+
+Usage:
+    parameter_space_plots.py --calculate
+    parameter_space_plots.py
+
+Options:
+    --calculate     If flagged, touch dedalus output files and do time averages.  If not, use post-processed data from before
+"""
+
+
+import matplotlib   
+matplotlib.rcParams.update({'font.size': 11})
+import matplotlib.pyplot as plt
+from matplotlib.colors import ColorConverter
+import os
+import numpy as np
+import glob
+from docopt import docopt
+from mpi4py import MPI
+comm_world = MPI.COMM_WORLD
+from collections import OrderedDict
+import h5py
+import matplotlib.gridspec as gridspec
+
+
+import dedalus.public as de
+
+EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
+FORCE_WRITE=False
+
+COLORS=['indigo', 'orange']
+MARKERS=['s', 'o', 'd', '*']
+MARKERSIZE=[5,4,5,7]
+
+MARKERS_2=['p', '^', '8']
+COLORS_2=['peru', 'gold', 'teal']
+MARKERSIZE_2=[5,5,5]
+
+base_dirs_post = [
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+            ]
+ra_runs = '6.01e4'
+
+info = OrderedDict()
+for a, base_dir in enumerate(base_dirs_post):
+    print(base_dir)
+
+    for i, d in enumerate(glob.glob('{:s}/*Ra{:s}*/'.format(base_dir, ra_runs))):
+        ra = d.split('_Ra')[-1].split('_')[0]
+        ra += '_{}'.format(a)
+
+        info[ra] = OrderedDict()
+
+        try:
+            with h5py.File('{:s}/profile_plots/profile_info.h5'.format(d), 'r') as f:
+                for k in f.keys():
+                    info[ra][k+'_profile'] = f[k].value
+        except:
+            print('cannot find profile file in {:s}'.format(d))
+        try:
[…]

### 2017-12-19 tex/bvp_paper.tex
puts figures into paper

@@
 \subsection{The Boundary Value Problem}
-The Boussinesq BVP is simply the time-stationary, horizontally- and time- averaged equations
-of hydrostatic balance and energy conservation,
+\begin{figure}[b]
+\includegraphics[width=\textwidth]{./figs/time_trace.png}
+\caption{\label{fig:time_trace} }
+\end{figure}
+
+One can skip the prohibitive thermal timescale required to reach an equilibrium temperature profile
+in a Direct Numerical Simulation (DNS) by coupling the DNS with a simple Boundary Value Problem
+(BVP) solve. Using information about the dynamics of the convection in the atmosphere, it is possible
+to skip a large portion of the thermal evolution, see Fig \ref{fig:time_trace}a\&b.
+
+The Boussinesq BVP contains equations of hydrostatic balance and thermal equilibrium,
 \begin{gather}
@@
 \end{gather}
-where $\angles{A}$ represents a time- and horizontally averaged profile of the quantity $A$.  These
+where $\angles{A}$ represents a time- and horizontally averaged profile of the quantity $A$.  
+These
 equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum}-\ref{eqn:bouss_energy})
@@
 The evolution of the atmosphere results in an asymmetric flux profile during 
-the slow thermal evolution of the atmosphere.  Furthermore, under our nondimensionalization,
-the convective flux (and the flux at the upper boundary layer) are O(1) during the convective
-transient, whereas the flux entering the atmosphere at the lower boundary is O(Ra$^{-1/2}$), so the asymmetry of the fluxes
-becomes increasingly pronounced as Ra is increased into the turbulent realm.
+the slow thermal evolution of the atmosphere (Fig. \ref{fig:time_trace}c).
 
@@
 in the convective, transient state, but the total amount of flux is too large until the system
-reaches the proper isotherm.
+reaches the proper isotherm.  This procedure seems to converge the atmosphere quite well
+(Fig. \ref{fig:time_trace}d\&e).
 
@@
 \begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
+\caption{\label{fig:pdf_comparison} }
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
+\caption{\label{fig:temp_comparison} }
+\end{figure}
+
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}

### 2017-12-19 code/plotting/time_trace.py

@@ -92,39 +92,11 @@ gs_info = (((0,0), 450, size_1), ((0, 1000-size_2),450, size_2))
 print(size_1, size_2, gs_info)
 axes = []
 axes_share = []
+
 for i in range(4):
     if i < 2:
         axes.append(plt.subplot(gs.new_subplotspec(*gs_info[i])))
         axes_share.append(axes[-1].twinx())
-    this_label = '{}_{}'.format(ra_runs, i)
-    axes[i % 2].plot(info[this_label]['sim_time'], info[this_label]['KE_scalar'], c='k')
-    axes[i % 2].set_yscale('log')
-    axes[i % 2].set_ylim(1e-3, 1e-1)
-    if i > 1:
-        axes[i % 2].axvline(info[this_label]['sim_time'][0], ls='-.')
-
-    axes_share[i % 2].plot(info[this_label]['sim_time'], 0.5 + info[this_label]['IE_scalar'], c='red')
-    axes_share[i % 2].set_yscale('log')
-    axes_share[i % 2].set_ylim(1e-1, 1e0)
-
-#Axes formatting
-axes[0].set_xlim(info['{}_0'.format(ra_runs)]['sim_time'][0], info['{}_2'.format(ra_runs)]['sim_time'][-1])
-axes[1].set_xlim(info['{}_1'.format(ra_runs)]['sim_time'][0], info['{}_3'.format(ra_runs)]['sim_time'][-1])
-axes[0].set_ylabel('Kinetic Energy')
-axes[0].set_xlabel('Simulation Time (freefall units)', labelpad=2)
-x, y = axes[0].xaxis.get_label().get_position()
-print(x, y)
-axes[0].xaxis.get_label().set_position((x/time_ratio, y))
-axes_share[1].set_ylabel(r'$T_1 - T_{\mathrm{top}}$', rotation=270, color='green')
-for tick in axes[1].get_yticklabels():
-    tick.set_size(0)
-axes[1].yaxis.set_ticks_position('none')
-for tick in axes_share[0].get_yticklabels():
-    tick.set_size(0)
-axes_share[0].yaxis.set_ticks_position('none')
-for tick in axes_share[1].get_yticklabels():
-    tick.set_color('g')
-
 #Overlaying bold areas on time traces
 this_label = '{}_0'.format(ra_runs, i)
[…]

### 2017-12-21 tex/bvp_paper.tex
updates to paper

@@
 \documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography]{revtex4-1}
+\usepackage{tabularx}
 \usepackage{graphicx}
@@
 \affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
-\author{Jeffrey Oishi}
-\affiliation{Bates}
+\author{Jeffrey S. Oishi}
+\affiliation{Department of Physics and Astronomy, Bates College, Lewiston, ME 04240, USA}
 \title{Accelerated convergence of convective simulations using boundary value problems}
@@
 \begin{abstract}
-WOW this is a really long sentence check out this abstract I'll just keep writing words to make this at least
-one line long so we know what the formatting looks like, ok?
+We present a method for using coupling Boundary value problems (BVPs) with Initial value problems (IVPs)
+in order to achieve thermally converged convective solutions on dynamical timescales, rather than the
+long thermal timescale.  We demonstrate the similarity between the solution reached via BVP and the
+solution reached by a long thermal rundown of the IVP, and demonstrate that this method works at a
+large range of supercriticalities.  We use this method to achieve converged solutions at high Ra,
+and discuss its extension to more complex scenarios, such as stratified, compressible convection.
 \end{abstract}
@@
 solar surface overturn on the order of 10 minutes, whereas deep motions in the Sun are likely at
-low Mach number and constrained by the solar rotation rate of \~1 month.  
+low Mach number and constrained by the solar rotation rate of $\sim$1 month.  
 Despite these relatively short dynamical times, the scale of energy transport on the
@@
 achieving even one overturn timescale becomes a harder problem.  
-These two effects combine to make thermally converging high-Ra, astrophysically interesting
-simulations intractable using modern numerical tools.
+These two effects combine such that achieving thermally converged, high-Ra, astrophysically interesting
+simulations is intractable using modern numerical tools.
 
@@
 However, many studies of convection do not contain stable layers above and below the convection
-zone, and the presence of hard boundaries and the boundary layers that they form means
-that the proper adiabat cannot be known \emph{a priori} until the simulation evolves the
+zone, and the presence of hard boundaries and the boundary layers that they form makes it difficult to
+know proper evolved adiabat \emph{a priori} before the dynamics of the simulation evolve the
 structure of the boundary layers.
-
-The chosen boundary conditions at the upper and lower plates
-determine key quantities of the dynamics of the evolved state.
-Studies of incompressible, Boussinesq, \RB convection (RBC) often
-employ fixed temperature (Dirichlet) or fixed heat flux
-(Neumann) boundary conditions at both plates.  
-Dirichlet conditions represent plates of infinite conductivity,
-whereas Neumann conditions model plates of finite conductivity.  
-In both cases, choosing symmetric boundary conditions maintains overall system symmetry, 
-and despite evolving towards different thermal structures, both types of conditions
-transport heat in the same manner \cite{johnston&doering2009}.
-
-Studies of convection which aim to model
-in astrophysical systems, such as the outer envelopes of low-to-moderate mass stars 
-like the Sun, often employ a mixture of these
-two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.  
-The flux at the lower boundary is fixed, modeling
-the constant energy generation of the stellar core, 
-while the outer boundary condition is held at a fixed temperature,
-modeling the surface of a star which must output the energy generated internally.
-While this setup is a useful model for understanding natural
-systems, simulations which employ this setup often suffer from a long 
-thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
-Dirichlet condition.
 
@@
 \begin{equation}
-\text{Ra} = \frac{g \alpha L^4 \left(\frac{dT}{dz}\right)_0}{\nu\chi} = \frac{(L\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
+\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\chi} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
 \end{equation}
@@
 at $z = -1/2$, and we impose a fixed temperature condition $T_1 = 0$ at $z = 1/2$. Both
-horizontal directions are periodic and have equal aspect ratio, $\gamma = 4$, such that
-the horizontal coordinates $x, y = [0, \Gamma]$.
+horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
+the aspect ratio is $\Gamma = 2 \lambda_c$, with
+$\lambda_c = 2\pi/k_c$, and $k_c=2.5519$ is the wavenumber of convective onset for this choice of
+boundary conditions.
+
+The chosen thermal boundary conditions at the upper and lower plates
+determine key quantities of the evolved state.
+Studies of incompressible, Boussinesq, \RB convection often
+employ fixed temperature (Dirichlet) or fixed heat flux
+(Neumann) boundary conditions at both plates.  
+Dirichlet conditions represent plates of infinite conductivity,
+whereas Neumann conditions model plates of finite conductivity.  
+In both cases, choosing symmetric boundary conditions maintains overall system symmetry, 
+and despite evolving towards different thermal structures, both types of conditions
+transport heat in the same manner \cite{johnston&doering2009}.
+Studies of convection which aim to model
+astrophysical systems such as stars often employ a mixture of these
+two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.  
+The flux at the lower boundary is fixed, modeling
+the constant energy generation of the stellar core, 
+while the outer boundary condition is held at a fixed temperature,
+modeling the surface of a star which must output the energy generated internally.
+This setup is a useful model for understanding natural
+systems, but simulations which employ these boundary conditions suffer from a long 
+thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
+Dirichlet condition.  We choose these conditions in part to better understand them, and in
+part because these conditions minimize the number of assumptions that must be made in
+setting up the boundary value problem.
 
@@
 
-One can skip the prohibitive thermal timescale required to reach an equilibrium temperature profile
-in a Direct Numerical Simulation (DNS) by coupling the DNS with a simple Boundary Value Problem
+The prohibitively long thermal timescale required to reach an equilibrium temperature profile
+in a Direct Numerical Simulation (DNS) can be skipped by coupling the DNS with a simple Boundary Value Problem
 (BVP) solve. Using information about the dynamics of the convection in the atmosphere, it is possible
@@
 These
-equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum}-\ref{eqn:bouss_energy})
-and neglecting terms that vanish due to symmetry in the evolved flows.  Convective flows
+equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum}\&\ref{eqn:bouss_energy}),
+neglecting terms that vanish due to symmetry, and assuming that the flows are in a stationary state.  
+Convective flows
 are perturbations around a thermal profile defined by these equations in the proper evolved state.
 
-In Boussinesq RBC, the thermal structure of the atmosphere is fully determined by the specification
-of the convective flux, $F_{conv} = \angles{w T_1}$.  If this profile is known, then $T_1$ and
-$\varpi$ can be found under the proper specifications of boundary conditions.  
-Under the choice of mixed thermal boundary conditions, the initial
-atmosphere contains more thermal energy ($\propto T$) than the 
-evolved adiabatic solution.  As the atmosphere adjusts to be nearly isothermal in the interior,
-it must evolve towards the (cold) temperature value specified at the upper boundary.
-The evolution of the atmosphere results in an asymmetric flux profile during 
-the slow thermal evolution of the atmosphere (Fig. \ref{fig:time_trace}c).
+Under eqns (\ref{eqn:bouss_BVP_momentum}\&\ref{eqn:bouss_BVP_energy}), 
+the thermal structure ($\angles{T_1}$, $\angles{\varpi}$) of the atmosphere is fully determined by the specification
+of the convective flux, $F_{conv} = \angles{w T_1}$.  If this profile is known, then 
+solving for $\angles{T_1}$ and
+$\angles{\varpi}$ depends only upon the choice of boundary conditions.
 
-In order to find the evolved temperature profile of the atmosphere using the Boussinesq BVP equations, 
-the evolved profile of the convective flux must be properly specified.  In order to construct
-this profile, we acknowledge that the evolved solution will in flux equilibrium, 
-carrying the amount of the flux entering through the bottom.  
+By definition, the profile of $F_{conv}$ is \emph{not} in its time stationary state near the
+beginning of the simulation.  In fact, under mixed boundary conditions, as the atmosphere approaches the
+isotherm specified by the upper boundary condition, the motions display an asymmetric flux as energy
+leaks through the upper boundary condition (Fig. \ref{fig:time_trace}c).  
+In order to construct the evolved convective flux from the current fluxes in the atmosphere,
+we acknowledge that the evolved solution will be in flux equilibrium, 
+carrying the amount of flux specified at the fixed-flux condition throughout the full depth of the atmosphere.  
 Thus, the steady-state profile of the convective flux can be approximated as
@@
 \end{equation}
-Or, put simply, the steady state convective flux is retrieved by properly removing the asymmettry
-from the flux profile.
-
-In our Boussinesq BVPs, we solve Eqns. (\ref{eqn:bouss_BVP_momentum}-\ref{eqn:bouss_BVP_energy}),
-substituting $\angles{wT_1} = F_{\text{conv, steady}}$ as defined in eqn. (\ref{eqn:bouss_BVP_fconv})
-to retrieve the proper vertical profile of $T_1$ and $\varpi$.  We then update the mean horizontal value
-of $T_1$ and $\varpi$ in a corresponding IVP, and continue to timestep forward with the newly adjusted
-atmosphere.
-
-In essence, solving the BVP is equivalent to saying that even though the magnitude of flux through
-the system is not initially correct, the system appropriately picks out the ratios
+In essence, the construction of this profile assumes that the system appropriately picks out the ratios
 \begin{equation}
@@
 \end{equation}
-in the convective, transient state, but the total amount of flux is too large until the system
-reaches the proper isotherm.  This procedure seems to converge the atmosphere quite well
-(Fig. \ref{fig:time_trace}d\&e).
+in the transient state.  Thus, even though the quantity of flux being carried is not correct, the
+system is carrying flux convectively where it needs to in the interior, and conductively in the boundaries.
+
+The choice of a fixed-flux boundary condition at the bottom appropriately scales the magnitude of
+$F_{\text{conv, steady}}$.  The choice of a fixed-temperature boundary condition at the top of the
+atmosphere appropriately sets the isotherm of the convective interior.  While this method can be used
+for other choices of thermal boundary conditions (see Discussion), dual fixed temperature conditions
+at the upper plate require a more careful handling of $F_{\text{bot}}$, and dual fixed flux boundary
+conditions have degenerate solutions for the constant offset of $T_1$.
+
+In general, the BVP solve takes the following form:
+\begin{enumerate}
+\item Run the convective IVP. Once the convection begins, start taking averages averages of $\angles{wT_1}$
+and $\partial_z^2\angles{T_1}$, which determine the fluxes through the system.  Update these averages every
+$\Delta t = 0.1$ freefall times.  Once these averages are converged to 1 part in 1000, the BVP is ready to be solved.
+\item Construct $F_{\text{conv, steady}}$ from the flux profiles, then use it to solve for $\angles{T_1}$ 
+and \angles{\varpi} of the
+evolved state.  Adjust the mean profiles in the BVP such that this is their mean profile.
+\item Divide the velocities and the $T_1$ fluctuations around the mean profile by 
+$\sqrt{\bar{F_{\text{bot}}/F_{\text{tot}}}}$. This lowers the convective flux through the system such that it is,
+on average, the convective flux used in the BVP solve.
+\item Continue running the IVP for a number of freefall times to allow the velocities and temperature perturbations
+to equilibrate to the new mean state.
+\end{enumerate}
+This procedure seems to work quite well, see Fig. \ref{fig:time_trace}d\&e.
 
@@
 
-\subsection{Results}
-We use the standard definition of the Nusselt number,
+\section{Results}
+While the differences in the fluxes in Fig. \ref{fig:time_trace} are small, it is important
+to determine if the velocity fluctuations and point-by-point nonlinear transport are the same
+in the evolved state.  Fig. \ref{fig:pdf_comparison} overlays the probability distribution functions
+of the vertical and horizontal velocities, as well as the fully nonlinear portion of the convective
+flux for the same case as is shown in Fig. \ref{fig:time_trace}.  The PDFs are quite similar visually,
+and have a similarity of (XYZ) according to a Kolmogorov-Smirnov statistic.
+
+In addition to getting the nonlinear dynamics mostly correct, we show that the BVP method retrieves the
+proper temperature profile, see e.g., Fig. \ref{fig:temp_comparison}.  Here the BVP profile retrieves the
+mean profile of the temperature to within 1\% accuracy, and temperature fluctuations in the two runs
+have a similarity of (XYZ) according to a Kolmogorov-Smirnov statistic.
+
+This method works across a broad range of supercriticality.  In Fig. \ref{fig:parameter_space_comparison},
+we show measurements of the volume-averaged Nusselt number, Reynolds number, and temperature.
+We use standard definitions of the Nusselt number and Reynolds numbers,
 \begin{equation}
 \text{Nu} = \frac{\angles{wT - (\text{Ra Pr})^{-1/2}\grad T}}{\angles{- (\text{Ra Pr})^{-1/2} \grad T}} =
-1 + \frac{\angles{wT}}{-\Delta T}\sqrt{\text{Ra Pr}},
+1 + \frac{\angles{wT}}{-\Delta T}\sqrt{\text{Ra Pr}}, \qquad \text{Re} = \frac{|\bm{u}| L_z}{\nu},
 \end{equation}
@@
 the system is not yet in flux equilibrium, and reduces to the standard fixed flux definition
-of Nu  = $[1 - \angles{wT} / P]^{-1}$ \cite{johnston&doering2009}.
+of Nu  = $[1 - \angles{wT} / P]^{-1}$ \cite{johnston&doering2009}. We find a scaling law of
+Nu $\propto \text{Ra}^{2/3}$, much steeper than a standard 2/7 or 1/3 scaling law
+\cite{johnston&doering2009}. Furthermore, we find that Re$\propto \text{Ra}^{0.425}$. The average temperature
+approaches the value at the top of the domain as Ra increases.
 
-Here we talk about how the solutions are different, or similar.  This includes:
-\begin{enumerate}
-\item Showing that the flow fields look similar
-\item Showing how the temperature / flux profiles look similar/different
-\item showing how Nu and Re scale with Ra in BVP / IVP.
-\item showing how the PDFs of $w$, $wT$, and $T$ change.
-\end{enumerate}
+The final morphology of the flows is very important in determining the exact value of Nu and Re.  In general,
+a two-roll state vs. a three-roll state will have entirely different statistics -- different Nu, Re, and average
+temprature (and as a result, different size boundary layers).  Thus, in 2D studies, it is essential to study flows
+of a similar morphology in order to see a clear trend.
 
@@
 
-Then we need to make some comments about whether this is good or bad
-
-Then we need to mention how the same thing can be done in stratified, just there you don't
-assume symmetrical boundary layers.
-
 \section{Discussion \& Conclusions}
 \label{sec:results}
+I don't have the mental stamina to write this section right now.  In general, here's what it's going to say:
+\begin{enumerate}
+\item This procedure works, as we've shown.
+\item How to apply this to more complicated cases, like stratified convection
+\item How to apply this to different boundary conditions
+\item Brief discussion of other methods that can be used to fast-forward, e.g., bootstrapping.
+\item This is just a first step.
+\end{enumerate}
 
@@
 \appendix
-\section{Table of Boussinesq Runs}
-
-\section{Table of stratified runs}
+\section{Table of Runs}
+\begin{center}
+\begin{tabularx}{\textwidth}{ X X X X X X X }
+\hline													
+Ra	&	Supercriticality	&	nz	&	nx	&	$t_{\text{therm}}$	&	$t_{\text{post BVP}}$	&	$t_{\text{avg}}$	\\[1ex]
+\hline		\hline											
+$2.79 \cdot 10^3$	&	$10^{1/3}$	&	32	&	128	&	$52.8$	&	50	&	100	\\
+$6.01 \cdot 10^3$	&	$10^{2/3}$	&	32	&	128	&	$77.6$	&	50	&	100	\\
+$1.30 \cdot 10^4$	&	$10^1$	&	32	&	128	&	$114$	&	50	&	100	\\
+$2.79 \cdot 10^4$	&	$10^{1 + 1/3}$	&	32	&	128	&	$167$	&	50	&	100	\\
+$6.01 \cdot 10^4$	&	$10^{1 + 2/3}$	&	32	&	128	&	$245$	&	50	&	100	\\
+$1.30 \cdot 10^5$	&	$10^2$	&	64	&	256	&	$360$	&	100	&	100	\\
+$2.79 \cdot 10^5$	&	$10^{2 + 1/3}$	&	64	&	256	&	$528$	&	100	&	100	\\
+$6.01 \cdot 10^5$	&	$10^{2 + 2/3}$	&	64	&	256	&	$776$	&	100	&	100	\\
+$1.30 \cdot 10^6$	&	$10^3$	&	128	&	512	&	$1.14 \cdot 10^3$	&	100	&	200	\\
+$2.79 \cdot 10^6$	&	$10^{3 + 1/3}$	&	128	&	512	&	$1.67 \cdot 10^3$	&	200	&	200	\\
+$6.01 \cdot 10^6$	&	$10^{3 + 2/3}$	&	256	&	1024	&	$2.45 \cdot 10^3$	&	200	&	200	\\
+$1.30 \cdot 10^7$	&	$10^4$	&	256	&	1024	&	$3.60 \cdot 10^3$	&	200	&	200	\\
+$2.79 \cdot 10^7$	&	$10^{4 + 1/3}$	&	256	&	1024	&	$5.28 \cdot 10^3$	&	200	&	200	\\
+$6.01 \cdot 10^7$	&	$10^{4 + 2/3}$	&	256	&	1024	&	$7.76 \cdot 10^3$	&	200	&	200	\\
+$1.30 \cdot 10^8$	&	$10^5$	&	512	&	2048	&	$1.14 \cdot 10^4$	&	500	&	500	\\
+$2.79 \cdot 10^8$	&	$10^{5 + 1/3}$	&	512	&	2048	&	$1.67 \cdot 10^4$	&	500	&	500	\\
+$6.01 \cdot 10^8$	&	$10^{5 + 2/3}$	&	512	&	2048	&	$2.45 \cdot 10^4$	&	500	&	500	\\
+$1.30 \cdot 10^9$	&	$10^6$	&	1024	&	4096	&	$3.60 \cdot 10^4$	&	500	&	500	\\
+\hline													
+\end{tabularx}
+\end{center}
 

### 2017-12-21 code/plotting/parameter_space_comparison.py

@@ -63,43 +63,69 @@ for a, base_dir in enumerate(base_dirs):
 print(info.keys())
 
 
-plt.figure(figsize=(8, 2.5))
+plt.figure(figsize=(8, 1.5))
 gs     = gridspec.GridSpec(*(1000,1000))
-gs_info = (((0,0), 1000, 270), ((0, 350), 1000, 270), ((0, 700), 1000, 270))
+gs_info = (((0,0), 1000, 270), ((0, 350), 1000, 250), ((0, 730), 1000, 270))
+ra_crit = 1295.78
 for i,k in enumerate(fields):
     ax = plt.subplot(gs.new_subplotspec(*gs_info[i]))
+    bx = ax.twiny()
     for ra_info, datum in info.items():
         try:
             good_data = datum[k]
             mean, std = np.mean(good_data), np.std(good_data)
             ra, ind = ra_info.split('_')
             if k == 'IE':
-                plt.errorbar(float(ra), 0.5+mean, yerr=std,  color=COLORS[int(ind)])
-                plt.scatter(float(ra), 0.5+mean, s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)
+                bx.scatter(float(ra)/ra_crit, 0.5+mean, s=0, alpha=0)
+                ax.errorbar(float(ra), 0.5+mean, yerr=std,  color=COLORS[int(ind)])
+                ax.scatter(float(ra), 0.5+mean, s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)
             elif k == 'Nu':
                 p=2/3
-                plt.errorbar(float(ra), mean/(4e-3*float(ra)**(p)), yerr=std/(4e-3*float(ra)**(p)),  color=COLORS[int(ind)])
-                plt.scatter(float(ra), mean/(4e-3*float(ra)**p), s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)
+                bx.scatter(float(ra)/ra_crit, mean/float(ra)**(p), s=0, alpha=0)
+                ax.errorbar(float(ra), mean/(float(ra)**(p)), yerr=std/(float(ra)**(p)),  color=COLORS[int(ind)])
+                ax.scatter(float(ra), mean/(float(ra)**p), s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)
[…]

### 2017-12-21 code/plotting/pdf_comparison.py

@@ -43,6 +43,7 @@ base_dirs_post = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
             ]
 ra_runs = '6.01e4'
+ra_runs = '2.79e7'
 
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_post):
@@ -88,7 +89,7 @@ axes[-1].fill_between(info[base_label]['w_xs_pdf'], 0, info[base_label]['w_pdf_p
 axes[-1].plot(info[base_label]['w_xs_pdf'], info[base_label]['w_pdf_pdf'], c='blue')
 axes[-1].fill_between(info[bvp_label]['w_xs_pdf'], 0, info[bvp_label]['w_pdf_pdf'], color='red', alpha=0.4)
 axes[-1].plot(info[bvp_label]['w_xs_pdf'], info[bvp_label]['w_pdf_pdf'], c='red')
-axes[-1].set_xlim(np.min(info[base_label]['w_xs_pdf']), np.max(info[base_label]['w_xs_pdf']))
+axes[-1].set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w_xs_pdf']))
 axes[-1].set_xlabel('w\'')
 axes[-1].set_ylabel('Probability')
 axes[-1].set_yscale('log')
@@ -99,7 +100,7 @@ axes[-1].fill_between(info[base_label]['u_xs_pdf'], 0, info[base_label]['u_pdf_p
 axes[-1].plot(info[base_label]['u_xs_pdf'], info[base_label]['u_pdf_pdf'], c='blue')
 axes[-1].fill_between(info[bvp_label]['u_xs_pdf'], 0, info[bvp_label]['u_pdf_pdf'], color='red', alpha=0.4)
 axes[-1].plot(info[bvp_label]['u_xs_pdf'], info[bvp_label]['u_pdf_pdf'], c='red')
-axes[-1].set_xlim(np.min(info[base_label]['u_xs_pdf']), np.max(info[base_label]['u_xs_pdf']))
+axes[-1].set_xlim(np.min(info[bvp_label]['u_xs_pdf']), np.max(info[bvp_label]['u_xs_pdf']))
 axes[-1].set_xlabel('u\'')
 axes[-1].set_ylabel('Probability')
 axes[-1].set_yscale('log')
[…]

### 2017-12-21 code/plotting/temp_comparison.py

@@ -43,6 +43,7 @@ base_dirs_post = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
             ]
 ra_runs = '6.01e4'
+ra_runs = '2.79e7'
 
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_post):
@@ -106,10 +107,12 @@ axes[-1].fill_between(info[base_label]['T_xs_pdf'], 0, info[base_label]['T_pdf_p
 axes[-1].plot(info[base_label]['T_xs_pdf'], info[base_label]['T_pdf_pdf'], c='blue')
 axes[-1].fill_between(info[bvp_label]['T_xs_pdf'], 0, info[bvp_label]['T_pdf_pdf'], color='red', alpha=0.4)
 axes[-1].plot(info[bvp_label]['T_xs_pdf'], info[bvp_label]['T_pdf_pdf'], c='red')
-x_ticks = np.array([-0.5, np.floor(100*info[base_label]['T_xs_pdf'][np.argmax(info[base_label]['T_pdf_pdf'][3:])])/100, 0])
+x_ticks = np.array([-0.5, np.max(info[base_label]['T_xs_pdf'])])
 axes[-1].set_xticks(x_ticks)
 axes[-1].set_xlabel('T')
 axes[-1].set_ylabel('Probability')
+axes[-1].set_yscale('log')
+axes[-1].set_xlim(-0.5, np.max(info[base_label]['T_xs_pdf']))
 
 
 

### 2017-12-21 code/plotting/time_trace.py

@@ -50,6 +50,7 @@ base_dirs_post = [
             ]
 
 ra_runs = '6.01e4'
+ra_runs = '2.79e7'
 
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
@@ -130,7 +131,7 @@ for i in range(4):
 
     axes_share[i % 2].plot(info[this_label]['sim_time'], 0.5 + info[this_label]['IE_scalar'], c='red')
     axes_share[i % 2].set_yscale('log')
-    axes_share[i % 2].set_ylim(1e-1, 1e0)
+    axes_share[i % 2].set_ylim(1e-2, 1e0)
 
 #Axes formatting
 axes[0].set_xlim(info['{}_0'.format(ra_runs)]['sim_time'][0], info['{}_2'.format(ra_runs)]['sim_time'][-1])

### 2017-12-21 code/join_data.py
adding join data file

@@ -1,0 +1,23 @@
+import os
+import sys
+import logging
+logger = logging.getLogger(__name__)
+
+import dedalus.public
+from dedalus.tools  import post
+
+data_dir = sys.argv[1]
+base_path = os.path.abspath(data_dir)+'/'
+
+logger.info("joining data from Dedalus run {:s}".format(data_dir))
+
+data_types = ['checkpoint', 'scalar', 'profiles', 'slices', 'powers', 'coeffs', 'volumes']
+
+for data_type in data_types:
+    logger.info("merging {}".format(data_type))
+    try:
+        post.merge_analysis(base_path+data_type)
+    except:
+        logger.info("missing {}".format(data_type))
+        
+logger.info("done join operation for {:s}".format(data_dir))

### 2017-12-21 code/rayleigh_benard.py
updates a bunch of run scripts; adds 3d

@@ -23,6 +23,7 @@ Options:
     --no_slip                  no slip boundary conditions top/bottom; default if no choice is made
 
     --3D                       Run in 3D
+    --mesh=<mesh>                        Processor mesh if distributing 3D run in 2D 
     
     --run_time=<run_time>             Run time, in hours [default: 23.5]
     --run_time_buoy=<run_time_bouy>   Run time, in buoyancy times
@@ -76,7 +77,7 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
                     data_dir='./', coeff_output=True, verbose=False, no_join=False,
                     do_bvp=False, num_bvps=10, bvp_convergence_factor=1e-2, bvp_equil_time=10, bvp_resolution_factor=1,
                     bvp_transient_time=30, bvp_final_equil_time=None, min_bvp_time=50,
-                    threeD=False, seed=42):
+                    threeD=False, seed=42, mesh=None):
     import os
     from dedalus.tools.config import config
     
@@ -112,7 +113,7 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
 
     if threeD:
         logger.info("resolution: [{}x{}x{}]".format(nx, ny, nz))
-        equations = BoussinesqEquations3D(nx=nx, nz=nz, Lx=Lx, Lz=Lz)
+        equations = BoussinesqEquations3D(nx=nx, ny=ny, nz=nz, Lx=Lx, Lz=Lz, mesh=mesh)
     else:
         logger.info("resolution: [{}x{}]".format(nx, nz))
         equations = BoussinesqEquations2D(nx=nx, nz=nz, Lx=Lx, Lz=Lz)
@@ -372,6 +373,13 @@ if __name__ == "__main__":
     bvp_final_equil_time=args['--bvp_final_equil_time']
     if not isinstance(bvp_final_equil_time, type(None)):
         bvp_final_equil_time = float(bvp_final_equil_time)
+
+    mesh = args['--mesh']
+    if mesh is not None:
+        mesh = mesh.split(',')
+        mesh = [int(mesh[0]), int(mesh[1])]
+
+
         
     Rayleigh_Benard(Rayleigh=float(args['--Rayleigh']),
                     Prandtl=float(args['--Prandtl']),
@@ -403,6 +411,7 @@ if __name__ == "__main__":
[…]

### 2017-12-29 code/run_scripts/2d/base_post/local_runs.sh
adds overwrite tag to post scripts

@@ -1,6 +1,6 @@
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e3 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e3_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e3 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e3_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=1.30e4 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra1.30e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e4 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e4 --restart=runs/base_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
[…]

### 2017-12-29 code/run_scripts/2d/bvp_post/local_runs.sh

@@ -1,6 +1,5 @@
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e3 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e3_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e3 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e3_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=1.30e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra1.30e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5
-
[…]

### 2017-12-29 tex/bvp_paper.tex
adds to-do list to paper
first draft of figure captions and discussion

@@
 \maketitle
+
+\section{To Do}
+\begin{enumerate}
+\item Get 3D cases in
+\item Continue Improving Figures
+\item Write figure captions
+\item Think about post-bvp multiplying.  Should it be a profile for both the velocity
+and for the T perturbations, rather than a scalar?  I'm starting to think it should.
+\end{enumerate}
 
@@
 horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
-the aspect ratio is $\Gamma = 2 \lambda_c$, with
-$\lambda_c = 2\pi/k_c$, and $k_c=2.5519$ is the wavenumber of convective onset for this choice of
-boundary conditions.
+the aspect ratio is $\Gamma = 2$.
 
@@
 \includegraphics[width=\textwidth]{./figs/time_trace.png}
-\caption{\label{fig:time_trace} }
+\caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
+(b) are shown for Ra = $1.30 \cdot 10^7$ ($S = 10^4$).  The two plots are scaled such that
+one time unit on the x-axis of either run takes up an equivalent amount of space on the paper
+to illustrate the time savings of the BVP run.  (c\&d) Flux plots, where black is the sum of the
+flux, blue is enthalphy flux and red is condcutive flux. (c) Fluxes are shown for the IVP at an early
+time to illustrate the asymmetry of the flux through the system. (d) Fluxes through the converged,
+rundown state are compared to the fluxes in the converged BVP solution, where their difference
+is shown in (e). \label{fig:time_trace} }
 \end{figure}
@@
 \includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{\label{fig:pdf_comparison} }
+\caption{We compare the time-variant dynamics in our 2D solutions by showing probability distribution
+functions of the values of vertical velocity (a), horizontal velocity (b), and nonlinear heat
+transport (c) in our converged solutions.  The horizontal velocities are very similar, with a
+KS test similarity of X.  The vertical velocities, too, are similar, with a KS similarity of
+Y.  The nonlinear heat transport, while overall quite similar, shows that the BVP experiences
+a greater number of extreme events.  The peak around zero for all three PDFs reflects the
+no-slip boundary conditions.\label{fig:pdf_comparison} }
 \end{figure}
@@
 \includegraphics[width=\textwidth]{./figs/temp_comparison.png}
-\caption{\label{fig:temp_comparison} }
+\caption{Here we compare the evolved thermodynamic state of a BVP to that of a rundown IVP that
+has been run through a thermal timescale.  (a) The temperature profiles, as a function of height,
+are shown. (b) The percentage difference between the temperature profiles, as a function of height,
+is shown.  (c) PDFs comparing the values of the point-by-point temperatures over the averaging
+window.  While the median of the PDF has a distinct offset between the two runs, the
+thermal fluctuations about the mean which drive the convection are nearly the same.
+\label{fig:temp_comparison} }
 \end{figure}
@@
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
-\caption{\label{fig:parameter_space_comparison} }
+\caption{Here we demonstrate the efficacy of the BVP method at many values of Ra.  We show
+(a) Nusselt number scaling, (b) Reynolds number scaling, and (c) scaling of the mean temperature
+over the whole simulation.  (a) The Nusselt number follows a classic 2/7 scaling law
+\cite{johnston&doering2009}, until it reaches S = $10^{3 + 2/3}$, at which point the
+two-roll solution begins oscillating horizontally, showing time-variant Nu.  The range of Nu
+over the averaging window is (blah), and the trend of Nu (the variance of the mean Nu) is shown
+as (blah).  (b) Re follows an expected 1/2 scaling law. (c) The mean value of temperature, minus
+the value at the fixed-temperature boundary, is shown.  As Ra increases, the boundary layers shrink,
+and the convection becomes more efficient, we anticipate this value to get closer and closer to
+zero as the atmosphere approaches the isotherm defined by the upper boundary.
+\label{fig:parameter_space_comparison} }
 \end{figure}
@@
 \label{sec:results}
-I don't have the mental stamina to write this section right now.  In general, here's what it's going to say:
-\begin{enumerate}
-\item This procedure works, as we've shown.
-\item How to apply this to more complicated cases, like stratified convection
-\item How to apply this to different boundary conditions
-\item Brief discussion of other methods that can be used to fast-forward, e.g., bootstrapping.
-\item This is just a first step.
-\end{enumerate}
+While imperfect, the method presented here is a first step towards taking meaningful measurements
+of highly turbulent convection on manageable, human timescales.  As demonstrated in Figs.
+1-4, this BVP method quickly converges simulations to within a few percent of the true final
+state, while preserving the natural behavior of the convective solution (such as the oscillatory
+nature of high-Ra 2D states in \ref{fig:parameter_space_comparison}).
+
+While not perfect, the BVP method here has one major benefit over some of the other methods
+currently being used to achieve high Ra solutions.  One oft-used method is that of bootstrapping,
+in which the converged solution of a low-Ra state is used as initial conditions for a higher-Ra
+simulation.  While these methods are extremely powerful, they are influenced by hysteresis effects,
+and the powerful, steady rolls achieved at low Ra can result in an artifically over-stable high-Ra
+roll solution.  The BVP method can be used with random noise initial conditions which allow the
+convective solution to be naturally chosen by the dynamics.
+
+One benefit of the method presented here is that it can be easily extended to more complicated
+configurations.  For example, to use this method in simulations of stratified compressible convection,
+one need only adapt the BVP equations to the appropriate equations of hydrostatic equilibrium,
+$\grad P = -\rho \bm{g}$, and thermal equilibrium, $\Div{F_{\text{cond}} + F_{\text{conv}}} = \text{sources}$,
+for the problem at hand.  In compressible convection, where the density is allowed to change,
+one must also use the knowledge of stellar structure codes and add an equation of mass conservation
+in order to ensure that the BVP does not spuriously add or remove mass from the system.
+
+This method can be extended to other boundary conditions, as well.  To solve for fixed temperature
+boundary conditions, the difficulty is in finding the amount of flux through the system -- but
+this can be done by using the ratios $f_{\text{conv}}$ and $f_{\text{cond}}$.  In the case of
+fixed flux boundary conditions, there is degeneracy in the temperature solution which can come
+out of the BVP, but in using knowledge about the system -- such as the initial symmetry of the
+RB state around $T_1 = 0$, the final solution can be pegged onto the proper profile.
 

### 2017-12-29 code/bvps/bvp_tools.py
updated bvp algorithm a bit

@@ -180,15 +180,17 @@ class BVPSolverBase:
         # Set up a dictionary of partial profiles to track averages locally so we
         # don't have to communicate each timestep.
         self.partial_prof_dict = OrderedDict()
+        self.partial_prof_dict_current = OrderedDict()
         self.current_local_avg = OrderedDict()
         self.current_local_l2  = OrderedDict()
         for fd, info in self.FIELDS.items():
             if info[1] == 0 or info[1] == 1 or info[1] == 2:
                 self.partial_prof_dict[fd]  = np.zeros(self.n_per_proc)
+                self.partial_prof_dict_current[fd]  = np.zeros(self.n_per_proc)
                 self.current_local_avg[fd]  = np.zeros(self.n_per_proc)
                 self.current_local_l2[fd]   = np.zeros(self.n_per_proc)
             else:
-                self.partial_prof_dict[fd]  = np.zeros((nx, self.n_per_proc))
+                self.partial_prof_dict_current[fd]  = np.zeros((nx, self.n_per_proc))
                 self.current_local_avg[fd]  = np.zeros((nx, self.n_per_proc))
 #            self.current_local_l2[fd] = 0
 
@@ -220,17 +222,18 @@ class BVPSolverBase:
             avg_type        - If 0, horiz avg.  If 1, full 2D field.
         """
         if avg_type == 0:
-            self.partial_prof_dict[prof_name] += \
-                        dt*self.flow.properties['{}'.format(prof_name)]['g'][0,:]
+            self.partial_prof_dict_current[prof_name] = \
+                        self.flow.properties['{}'.format(prof_name)]['g'][0,:]
         elif avg_type == 1:
-            self.partial_prof_dict[prof_name] += \
-                        dt*self.flow.properties['{}'.format(prof_name)]['g'][0,:]**2
+            self.partial_prof_dict_current[prof_name] = \
+                        self.flow.properties['{}'.format(prof_name)]['g'][0,:]**2
         elif avg_type == 2:
-            self.partial_prof_dict[prof_name] += \
-                        dt*np.sum((self.flow.properties['{}'.format(prof_name)]['g'] - np.mean(self.flow.properties['{}'.format(prof_name)]['g'], axis=0))**2, axis=0)
+            self.partial_prof_dict_current[prof_name] = \
[…]

### 2017-12-29 code/plotting/parameter_space_comparison.py

@@ -80,12 +80,12 @@ for i,k in enumerate(fields):
                 ax.errorbar(float(ra), 0.5+mean, yerr=std,  color=COLORS[int(ind)])
                 ax.scatter(float(ra), 0.5+mean, s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)
             elif k == 'Nu':
-                p=0#2/3
+                p=2/7#2/3
                 bx.scatter(float(ra)/ra_crit, mean/float(ra)**(p), s=0, alpha=0)
                 ax.errorbar(float(ra), mean/(float(ra)**(p)), yerr=std/(float(ra)**(p)),  color=COLORS[int(ind)])
                 ax.scatter(float(ra), mean/(float(ra)**p), s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)
             elif k == 'Re':
-                pRe = 0.425
+                pRe = 0.5
                 bx.scatter(float(ra)/ra_crit, mean/float(ra)**(pRe), s=0, alpha=0)
                 ax.errorbar(float(ra), mean/float(ra)**(pRe), yerr=std/float(ra)**(pRe),  color=COLORS[int(ind)])
                 ax.scatter(float(ra), mean/float(ra)**(pRe), s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)

### 2017-12-29 code/rayleigh_benard.py

@@ -290,7 +290,7 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
         logger.info('iter/sec: {:f} (main loop only)'.format(n_iter_loop/main_loop_time))
         try:
             final_checkpoint = Checkpoint(data_dir, checkpoint_name='final_checkpoint')
-            final_checkpoint.set_checkpoint(solver, wall_dt=1, mode="append")
+            final_checkpoint.set_checkpoint(solver, wall_dt=1, mode=mode)
             solver.step(dt) #clean this up in the future...works for now.
             post.merge_process_files(data_dir+'/final_checkpoint/', cleanup=False)
         except:

### 2018-01-05 tex/bvp_paper.tex
improvements to BVP code, need to verify they all work, try out changing delta_t

@@
 \item Write figure captions
-\item Think about post-bvp multiplying.  Should it be a profile for both the velocity
-and for the T perturbations, rather than a scalar?  I'm starting to think it should.
 \end{enumerate}
@@
 low Mach number and constrained by the solar rotation rate of $\sim$1 month.  
-Despite these relatively short dynamical times, the scale of energy transport on the
-Sun occurs on the Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
+Both of these dynamical timescales are vastly shorter than the Sun's average timescale of energy transport,
+which is the Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
 As simulations aim to model natural convection
@@
 Furthermore, with increasing Ra and decreasing diffusivities, motions become more turbulent
-and require finer grid meshes and smaller timesteps to resolve turbulent motions, meaning that
-achieving even one overturn timescale becomes a harder problem.  
-These two effects combine such that achieving thermally converged, high-Ra, astrophysically interesting
-simulations is intractable using modern numerical tools.
+and require finer grid meshes and shorter timesteps to resolve turbulent motions, increasing the simulation
+time required for each overturn timescale.  
+These two effects conspire to make achieving thermally converged, high-Ra, astrophysically interesting
+simulations an intractable problem using modern numerical tools.
 
-In studies of stratified convection where a convective layer lies between stable layers, studies
-have used the knowledge of Mixing Length Theory (MLT) to adjust the initial thermal profile of
-atmospheres to a state which is closer to the adiabat chosen by convection \cite{brandenburg&all2005}.
-However, many studies of convection do not contain stable layers above and below the convection
-zone, and the presence of hard boundaries and the boundary layers that they form makes it difficult to
-know proper evolved adiabat \emph{a priori} before the dynamics of the simulation evolve the
-structure of the boundary layers.
+Prior studies of stratified convection in which a convective layer lies between stable layers
+have used the knowledge of Mixing Length Theory (MLT) to adjust the initial thermodynamic structure of
+the atmosphere to a state which is closer to the adiabat chosen by convection \cite{brandenburg&all2005}.
+However, most studies of convection do not contain stable layers above and below the convection
+zone, and the presence of hard boundaries and the boundary layers that they form make it difficult to
+know the correct evolved adiabat \emph{a priori}.
 
@@
 In our study, we adopt the Oberbeck-Boussinesq approximation.  Here, the
-fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
-of thermal expansion ($\alpha$).  We non-dimensionalize length by the layer height ($L_z$) ,
-temperature by the (constant) initial temperature gradient across the layer ($\grad T_0$), and time
-by the freefall timescale ($L_z / v_{\text{ff}}$, with $v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$, where $g$ is 
-uniform gravitational acceleration in the $-\hat{z}$ direction). The dimensionless Boussinesq
+fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), fluid density ($\rho_0$), and coefficient
+of thermal expansion ($\alpha$).   The Boussinesq
 equations governing the velocity $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, temperature
-$T = T_0 + T_1$, and reduced pressure $\varpi$ are \cite{spiegel&veronis1960}
+$T = T_0 + T_1$, and pressure $P$ are \cite{spiegel&veronis1960}
+\begin{gather}
+\DivU = 0, 
+	\label{eqn:dim_incompressible}
+\\
+\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
+-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
+	\label{eqn:dim_bouss_momentum}
+\\
+\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
+	\label{eqn:dim_bouss_energy}
+\end{gather}
+We non-dimensionalize these equations on a length scale of the layer height ($L_z$),
+a temperature of the (constant) initial temperature gradient across the layer ($\grad T_0$), and a timescale
+of the freefall timescale ($L_z / v_{\text{ff}}$, with $v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$, where $g$ is 
+uniform gravitational acceleration in the $-\hat{z}$ direction).
+We non-dimensionalize the equations and re-arrange the momentum equation, introducing a reduced pressure
+$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where $\phi$ is the gravitational potential, we time evolve
+the following equations,
 \begin{gather}
@@
 \\
-\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
--\grad\varpi + T_1\hat{z} + \frac{\text{Pr}}{\text{Ra}}\grad^2\bm{u}, 
+\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega}
 	\label{eqn:bouss_momentum}
 \\
-\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \frac{1}{\text{Pr}\,\text{Ra}}\grad^2 T_1,
+\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
 	\label{eqn:bouss_energy}
 \end{gather}
-where the dimensionless control parameters are the Rayleigh and Prandtl numbers,
+where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.  
+Here the dimensionless control parameters are the Rayleigh and Prandtl numbers,
 \begin{equation}
+\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
 \text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\chi} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
@@
 the aspect ratio is $\Gamma = 2$.
+
+These equations are expressed with linear terms on the left-hand side and
+nonlinear terms on the right-hand side.  Because $P$ is a (whatever it's called) in boussinesq, \RB convection, we are able to
+evolve $\varpi$ as a linear variable even though it contains a nonlinear velocity component.  This formulation
+of the equations gives us a modest improvement in timestepping speed compared to Eqns. (\ref{eqn:dim_incompressible}-\ref{eqn:dim_bouss_energy}).
+have been expressed with the linear terms (which we solve implicitly) on the LHS, and the
+nonlinear terms on the RHS. Here, the reduced pressure is $\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$,
+where $\phi$ is the gravitational potential and where $P$ is a (I forget the word) that enforces incompressibility
+in the Boussinesq system.
 

### 2018-01-05 code/bvps/bvp_tools.py

@@ -112,7 +112,7 @@ class BVPSolverBase:
         self.num_bvps           = num_bvps
         self.min_bvp_time       = min_bvp_time
         self.min_avg_dt         = min_avg_dt
-        self.curr_avg_dt        = 0.
+        self.time_since_avg_adjust        = 0.
         self.completed_bvps     = 0
         self.avg_time_elapsed   = 0.
         self.avg_time_start     = 0.
@@ -127,6 +127,7 @@ class BVPSolverBase:
         self.bvp_l2_last_check_time = 0
         self.do_bvp                 = False
         self.first_l2               = True
+        self.re_switch              = False
 
         #Get info about MPI distribution
         self.comm           = comm
@@ -150,25 +151,25 @@ class BVPSolverBase:
                 
         if self.rank == 0:
             self.profiles_dict = OrderedDict()
-            self.profiles_dict_last= OrderedDict()
             for fd, info in self.FIELDS.items():
                 if info[1] == 0 or info[1] == 1:    
                     self.profiles_dict[fd]      = np.zeros(nz)
-                    self.profiles_dict_last[fd] = np.zeros(nz)
 
 
 
         # Set up a dictionary of partial profiles to track averages locally so we
         # don't have to communicate each timestep.
-        self.partial_prof_dict = OrderedDict()
         self.profiles_dict_curr = OrderedDict()
         self.current_local_avg = OrderedDict()
+        self.current_profiles = OrderedDict()
+        self.current_times = OrderedDict()
         self.current_local_l2  = OrderedDict()
         for fd, info in self.FIELDS.items():
             if info[1] == 0 or info[1] == 1:
-                self.partial_prof_dict[fd]  = np.zeros(self.nz_per_proc)
                 self.current_local_avg[fd]  = np.zeros(self.nz_per_proc)
                 self.current_local_l2[fd]   = np.zeros(self.nz_per_proc)
+                self.current_profiles[fd]   = np.zeros((2,self.nz_per_proc))
+                self.current_times[fd]      = np.zeros(2)
         for fd in self.LOCAL_TRACK.keys():
             self.profiles_dict_curr[fd] = np.zeros(self.nz_per_proc)
 
@@ -188,7 +189,7 @@ class BVPSolverBase:
                 os.mkdir('{:s}'.format(self.plot_dir))
 
 
-    def update_local_profiles(self, dt, prof_name, avg_type=0):
+    def get_local_profile(self, prof_name, avg_type=0):
         """
[…]

### 2018-01-05 code/plotting/parameter_space_comparison.py

@@ -27,21 +27,16 @@ import matplotlib.gridspec as gridspec
 
 import dedalus.public as de
 
-EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
-FORCE_WRITE=False
-
 COLORS=['indigo', 'orange']
 MARKERS=['s', 'o', 'd', '*']
 MARKERSIZE=[5,4,5,7]
 
-MARKERS_2=['p', '^', '8']
-COLORS_2=['peru', 'gold', 'teal']
-MARKERSIZE_2=[5,5,5]
-
 fields = ['Nu', 'Re', 'IE']
 base_dirs = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post',
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/3d/base_post',
+            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/3d/bvp_post'
             ]
 
 info = OrderedDict()
@@ -75,24 +70,30 @@ for i,k in enumerate(fields):
             good_data = datum[k]
             mean, std = np.mean(good_data), np.std(good_data)
             ra, ind = ra_info.split('_')
+            ind = int(ind)
+            if ind >= 2:
+                mrkr = '*'
+            else:
+                mrkr = 'o'
+            ind = int(ind) % 2
             if k == 'IE':
                 bx.scatter(float(ra)/ra_crit, 0.5+mean, s=0, alpha=0)
                 ax.errorbar(float(ra), 0.5+mean, yerr=std,  color=COLORS[int(ind)])
-                ax.scatter(float(ra), 0.5+mean, s=12*(3 - 2*int(ind)), marker='o', color=COLORS[int(ind)], alpha=0.75)
+                ax.scatter(float(ra), 0.5+mean, s=12*(3 - 2*int(ind)), marker=mrkr, color=COLORS[int(ind)], alpha=0.75)
             elif k == 'Nu':
                 p=2/7#2/3
                 bx.scatter(float(ra)/ra_crit, mean/float(ra)**(p), s=0, alpha=0)
[…]

### 2018-01-05 code/plotting/pdf_comparison.py

@@ -43,7 +43,7 @@ base_dirs_post = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
             ]
 ra_runs = '6.01e4'
-ra_runs = '2.79e7'
+ra_runs = '1.30e8'
 
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_post):

### 2018-01-05 code/plotting/time_trace.py

@@ -27,18 +27,11 @@ import matplotlib.gridspec as gridspec
 
 import dedalus.public as de
 
-EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
-FORCE_WRITE=False
 
 COLORS=['indigo', 'orange']
 MARKERS=['s', 'o', 'd', '*']
 MARKERSIZE=[5,4,5,7]
 
-MARKERS_2=['p', '^', '8']
-COLORS_2=['peru', 'gold', 'teal']
-MARKERSIZE_2=[5,5,5]
-
-fields = ['Nu', 'Re', 'IE', 'KE', 'TE']
 base_dirs_pre = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_pre',
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_pre'
@@ -48,10 +41,11 @@ base_dirs_post = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
             ]
+fields = ['Nu', 'Re', 'IE', 'KE', 'TE']
 
-ra_runs = '6.01e4'
-ra_runs = '2.79e7'
+ra_runs = '1.30e8'
 
+##### INFO grabbing from post-plot buddy files
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
     print(base_dir)
@@ -65,9 +59,10 @@ for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
             with h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(d), 'r') as f:
                 for k in fields:
                     info[ra][k+'_scalar'] = f[k].value
+                print('hi')
                 info[ra]['sim_time'] = f['sim_time'].value
         except:
-            print('cannot find file in {:s}'.format(d))
+            print('cannot find scalar file in {:s}'.format(d))
 
         try:
             with h5py.File('{:s}/profile_plots/profile_info.h5'.format(d), 'r') as f:
@@ -77,19 +72,21 @@ for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
[…]

### 2018-01-05 code/rayleigh_benard.py

@@ -48,7 +48,7 @@ Options:
     --num_bvps=<num>                     Max number of bvps to solve [default: 1]
     --bvp_equil_time=<time>              How long to wait after a previous BVP before starting to average for next one, in tbuoy [default: 50]
     --bvp_final_equil_time=<time>        How long to wait after last bvp before ending simulation 
-    --bvp_transient_time=<time>          How long to wait at beginning of run before starting to average for next one, in tbuoy [default: 20]
+    --bvp_transient_time=<time>          How long to wait at beginning of run before starting to average for next one, in tbuoy [default: 50]
     --min_bvp_time=<time>                Minimum avg time for a bvp (in tbuoy) [default: 10]
     --bvp_resolution_factor=<mult>       an int, how many times larger than nz should the bvp nz be? [default: 1]
     --bvp_convergence_factor=<fact>      How well converged time averages need to be for BVP [default: 1e-2]
@@ -68,6 +68,7 @@ from boussinesq_dynamics.equations import *
 from bvps.bvp_tools import BoussinesqBVPSolver
 from tools.checkpointing import Checkpoint
 checkpoint_min = 30
+RA_CRIT = 1295.78
     
 def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
                     fixed_flux=False, fixed_T=False, mixed_flux_T = True,
@@ -138,6 +139,9 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
         bc_dict['stress_free'] = True
     elif no_slip:
         bc_dict['no_slip'] = True
+
+
+    supercrit = Rayleigh/RA_CRIT
 
     equations.set_BC(**bc_dict)
 
@@ -245,7 +249,7 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
                 not_corrected_times = False
 
             if do_bvp:
-                bvp_solver.update_avgs(dt, Re_avg, min_Re=1e0)
+                bvp_solver.update_avgs(dt, Re_avg, min_Re=np.sqrt(supercrit)/2)
                 if bvp_solver.check_if_solve():
                     atmo_kwargs = { 'nz'              : nz*bvp_resolution_factor,
                                     'Lz'              : Lz

### 2018-01-09 tex/bvp_paper.tex
rewrite of BVP procedure

@@
 \label{sec:experiment}
-In our study, we adopt the Oberbeck-Boussinesq approximation.  Here, the
-fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), fluid density ($\rho_0$), and coefficient
-of thermal expansion ($\alpha$).   The Boussinesq
-equations governing the velocity $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, temperature
-$T = T_0 + T_1$, and pressure $P$ are \cite{spiegel&veronis1960}
+We adopt the Oberbeck-Boussinesq approximation.  Under this choice, the
+fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
+of thermal expansion ($\alpha$). The variables of the fluid that are evolved are the velocity,
+$\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure.
+The density of the fluid is a constant $\rho_0$, except on the
+term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$ acts in the vertical momentum equation, 
+in which case it is $\rho = \rho_0(1  - \alpha T_1)$.  
+Under these choices, the equations of motion are \cite{spiegel&veronis1960}
 \begin{gather}
@@
 \end{gather}
-We non-dimensionalize these equations on a length scale of the layer height ($L_z$),
-a temperature of the (constant) initial temperature gradient across the layer ($\grad T_0$), and a timescale
-of the freefall timescale ($L_z / v_{\text{ff}}$, with $v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$, where $g$ is 
-uniform gravitational acceleration in the $-\hat{z}$ direction).
-We non-dimensionalize the equations and re-arrange the momentum equation, introducing a reduced pressure
-$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where $\phi$ is the gravitational potential, we time evolve
-the following equations,
+We non-dimensionalize these equations such that length scales are in units of the layer height ($L_z$),
+temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
+and time is in units of the freefall timescale ($L_z / v_{\text{ff}}$), where the freefall velocity is
+$v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$.
+We further re-arrange the momentum equation by introducing a reduced pressure
+$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where $\bm{g} = -\grad \phi$ is the gravitational potential.
+Despite containing a nonlinear $\bm{u}$ component, the nature of $P$ in \RB convection, as a (whatever it's called)
+allows us to treat $\varpi$ as a linear unknown, without a need to resolve its different components.
+We time evolve the equations in the form,
 \begin{gather}
@@
 \end{gather}
-where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.  
-Here the dimensionless control parameters are the Rayleigh and Prandtl numbers,
+where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity. We find this form of the momentum equation to
+be slightly faster numerically than the standard form in Eq. (\ref{eqn:dim_bouss_momentum}).
+The dimensionless control parameters are set by the Rayleigh and Prandtl numbers,
 \begin{equation}
@@
 the aspect ratio is $\Gamma = 2$.
-
-These equations are expressed with linear terms on the left-hand side and
-nonlinear terms on the right-hand side.  Because $P$ is a (whatever it's called) in boussinesq, \RB convection, we are able to
-evolve $\varpi$ as a linear variable even though it contains a nonlinear velocity component.  This formulation
-of the equations gives us a modest improvement in timestepping speed compared to Eqns. (\ref{eqn:dim_incompressible}-\ref{eqn:dim_bouss_energy}).
-have been expressed with the linear terms (which we solve implicitly) on the LHS, and the
-nonlinear terms on the RHS. Here, the reduced pressure is $\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$,
-where $\phi$ is the gravitational potential and where $P$ is a (I forget the word) that enforces incompressibility
-in the Boussinesq system.
 
@@
 \subsection{The Boundary Value Problem}
-\begin{figure}[b]
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{./figs/time_trace.png}
@@
 
-The prohibitively long thermal timescale required to reach an equilibrium temperature profile
-in a Direct Numerical Simulation (DNS) can be skipped by coupling the DNS with a simple Boundary Value Problem
-(BVP) solve. Using information about the dynamics of the convection in the atmosphere, it is possible
-to skip a large portion of the thermal evolution, see Fig \ref{fig:time_trace}a\&b.
+It is a reasonable assumption to naively guess that convection will evolve the mean temperature profile that
+drives it over the course of a thermal diffusion time, $t_\chi \approx \mathcal{P}^{-1}$. Thus, as Ra
+increases, the timescale for achieving a thermally converged mean temperature profile becomes intractable.
+This prohibitively long thermal timescale in a Direct Numerical Simulation (DNS) 
+can be skipped by coupling the DNS with a simple Boundary Value Problem
+(BVP) solve. By using information about the evolved dynamical state of the atmosphere,
+a BVP can be used to solve for the evolved atmospheric state on short timescales.
+A comparison of a simulation running for the thermal timescale, and another where a BVP is used
+to fast-forward atmospheric evolution, are shown in Fig \ref{fig:time_trace}a\&b.
 
-The Boussinesq BVP contains equations of hydrostatic balance and thermal equilibrium,
+The Boussinesq BVP in essence contains equations of hydrostatic balance and thermal equilibrium,
 \begin{gather}
-\frac{\partial}{\partial z}\angles{\varpi} = \angles{T_1}\hat{z},
+\frac{\partial}{\partial z}\angles{\varpi} - \angles{T_1}\hat{z} = \angles{\bm{u}\times\bm{\omega}},
 	\label{eqn:bouss_BVP_momentum}
 \\
-\frac{\partial}{\partial z}\angles{wT_1} = \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1},
+\frac{\partial}{\partial z}\angles{wT_1} - \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1} = 0,
 	\label{eqn:bouss_BVP_energy}
@@
 These
-equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum}\&\ref{eqn:bouss_energy}),
-neglecting terms that vanish due to symmetry, and assuming that the flows are in a stationary state.  
+equations arise from assuming that the atmosphere is in a steady state ($\partial_t \rightarrow 0$),
+then taking time and horizontal averages of Eqns (\ref{eqn:bouss_momentum}\&\ref{eqn:bouss_energy}) and
+neglecting terms that vanish due to the symmetry of the problem.
 Convective flows
-are perturbations around a thermal profile defined by these equations in the proper evolved state.
+are perturbations around a thermal profile defined by these equations in the proper evolved, statistically stationary state.
 
@@
 the thermal structure ($\angles{T_1}$, $\angles{\varpi}$) of the atmosphere is fully determined by the specification
-of the convective flux, $F_{conv} = \angles{w T_1}$.  If this profile is known, then 
+of two profiles: the convective flux, $F_{conv} = \angles{w T_1}$, and the nonlinear advection, $\angles{\bm{u}\times\bm{\omega}}$.  
+If these profiles are known, then 
 solving for $\angles{T_1}$ and
@@
 
-By definition, the profile of $F_{conv}$ is \emph{not} in its time stationary state near the
-beginning of the simulation.  In fact, under mixed boundary conditions, as the atmosphere approaches the
-isotherm specified by the upper boundary condition, the motions display an asymmetric flux as energy
-leaks through the upper boundary condition (Fig. \ref{fig:time_trace}c).  
+By definition, the profile of $F_{conv}$ is not in its time stationary early in the DNS.  
+In fact, as the atmosphere approaches the
+isotherm specified by the upper (fixed $T$) boundary condition, the motions display an asymmetric flux as energy
+leaks through the upper boundary condition (Fig. \ref{fig:time_trace}c) in order to reach a lower temperature state.
 In order to construct the evolved convective flux from the current fluxes in the atmosphere,
-we acknowledge that the evolved solution will be in flux equilibrium, 
-carrying the amount of flux specified at the fixed-flux condition throughout the full depth of the atmosphere.  
-Thus, the steady-state profile of the convective flux can be approximated as
-\begin{equation}
-F_{\text{conv, steady}} = F_{\text{bot}}\frac{\angles{wT_1}}{\angles{wT_1 - \kappa \partial_z (T_0 + T_1)}}
-= F_{\text{bot}}\frac{\angles{F_{\text{conv, IVP}}}}{\angles{F_{\text{tot, IVP}}}}.
-\label{eqn:bouss_BVP_fconv}
-\end{equation}
-In essence, the construction of this profile assumes that the system appropriately picks out the ratios
+we assume that the atmospheric dynamics have properly developed the thickness of the boundary layers, 
+or that the quantities
 \begin{equation}
 f_{\text{conv}} = \frac{F_{\text{conv}}}{F_{\text{tot}}}\qquad
-f_{\text{cond}} = \frac{F_{\text{cond}}}{F_{\text{tot}}}.
+f_{\text{cond}} = \frac{F_{\text{cond}}}{F_{\text{tot}}}
 \end{equation}
-in the transient state.  Thus, even though the quantity of flux being carried is not correct, the
-system is carrying flux convectively where it needs to in the interior, and conductively in the boundaries.
+early in the evolution are the same as those in the final steady state solution. By definition, the
+evolved total flux through the atmosphere must be the same as the flux entering the atmosphere at the
+bottom boundary, $F_{\text{tot, steady}} = F_{\text{bot}}$.  The proper enthalpy flux profile to feed in
+to Eqn. (\ref{eqn:bouss_BVP_energy}) is then 
+$\angles{w T_1}_{\text{steady}} = F_{\text{tot, steady}} \cdot f_{\text{conv}}$.  Presumably, over the
+course of the simulation, the velocity field and temperature fluctuations naturally scale like
+$d(z) = \angles{w T_1}_{\text{steady}}/\angles{w T_1}$, and so it is necessary to multiply the velocity
+field and the fluctuations around the mean in $T_1$ by $\sqrt{d}$.  This also means that
+$\angles{\bm{u}\times\bm{\omega}}_{\text{steady}} = d \angles{\bm{u}\times\bm{\omega}}$. Once these profiles
+are appropriately adjusted, they can be used in the BVP solve to find the mean profiles of $T$ and $\varpi$.
 
-The choice of a fixed-flux boundary condition at the bottom appropriately scales the magnitude of
-$F_{\text{conv, steady}}$.  The choice of a fixed-temperature boundary condition at the top of the
-atmosphere appropriately sets the isotherm of the convective interior.  While this method can be used
-for other choices of thermal boundary conditions (see Discussion), dual fixed temperature conditions
-at the upper plate require a more careful handling of $F_{\text{bot}}$, and dual fixed flux boundary
-conditions have degenerate solutions for the constant offset of $T_1$.
-
-In general, the BVP solve takes the following form:
+In general, the BVP solve is completed in the following steps:
 \begin{enumerate}
-\item Run the convective IVP. Once the convection begins, start taking averages averages of $\angles{wT_1}$
-and $\partial_z^2\angles{T_1}$, which determine the fluxes through the system.  Update these averages every
-$\Delta t = 0.1$ freefall times.  Once these averages are converged to 1 part in 1000, the BVP is ready to be solved.
-\item Construct $F_{\text{conv, steady}}$ from the flux profiles, then use it to solve for $\angles{T_1}$ 
-and \angles{\varpi} of the
-evolved state.  Adjust the mean profiles in the BVP such that this is their mean profile.
-\item Divide the velocities and the $T_1$ fluctuations around the mean profile by 
-$\sqrt{\bar{F_{\text{bot}}/F_{\text{tot}}}}$. This lowers the convective flux through the system such that it is,
-on average, the convective flux used in the BVP solve.
-\item Continue running the IVP for a number of freefall times to allow the velocities and temperature perturbations
-to equilibrate to the new mean state.
+\item Run the convective DNS. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
+wait for 50 time units.  Then, start taking the averages of $F_{\text{conv}}$ and $F_{\text{tot}}$, waiting either
+30 time units or until the profiles are converged to 1 part in 1000, whichever is a more difficult. This ensures that
+the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
+\item Construct $\angles{w T_1}_{\text{steady}}$ and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
+from the flux profiles.
+\item Solve for $\angles{T_1}$ and \angles{\varpi} of the
+evolved state.  Adjust the mean profiles in the IVP.
+\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{d}$ in the IVP. 
+\item Continue running the IVP for 50 time units to allow for the velocities to equilibrate to their new background state.
 \end{enumerate}
-This procedure seems to work quite well, see Fig. \ref{fig:time_trace}d\&e.
 

### 2018-01-09 code/plotting/pdf_comparison.py

@@ -23,6 +23,38 @@ comm_world = MPI.COMM_WORLD
 from collections import OrderedDict
 import h5py
 import matplotlib.gridspec as gridspec
+from scipy.interpolate import interp1d
+
+
+def calculate_CDF(x, pdf):
+    """ Calculate the CDF of a PDF using trapezoidal rule integration """
+    dx = np.diff(x)
+    new_x = x[0:-1] + dx
+    d_cdf   = (dx/2) * (pdf[0:-1] + pdf[1:])
+    cdf = np.zeros_like(d_cdf)
+    for i in range(len(cdf)):
+        cdf[i] = np.sum(d_cdf[:i+1])
+    return new_x, cdf
+
+def ks_test(x1, y1, N1, x2, y2, N2, n=1000):
+    x_range = [np.min(x1), np.max(x1)]
+    if np.min(x2) > x_range[0]:
+        x_range[0] = np.min(x2)
+    if np.max(x2) < x_range[1]:
+        x_range[1] = np.max(x2)
+
+    x_points = np.linspace(*tuple(x_range), n)
+
+    f1 = interp1d(x1, y1, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
+    f2 = interp1d(x2, y2, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
+
+    y1_interp = f1(x_points)
+    y2_interp = f2(x_points)
+    diff = np.abs(y1_interp - y2_interp)
+    
+    max_diff = np.max(diff)
+    return max_diff, np.sqrt((N1+N2)/(N1*N2))
+
 
 
 import dedalus.public as de
@@ -93,6 +125,19 @@ axes[-1].set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w
 axes[-1].set_xlabel('w\'')
 axes[-1].set_ylabel('Probability')
 axes[-1].set_yscale('log')
+
+#plt.figure()
+#cdf_x_bvp, cdf_y_bvp = calculate_CDF(info[bvp_label]['u_xs_pdf'], info[bvp_label]['u_pdf_pdf'])
+#cdf_x_base, cdf_y_base = calculate_CDF(info[base_label]['u_xs_pdf'], info[base_label]['u_pdf_pdf'])
+#plt.plot(cdf_x_bvp, cdf_y_bvp)
+#plt.plot(cdf_x_base, cdf_y_base)
[…]

### 2018-01-09 code/plotting/parameter_space_comparison.py
updates to parameter space figure

@@ -60,7 +60,7 @@ print(info.keys())
 
 plt.figure(figsize=(8, 1.5))
 gs     = gridspec.GridSpec(*(1000,1000))
-gs_info = (((0,0), 1000, 270), ((0, 350), 1000, 250), ((0, 730), 1000, 270))
+gs_info = (((100,0), 800, 250), ((100, 370), 800, 250), ((100, 750), 800, 250))
 ra_crit = 1295.78
 for i,k in enumerate(fields):
     ax = plt.subplot(gs.new_subplotspec(*gs_info[i]))
@@ -73,42 +73,59 @@ for i,k in enumerate(fields):
             ind = int(ind)
             if ind >= 2:
                 mrkr = '*'
+                threeD = True
             else:
                 mrkr = 'o'
+                threeD = False
             ind = int(ind) % 2
+
+            if threeD:
+                s = 24*(3 - 2*int(ind))
+                alph = 0.7
+            else:
+                s = 12*(3 - 2*int(ind))
+                alph = 1
             if k == 'IE':
                 bx.scatter(float(ra)/ra_crit, 0.5+mean, s=0, alpha=0)
                 ax.errorbar(float(ra), 0.5+mean, yerr=std,  color=COLORS[int(ind)])
-                ax.scatter(float(ra), 0.5+mean, s=12*(3 - 2*int(ind)), marker=mrkr, color=COLORS[int(ind)], alpha=0.75)
+                ax.scatter(float(ra), 0.5+mean, s=s, marker=mrkr, color=COLORS[int(ind)], alpha=alph)
             elif k == 'Nu':
-                p=2/7#2/3
+                p=1/5#2/7#2/3
                 bx.scatter(float(ra)/ra_crit, mean/float(ra)**(p), s=0, alpha=0)
                 ax.errorbar(float(ra), mean/(float(ra)**(p)), yerr=std/(float(ra)**(p)),  color=COLORS[int(ind)])
-                ax.scatter(float(ra), mean/(float(ra)**p), s=12*(3 - 2*int(ind)), marker=mrkr, color=COLORS[int(ind)], alpha=0.75)
+                ax.scatter(float(ra), mean/(float(ra)**p), s=s, marker=mrkr, color=COLORS[int(ind)], alpha=alph)
             elif k == 'Re':
-                pRe = 0.5
[…]

### 2018-01-11 tex/bvp_paper.tex
figure improvements, figure caption updates

@@
 \maketitle
-
-\section{To Do}
-\begin{enumerate}
-\item Get 3D cases in
-\item Continue Improving Figures
-\item Write figure captions
-\end{enumerate}
 
@@
 \caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
-(b) are shown for Ra = $1.30 \cdot 10^7$ ($S = 10^4$).  The two plots are scaled such that
-one time unit on the x-axis of either run takes up an equivalent amount of space on the paper
-to illustrate the time savings of the BVP run.  (c\&d) Flux plots, where black is the sum of the
-flux, blue is enthalphy flux and red is condcutive flux. (c) Fluxes are shown for the IVP at an early
-time to illustrate the asymmetry of the flux through the system. (d) Fluxes through the converged,
-rundown state are compared to the fluxes in the converged BVP solution, where their difference
-is shown in (e). \label{fig:time_trace} }
+(b) are shown for Ra = $1.30 \cdot 10^8$ ($S = 10^5$).  The horizontal extent of the subplots is set
+such that one simulation time unit takes up an equal amount of paper space in (a) and (b).
+The dashed vertical line on (a) represents the time at which the BVP is solved on the run in (b),
+and the horizontal dashed lines show the equilibrium value of the energies.
+(c) System fluxes early in the run (the orange highlights in (a)).  Black is the sum of the flux, purple
+is the convective flux, and red is the conductive flux.
+(d) Fluxes in the converged rundown IVP compared to the ``converged'' BVP.  The sum of flux is shown in
+black \& grey, the convective flux is shown in purple \& pink, and the conductive flux is shown in red \& orange.
+(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, the BVP fluxes
+are much closer to the converged state than the initial fluxes, as in (c).
+\label{fig:time_trace} }
 \end{figure}
@@
 \includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{We compare the time-variant dynamics in our 2D solutions by showing probability distribution
-functions of the values of vertical velocity (a), horizontal velocity (b), and nonlinear heat
-transport (c) in our converged solutions.  The horizontal velocities are very similar, with a
-KS test similarity of X.  The vertical velocities, too, are similar, with a KS similarity of
-Y.  The nonlinear heat transport, while overall quite similar, shows that the BVP experiences
-a greater number of extreme events.  The peak around zero for all three PDFs reflects the
-no-slip boundary conditions.\label{fig:pdf_comparison} }
+\caption{Frequency distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
+vertical transport (c) are shown for a 2D run at $S = 10^5$.  We sample flows every 0.1 time units for 500 freefall
+times, and include the flows at all points on the grid at each of these samples in these distributions.  All
+distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
+Chebyshev grids near the boundaries, so there is a large peak around zero. The distributions, and thus the nonlinear
+dynamics, are broadly similar, but they do not pass a two-tailed Kolmogorov-Smirnov similarity test. (NOTE TO
+CO-AUTHORS: I NEED TO THINK BETTER ON HOW TO COMPARE PDFS, IF YOU HAVE IDEAS PLEASE SEND THEM)
+\label{fig:pdf_comparison} }
 \end{figure}
@@
 \includegraphics[width=\textwidth]{./figs/temp_comparison.png}
-\caption{Here we compare the evolved thermodynamic state of a BVP to that of a rundown IVP that
-has been run through a thermal timescale.  (a) The temperature profiles, as a function of height,
-are shown. (b) The percentage difference between the temperature profiles, as a function of height,
-is shown.  (c) PDFs comparing the values of the point-by-point temperatures over the averaging
-window.  While the median of the PDF has a distinct offset between the two runs, the
-thermal fluctuations about the mean which drive the convection are nearly the same.
+\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
+$S = 10^5$ are shown.  (a) Evolved temperature profiles, as a function of height.
+(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
+(c) Frequency distributions, as in Fig. \ref{fig:pdf_comparison},
+comparing the values of the point-by-point temperatures over the averaging
+window. The mode of the frequency distribution has a distinct offset between the two runs due to
+the clear difference between the profiles in (a), but the
+thermal fluctuations about the mean which drive the convection are similar (AS IN FIG. \ref{fig:pdf_comparison},
+I NEED TO THINK MORE ON THE PDF COMPARISON).
 \label{fig:temp_comparison} }
@@
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
-\caption{Here we demonstrate the efficacy of the BVP method at many values of Ra.  We show
-(a) Nusselt number scaling, (b) Reynolds number scaling, and (c) scaling of the mean temperature
-over the whole simulation.  (a) The Nusselt number follows a classic 2/7 scaling law
-\cite{johnston&doering2009}, until it reaches S = $10^{3 + 2/3}$, at which point the
-two-roll solution begins oscillating horizontally, showing time-variant Nu.  The range of Nu
-over the averaging window is (blah), and the trend of Nu (the variance of the mean Nu) is shown
-as (blah).  (b) Re follows an expected 1/2 scaling law. (c) The mean value of temperature, minus
-the value at the fixed-temperature boundary, is shown.  As Ra increases, the boundary layers shrink,
-and the convection becomes more efficient, we anticipate this value to get closer and closer to
-zero as the atmosphere approaches the isotherm defined by the upper boundary.
+\caption{Compensated scaling plots are shown for the Nusselt number (a), the
+Reynolds number (b), and the volume-averaged temperature (c).  All plots are linear(y)-log(x),
+and any differences vertically are generally small.  Symbols represent the mean value of
+a measurement, vertical lines represent the standard deviation of the measurement over the
+time window, and error bars represent the shift in the mean value over the window.
+(a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
+simulations display horizontally oscillating plumes which have oscillating periods of high transport
+and low transport.  The mean value is marginally diminished as a result, and the range of Nu over time
+is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
+Ra$^{0.45}$ in 2D and (something else) in 3D. (c) The average temperature flucutation, minus the top
+temperature, gives us a measure of the extent of the upper boundary, and is in some ways a more stationary
+proxy for Nu, and it displays similar scaling.  The temperature profile is slow to adjust, and differences between
+BVP solutions and rundown solutions are easier to pick out.
 \label{fig:parameter_space_comparison} }

### 2018-01-11 code/plotting/parameter_space_comparison.py

@@ -62,61 +62,121 @@ plt.figure(figsize=(8, 1.5))
 gs     = gridspec.GridSpec(*(1000,1000))
 gs_info = (((100,0), 800, 250), ((100, 370), 800, 250), ((100, 750), 800, 250))
 ra_crit = 1295.78
+pNu = 0.2  
+pRe = 0.45
+pIE = -0.2
 for i,k in enumerate(fields):
     ax = plt.subplot(gs.new_subplotspec(*gs_info[i]))
     bx = ax.twiny()
-    for ra_info, datum in info.items():
-        try:
-            good_data = datum[k]
-            mean, std = np.mean(good_data), np.std(good_data)
-            ra, ind = ra_info.split('_')
-            ind = int(ind)
-            if ind >= 2:
-                mrkr = '*'
-                threeD = True
-            else:
-                mrkr = 'o'
-                threeD = False
-            ind = int(ind) % 2
+    for j in range(len(base_dirs)):
+        ra_list = []
+        mean_list = []
+        max_list  = []
+        min_list  = []
+        m_max_list = []
+        m_min_list = []
+        for ra_info, datum in info.items():
+            try:
+                ra, ind = ra_info.split('_')
+                ind = int(ind)
+                if ind != j:
+                    continue
 
-            if threeD:
-                s = 24*(3 - 2*int(ind))
-                alph = 0.7
+                time = datum['sim_time']
+                good_data = datum[k]
+                mean, std = np.mean(good_data), np.std(good_data)
+                d_max, d_min = mean + std, mean - std #np.min(good_data), np.max(good_data)
+
+                line_fit = np.polyfit(time, good_data, 1)
+                line = line_fit[1] + line_fit[0] * time
+                m_max, m_min = np.max(line), np.min(line)
+
+                ra_list += [ra]
+                mean_list += [mean]
+                max_list += [d_max]
+                min_list += [d_min]
+                m_max_list += [m_max]
+                m_min_list += [m_min]
+
+            except:
+                continue
+        ra_list = np.array(ra_list, dtype=np.float64)*(1.075-0.05*j)
[…]

### 2018-01-11 code/plotting/pdf_comparison.py

@@ -103,7 +103,7 @@ for a, base_dir in enumerate(base_dirs_post):
 
 
 print(info['{}_0'.format(ra_runs)].keys())
-plt.figure(figsize=(8, 2.5))
+plt.figure(figsize=(8, 1.5))
 gs     = gridspec.GridSpec(*(1000,1000))
 
 
@@ -117,14 +117,17 @@ axes.append(plt.subplot(gs.new_subplotspec(*gs_info[0])))
 base_label = '{}_0'.format(ra_runs)
 bvp_label = '{}_1'.format(ra_runs)
 
-axes[-1].fill_between(info[base_label]['w_xs_pdf'], 0, info[base_label]['w_pdf_pdf'], color='blue', alpha=0.4)
-axes[-1].plot(info[base_label]['w_xs_pdf'], info[base_label]['w_pdf_pdf'], c='blue')
-axes[-1].fill_between(info[bvp_label]['w_xs_pdf'], 0, info[bvp_label]['w_pdf_pdf'], color='red', alpha=0.4)
-axes[-1].plot(info[bvp_label]['w_xs_pdf'], info[bvp_label]['w_pdf_pdf'], c='red')
+axes[-1].fill_between(info[base_label]['w_xs_pdf'], 0, info[base_label]['w_pdf_pdf']*info[base_label]['w_denorm_pdf'], color='blue', alpha=0.4)
+axes[-1].plot(info[base_label]['w_xs_pdf'], info[base_label]['w_pdf_pdf']*info[base_label]['w_denorm_pdf'], c='blue')
+axes[-1].fill_between(info[bvp_label]['w_xs_pdf'], 0, info[bvp_label]['w_pdf_pdf']*info[bvp_label]['w_denorm_pdf'], color='red', alpha=0.4)
+axes[-1].plot(info[bvp_label]['w_xs_pdf'], info[bvp_label]['w_pdf_pdf']*info[bvp_label]['w_denorm_pdf'], c='red')
 axes[-1].set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w_xs_pdf']))
-axes[-1].set_xlabel('w\'')
-axes[-1].set_ylabel('Probability')
+axes[-1].set_xlabel('Vertical velocity', labelpad=-1)
+axes[-1].set_ylabel('Frequency')
 axes[-1].set_yscale('log')
+
+for tick in axes[-1].get_xticklabels():
[…]

### 2018-01-11 code/plotting/temp_comparison.py

@@ -71,7 +71,7 @@ for a, base_dir in enumerate(base_dirs_post):
 
 
 print(info['{}_0'.format(ra_runs)].keys())
-plt.figure(figsize=(8, 2.5))
+plt.figure(figsize=(8, 1.5))
 gs     = gridspec.GridSpec(*(1000,1000))
 
 
@@ -90,11 +90,14 @@ plt.legend(frameon=False, loc='upper right', fontsize=10)
 axes[-1].set_xlabel('z')
 axes[-1].set_ylabel(r'$T$' + ' profile')
 
+y_ticks = [-0.5, -0.48, -0.46, -0.44, -0.42]
+axes[-1].set_yticks(y_ticks)
+
 #Plot 2
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[1])))
 
 axes[-1].plot(info[base_label]['z_profile'], 100*np.abs(info[base_label]['T_profile'][0,:] - info[bvp_label]['T_profile'][0,:])/np.abs(info[base_label]['T_profile'][0,:]))
-y_ticks = np.array([0, 0.5, 1])
+y_ticks = np.array([0, 0.5, 1, 1.5, 2])
 axes[-1].set_yticks(y_ticks)
 x_ticks = np.array([0, 0.5, 1])
 axes[-1].set_xticks(x_ticks)
@@ -103,14 +106,14 @@ axes[-1].set_ylabel('% difference')
 
 ##Plot 3
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[2])))
-axes[-1].fill_between(info[base_label]['T_xs_pdf'], 0, info[base_label]['T_pdf_pdf'], color='blue', alpha=0.4)
-axes[-1].plot(info[base_label]['T_xs_pdf'], info[base_label]['T_pdf_pdf'], c='blue')
-axes[-1].fill_between(info[bvp_label]['T_xs_pdf'], 0, info[bvp_label]['T_pdf_pdf'], color='red', alpha=0.4)
-axes[-1].plot(info[bvp_label]['T_xs_pdf'], info[bvp_label]['T_pdf_pdf'], c='red')
-x_ticks = np.array([-0.5, np.max(info[base_label]['T_xs_pdf'])])
+axes[-1].fill_between(info[base_label]['T_xs_pdf'], 0, info[base_label]['T_pdf_pdf']*info[base_label]['T_denorm_pdf'], color='blue', alpha=0.4)
[…]

### 2018-01-11 code/plotting/time_trace.py

@@ -125,6 +125,7 @@ for i in range(4):
         f = 0.5 + info[this_label]['IE_scalar']
         df = np.abs(f[1:] - f[:-1])
         t_bvp_ind = np.argmax(df) + 1
+        axes[0].axvline(info['{}_1'.format(ra_runs)]['sim_time'][t_bvp_ind], ls='--', c='k')
         axes[i % 2].plot(info[this_label]['sim_time'][:t_bvp_ind], info[this_label]['KE_scalar'][:t_bvp_ind], c='k')
         axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind:], info[this_label]['KE_scalar'][t_bvp_ind:], c='k')
         axes[i % 2].set_yscale('log')
@@ -136,6 +137,13 @@ for i in range(4):
         axes_share[i % 2].set_ylim(1e-2, 5e-1)
 
     else:
+        if i == 2:
+            axes[0].axhline(np.mean(info[this_label]['KE_scalar']), c= 'k', ls = '--')
+            axes_share[0].axhline(np.mean(info[this_label]['IE_scalar']) + 0.5, c= 'r', ls = '--')
+            axes[1].axhline(np.mean(info[this_label]['KE_scalar']), c= 'k', ls = '--')
+            axes_share[1].axhline(np.mean(info[this_label]['IE_scalar']) + 0.5, c= 'r', ls = '--')
+            
+
         axes[i % 2].plot(info[this_label]['sim_time'], info[this_label]['KE_scalar'], c='k')
         axes[i % 2].set_yscale('log')
         axes[i % 2].set_ylim(1e-3, 1e-1)
@@ -149,6 +157,10 @@ for i in range(4):
 #Axes formatting
 axes[0].set_xlim(info['{}_0'.format(ra_runs)]['sim_time'][0], info['{}_2'.format(ra_runs)]['sim_time'][-1])
 axes[1].set_xlim(info['{}_1'.format(ra_runs)]['sim_time'][0], info['{}_3'.format(ra_runs)]['sim_time'][-1])
+x_ticks = [0, info['{}_3'.format(ra_runs)]['sim_time'][-1], 2000, 4000, 6000, 8000, 10000]
+axes[0].set_xticks(x_ticks)
+x_ticks = [0, info['{}_3'.format(ra_runs)]['sim_time'][-1]]
+axes[1].set_xticks(x_ticks)
[…]

### 2018-01-12 code/plotting/parameter_space_comparison.py
adds (a), (b) etc annotations to all plots

@@ -170,17 +170,20 @@ for i,k in enumerate(fields):
     ax.legend(fontsize=8, loc='upper left', ncol=2, scatterpoints=1, handlelength=1, frameon=False)
 
     if k == 'IE':
+        ax.annotate(r'$\mathrm{(c)}$', (1.8e3, 1.82), fontsize=10)
         label_end = '{:.2g}'.format(-pIE)
         label_end = '$(\\langle T_1\\rangle - T_{\mathrm{top}})\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end), fontsize=10, labelpad=4)
 #        ax.set_ylabel(r'$\langle T_1 \rangle - T_{\mathrm{top}}$', fontsize=10, labelpad=4)
         ax.set_ylim(1, 2)
     elif k == 'Nu':
+        ax.annotate(r'$\mathrm{(a)}$', (1.8e3, 0.225), fontsize=10)
         label_end = '-{:.2g}'.format(pNu)
         label_end = '$\\langle\\mathrm{Nu}\\rangle\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end), fontsize=10, labelpad=0)
         ax.set_ylim(2e-1, 5e-1)
     elif k == 'Re':
+        ax.annotate(r'$\mathrm{(b)}$', (1e8, 0.12), fontsize=10)
         label_end = '-{:.3g}'.format(pRe)
         label_end = '$\\langle\\mathrm{Re}\\rangle\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end),fontsize=10, labelpad=0)

### 2018-01-12 code/plotting/pdf_comparison.py

@@ -125,6 +125,7 @@ axes[-1].set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w
 axes[-1].set_xlabel('Vertical velocity', labelpad=-1)
 axes[-1].set_ylabel('Frequency')
 axes[-1].set_yscale('log')
+axes[-1].annotate(r'$\mathrm{(a)}$', (-0.145, 1e8), fontsize=10)
 
 for tick in axes[-1].get_xticklabels():
     tick.set_rotation(45)
@@ -151,6 +152,7 @@ axes[-1].plot(info[bvp_label]['u_xs_pdf'], info[bvp_label]['u_pdf_pdf']*info[bvp
 axes[-1].set_xlim(np.min(info[bvp_label]['u_xs_pdf']), np.max(info[bvp_label]['u_xs_pdf']))
 axes[-1].set_xlabel('Horizontal velocity', labelpad=-0.5)
 axes[-1].set_yscale('log')
+axes[-1].annotate(r'$\mathrm{(b)}$', (-0.175, 1e8), fontsize=10)
 
 
 for tick in axes[-1].get_xticklabels():
@@ -166,6 +168,7 @@ axes[-1].set_xlim(np.min(info[bvp_label]['w*T_xs_pdf']), np.max(info[bvp_label][
 plt.legend(frameon=False, fontsize=8, loc='upper right')
 axes[-1].set_xlabel(r'$w(T - \bar{T})$', labelpad=-5)
 axes[-1].set_yscale('log')
+axes[-1].annotate(r'$\mathrm{(c)}$', (-1.2e-3, 5e8), fontsize=10)
 
 
 for tick in axes[-1].get_xticklabels():

### 2018-01-12 code/plotting/temp_comparison.py

@@ -89,6 +89,7 @@ axes[-1].plot(info[bvp_label]['z_profile'], info[bvp_label]['T_profile'][0,:], c
 plt.legend(frameon=False, loc='upper right', fontsize=10)
 axes[-1].set_xlabel('z')
 axes[-1].set_ylabel(r'$T$' + ' profile')
+axes[-1].annotate(r'$\mathrm{(a)}$', (0.04, -0.494), fontsize=10)
 
 y_ticks = [-0.5, -0.48, -0.46, -0.44, -0.42]
 axes[-1].set_yticks(y_ticks)
@@ -103,6 +104,7 @@ x_ticks = np.array([0, 0.5, 1])
 axes[-1].set_xticks(x_ticks)
 axes[-1].set_xlabel('z')
 axes[-1].set_ylabel('% difference')
+axes[-1].annotate(r'$\mathrm{(b)}$', (0.04, 0.15), fontsize=10)
 
 ##Plot 3
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[2])))
@@ -116,6 +118,7 @@ axes[-1].set_xlabel('T')
 axes[-1].set_ylabel('Frequency')
 axes[-1].set_yscale('log')
 axes[-1].set_xlim(-0.5, np.max(info[base_label]['T_xs_pdf']))
+axes[-1].annotate(r'$\mathrm{(c)}$', (-0.495, 1.2e8), fontsize=10)
 
 
 

### 2018-01-12 code/plotting/time_trace.py

@@ -180,6 +180,10 @@ for tick in axes_share[1].get_yticklabels():
 spines = ['bottom', 'top', 'right', 'left']
 axis_names   = ['x', 'y']
 
+
+axes[0].annotate(r'$\mathrm{(a)}$', (200, 7e-2), fontsize=10)
+axes[1].annotate(r'$\mathrm{(b)}$', (250, 7e-2), fontsize=10)
+
 ##################################
 # Bottom three plots
 ###################################
@@ -213,6 +217,7 @@ axes[-1].set_xlabel('z')
 [axes[-1].tick_params(axis=axis, colors='orange') for axis in axis_names]
 [t.set_color('k') for t in axes[-1].get_xticklabels()]
 [t.set_color('k') for t in axes[-1].get_yticklabels()]
+axes[-1].annotate(r'$\mathrm{(c)}$', (0.04, 6.2), fontsize=10)
 
 #Plot 2
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[1])))
@@ -253,6 +258,7 @@ x_ticks = np.array([0, 0.5, 1])
 axes[-1].set_xticks(x_ticks)
 axes[-1].set_xlabel('z')
 plt.legend(frameon=False, loc='center', fontsize=10)
+axes[-1].annotate(r'$\mathrm{(d)}$', (0.45, 0.06), fontsize=10)
 
 #Plot 3
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[2])))
@@ -260,7 +266,10 @@ axes[-1].axhline(0, c='k')
 axes[-1].plot(info[this_label]['z_profile'], ((enth-base_enth)), c=f_conv_color)
 axes[-1].plot(info[this_label]['z_profile'], ((kappa-base_kappa)), c=f_cond_color)
 axes[-1].plot(info[this_label]['z_profile'], ((sum_f - base_sum_f)), c=f_sum_color)
+x_ticks = np.array([0, 0.5, 1])
+axes[-1].set_xticks(x_ticks)
 axes[-1].set_ylabel(r'$\mathrm{(BVP - Rundown)}\cdot\sqrt{\mathrm{Ra \,Pr}}$')
+axes[-1].annotate(r'$\mathrm{(e)}$', (0.04, -0.185), fontsize=10)
 
 
 plt.savefig('time_trace.png'.format(k), bbox_inches='tight', dpi=200)

### 2018-01-12 code/bvps/bvp_tools.py
lots of run script changes

@@ -307,7 +307,6 @@ class BVPSolverBase:
                     else:
                         self.do_bvp = False
                     self.bvp_l2_last_check_time = solver_sim_time
-                self.time_since_avg_adjust = 0.
                 self.first_l2 = False
 
 
@@ -349,13 +348,14 @@ class BVPSolverBase:
     def _reset_fields(self):
         """ Reset all local fields after doing a BVP """
         self.do_bvp = False
-        self.first_l2 = False
+        self.first_l2 = True
         # Reset profile arrays for getting the next bvp average
         for fd, info in self.FIELDS.items():
             if self.rank == 0:
                 self.profiles_dict[fd]      *= 0
             self.current_local_avg[fd]  *= 0
             self.current_local_l2[fd]  *= 0
+            self.current_avg_times *= 0
 
     def _set_subs(self, problem):
         pass

### 2018-01-12 code/rayleigh_benard.py

@@ -49,9 +49,9 @@ Options:
     --bvp_equil_time=<time>              How long to wait after a previous BVP before starting to average for next one, in tbuoy [default: 50]
     --bvp_final_equil_time=<time>        How long to wait after last bvp before ending simulation 
     --bvp_transient_time=<time>          How long to wait at beginning of run before starting to average for next one, in tbuoy [default: 50]
-    --min_bvp_time=<time>                Minimum avg time for a bvp (in tbuoy) [default: 25]
+    --min_bvp_time=<time>                Minimum avg time for a bvp (in tbuoy) [default: 30]
     --bvp_resolution_factor=<mult>       an int, how many times larger than nz should the bvp nz be? [default: 1]
-    --bvp_convergence_factor=<fact>      How well converged time averages need to be for BVP [default: 3e-3]
+    --bvp_convergence_factor=<fact>      How well converged time averages need to be for BVP [default: 1e-3]
 """
 import logging
 logger = logging.getLogger(__name__)
@@ -211,7 +211,7 @@ def Rayleigh_Benard(Rayleigh=1e6, Prandtl=1, nz=64, nx=None, ny=None, aspect=4,
                                    bvp_run_threshold=bvp_convergence_factor, \
                                    bvp_l2_check_time=1, mesh=mesh,\
                                    plot_dir='{}/bvp_plots/'.format(data_dir),\
-                                   min_avg_dt=0.1, final_equil_time=bvp_final_equil_time,
+                                   min_avg_dt=1e-10, final_equil_time=bvp_final_equil_time,
                                    min_bvp_time=min_bvp_time)
         bc_dict.pop('stress_free')
         bc_dict.pop('no_slip')

### 2018-01-12 tex/bvp_paper.tex
basically completes rough draft of paper, need to get new data in and see how it looks

@@
 \begin{abstract}
-We present a method for using coupling Boundary value problems (BVPs) with Initial value problems (IVPs)
+We present a method for coupling Boundary value problems (BVPs) with Initial value problems (IVPs)
 in order to achieve thermally converged convective solutions on dynamical timescales, rather than the
-long thermal timescale.  We demonstrate the similarity between the solution reached via BVP and the
+long thermal timescale.  We demonstrate the similarity between the solution reached by BVP and the
 solution reached by a long thermal rundown of the IVP, and demonstrate that this method works at a
@@
 by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much
-longer than dynamical timescales \cite{Anders&Brown2017}, achieving converged simulations will 
+longer than dynamical timescales \cite{anders&brown2017}, achieving converged simulations will 
 require runs which span a greater number of convective timescales in order to thermally converge.
@@
 the atmosphere to a state which is closer to the adiabat chosen by convection \cite{brandenburg&all2005}.
-However, most studies of convection do not contain stable layers above and below the convection
+However, many modern studies of convection do not contain stable layers above and below the convection
 zone, and the presence of hard boundaries and the boundary layers that they form make it difficult to
@@
 We run two sets of experiments: one in which we allow convective simulations to evolve for a
-full thermal timescale before taking measurements, and another in which we employ a fast-forwarding,
+full thermal timescale before taking measurements, and another in which we employ a fast,
 BVP technique which occurs on dynamical timescales. We compare these two sets of simulations to
-show the validity of the BVP technique.  Then, we use the BVP technique to run simulations
+show the validity of the BVP technique.  We use the BVP technique to run simulations
 at high Ra, in the regime where running for thermal timescales becomes computationally intractable.
@@
 of thermal expansion ($\alpha$). The variables of the fluid that are evolved are the velocity,
-$\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure.
+$\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure, $P$.
 The density of the fluid is a constant $\rho_0$, except on the
@@
 $v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$.
-We further re-arrange the momentum equation by introducing a reduced pressure
+We further re-arrange the momentum equation by introducing a reduced kinematic pressure,
 $\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where $\bm{g} = -\grad \phi$ is the gravitational potential.
-Despite containing a nonlinear $\bm{u}$ component, the nature of $P$ in \RB convection, as a (whatever it's called)
+Despite containing a nonlinear $\bm{u}$ component, the nature of $P$ in \RB convection, as a
+Lagrange multiplier,
 allows us to treat $\varpi$ as a linear unknown, without a need to resolve its different components.
@@
 \end{gather}
-where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity. We find this form of the momentum equation to
+where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity. We find Eq. (\ref{eqn:bouss_momentum}) to
 be slightly faster numerically than the standard form in Eq. (\ref{eqn:dim_bouss_momentum}).
@@
 horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
-the aspect ratio is $\Gamma = 2$.
+the aspect ratio is $\Gamma = 2$. In our 2D cases, we only examine the $x$ and $z$ dimensions
+and we set $v = \partial_y = 0$.
 
@@
 part because these conditions minimize the number of assumptions that must be made in
-setting up the boundary value problem.
+setting up the boundary value problem.  For this choice of boundary conditions, the
+critical Ra is Ra$_{\text{crit}} = 1295.78$, and we will often speak in terms of the
+supercriticality, $S = \text{Ra}/\text{Ra}_{\text{crit}}$.
 
@@
 
-It is a reasonable assumption to naively guess that convection will evolve the mean temperature profile that
-drives it over the course of a thermal diffusion time, $t_\chi \approx \mathcal{P}^{-1}$. Thus, as Ra
+It is reasonable to assume that convection will evolve the mean temperature profile that
+drives it over the course of a thermal diffusion time, $t_\chi = \mathcal{P}^{-1}$. Thus, as Ra
 increases, the timescale for achieving a thermally converged mean temperature profile becomes intractable.
-This prohibitively long thermal timescale in a Direct Numerical Simulation (DNS) 
-can be skipped by coupling the DNS with a simple Boundary Value Problem
-(BVP) solve. By using information about the evolved dynamical state of the atmosphere,
-a BVP can be used to solve for the evolved atmospheric state on short timescales.
+This prohibitively long thermal timescale in an Initial Value Problem (IVP)
+can be skipped by coupling the IVP with a simple Boundary Value Problem
+(BVP) solve. By using information about the convecting dynamical state of an unconverged solution,
+a BVP can be used to solve for the evolved system state.
 A comparison of a simulation running for the thermal timescale, and another where a BVP is used
@@
 \\
-\frac{\partial}{\partial z}\angles{wT_1} - \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1} = 0,
+\frac{\partial}{\partial z}\angles{wT_1} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1} = 0,
 	\label{eqn:bouss_BVP_energy}
@@
 
-By definition, the profile of $F_{conv}$ is not in its time stationary early in the DNS.  
+By definition, the profile of $F_{\text{conv}}$ is not in a time stationary state early in the IVP.  
 In fact, as the atmosphere approaches the
@@
 In order to construct the evolved convective flux from the current fluxes in the atmosphere,
-we assume that the atmospheric dynamics have properly developed the thickness of the boundary layers, 
-or that the quantities
+we assume that the atmospheric dynamics have properly developed the thickness of the boundary layers.
+In other words, if we know the quantities $F_{\text{conv}}$, $F_{\text{cond}} = \angles{-P \partial_z T}$,
+and $F_{\text{tot}} = F_{\text{conv}} + F_{\text{cond}}$, we assume that the profiles
 \begin{equation}
-f_{\text{conv}} = \frac{F_{\text{conv}}}{F_{\text{tot}}}\qquad
-f_{\text{cond}} = \frac{F_{\text{cond}}}{F_{\text{tot}}}
+f_{\text{conv}}(z) = \frac{F_{\text{conv}}}{F_{\text{tot}}},\qquad
+f_{\text{cond}}(z) = \frac{F_{\text{cond}}}{F_{\text{tot}}}
+\label{eqn:bvp_ratios}
 \end{equation}
-early in the evolution are the same as those in the final steady state solution. By definition, the
+early in the evolution are the same as they will be in the final steady state solution. By definition, the
 evolved total flux through the atmosphere must be the same as the flux entering the atmosphere at the
-bottom boundary, $F_{\text{tot, steady}} = F_{\text{bot}}$.  The proper enthalpy flux profile to feed in
-to Eqn. (\ref{eqn:bouss_BVP_energy}) is then 
-$\angles{w T_1}_{\text{steady}} = F_{\text{tot, steady}} \cdot f_{\text{conv}}$.  Presumably, over the
-course of the simulation, the velocity field and temperature fluctuations naturally scale like
-$d(z) = \angles{w T_1}_{\text{steady}}/\angles{w T_1}$, and so it is necessary to multiply the velocity
-field and the fluctuations around the mean in $T_1$ by $\sqrt{d}$.  This also means that
-$\angles{\bm{u}\times\bm{\omega}}_{\text{steady}} = d \angles{\bm{u}\times\bm{\omega}}$. Once these profiles
-are appropriately adjusted, they can be used in the BVP solve to find the mean profiles of $T$ and $\varpi$.
+bottom boundary, $F_{\text{tot, steady}} = F_{\text{bot}}$.  The proper convective flux profile to use in
+Eqn. (\ref{eqn:bouss_BVP_energy}) is then 
+$\angles{w T_1}_{\text{steady}} = F_{\text{tot, steady}} \cdot f_{\text{conv}}$.
+
+In order to carry the converged amount of flux appropriately, 
+the velocity field and temperature fluctuations in the system must be scaled by a quantity
+$\xi(z) = \angles{w T_1}_{\text{steady}}/\angles{w T_1}$.  Thus, we multiply the velocities
+and the thermal fluctuations, $T - \angles{T}$, by $\sqrt{\xi}$, such that the product of all fluctuations
+(which carry the convective flux) are diminished by a factor of $\xi$.  This also means that
+$\angles{\bm{u}\times\bm{\omega}}_{\text{steady}} = \xi \angles{\bm{u}\times\bm{\omega}}$. Once these profiles
+are appropriately adjusted, they can be used in the BVP solve to find $\angles{T}$ and $\angles{\varpi}$.
 
@@
 \begin{enumerate}
-\item Run the convective DNS. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
-wait for 50 time units.  Then, start taking the averages of $F_{\text{conv}}$ and $F_{\text{tot}}$, waiting either
-30 time units or until the profiles are converged to 1 part in 1000, whichever is a more difficult. This ensures that
+\item Run the convective IVP. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
+wait for 50 freefall time units.  
+\item Start taking the averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$, waiting either
+30 freefall time units or until the average profiles change by no more than 1 part in 1000 on a
+given timestep, whichever is a more difficult criterion. This ensures that
 the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
-\item Construct $\angles{w T_1}_{\text{steady}}$ and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
+\item Construct $\angles{w T_1}_{\text{steady}}$, $\xi$, and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
 from the flux profiles.
@@
 evolved state.  Adjust the mean profiles in the IVP.
-\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{d}$ in the IVP. 
-\item Continue running the IVP for 50 time units to allow for the velocities to equilibrate to their new background state.
+\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{\xi}$ in the IVP. 
+\item Continue running the IVP for freefall 50 time units to allow for the velocities to equilibrate to their new background state.
+\item Repeat steps 2-6 to complete a second BVP and get closer to the right solution now that we
+are far from the very unstable transient period.
+\item Take averages for the amount of time specified for the given run in Appendix \ref{section:appendix_table}.
 \end{enumerate}
@@
 physical grid dimensions are 3/2 the size of the coefficient grid.
-Domain sizes range from
-32x128 coefficients at the lowest values of 
-Ra to 1024x4096 coefficients at Ra $> 10^{9}$ in 2D.
 
@@
 
-In 2D, there are often multiple steady state solutions (e.g., 2-roll and 3-roll
-solutions) which have slightly different flow properties (heat transport, etc.).
-Even though the initial perturbations are very small, they shape the convective
-transient and thus determine the nature of the steady state convection, at least in
-the laminar regime.  In order to ensure that our results are not biased by differences
-in flow structure, we ran the simulations using distinct random temperature perturbations
-so as to compare statistics in comparable flow fields.  In 3D, rolls are nonstationary over
-convective timescales, and so these effects need not be considered there.
-
 \section{Results}
-While the differences in the fluxes in Fig. \ref{fig:time_trace} are small, it is important
-to determine if the velocity fluctuations and point-by-point nonlinear transport are the same
-in the evolved state.  Fig. \ref{fig:pdf_comparison} overlays the probability distribution functions
-of the vertical and horizontal velocities, as well as the fully nonlinear portion of the convective
-flux for the same case as is shown in Fig. \ref{fig:time_trace}.  The PDFs are quite similar visually,
-and have a similarity of (XYZ) according to a Kolmogorov-Smirnov statistic.
-
-In addition to getting the nonlinear dynamics mostly correct, we show that the BVP method retrieves the
-proper temperature profile, see e.g., Fig. \ref{fig:temp_comparison}.  Here the BVP profile retrieves the
-mean profile of the temperature to within 1\% accuracy, and temperature fluctuations in the two runs
-have a similarity of (XYZ) according to a Kolmogorov-Smirnov statistic.
-
-This method works across a broad range of supercriticality.  In Fig. \ref{fig:parameter_space_comparison},
-we show measurements of the volume-averaged Nusselt number, Reynolds number, and temperature.
-We use standard definitions of the Nusselt number and Reynolds numbers,
-\begin{equation}
-\text{Nu} = \frac{\angles{wT - (\text{Ra Pr})^{-1/2}\grad T}}{\angles{- (\text{Ra Pr})^{-1/2} \grad T}} =
-1 + \frac{\angles{wT}}{-\Delta T}\sqrt{\text{Ra Pr}}, \qquad \text{Re} = \frac{|\bm{u}| L_z}{\nu},
-\end{equation}
-where $\Delta T = T(z = 1/2) - T(z = -1/2)$ is the evolved temperature difference
-between the top and bottom plates.  This form of the Nusselt number is valid even when
-the system is not yet in flux equilibrium, and reduces to the standard fixed flux definition
-of Nu  = $[1 - \angles{wT} / P]^{-1}$ \cite{johnston&doering2009}. We find a scaling law of
-Nu $\propto \text{Ra}^{2/3}$, much steeper than a standard 2/7 or 1/3 scaling law
-\cite{johnston&doering2009}. Furthermore, we find that Re$\propto \text{Ra}^{0.425}$. The average temperature
-approaches the value at the top of the domain as Ra increases.
-
-The final morphology of the flows is very important in determining the exact value of Nu and Re.  In general,
-a two-roll state vs. a three-roll state will have entirely different statistics -- different Nu, Re, and average
-temprature (and as a result, different size boundary layers).  Thus, in 2D studies, it is essential to study flows
-of a similar morphology in order to see a clear trend.
-
-\begin{figure}[t]
-\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{Frequency distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
-vertical transport (c) are shown for a 2D run at $S = 10^5$.  We sample flows every 0.1 time units for 500 freefall
-times, and include the flows at all points on the grid at each of these samples in these distributions.  All
-distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
-Chebyshev grids near the boundaries, so there is a large peak around zero. The distributions, and thus the nonlinear
-dynamics, are broadly similar, but they do not pass a two-tailed Kolmogorov-Smirnov similarity test. (NOTE TO
-CO-AUTHORS: I NEED TO THINK BETTER ON HOW TO COMPARE PDFS, IF YOU HAVE IDEAS PLEASE SEND THEM)
-\label{fig:pdf_comparison} }
-\end{figure}
+While Fig. \ref{fig:time_trace} shows us that the post-BVP and post-rundown solutions
+exhibit similar system energies and fluxes, it is important to examine other aspects of
+the evolved solution. The BVP mainly serves to adjust the thermodynamic state of the solution;
+in \RB convection, this means that the evolved temperature profile is a good measure of whether
+or not the BVP achieves the proper solution.
 
@@
 \end{figure}
+
+The temperature profiles of a 2D run at $S = 10^5$ 
+for both the BVP solve and the long rundown are shown in
+Fig. \ref{fig:temp_comparison}a.  While they are not perfectly aligned they are within less than
+2\% of each other throughout the depth of the atmosphere, as shown in Fig. \ref{fig:temp_comparison}b.
+While the mean temperature profile is interesting, the point-by-point fluctuations in the
+temperature are what lead to convective transport, and thus examining the spread of temperature
+and the allowed values that it can take are important to characterizing the system.  As seen
+in Fig. \ref{fig:temp_comparison}c, aside from the noticeable difference in the mode of the
+temperatures, the two runs exhibit largely the same spread of temperatures, with the rundown
+achieving higher temperatures at the base of the atmosphere.  These two profiles do not pass
+a Kolmogorov-Smirnov test for similarity (AUTHOR NOTE: we need to collaborate on different measures
+of comparing PDFs).
+
+In addition to examining the thermodynamics of the solutions, we are especially interested in
+determining if the post-BVP solution appropriately captures key features of the nonlinear dynamics.
+We show point-by-point frequency distributions of the horizontal velocity, vertical velocity,
+and nonlinear transport in Fig. \ref{fig:pdf_comparison}.  All of these measures have a sharp
+peak at zero due to the no-slip, impenetrable boundary conditions and the denser grid sampling
+near the boundaries of our Chebyshev grid.  Regardless, we see that the velocities of the 
+two solutions are largely consistent.  The nonlinear transport in Fig. \ref{fig:pdf_comparison}
+shows that the post-BVP solution experiences more extreme events which carry a large amount of
+flux than the rundown solution, which is to be expected since it is not quite in equilibrium,
+as shown in Fig. \ref{fig:time_trace}d.  None of these profiles pass a KS test for similarity
+(AUTHOR NOTE: see previous paragraph comment).
+
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
+\caption{Frequency distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
+vertical transport (c) are shown for a 2D run at $S = 10^5$.  We sample flows every 0.1 time units for 500 freefall
+times, and include the flows at all points on the grid at each of these samples in these distributions.  All
+distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
+Chebyshev grids near the boundaries, so there is a large peak around zero. The distributions, and thus the nonlinear
+dynamics, are broadly similar, but they do not pass a two-tailed Kolmogorov-Smirnov similarity test. (NOTE TO
+CO-AUTHORS: I NEED TO THINK BETTER ON HOW TO COMPARE PDFS, IF YOU HAVE IDEAS PLEASE SEND THEM)
+\label{fig:pdf_comparison} }
+\end{figure}
+
+The goodness of this method has been tested across a broad range of supercriticality.  We have
+examined both Rundown and BVP solutions in the range $S = [10^{1/3}, 10^5]$ in 2D and
+$S = [10^1, 10^4]$ in 3D (3D points to come).  We have also further explored up to $S = 10^6$
+(AUTHOR NOTE: should we go up to $10^8$?  $10^7$ is easily in reach. Also, 3D data points are
+sparse and will change -- need to rerun with proper BVP procedure).  We compare scalar, 
+volume-averaged measurements of all of these runs in Fig. \ref{fig:parameter_space_comparison}.
+
+In Fig. \ref{fig:parameter_space_comparison}a, we compare the Nusselt number scaling in 2D,
+3D, and for BVP and rundown solutions.  We use a classic definition of the Nusselt number
+to measure the heat transport in these systems, where
+\begin{equation}
+\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
+ = \frac{\angles{wT - (\text{Ra Pr})^{-1/2}\grad T}}{\angles{- (\text{Ra Pr})^{-1/2} \grad T}}.
+\end{equation}
+At small values of $S$, we achieve a steady state solution with a clear value of Nu.  Near
+$S \sim 10^3$, our simulations begin to achieve a horizontally oscillatory state.  Due to the
+use of no-slip boundaries, these states never give way to full scale shearing states, but they
+do reduce the overall heat transport through the system and cause the systems to oscillate between
+periods of high- and low- heat transport.  The vertical lines represent the standard deviation 
+of Nu associated with these oscillations, while the error bars show the drift of the mean
+value of Nu over the averaging window.  We find that $\text{Nu} \propto \text{Ra}^{1/5}$,
+a weaker scaling law than that seen in traditional \RB convection \cite{johnston&doering2009},
+but similar to that seen in shearing states [cite Goluskin].
+(AUTHOR NOTE: Ben, I think this is entirely because of the oscillatory states.  I wonder what
+would happen if we included viscous fluxes...)
+
+In Fig. \ref{fig:parameter_space_comparison}b, we measure the rms Reynolds number, where
+$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  We find that this scales roughly as
+$\text{Re} \propto \text{Ra}^{0.45}$, and find good agreement between BVP and rundown solutions.
+
+In Fig. \ref{fig:parameter_space_comparison}c, we measure the volume averaged 
+temperature of our solution, then subtract out the value at the upper (fixed $T$) boundary.
+If the atmosphere were perfectly isothermal, this value would be exactly zero.  Thus, this is
+a measure of the temperature jump across the boundary layers, and it provides insight both
+into whether or not the temperature profiles of two runs are the same and into whether
+the fluxes through the two systems are the same (it is in some ways an alternate measure of Nu
+[cite King 2009 supp materials]).
+We find that this measure is $\propto \text{Ra}^{-1/5}$, approaching zero, as expected.
 
@@
 \label{sec:results}
-While imperfect, the method presented here is a first step towards taking meaningful measurements
+The method presented here is a first step towards taking meaningful measurements
 of highly turbulent convection on manageable, human timescales.  As demonstrated in Figs.
 1-4, this BVP method quickly converges simulations to within a few percent of the true final
-state, while preserving the natural behavior of the convective solution (such as the oscillatory
-nature of high-Ra 2D states in \ref{fig:parameter_space_comparison}).
+state. Furthermore, the total simulation time required to use the BVPs does not change drastically from
+low $S$ to high $S$, so the main prohibition on high Ra states is the difficulty of timesteps becoming
+increasingly small as turbulence increases.  Additionally, post-BVP, we generally see an increase of the
+timestep size by nearly a factor of two due to the less intense driving of the near-converged state that
+is achieved quickly.
 
-While not perfect, the BVP method here has one major benefit over some of the other methods
-currently being used to achieve high Ra solutions.  One oft-used method is that of bootstrapping,
+One major benefit of the BVP method used here is that it preserves the natural behavior of 
+the convective solution (such as the horizontally oscillatory rolls
+of high-Ra 2D states in Fig. \ref{fig:parameter_space_comparison}).
+One frequently used method of measuring dynamics in high-Ra simulations is that of bootstrapping,
 in which the converged solution of a low-Ra state is used as initial conditions for a higher-Ra
-simulation.  While these methods are extremely powerful, they are influenced by hysteresis effects,
-and the powerful, steady rolls achieved at low Ra can result in an artifically over-stable high-Ra
-roll solution.  The BVP method can be used with random noise initial conditions which allow the
-convective solution to be naturally chosen by the dynamics.
+simulation.  While this method is powerful, it can be influenced by hysteresis effects,
+and the steady rolls achieved at low Ra can result in an artifically over-stable high-Ra
+roll solution.  The BVP method we present here uses random noise initial conditions which allows the
+convective solution to naturally choose the dynamics.
 
-One benefit of the method presented here is that it can be easily extended to more complicated
+Another benefit of our BVP method is that it can be easily extended to more complicated
 configurations.  For example, to use this method in simulations of stratified compressible convection,
-one need only adapt the BVP equations to the appropriate equations of hydrostatic equilibrium,
-$\grad P = -\rho \bm{g}$, and thermal equilibrium, $\Div{F_{\text{cond}} + F_{\text{conv}}} = \text{sources}$,
-for the problem at hand.  In compressible convection, where the density is allowed to change,
-one must also use the knowledge of stellar structure codes and add an equation of mass conservation
-in order to ensure that the BVP does not spuriously add or remove mass from the system.
+one need only adapt the BVP equations to the appropriate equations of hydrostatic equilibrium
+and thermal equilibrium obtained by averaging the fully compressible, ideal gas
+steady state momentum and energy equations \cite{anders&brown2017, lecoanet&all2014}.
+In compressible convection, where the density is allowed to change,
+it is also essential to conserve mass by adding boundary conditions on the integrated mas density at
+the upper and lower boundaries, much as stellar structure codes do \cite{paxton&all2011}.
 
-This method can be extended to other boundary conditions, as well.  To solve for fixed temperature
-boundary conditions, the difficulty is in finding the amount of flux through the system -- but
-this can be done by using the ratios $f_{\text{conv}}$ and $f_{\text{cond}}$.  In the case of
-fixed flux boundary conditions, there is degeneracy in the temperature solution which can come
-out of the BVP, but in using knowledge about the system -- such as the initial symmetry of the
-RB state around $T_1 = 0$, the final solution can be pegged onto the proper profile.
+While we have not chosen to use them here, this BVP method can be extended to other boundary conditions.  
+To solve for fixed temperature boundary conditions, the 
+main difficulty is in finding the amount of flux through the system, $F_{\text{tot, steady}}$.
+However, by knowing the averaged value of the conductive flux (from the boundary conditions)
+and the ratios in Eqn. (\ref{eqn:bvp_ratios}), $F_{\text{tot, steady}}$ can be found.
+In the case of
+fixed flux boundary conditions, the temperature solution is degenerate.
+However, using knowledge about the system -- such as the initial symmetry of the
+RB state around $T = 0$, the final solution can be pegged onto the proper profile.
+
+Future work will aim to apply the methods presented here to compressible systems,
+internally heated systems, and systems with more complex forms of the conductive flux.
 
@@
 \section{Table of Runs}
+\label{section:appendix_table}
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X X X X }
+\begin{tabularx}{\textwidth}{ X X X X X X X X X}
 \hline															
-Ra	&	Supercriticality	&	nz	&	nx	&	$t_{\text{therm}}$	&	$t_{\text{post BVP}}$	&	$t_{\text{avg}}$	\\[1ex]
-\hline		\hline											
-$2.79 \cdot 10^3$	&	$10^{1/3}$	&	32	&	128	&	$52.8$	&	50	&	100	\\
-$6.01 \cdot 10^3$	&	$10^{2/3}$	&	32	&	128	&	$77.6$	&	50	&	100	\\
-$1.30 \cdot 10^4$	&	$10^1$	&	32	&	128	&	$114$	&	50	&	100	\\
-$2.79 \cdot 10^4$	&	$10^{1 + 1/3}$	&	32	&	128	&	$167$	&	50	&	100	\\
-$6.01 \cdot 10^4$	&	$10^{1 + 2/3}$	&	32	&	128	&	$245$	&	50	&	100	\\
-$1.30 \cdot 10^5$	&	$10^2$	&	64	&	256	&	$360$	&	100	&	100	\\
-$2.79 \cdot 10^5$	&	$10^{2 + 1/3}$	&	64	&	256	&	$528$	&	100	&	100	\\
-$6.01 \cdot 10^5$	&	$10^{2 + 2/3}$	&	64	&	256	&	$776$	&	100	&	100	\\
-$1.30 \cdot 10^6$	&	$10^3$	&	128	&	512	&	$1.14 \cdot 10^3$	&	100	&	200	\\
-$2.79 \cdot 10^6$	&	$10^{3 + 1/3}$	&	128	&	512	&	$1.67 \cdot 10^3$	&	200	&	200	\\
-$6.01 \cdot 10^6$	&	$10^{3 + 2/3}$	&	256	&	1024	&	$2.45 \cdot 10^3$	&	200	&	200	\\
-$1.30 \cdot 10^7$	&	$10^4$	&	256	&	1024	&	$3.60 \cdot 10^3$	&	200	&	200	\\
-$2.79 \cdot 10^7$	&	$10^{4 + 1/3}$	&	256	&	1024	&	$5.28 \cdot 10^3$	&	200	&	200	\\
-$6.01 \cdot 10^7$	&	$10^{4 + 2/3}$	&	256	&	1024	&	$7.76 \cdot 10^3$	&	200	&	200	\\
-$1.30 \cdot 10^8$	&	$10^5$	&	512	&	2048	&	$1.14 \cdot 10^4$	&	500	&	500	\\
-$2.79 \cdot 10^8$	&	$10^{5 + 1/3}$	&	512	&	2048	&	$1.67 \cdot 10^4$	&	500	&	500	\\
-$6.01 \cdot 10^8$	&	$10^{5 + 2/3}$	&	512	&	2048	&	$2.45 \cdot 10^4$	&	500	&	500	\\
-$1.30 \cdot 10^9$	&	$10^6$	&	1024	&	4096	&	$3.60 \cdot 10^4$	&	500	&	500	\\
+$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{rundown}}$	&	Nu$_{\text{BVP}}$	\\
+\hline															
+$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	128	&	$52.8$	&	100	&	(TBD)	&	(TBD)	\\
+$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	128	&	$77.6$	&	100	&	--	&	--	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	128	&	$114$	&	100	&	--	&	--	\\
+$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	128	&	$167$	&	100	&	--	&	--	\\
+$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	128	&	$245$	&	100	&	--	&	--	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	256	&	$360$	&	100	&	--	&	--	\\
+$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	256	&	$528$	&	100	&	--	&	--	\\
+$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	256	&	$776$	&	100	&	--	&	--	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	512	&	$1.14 \cdot 10^3$	&	200	&	--	&	--	\\
+$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	512	&	$1.67 \cdot 10^3$	&	500	&	--	&	--	\\
+$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	1024	&	$2.45 \cdot 10^3$	&	500	&	--	&	--	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	1024	&	$3.60 \cdot 10^3$	&	500	&	--	&	--	\\
+$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	1024	&	$5.28 \cdot 10^3$	&	500	&	--	&	--	\\
+$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	1024	&	$7.76 \cdot 10^3$	&	500	&	--	&	--	\\
+$10^5$	&	$1.30 \cdot 10^8$	&	512	&	2048	&	$1.14 \cdot 10^4$	&	500	&	--	&	--	\\
+$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	2048	&	$1.67 \cdot 10^4$	&	500	&	--	&	--	\\
+$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	2048	&	$2.45 \cdot 10^4$	&	500	&	--	&	--	\\
+$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	4096	&	$3.60 \cdot 10^4$	&	500	&	--	&	--	\\
 \hline															

### 2018-01-12 code/plotting/parameter_space_comparison.py

@@ -172,7 +172,7 @@ for i,k in enumerate(fields):
     if k == 'IE':
         ax.annotate(r'$\mathrm{(c)}$', (1.8e3, 1.82), fontsize=10)
         label_end = '{:.2g}'.format(-pIE)
-        label_end = '$(\\langle T_1\\rangle - T_{\mathrm{top}})\\mathrm{ Ra}^{' + label_end + '}$'
+        label_end = '$(\\langle T\\rangle - T_{\mathrm{top}})\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end), fontsize=10, labelpad=4)
 #        ax.set_ylabel(r'$\langle T_1 \rangle - T_{\mathrm{top}}$', fontsize=10, labelpad=4)
         ax.set_ylim(1, 2)

### 2018-01-12 code/plotting/time_trace.py

@@ -45,6 +45,7 @@ fields = ['Nu', 'Re', 'IE', 'KE', 'TE']
 
 ra_runs = '1.30e8'
 
+pre_flux_file = None
 ##### INFO grabbing from post-plot buddy files
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
@@ -53,6 +54,8 @@ for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
     for i, d in enumerate(glob.glob('{:s}/*Ra{:s}*/'.format(base_dir, ra_runs))):
         ra = d.split('_Ra')[-1].split('_')[0]
         ra += '_{}'.format(a)
+        if a == 1 and ra_runs in d:
+            pre_flux_file = h5py.File('{:s}/bvp_plots/profile_dict_file_0000.h5'.format(d), 'r')
 
         info[ra] = OrderedDict()
         try:
@@ -199,9 +202,16 @@ axes = []
 gs_info = (((550,0), 450, 267), ((550, 366), 450, 267), ((550, 800), 450, 200))
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[0])))
 this_label = '{}_0'.format(ra_runs)
-enth = info[this_label]['enth_flux_profile'][1,:]*np.sqrt(float(ra_runs))
-kappa = info[this_label]['kappa_flux_profile'][1,:]*np.sqrt(float(ra_runs))
-sum_f = (enth + kappa)
+#enth = info[this_label]['enth_flux_profile'][1,:]*np.sqrt(float(ra_runs))
+#kappa = info[this_label]['kappa_flux_profile'][1,:]*np.sqrt(float(ra_runs))
+#sum_f = (enth + kappa)
+
+enth = pre_flux_file['enth_flux_IVP'].value*np.sqrt(float(ra_runs))
+sum_f = pre_flux_file['tot_flux_IVP'].value*np.sqrt(float(ra_runs))
+kappa = sum_f - enth
+
+
+
 axes[-1].axhline(1, c='k', ls='-.')
 axes[-1].axhline(0, c='orange', ls='--')
 axes[-1].plot(info[this_label]['z_profile'], enth,  c=f_conv_color)
@@ -217,7 +227,7 @@ axes[-1].set_xlabel('z')
 [axes[-1].tick_params(axis=axis, colors='orange') for axis in axis_names]
[…]

### 2018-01-12 tex/bvp_paper.tex
first draft of paper done enough for co-authors to see

@@
 \caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
-(b) are shown for Ra = $1.30 \cdot 10^8$ ($S = 10^5$).  The horizontal extent of the subplots is set
-such that one simulation time unit takes up an equal amount of paper space in (a) and (b).
-The dashed vertical line on (a) represents the time at which the BVP is solved on the run in (b),
-and the horizontal dashed lines show the equilibrium value of the energies.
-(c) System fluxes early in the run (the orange highlights in (a)).  Black is the sum of the flux, purple
+(b) are shown for $S = 10^{4 + 2/3}$.  The horizontal extent of the subplots is set
+such that one simulation time unit takes up an equal amount of paper space in (a) and (b). Volume averaged
+kinetic energy is shown in black, and the volume averaged temperature with the top value removed, is shown
+in red.
+The dashed vertical line on (a) represents the time at which averaging begins in the BVP solution in (b),
+and the horizontal dashed lines show the equilibrium value of the energies. The blue vertical lines represent
+the beginning of the time-averaging window.
+(c) System fluxes early in the run (the orange highlights in (a)) are shown.  
+Black is the sum of the flux, purple
 is the convective flux, and red is the conductive flux.
-(d) Fluxes in the converged rundown IVP compared to the ``converged'' BVP.  The sum of flux is shown in
+(d) Fluxes in the converged rundown IVP compared to the converged BVP.  The sum of flux is shown in
 black \& grey, the convective flux is shown in purple \& pink, and the conductive flux is shown in red \& orange.
-(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, the BVP fluxes
+(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, 
+the BVP fluxes deviate from the rundown fluxes by only a few percent of the total flux, and
 are much closer to the converged state than the initial fluxes, as in (c).
@@
 \caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
-$S = 10^5$ are shown.  (a) Evolved temperature profiles, as a function of height.
+$S = 10^{4 + 2/3}$ are shown.  (a) Evolved temperature profiles, as a function of height.
 (b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
-(c) Frequency distributions, as in Fig. \ref{fig:pdf_comparison},
-comparing the values of the point-by-point temperatures over the averaging
-window. The mode of the frequency distribution has a distinct offset between the two runs due to
-the clear difference between the profiles in (a), but the
-thermal fluctuations about the mean which drive the convection are similar (AS IN FIG. \ref{fig:pdf_comparison},
-I NEED TO THINK MORE ON THE PDF COMPARISON).
+(c) Frequency distributions of point-by-point measurements of $T$ throughout the two domains over the
+averaging windows are shown.
+The BVP shows excellent agreement with the thermal rundown (AUTHOR NOTE: I need to perform quantitative PDF
+comparisons, still).
 \label{fig:temp_comparison} }
@@
 
-The temperature profiles of a 2D run at $S = 10^5$ 
+The temperature profiles of a 2D run at $S = 10^{4 + 2/3}$ 
 for both the BVP solve and the long rundown are shown in
 Fig. \ref{fig:temp_comparison}a.  While they are not perfectly aligned they are within less than
-2\% of each other throughout the depth of the atmosphere, as shown in Fig. \ref{fig:temp_comparison}b.
+0.25\% of each other throughout the depth of the atmosphere, as shown in Fig. \ref{fig:temp_comparison}b.
 While the mean temperature profile is interesting, the point-by-point fluctuations in the
@@
 in Fig. \ref{fig:temp_comparison}c, aside from the noticeable difference in the mode of the
-temperatures, the two runs exhibit largely the same spread of temperatures, with the rundown
-achieving higher temperatures at the base of the atmosphere.  These two profiles do not pass
-a Kolmogorov-Smirnov test for similarity (AUTHOR NOTE: we need to collaborate on different measures
-of comparing PDFs).
+temperatures, the two runs exhibit largely the same spread of temperatures.
+(AUTHOR NOTE: I'll run a Kolmogorov-Smirnov test to compare the PDFs, but I need to collaborate on this
+to make sure that what I'm planning on doing makes sense -- we should talk about this.)
 
@@
 two solutions are largely consistent.  The nonlinear transport in Fig. \ref{fig:pdf_comparison}
-shows that the post-BVP solution experiences more extreme events which carry a large amount of
-flux than the rundown solution, which is to be expected since it is not quite in equilibrium,
-as shown in Fig. \ref{fig:time_trace}d.  None of these profiles pass a KS test for similarity
+shows that the rundown solution experiences more extreme events which carry a large amount of
+flux than the BVP solution, but the distributions are largely consistent.
 (AUTHOR NOTE: see previous paragraph comment).
@@
 \caption{Frequency distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
-vertical transport (c) are shown for a 2D run at $S = 10^5$.  We sample flows every 0.1 time units for 500 freefall
+vertical transport (c) are shown for a 2D run at $S = 10^{4 + 2/3}$.  We sample flows every 0.1 time units for 500 freefall
 times, and include the flows at all points on the grid at each of these samples in these distributions.  All
@@
 Chebyshev grids near the boundaries, so there is a large peak around zero. The distributions, and thus the nonlinear
-dynamics, are broadly similar, but they do not pass a two-tailed Kolmogorov-Smirnov similarity test. (NOTE TO
-CO-AUTHORS: I NEED TO THINK BETTER ON HOW TO COMPARE PDFS, IF YOU HAVE IDEAS PLEASE SEND THEM)
+dynamics, are broadly similar, but they  (maybe?) do not pass a two-tailed Kolmogorov-Smirnov similarity test. (AUTHOR NOTE: 
+I just revamped the BVP method a bit on 1/12/2018, so I haven't had the time to run full tests on all the plots here)
 \label{fig:pdf_comparison} }
@@
 time window, and error bars represent the shift in the mean value over the window.
+All data points are staggered slightly off of their original value in the x-direction
+so as to show clearly the values of overlapping points at the same value of Ra. 
 (a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
 simulations display horizontally oscillating plumes which have oscillating periods of high transport
-and low transport.  The mean value is marginally diminished as a result, and the range of Nu over time
+and low transport.  The mean value is marginally diminished as a result, and the variance of Nu with time
 is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
-Ra$^{0.45}$ in 2D and (something else) in 3D. (c) The average temperature flucutation, minus the top
-temperature, gives us a measure of the extent of the upper boundary, and is in some ways a more stationary
-proxy for Nu, and it displays similar scaling.  The temperature profile is slow to adjust, and differences between
-BVP solutions and rundown solutions are easier to pick out.
+Ra$^{0.45}$ in 2D and (something else?) in 3D. (c) The average temperature flucutation, minus the top
+temperature, which is a scalar measure of the final average thermodynamic state and should approach zero
+in the limit of infinitely large Ra.
+The temperature profile is slow to adjust, and differences between
+BVP solutions and rundown solutions are quite easy to pick out in this measure.
 \label{fig:parameter_space_comparison} }

### 2018-01-12 code/plotting/parameter_space_comparison.py

@@ -27,7 +27,7 @@ import matplotlib.gridspec as gridspec
 
 import dedalus.public as de
 
-COLORS=['indigo', 'orange']
+COLORS=['indigo', 'red']
 MARKERS=['s', 'o', 'd', '*']
 MARKERSIZE=[5,4,5,7]
 
@@ -116,6 +116,10 @@ for i,k in enumerate(fields):
             mrkr = 'o'
             threeD = False
         ind = int(j) % 2
+        if ind == 1:
+            mec = 'black'
+        else:
+            mec = None
 
         if threeD:
             s = 20*(3 - 2*int(ind))
@@ -172,20 +176,20 @@ for i,k in enumerate(fields):
     if k == 'IE':
         ax.annotate(r'$\mathrm{(c)}$', (1.8e3, 1.82), fontsize=10)
         label_end = '{:.2g}'.format(-pIE)
-        label_end = '$(\\langle T\\rangle - T_{\mathrm{top}})\\mathrm{ Ra}^{' + label_end + '}$'
+        label_end = '$(\\overline{T} - T_{\mathrm{top}})\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end), fontsize=10, labelpad=4)
 #        ax.set_ylabel(r'$\langle T_1 \rangle - T_{\mathrm{top}}$', fontsize=10, labelpad=4)
         ax.set_ylim(1, 2)
     elif k == 'Nu':
         ax.annotate(r'$\mathrm{(a)}$', (1.8e3, 0.225), fontsize=10)
         label_end = '-{:.2g}'.format(pNu)
-        label_end = '$\\langle\\mathrm{Nu}\\rangle\\mathrm{ Ra}^{' + label_end + '}$'
+        label_end = '$\\overline{\\mathrm{Nu}}\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end), fontsize=10, labelpad=0)
         ax.set_ylim(2e-1, 5e-1)
     elif k == 'Re':
         ax.annotate(r'$\mathrm{(b)}$', (1e8, 0.12), fontsize=10)
         label_end = '-{:.3g}'.format(pRe)
-        label_end = '$\\langle\\mathrm{Re}\\rangle\\mathrm{ Ra}^{' + label_end + '}$'
[…]

### 2018-01-12 code/plotting/time_trace.py

@@ -44,6 +44,7 @@ base_dirs_post = [
 fields = ['Nu', 'Re', 'IE', 'KE', 'TE']
 
 ra_runs = '1.30e8'
+ra_runs = '6.01e7'
 
 pre_flux_file = None
 ##### INFO grabbing from post-plot buddy files
@@ -128,30 +129,34 @@ for i in range(4):
         f = 0.5 + info[this_label]['IE_scalar']
         df = np.abs(f[1:] - f[:-1])
         t_bvp_ind = np.argmax(df) + 1
-        axes[0].axvline(info['{}_1'.format(ra_runs)]['sim_time'][t_bvp_ind], ls='--', c='k')
+        df[t_bvp_ind-1] = 0
+        t_bvp_ind2 = np.argmax(df) + 1
+        axes[0].axvline(info['{}_1'.format(ra_runs)]['sim_time'][-1], ls='--', c='k')
         axes[i % 2].plot(info[this_label]['sim_time'][:t_bvp_ind], info[this_label]['KE_scalar'][:t_bvp_ind], c='k')
-        axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind:], info[this_label]['KE_scalar'][t_bvp_ind:], c='k')
+        axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind:t_bvp_ind2], info[this_label]['KE_scalar'][t_bvp_ind:t_bvp_ind2], c='k')
+        axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind2:], info[this_label]['KE_scalar'][t_bvp_ind2:], c='k')
         axes[i % 2].set_yscale('log')
         axes[i % 2].set_ylim(1e-3, 1e-1)
 
         axes_share[i % 2].plot(info[this_label]['sim_time'][:t_bvp_ind], 0.5 + info[this_label]['IE_scalar'][:t_bvp_ind], c='r')
-        axes_share[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind:], 0.5 + info[this_label]['IE_scalar'][t_bvp_ind:], c='r')
+        axes_share[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind:t_bvp_ind2], 0.5 + info[this_label]['IE_scalar'][t_bvp_ind:t_bvp_ind2], c='r')
[…]

### 2018-01-12 code/run_scripts/2d/base_pre/local_runs.sh

@@ -1,5 +1,5 @@
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=2.79e3
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=6.01e3
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=1.30e4
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=2.79e4
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=6.01e4 --seed=200
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=2.79e3
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=6.01e3
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=1.30e4
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=2.79e4
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/base_pre --run_time_therm=1 --mixed_flux_T --no_slip --Rayleigh=6.01e4

### 2018-01-12 code/run_scripts/2d/bvp_post/local_runs.sh

@@ -1,5 +1,5 @@
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e3 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e3_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5 --overwrite
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e3 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e3_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5 --overwrite
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=1.30e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra1.30e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5 --overwrite
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=2.79e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra2.79e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5 --overwrite
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_post --run_time_buoy=100 --mixed_flux_T --no_slip --Rayleigh=6.01e4 --restart=runs/bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra6.01e4_Pr1_a2/final_checkpoint/final_checkpoint_s1.h5 --overwrite
[…]

### 2018-01-12 code/run_scripts/2d/bvp_pre/local_runs.sh

@@ -1,5 +1,5 @@
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e3   --do_bvp --bvp_final_equil_time=50  
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e3   --do_bvp --bvp_final_equil_time=50 
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=1.30e4   --do_bvp --bvp_final_equil_time=50 
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e4   --do_bvp --bvp_final_equil_time=50 
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=128 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e4   --do_bvp --bvp_final_equil_time=50  --seed=200
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e3   --do_bvp --num_bvps=2 --bvp_final_equil_time=50  
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e3   --do_bvp --num_bvps=2 --bvp_final_equil_time=50 
[…]

### 2018-02-06 tex/bvp_paper.tex
moving a fig to the bottom of page for cleanliness
paper is better

@@
 \begin{abstract}
-We present a method for coupling Boundary value problems (BVPs) with Initial value problems (IVPs)
+We present a method for coupling boundary value problems (BVPs) with initial value problems (IVPs)
 in order to achieve thermally converged convective solutions on dynamical timescales, rather than the
-long thermal timescale.  We demonstrate the similarity between the solution reached by BVP and the
-solution reached by a long thermal rundown of the IVP, and demonstrate that this method works at a
-large range of supercriticalities.  We use this method to achieve converged solutions at high Ra,
-and discuss its extension to more complex scenarios, such as stratified, compressible convection.
+long thermal timescale. We study this method in the context of \RB convection. 
+We demonstrate that the solution reached by BVP and the
+solution reached by a long thermal rundown of the IVP are similar, and demonstrate that this method works at a
+large range of supercriticalities.  The BVP method is used to achieve converged solutions at high supercriticality ($10^8$),
+and its extensions to more complex scenarios are discussed.
 \end{abstract}
@@
 Natural convection occurs in the presence of disparate timescales. Granules on the
-solar surface overturn on the order of 10 minutes, whereas deep motions in the Sun are likely at
-low Mach number and constrained by the solar rotation rate of $\sim$1 month.  
-Both of these dynamical timescales are vastly shorter than the Sun's average timescale of energy transport,
-which is the Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
-As simulations aim to model natural convection
-by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much
-longer than dynamical timescales \cite{anders&brown2017}, achieving converged simulations will 
-require runs which span a greater number of convective timescales in order to thermally converge.
-Furthermore, with increasing Ra and decreasing diffusivities, motions become more turbulent
-and require finer grid meshes and shorter timesteps to resolve turbulent motions, increasing the simulation
-time required for each overturn timescale.  
-These two effects conspire to make achieving thermally converged, high-Ra, astrophysically interesting
-simulations an intractable problem using modern numerical tools.
+solar surface overturn on the order of 10 minutes, whereas deep motions in the Sun at
+low Mach number are constrained by the solar rotation rate of $\sim$1 month.  
+These dynamical timescales are vastly shorter than the Sun's 
+Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
+Modern simulations aim to model natural convection
+by increasing into the high-Rayleigh-Number (Ra) regime, in which energy transportation occurs on
+timescales much larger than dynamical timescales \cite{anders&brown2017}.
+In this regime, simulations must pass through a great number
+of convective timescales to reach a thermally converged state.
+Furthermore, as Ra increases and diffusivities correspondingly decrease, 
+motions become more turbulent. To properly resolve these turbulent motions, fine grid meshes
+and short timesteps are required; these requirements increase the computational
+cost of evolving through a single convective overturn time.
+In short, achieving thermally converged, high-Ra, astrophysically interesting
+simulations is an intractably expensive problem using modern numerical tools.
 
@@
 $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure, $P$.
-The density of the fluid is a constant $\rho_0$, except on the
-term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$ acts in the vertical momentum equation, 
-in which case it is $\rho = \rho_0(1  - \alpha T_1)$.  
+The density of the fluid is a constant, $\rho_0$, except on the
+term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, acts in the vertical momentum equation, 
+where $\rho = \rho_0(1  - \alpha T_1)$.  
 Under these choices, the equations of motion are \cite{spiegel&veronis1960}
@@
 \end{gather}
-We non-dimensionalize these equations such that length scales are in units of the layer height ($L_z$),
-temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
-and time is in units of the freefall timescale ($L_z / v_{\text{ff}}$), where the freefall velocity is
-$v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$.
+We non-dimensionalize these equations on the layer height ($L_z$),
+the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
+and the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
+by these choices, one time unit is a freefall time ($L_z/v_{ff}$).
 We further re-arrange the momentum equation by introducing a reduced kinematic pressure,
-$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where $\bm{g} = -\grad \phi$ is the gravitational potential.
-Despite containing a nonlinear $\bm{u}$ component, the nature of $P$ in \RB convection, as a
+$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where the gravitational
+potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$.
+The nature of $P$ in \RB convection, as a
 Lagrange multiplier,
-allows us to treat $\varpi$ as a linear unknown, without a need to resolve its different components.
+allows the treatment of $\varpi$ as a linear variable.
 We time evolve the equations in the form,
@@
 \end{gather}
-where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity. We find Eq. (\ref{eqn:bouss_momentum}) to
+where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity, and the temperature
+has been decomposed as $T \equiv T_0 + T_1$ where $T_0$ is the initial temperature
+profile. We find Eq. (\ref{eqn:bouss_momentum}) to
 be slightly faster numerically than the standard form in Eq. (\ref{eqn:dim_bouss_momentum}).
@@
 \end{equation}
-The dimensionless vertical extent of the domain is $z = [-1/2, 1/2]$, and at the boundaries
-we impose no-slip, impenetrable boundary conditions such that $w = u = v = 0$ at $z = \pm 1/2$.
+The dimensionless vertical extent of the domain is $z = [-1/2, 1/2]$, and at the top and bottom boundaries
+we impose no-slip, impenetrable boundary conditions such that $u = v = w = 0$ at $z = \pm 1/2$.
 At the lower boundary, we employ a fixed flux condition such that $\partial T_1 / \partial z = 0$
-at $z = -1/2$, and we impose a fixed temperature condition $T_1 = 0$ at $z = 1/2$. Both
+at $z = -1/2$, and we impose a fixed temperature condition of $T_1 = 0$ at $z = 1/2$. Both
 horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
@@
 whereas Neumann conditions model plates of finite conductivity.  
-In both cases, choosing symmetric boundary conditions maintains overall system symmetry, 
-and despite evolving towards different thermal structures, both types of conditions
-transport heat in the same manner \cite{johnston&doering2009}.
+Both types of conditions
+transport heat in the same manner \cite{johnston&doering2009},
+at least when the upper and lower conditions are symmetric.
 Studies of convection which aim to model
@@
 while the outer boundary condition is held at a fixed temperature,
-modeling the surface of a star which must output the energy generated internally.
+modeling the stellar surface which must output the energy generated internally.
 This setup is a useful model for understanding natural
@@
 thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
-Dirichlet condition.  We choose these conditions in part to better understand them, and in
+Dirichlet condition.  We choose these mixed conditions in part to better understand them, and in
 part because these conditions minimize the number of assumptions that must be made in
@@
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
+The linear terms (on the LHS of the equations) are solved implicitly,
+while the nonlinear terms (RHS) are explicitly solved.
 The temperature field is decomposed as $T = T_0(z) + T_1(x, y, z, t)$
@@
 (b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
-(c) Frequency distributions of point-by-point measurements of $T$ throughout the two domains over the
-averaging windows are shown.
-The BVP shows excellent agreement with the thermal rundown (AUTHOR NOTE: I need to perform quantitative PDF
-comparisons, still).
+(c) Probability distributions of point-by-point measurements of $T$ throughout the two domains over the
+averaging windows are shown.  The cumulative distribution functions are overplotted and the maximum
+difference between them in 0.0407. This difference arises due to the imperfect alignment of the
+mean domain temperatures, but it is clear that otherwise the statistics are quite similar.
 \label{fig:temp_comparison} }
@@
 temperatures, the two runs exhibit largely the same spread of temperatures.
-(AUTHOR NOTE: I'll run a Kolmogorov-Smirnov test to compare the PDFs, but I need to collaborate on this
-to make sure that what I'm planning on doing makes sense -- we should talk about this.)
+(AUTHOR NOTE: we aren't quite sure how to do a KS test properly here, but we can at least
+list the KS statistic -- currently this is in the caption.)
 
@@
 determining if the post-BVP solution appropriately captures key features of the nonlinear dynamics.
-We show point-by-point frequency distributions of the horizontal velocity, vertical velocity,
+We show point-by-point probability distributions of the horizontal velocity, vertical velocity,
 and nonlinear transport in Fig. \ref{fig:pdf_comparison}.  All of these measures have a sharp
@@
 near the boundaries of our Chebyshev grid.  Regardless, we see that the velocities of the 
-two solutions are largely consistent.  The nonlinear transport in Fig. \ref{fig:pdf_comparison}
-shows that the rundown solution experiences more extreme events which carry a large amount of
-flux than the BVP solution, but the distributions are largely consistent.
-(AUTHOR NOTE: see previous paragraph comment).
+two solutions are largely consistent.  The nonlinear transport in Fig. \ref{fig:pdf_comparison}c
+shows that the rundown solution experiences a larger number of energetic, extreme events,
+but the BVP displays a larger number of moderately energetic events than the IVP (as
+evidenced by the differences in the cumulative distribution functions).
 
-\begin{figure}[t]
+\begin{figure}[b]
 \includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{Frequency distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
+\caption{Probability distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
 vertical transport (c) are shown for a 2D run at $S = 10^{4 + 2/3}$.  We sample flows every 0.1 time units for 500 freefall
@@
 distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
-Chebyshev grids near the boundaries, so there is a large peak around zero. The distributions, and thus the nonlinear
-dynamics, are broadly similar, but they  (maybe?) do not pass a two-tailed Kolmogorov-Smirnov similarity test. (AUTHOR NOTE: 
-I just revamped the BVP method a bit on 1/12/2018, so I haven't had the time to run full tests on all the plots here)
+Chebyshev grids near the boundaries, so there is a large peak around zero. 
+The cumulative distribution function is overplotted on each plot, with a maximum difference of
+(a) 0.027, (b) 0.0061, and (c) 0.035. There is an excess of higher-flux carrying
+elements in the BVP solution than in the IVP rundown, despite the rundown's distribution
+having more powerful, rare events.
 \label{fig:pdf_comparison} }
@@
 examined both Rundown and BVP solutions in the range $S = [10^{1/3}, 10^5]$ in 2D and
-$S = [10^1, 10^4]$ in 3D (3D points to come).  We have also further explored up to $S = 10^6$
-(AUTHOR NOTE: should we go up to $10^8$?  $10^7$ is easily in reach. Also, 3D data points are
-sparse and will change -- need to rerun with proper BVP procedure).  We compare scalar, 
-volume-averaged measurements of all of these runs in Fig. \ref{fig:parameter_space_comparison}.
+$S = [10^1, 10^4]$ in 3D.  We have also further explored up to $S = 10^6$
+(AUTHOR NOTE: we're going up to $10^8$ in 2D right now, need to mention this is state of
+the art and give refs).
+We show the volume averaged Nusselt number, RMS Reynolds number, and mean temperature in
+the evolved BVP solutions in in Fig. \ref{fig:parameter_space_comparison}a-c.
+The relative error of the BVP measurements of these values is compared to the IVP
+measurements for these values in Fig. \ref{fig:parameter_space_comparison}d-f.
 
-In Fig. \ref{fig:parameter_space_comparison}a, we compare the Nusselt number scaling in 2D,
-3D, and for BVP and rundown solutions.  We use a classic definition of the Nusselt number
+In Fig. \ref{fig:parameter_space_comparison}a, we show the Nusselt number scaling in 2D and
+3D.  We use a classic definition of the Nusselt number
 to measure the heat transport in these systems, where
@@
 $\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  We find that this scales roughly as
-$\text{Re} \propto \text{Ra}^{0.45}$, and find good agreement between BVP and rundown solutions.
+$\text{Re} \propto \text{Ra}^{0.45}$.
 
@@
 
+For each of these measurements, the BVP achieves the same value as the IVP to
+within about 3\% (Fig. \ref{fig:parameter_space_comparison}d-f).  This is good agreement,
+and the residuals have a scattered distribution of positive and negative values, indicating
+that the method is not biased towards the wrong answer in a clear manner.
+
 \begin{figure}[t]
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
-\caption{Compensated scaling plots are shown for the Nusselt number (a), the
-Reynolds number (b), and the volume-averaged temperature (c).  All plots are linear(y)-log(x),
-and any differences vertically are generally small.  Symbols represent the mean value of
+\caption{Scaling plots are shown for the Nusselt number (a), the
+Reynolds number (b), and the volume-averaged temperature (c).  
+Symbols represent the mean value of
 a measurement, vertical lines represent the standard deviation of the measurement over the
 time window, and error bars represent the shift in the mean value over the window.
-All data points are staggered slightly off of their original value in the x-direction
-so as to show clearly the values of overlapping points at the same value of Ra. 
 (a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
@@
 is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
-Ra$^{0.45}$ in 2D and (something else?) in 3D. (c) The average temperature flucutation, minus the top
+Ra$^{0.45}$ in 2D and is not distinctly different in 3D. (c) The average temperature flucutation, minus the top
 temperature, which is a scalar measure of the final average thermodynamic state and should approach zero
@@
 The temperature profile is slow to adjust, and differences between
-BVP solutions and rundown solutions are quite easy to pick out in this measure.
+BVP solutions and rundown solutions are quite easy to pick out in this measure. (d-f)
+Relative error is shown between the BVP and IVP measurements of Nu (d), Re (e), and the
+mean temperature (f). The grey box indicates the region in which only BVP runs were
+carried out due to computational expense.
 \label{fig:parameter_space_comparison} }
@@
 is achieved quickly.
+
+It is important to note that the measurements made in
+this paper were generally done for short timescales (a few hundred buoyancy times) in
+order to show the precise differences between the BVP solutions and the IVP solutions.
+Where there are differences, the BVP solution is trending towards the IVP solution,
+and if measurements were taken over long timescales (e.g., a thermal time), the
+differences between the BVP solution and IVP solution would be negligible.
 

### 2018-02-06 code/bvps/bvp_tools.py

@@ -324,7 +324,6 @@ class BVPSolverBase:
                 self.first_l2 = False
 
 
-
     def check_if_solve(self):
         """ Returns a boolean.  If True, it's time to solve a BVP """
 #        logger.debug('start bvp {}'.format((self.avg_started and self.avg_time_elapsed >= self.min_bvp_time) and (self.do_bvp and (self.completed_bvps < self.num_bvps))))
@@ -408,8 +407,7 @@ class BoussinesqBVPSolver(BVPSolverBase):
     Solves energy equation.  Makes no approximations other than time-stationary dynamics.
     """
 
-    # 0 - full avg profile
-    # 1 - stdev profile
+
     FIELDS = OrderedDict([  
                 ('enth_flux_IVP',       'w*(T0+T1)'),                      
                 ('tot_flux_IVP',        '(w*(T0+T1) - P*(T0_z+T1_z))'),                      
@@ -506,7 +504,6 @@ class BoussinesqBVPSolver(BVPSolverBase):
             plt.plot(z, init_kappa_flux + init_enth_flux)
             plt.plot(z, init_kappa_flux)
             plt.plot(z, init_enth_flux)
-            plt.plot(z, self.profiles_dict['enth_flux_IVP'], lw=2, ls='--')
             plt.plot(z, flux_through_system)
             plt.savefig('{}/fluxes_before_{:04d}.png'.format(self.plot_dir, self.plot_count))
             plt.close()
@@ -589,7 +586,6 @@ class BoussinesqBVPSolver(BVPSolverBase):
             while np.sum(np.abs(pert)) > tolerance:
                 solver.newton_iteration()
                 logger.info('Perturbation norm: {}'.format(np.sum(np.abs(pert))))
-
 
             T1 = solver.state['T1']
             P1   = solver.state['p1']

### 2018-02-06 code/plotting/parameter_space_comparison.py

@@ -26,6 +26,7 @@ import matplotlib.gridspec as gridspec
 
 
 import dedalus.public as de
+plt.rc('font',family='Times New Roman')
 
 COLORS=['indigo', 'red']
 MARKERS=['s', 'o', 'd', '*']
@@ -58,17 +59,22 @@ for a, base_dir in enumerate(base_dirs):
 print(info.keys())
 
 
-plt.figure(figsize=(8, 1.5))
+plt.figure(figsize=(8, 4))
 gs     = gridspec.GridSpec(*(1000,1000))
-gs_info = (((100,0), 800, 250), ((100, 370), 800, 250), ((100, 750), 800, 250))
+gs_info = (((100,0), 400, 250), ((100, 370), 400, 250), ((100, 750), 400, 250))
 ra_crit = 1295.78
-pNu = 0.2  
-pRe = 0.45
-pIE = -0.2
+pNu = 0#0.2  
+pRe = 0#0.45
+pIE = 0#-0.2
 for i,k in enumerate(fields):
     ax = plt.subplot(gs.new_subplotspec(*gs_info[i]))
     bx = ax.twiny()
+    ax.axvline(2.79e8, ls='--', c='k')
+    ax.fill_between(np.logspace(np.log10(2.79e8), 15, 2), 1e-5, 1e15, color='grey', alpha=0.4)
+    ax.set_xlim(1e3, 1e10)
     for j in range(len(base_dirs)):
+        if j == 0 or j == 2:
+            continue
         ra_list = []
         mean_list = []
         max_list  = []
@@ -100,7 +106,7 @@ for i,k in enumerate(fields):
 
             except:
                 continue
-        ra_list = np.array(ra_list, dtype=np.float64)*(1.075-0.05*j)
+        ra_list = np.array(ra_list, dtype=np.float64)
         mean_list = np.array(mean_list, dtype=np.float64)
         max_list = np.array(max_list, dtype=np.float64)
         min_list = np.array(min_list, dtype=np.float64)
@@ -112,29 +118,15 @@ for i,k in enumerate(fields):
         if j >= 2:
             mrkr = '*'
             threeD = True
+            label = '3D'
+            color  = 'red'
+            s = 20
         else:
             mrkr = 'o'
             threeD = False
-        ind = int(j) % 2
-        if ind == 1:
-            mec = 'black'
-        else:
-            mec = None
-
-        if threeD:
[…]

### 2018-02-06 code/plotting/pdf_comparison.py

@@ -13,6 +13,7 @@ Options:
 import matplotlib   
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
+plt.rc('font',family='Times New Roman')
 from matplotlib.colors import ColorConverter
 import os
 import numpy as np
@@ -118,62 +119,99 @@ axes.append(plt.subplot(gs.new_subplotspec(*gs_info[0])))
 base_label = '{}_0'.format(ra_runs)
 bvp_label = '{}_1'.format(ra_runs)
 
-axes[-1].fill_between(info[base_label]['w_xs_pdf'], 0, info[base_label]['w_pdf_pdf']*info[base_label]['w_denorm_pdf'], color='blue', alpha=0.4)
-axes[-1].plot(info[base_label]['w_xs_pdf'], info[base_label]['w_pdf_pdf']*info[base_label]['w_denorm_pdf'], c='blue')
-axes[-1].fill_between(info[bvp_label]['w_xs_pdf'], 0, info[bvp_label]['w_pdf_pdf']*info[bvp_label]['w_denorm_pdf'], color='red', alpha=0.4)
-axes[-1].plot(info[bvp_label]['w_xs_pdf'], info[bvp_label]['w_pdf_pdf']*info[bvp_label]['w_denorm_pdf'], c='red')
+axes[-1].fill_between(info[base_label]['w_xs_pdf'], 0, info[base_label]['w_pdf_pdf'], color='blue', alpha=0.4)
+axes[-1].plot(info[base_label]['w_xs_pdf'], info[base_label]['w_pdf_pdf'], c='blue')
+axes[-1].fill_between(info[bvp_label]['w_xs_pdf'], 0, info[bvp_label]['w_pdf_pdf'], color='red', alpha=0.4)
+axes[-1].plot(info[bvp_label]['w_xs_pdf'], info[bvp_label]['w_pdf_pdf'], c='red')
 axes[-1].set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w_xs_pdf']))
-axes[-1].set_xlabel('Vertical velocity', labelpad=-1)
-axes[-1].set_ylabel('Frequency')
+axes[-1].set_xlabel('Vertical Velocity', labelpad=-1)
[…]

### 2018-02-06 code/plotting/temp_comparison.py

@@ -13,6 +13,7 @@ Options:
 import matplotlib   
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
+plt.rc('font',family='Times New Roman')
 from matplotlib.colors import ColorConverter
 import os
 import numpy as np
@@ -26,6 +27,41 @@ import matplotlib.gridspec as gridspec
 
 
 import dedalus.public as de
+from scipy.interpolate import interp1d
+
+
+
+def calculate_CDF(x, pdf):
+    """ Calculate the CDF of a PDF using trapezoidal rule integration """
+    dx = np.diff(x)
+    new_x = x[0:-1] + dx
+    d_cdf   = (dx/2) * (pdf[0:-1] + pdf[1:])
+    cdf = np.zeros_like(d_cdf)
+    for i in range(len(cdf)):
+        cdf[i] = np.sum(d_cdf[:i+1])
+    return new_x, cdf
+
+def ks_test(x1, y1, N1, x2, y2, N2, n=1000):
+    x_range = [np.min(x1), np.max(x1)]
+    if np.min(x2) > x_range[0]:
+        x_range[0] = np.min(x2)
+    if np.max(x2) < x_range[1]:
+        x_range[1] = np.max(x2)
+
+    x_points = np.linspace(*tuple(x_range), n)
+
+    f1 = interp1d(x1, y1, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
+    f2 = interp1d(x2, y2, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
+
+    y1_interp = f1(x_points)
+    y2_interp = f2(x_points)
+    print(y1_interp - y2_interp)
+    diff = np.abs(y1_interp - y2_interp)
+    
+    max_diff = np.max(diff)
+    return max_diff, np.sqrt((N1+N2)/(N1*N2))
+
+
 
 EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
 FORCE_WRITE=False
@@ -108,19 +144,33 @@ axes[-1].annotate(r'$\mathrm{(b)}$', (0.04, 0.03), fontsize=10)
 
 ##Plot 3
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[2])))
[…]

### 2018-02-06 code/plotting/time_trace.py

@@ -13,6 +13,7 @@ Options:
 import matplotlib   
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
+plt.rc('font',family='Times New Roman')
 from matplotlib.colors import ColorConverter
 import os
 import numpy as np
@@ -287,6 +288,7 @@ x_ticks = np.array([0, 0.5, 1])
 axes[-1].set_xticks(x_ticks)
 axes[-1].set_ylabel(r'$\mathrm{(BVP - Rundown)}\cdot\sqrt{\mathrm{Ra \,Pr}}$')
 axes[-1].annotate(r'$\mathrm{(e)}$', (0.04, -0.028), fontsize=10)
+axes[-1].set_xlabel('z')
 
 
 plt.savefig('time_trace.png'.format(k), bbox_inches='tight', dpi=200)

### 2018-02-13 tex/bvp_paper.tex
rough restructure of the intro; adds 7 sources and some discussion of various methods for converging solutions fast used historically; will come back to it tomorrow.

@@
 
-Prior studies of stratified convection in which a convective layer lies between stable layers
-have used the knowledge of Mixing Length Theory (MLT) to adjust the initial thermodynamic structure of
-the atmosphere to a state which is closer to the adiabat chosen by convection \cite{brandenburg&all2005}.
-However, many modern studies of convection do not contain stable layers above and below the convection
-zone, and the presence of hard boundaries and the boundary layers that they form make it difficult to
-know the correct evolved adiabat \emph{a priori}.
+The vast difference between convective and diffusive timescales has long plagued
+numericists studying convection, and a vast number of approaches has been used to
+study thermally converged solutions. ``Bootstrapping'' is the process of using
+a converged solution at lower Ra as initial conditions for a simulation at a higher
+Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
+but it is not without its faults.  This method is likely to run into hystersis
+effects, in which large-scale convective structures present in the
+low Ra solution imprint onto the dynamics of the new, high Ra solution. 
+For moderate-Ra solutions, a commonly-used tactic is to use initial conditions from
+a simpler model of the full convective state.  For example, using the results of
+a linear solve \cite{hurlburt&all1984} or using an axisymmetric solution for a full
+3D cylinder of convection \cite{verzicco&camussi1997}. In certain systems, 
+the physics of the evolved solution can be approximately known based on the initial
+conditions, and there a better set of initial conditions can be solved for analytically
+\cite{couston&all2017} or by using knowledge of Mixing Length Theory or other convective
+theories to adjust the initial profile towards the proper adiabat \cite{brandenburg&all2005}.
 
-Here we present a method for using simple boundary value problems (BVPs), 
-along with information about the evolved flow fields,
-to fast-forward the slow thermal evolution of convecting simulations.  
+Regardless, the most straightforward way of achieving a thermally converged solution
+is by simply allowing a simulation to run for a thermal timescale, which some
+studies do \cite{featherstone&hindman2016}.  Unfortunately, such a procedure is
+\emph{expensive}, and state-of-the-art simulations can often only be reasonably run
+for tens to hundreds of buoyancy times \cite{stevens&all2011}, much less the
+thousands-to-millions of buoyancy timescales required to reach a thermal time
+at high Ra.
+
+One further method of adjusting the atmospheric profile is by using information about
+the convective dynamics, as well as knowledge about energy balances and fluxes in
+the evolved solution, to carefully adjust the mean thermodynamic profile towards
+its proper solution.  Such methods have some history, \cite{hurlburt&all1986}, but
+a clear presentation of such a method and a comparison of such a method to solutions
+which were achieved through a long thermal rundown are lacking.
+Here we present a simple 1D model that uses information about evolving flow fields
+to accelerate the evolution of the thermal profile in convective simulations.
 We run two sets of experiments: one in which we allow convective simulations to evolve for a

### 2018-02-13 code/plotting/parameter_space_comparison.py

@@ -208,11 +208,11 @@ gs_info = (((500,0), 400, 250), ((500, 370), 400, 250), ((500, 750), 400, 250))
 for i,k in enumerate(fields):
     ax = plt.subplot(gs.new_subplotspec(*gs_info[i]))
     if i == 0:
-        ax.annotate(r'$\mathrm{(d)}$', (2e3, 0.03), fontsize=10)
+        ax.annotate(r'$\mathrm{(d)}$', (2e3, 0.015), fontsize=10)
     if i == 1:
-        ax.annotate(r'$\mathrm{(e)}$', (2e3, 0.03), fontsize=10)
+        ax.annotate(r'$\mathrm{(e)}$', (2e3, 0.015), fontsize=10)
     if i == 2:
-        ax.annotate(r'$\mathrm{(f)}$', (2e3, 0.03), fontsize=10)
+        ax.annotate(r'$\mathrm{(f)}$', (2e3, 0.015), fontsize=10)
     mean_lists = []
     for j in range(len(base_dirs)):
         ra_list = []
@@ -255,7 +255,8 @@ for i,k in enumerate(fields):
     ax.axhline(0, ls='--', c='k')
     ax.axvline(2.79e8, ls='--', c='k')
     ax.fill_between(np.logspace(np.log10(2.79e8), 15, 2), -0.05, 0.05, color='grey', alpha=0.4)
-    ax.scatter(mean_lists[1][0][:twoD_len], twoD_diff)
+    ax.scatter(mean_lists[1][0][:twoD_len], twoD_diff, color='indigo')
+    ax.scatter(mean_lists[3][0][:threeD_len], threeD_diff, marker='*', color='red')
 #    ax.set_yscale('log')
     ax.set_xscale('log')
     ax.set_xlim(1e3, 1e10)
@@ -263,9 +264,9 @@ for i,k in enumerate(fields):
     if i == 0:
         ax.set_ylabel ('( BVP - IVP ) / IVP')
 
-    ax.set_ylim(-0.02, 0.04)
+    ax.set_ylim(-0.05, 0.03)
 
-    ax.set_yticks([-0.02, -0.01, 0, 0.01, 0.02, 0.03])
+    ax.set_yticks([-0.04, -0.02, 0, 0.02])
 
     [t.set_fontsize(10) for t in ax.get_xticklabels()]
     [t.set_fontsize(10) for t in ax.get_yticklabels()]

### 2018-02-13 code/plotting/time_trace.py

@@ -45,7 +45,7 @@ base_dirs_post = [
 fields = ['Nu', 'Re', 'IE', 'KE', 'TE']
 
 ra_runs = '1.30e8'
-ra_runs = '6.01e7'
+#ra_runs = '6.01e7'
 
 pre_flux_file = None
 ##### INFO grabbing from post-plot buddy files

### 2018-02-14 tex/bvp_paper.tex
rewrite of intro; needs lots of polish, but has more info/structure.

--- 2018-02-06 tex/bvp_paper.tex
@@
 \label{sec:intro}
-Natural convection occurs in the presence of disparate timescales. Granules on the
-solar surface overturn on the order of 10 minutes, whereas deep motions in the Sun at
-low Mach number are constrained by the solar rotation rate of $\sim$1 month.  
-These dynamical timescales are vastly shorter than the Sun's 
-Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
-Modern simulations aim to model natural convection
-by increasing into the high-Rayleigh-Number (Ra) regime, in which energy transportation occurs on
-timescales much larger than dynamical timescales \cite{anders&brown2017}.
-In this regime, simulations must pass through a great number
-of convective timescales to reach a thermally converged state.
-Furthermore, as Ra increases and diffusivities correspondingly decrease, 
-motions become more turbulent. To properly resolve these turbulent motions, fine grid meshes
-and short timesteps are required; these requirements increase the computational
-cost of evolving through a single convective overturn time.
-In short, achieving thermally converged, high-Ra, astrophysically interesting
-simulations is an intractably expensive problem using modern numerical tools.
+Natural convection occurs in the presence of disparate timescales which
+prohibit numericists from studying realistic models of natural systems.  For example,
+flows in the Sun's convection zone range from a Mach number (Ma) of order unity
+near the solar surface to order $10^{-5}$ deep in the solar interior.
+Explicit methods which are bound by the Courant-Friedrich-Lewy
+(CFL) timestep limit must resolve the fastest motions (sound
+waves and surface convection), resulting in timesteps which are prohibitively
+small for studies of the deep, low-Ma motions. These systems are numerically
+stiff. Even in the absence of the fast surface motions, the disparity between
+the sound crossing time and the deep flows have made studies of low-Ma stellar
+convection difficult. Traditionally, approximations such as
+the anelastic approximation, in which sound waves are explicitly filtered out,
+have been used to study low-Ma flows \cite{brown&all2010, featherstone&hindman2016}.
+More recently, advanced numerical techniques which use implicit or mixed
+implicit-explicit timestepping mechanisms have made it feasible to study
+convection at low Mach numbers \cite{viallet&all2011, viallet&all2013, viallet&all2016, lecoanet&all2014,
+anders&brown2017, bordwell&all2018}, and careful studies of deep convection which
+would have been impossible a decade ago are now widely accessible.
 
-Prior studies of stratified convection in which a convective layer lies between stable layers
-have used the knowledge of Mixing Length Theory (MLT) to adjust the initial thermodynamic structure of
-the atmosphere to a state which is closer to the adiabat chosen by convection \cite{brandenburg&all2005}.
-However, many modern studies of convection do not contain stable layers above and below the convection
-zone, and the presence of hard boundaries and the boundary layers that they form make it difficult to
-know the correct evolved adiabat \emph{a priori}.
+While solutions to problem of disparate dynamical timescales have proven useful,
+the difference between convective timescales and system relaxation timescales remains
+a significant problem facing studies of convection. 
+As modern simulations aim to model natural convection
+by increasing into the high-Rayleigh-number (Ra) regime,
+the thermal diffusion timescale on which the system relaxes grows with respect
+to the dynamical timescale, which stays roughly constant across all Ra
+\cite{anders&brown2017}.
+Solar convection is, once again, a prime example of this phenomenon.
+Dynamical timescales in the Solar convective zone are relatively short 
+(10 min overturn at solar surface, one month solar
+rotation rate) compared to the Kelvin-Helmholtz timescale of
+$3 \cdot 10^7$ years \cite{stix2003}.  
+Furthermore, as dynamical and diffusive timescales separate, 
+simulations become more turbulent. More turbulent motions 
+require finer grid meshes and smaller timesteps
+to capture advective dynamics. Thus, the progression of simulations into the high-Ra
+regime of natural convection is slowed by two simultaneous effects: timestepping
+through a single convective overturn time becomes more computationally expensive
+while the number of overturn times required for systems to reach thermal equilibration
+grows.
 
-Here we present a method for using simple boundary value problems (BVPs), 
-along with information about the evolved flow fields,
-to fast-forward the slow thermal evolution of convecting simulations.  
-We run two sets of experiments: one in which we allow convective simulations to evolve for a
-full thermal timescale before taking measurements, and another in which we employ a fast,
-BVP technique which occurs on dynamical timescales. We compare these two sets of simulations to
-show the validity of the BVP technique.  We use the BVP technique to run simulations
-at high Ra, in the regime where running for thermal timescales becomes computationally intractable.
+The vast difference between convective and diffusive timescales has long plagued
+numericists studying convection, and a plethora of approaches has been employed to
+study thermally converged solutions. One popular method for accelerating the convergence
+of high-Ra solutions is by ``Bootstrapping,'' or the process of using the flow
+fields in a converged solution at lower Ra as initial conditions for a simulation at a higher
+Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
+but it is not without its faults.  Bootstrapped solutions are succeptible to hysteresis
+effects, in which large-scale convective structures present in the
+low Ra solution imprint onto the dynamics of the new, high Ra solution. 
+In moderate-Ra simulations, a commonly-used tactic is to use 
+a simple model of the full convective state as initial conditions.  
+For example, past studies have used a linear eigenvalue solve to set the initial
+convective state \cite{hurlburt&all1984} or used an axisymmetric solution 
+as initial conditions for convection in a 3D cylinder \cite{verzicco&camussi1997}. 
+In certain systems, 
+the approximate state of the evolved solution can be estimated, and there an
+appropriate set of initial conditions can either be solved for analytically
+\cite{couston&all2017} or by using knowledge of Mixing Length Theory or other convective
+theories to adjust the initial profile towards the proper adiabatic state \cite{brandenburg&all2005}.
+
+Despite the plethora of methods that have been used,
+the most straightforward way to achieve a thermally converged solution
+is to evolve a convective simulation through a thermal timescale. Some modern
+studies do just that \cite{featherstone&hindman2016}, but it is becoming
+increasingly difficult. Such evolution is
+\emph{expensive}, and state-of-the-art simulations at the highest values of Ra
+can only be reasonably run
+for tens to hundreds of buoyancy times \cite{stevens&all2011}, much less the
+thousands of buoyancy timescales required for thermal convergence.
+
+In this work, we study a method of achieving accelerated evolution of a
+convective simulation through adjusting the thermodynamic state using information 
+from resolved, convective dynamics. We couple measurements of the (non-converged)
+convective solution with knowledge about energy balances in the eventual solution
+to self-consistently adjust the mean thermodynamic profile towards. 
+While such a method has been used previously \cite{hurlburt&all1986}, 
+we find no explanation in the current literature of the steps involved in employing
+this method, nor any study into the accuracy of such a method.
+In section \ref{sec:experiment}, we describe our convective simulations, our
+numerical methods, and our method for achieving accelerated evolution. In
+section \ref{sec:results}, we compare solutions reached through the accelerated evolution
+method to those that have been evolved through a full diffusive timescale, and we
+examine select simulations at very high Ra which have achieved accelerated evolution. Finally,
+in section \ref{sec:discussion}, we discuss extensions of the methods presented
+here to stratified, compressible systems.
 
@@
 \section{Results}
+\label{sec:results}
 While Fig. \ref{fig:time_trace} shows us that the post-BVP and post-rundown solutions
@@
 \section{Discussion \& Conclusions}
-\label{sec:results}
+\label{sec:discussion}
 The method presented here is a first step towards taking meaningful measurements

### 2018-02-14 tex/bvp_paper.tex
starts cleaning up experiment section

@@
 \label{sec:experiment}
-We adopt the Oberbeck-Boussinesq approximation.  Under this choice, the
-fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
-of thermal expansion ($\alpha$). The variables of the fluid that are evolved are the velocity,
-$\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure, $P$.
-The density of the fluid is a constant, $\rho_0$, except on the
+We study incompressible \RB convection under the Oberbeck-Boussinesq approximation,
+such that our fluid
+has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
+of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$, except on the
 term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, acts in the vertical momentum equation, 
 where $\rho = \rho_0(1  - \alpha T_1)$.  
-Under these choices, the equations of motion are \cite{spiegel&veronis1960}
+Under these constraints, the equations of motion are \cite{spiegel&veronis1960}
 \begin{gather}
 \DivU = 0, 
-	\label{eqn:dim_incompressible}
+	\label{eqn:incompressible}
 \\
@@
 \end{gather}
-We non-dimensionalize these equations on the layer height ($L_z$),
-the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
-and the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
+where $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$ is the velocity, 
+$T = T_0 + T_1$ are the initial and fluctuating components of temperature, 
+and $P$ is the pressure.
+We non-dimensionalize these equations such that the dimensionless unit of
+length is the layer height ($L_z$),
+temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
+and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
 by these choices, one time unit is a freefall time ($L_z/v_{ff}$).
-We further re-arrange the momentum equation by introducing a reduced kinematic pressure,
+We introduce a reduced kinematic pressure,
 $\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where the gravitational
-potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$.
-The nature of $P$ in \RB convection, as a
-Lagrange multiplier,
-allows the treatment of $\varpi$ as a linear variable.
-We time evolve the equations in the form,
+potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. As $P$ is a
+Langrange multiplier under the Oberbeck-Boussinesq approximation, $\varpi$
+can be treated straightforwardly as a linear variable. 
+In non-dimensional form, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
+are
 \begin{gather}
-\DivU = 0, 
-	\label{eqn:incompressible}
-\\
 \frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega}
@@
 \\
-\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
+\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1.
 	\label{eqn:bouss_energy}
 \end{gather}
-where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity, and the temperature
-has been decomposed as $T \equiv T_0 + T_1$ where $T_0$ is the initial temperature
-profile. We find Eq. (\ref{eqn:bouss_momentum}) to
-be slightly faster numerically than the standard form in Eq. (\ref{eqn:dim_bouss_momentum}).
-The dimensionless control parameters are set by the Rayleigh and Prandtl numbers,
+where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
+The dimensionless control parameters $\mathcal{P}$ and $\mathcal{R}$ 
+are set by the Rayleigh and Prandtl numbers,
 \begin{equation}
 \mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
-\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\chi} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
+\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
 \end{equation}
-The dimensionless vertical extent of the domain is $z = [-1/2, 1/2]$, and at the top and bottom boundaries
-we impose no-slip, impenetrable boundary conditions such that $u = v = w = 0$ at $z = \pm 1/2$.
-At the lower boundary, we employ a fixed flux condition such that $\partial T_1 / \partial z = 0$
-at $z = -1/2$, and we impose a fixed temperature condition of $T_1 = 0$ at $z = 1/2$. Both
-horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
-the aspect ratio is $\Gamma = 2$. In our 2D cases, we only examine the $x$ and $z$ dimensions
-and we set $v = \partial_y = 0$.
 
-The chosen thermal boundary conditions at the upper and lower plates
-determine key quantities of the evolved state.
-Studies of incompressible, Boussinesq, \RB convection often
-employ fixed temperature (Dirichlet) or fixed heat flux
-(Neumann) boundary conditions at both plates.  
-Dirichlet conditions represent plates of infinite conductivity,
-whereas Neumann conditions model plates of finite conductivity.  
-Both types of conditions
-transport heat in the same manner \cite{johnston&doering2009},
-at least when the upper and lower conditions are symmetric.
+We study 2D and 3D convection in which the domain is a cartesian box, 
+whose dimensionless vertical extent is $z \in [-1/2, 1/2]$, 
+and which is horizontally period with an extent of $x, y \in [0, \Gamma]$ where $\Gamma = 2$ is the aspect
+ratio. 
+In the 2D cases, we set $v = \partial_y = 0$.
+We specify no-slip, impenetrable boundary conditions at both the top and
+bottom boundary and we use mixed thermal boundary conditions, such that
+\begin{equation}
+u = v = w \, \, \text{at}\,\,z = \pm 1/2, \qquad T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
+\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=-1/2.
+\label{eqn:bcs}
+\end{equation}
+For this choice of boundary conditions, the critical value of Ra at which
+the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$, and the
+supercriticality of a run is defined as $S \equiv \text{Ra}/\text{Ra}_{\text{crit}}$.
 Studies of convection which aim to model
-astrophysical systems such as stars often employ a mixture of these
-two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.  
-The flux at the lower boundary is fixed, modeling
-the constant energy generation of the stellar core, 
-while the outer boundary condition is held at a fixed temperature,
-modeling the stellar surface which must output the energy generated internally.
-This setup is a useful model for understanding natural
-systems, but simulations which employ these boundary conditions suffer from a long 
-thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
-Dirichlet condition.  We choose these mixed conditions in part to better understand them, and in
-part because these conditions minimize the number of assumptions that must be made in
-setting up the boundary value problem.  For this choice of boundary conditions, the
-critical Ra is Ra$_{\text{crit}} = 1295.78$, and we will often speak in terms of the
-supercriticality, $S = \text{Ra}/\text{Ra}_{\text{crit}}$.
+astrophysical systems such as stars often employ mixed thermal
+boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017},
+as we do here; however, our choice of thermal boundary conditions here
+reflects the fact that the conditions in Eqn. \ref{eqn:bcs} are the simplest
+to implement in the process of accelerated evolution (see section \ref{subsection:ae})
+we study here.
 
-\subsection{The Boundary Value Problem}
+We utilize the 
+Dedalus\footnote{\url{http://dedalus-project.org/}} 
+pseudospectral framework \cite{burns&all2016} to evolve  
+Eqns. (\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}) 
+forward in time
+using an implicit-explicit (IMEX), third-order, four-step 
+Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
+The linear terms (on the LHS of the equations) are solved implicitly,
+while the nonlinear terms (RHS) are explicitly solved.
+Variables are time-evolved on a dealiased Chebyshev (vertical)
+and Fourier (horizontal, periodic) domain in which the
+physical grid dimensions are 3/2 the size of the coefficient grid.
+
+As initial conditions, we fill $T_1$ with
+random white noise whose magnitude is $10^{-6}\mathcal{P}$.
+This ensures that the initial perturbations are much smaller than the
+evolved convective temperature perturbations, even at large Ra.
+We filter this noise spectrum in coefficient space, 
+such that only the lower 25\% of the coefficients
+have power.
+
+\subsection{The method of accelerated evolution}
+\label{subsection:ae}
+Here we describe a method of Accelerated Evolution (AE), and compare it to Standard Evolution
+(SE).
+It is reasonable to assume that convection will evolve the mean temperature profile that
+drives it over the course of a thermal diffusion time, $t_\chi = \mathcal{P}^{-1}$. Thus, as Ra
+increases, the timescale for achieving a thermally converged mean temperature profile becomes intractable.
+This prohibitively long thermal timescale in an Initial Value Problem (IVP)
+can be skipped by coupling the IVP with a simple Boundary Value Problem
+(BVP) solve. By using information about the convecting dynamical state of an unconverged solution,
+a BVP can be used to solve for the evolved system state.
+A comparison of a simulation running for the thermal timescale, and another where a BVP is used
+to fast-forward atmospheric evolution, are shown in Fig \ref{fig:time_trace}a\&b.
+
 \begin{figure}[t]
@@
 \end{figure}
-
-It is reasonable to assume that convection will evolve the mean temperature profile that
-drives it over the course of a thermal diffusion time, $t_\chi = \mathcal{P}^{-1}$. Thus, as Ra
-increases, the timescale for achieving a thermally converged mean temperature profile becomes intractable.
-This prohibitively long thermal timescale in an Initial Value Problem (IVP)
-can be skipped by coupling the IVP with a simple Boundary Value Problem
-(BVP) solve. By using information about the convecting dynamical state of an unconverged solution,
-a BVP can be used to solve for the evolved system state.
-A comparison of a simulation running for the thermal timescale, and another where a BVP is used
-to fast-forward atmospheric evolution, are shown in Fig \ref{fig:time_trace}a\&b.
 
@@
 are appropriately adjusted, they can be used in the BVP solve to find $\angles{T}$ and $\angles{\varpi}$.
-
-In general, the BVP solve is completed in the following steps:
-\begin{enumerate}
-\item Run the convective IVP. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
-wait for 50 freefall time units.  
-\item Start taking the averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$, waiting either
-30 freefall time units or until the average profiles change by no more than 1 part in 1000 on a
-given timestep, whichever is a more difficult criterion. This ensures that
-the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
-\item Construct $\angles{w T_1}_{\text{steady}}$, $\xi$, and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
-from the flux profiles.
-\item Solve for $\angles{T_1}$ and \angles{\varpi} of the
-evolved state.  Adjust the mean profiles in the IVP.
-\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{\xi}$ in the IVP. 
-\item Continue running the IVP for freefall 50 time units to allow for the velocities to equilibrate to their new background state.
-\item Repeat steps 2-6 to complete a second BVP and get closer to the right solution now that we
-are far from the very unstable transient period.
-\item Take averages for the amount of time specified for the given run in Appendix \ref{section:appendix_table}.
-\end{enumerate}
-
-\subsection{Numerics}
-We utilize the 
-Dedalus\footnote{\url{http://dedalus-project.org/}} 
-pseudospectral framework \cite{burns&all2016} to time-evolve  
-(\ref{eqn:incompressible})-(\ref{eqn:bouss_energy}) 
-using an implicit-explicit (IMEX), third-order, four-step 
-Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
-The linear terms (on the LHS of the equations) are solved implicitly,
-while the nonlinear terms (RHS) are explicitly solved.
-The temperature field is decomposed as $T = T_0(z) + T_1(x, y, z, t)$
-and the velocity is $\bm{u} = w\bm{\hat{z}} + u\bm{\hat{x}} + v\bm{\hat{y}}$.
-In our 2D runs, $v = 0$.
-Variables are time-evolved on a dealiased Chebyshev (vertical)
-and Fourier (horizontal, periodic) domain in which the
-physical grid dimensions are 3/2 the size of the coefficient grid.
-
-As initial conditions, we fill $T_1$ with
-random white noise whose magnitude is $10^{-6}(\text{Ra Pr})^{-1/2}$.
-This ensures that the initial perturbations are much smaller than the
-evolved convective temperature perturbations, even at large Ra.
-We filter this noise spectrum in coefficient space, 
-such that only the lower 25\% of the coefficients
-have power.
 
@@
 \section{Table of Runs}
-\label{section:appendix_table}
+\label{appendix:run_table}
 \begin{center}
@@
 
+\section{Accelerated Evolution Recipe}
+\label{appendix:recipe}
+In general, the BVP solve is completed in the following steps:
+\begin{enumerate}
+\item Run the convective IVP. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
+wait for 50 freefall time units.  
+\item Start taking the averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$, waiting either
+30 freefall time units or until the average profiles change by no more than 1 part in 1000 on a
+given timestep, whichever is a more difficult criterion. This ensures that
+the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
+\item Construct $\angles{w T_1}_{\text{steady}}$, $\xi$, and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
+from the flux profiles.
+\item Solve for $\angles{T_1}$ and \angles{\varpi} of the
+evolved state.  Adjust the mean profiles in the IVP.
+\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{\xi}$ in the IVP. 
+\item Continue running the IVP for freefall 50 time units to allow for the velocities to equilibrate to their new background state.
+\item Repeat steps 2-6 to complete a second BVP and get closer to the right solution now that we
+are far from the very unstable transient period.
+\item Take averages for the amount of time specified for the given run in Appendix \ref{section:appendix_table}.
+\end{enumerate}
+
 \bibliography{biblio.bib}

### 2018-02-14 code/plotting/time_trace.py

@@ -101,27 +101,11 @@ for i in range(4):
         axes.append(plt.subplot(gs.new_subplotspec(*gs_info[i])))
         axes_share.append(axes[-1].twinx())
 #Overlaying bold areas on time traces
-this_label = '{}_0'.format(ra_runs, i)
-t = info[this_label]['sim_time']
-ke = info[this_label]['KE_scalar']
-ie = info[this_label]['IE_scalar'] + 0.5
-axes[0].plot(t[(t > 50)*(t <=100)], ke[(t > 50)*(t <=100)], c='orange', lw=4)
-axes_share[0].plot(t[(t > 50)*(t <=100)], ie[(t > 50)*(t <=100)], c='orange', lw=4)
+axes[0].fill_between(np.linspace(-10, 70, 10), 1e-5, 1e15, color='orange', alpha=1)
+axes[1].fill_between(np.linspace(-10, 70, 10), 1e-5, 1e15, color='orange', alpha=1)
 
-this_label = '{}_2'.format(ra_runs, i)
-t = info[this_label]['sim_time']
-ke = info[this_label]['KE_scalar']
-ie = info[this_label]['IE_scalar'] + 0.5
-axes[0].plot(t, ke, c='green', lw=4)
-axes_share[0].plot(t, ie, c='green', lw=4)
-
-this_label = '{}_3'.format(ra_runs, i)
-t = info[this_label]['sim_time']
-ke = info[this_label]['KE_scalar']
-ie = info[this_label]['IE_scalar'] + 0.5
-axes[1].plot(t, ke, c='green', lw=4)
-axes_share[1].plot(t, ie, c='green', lw=4)
-
+axes[0].fill_between(np.linspace(1.14e4, 1e5, 10), 1e-5, 1e15, color='green', alpha=0.4)
+axes[1].fill_between(np.linspace(410, 915, 10), 1e-5, 1e15, color='green', alpha=0.4)
 # Time traces
 for i in range(4):
     this_label = '{}_{}'.format(ra_runs, i)
@@ -132,6 +116,7 @@ for i in range(4):
         t_bvp_ind = np.argmax(df) + 1
         df[t_bvp_ind-1] = 0
         t_bvp_ind2 = np.argmax(df) + 1
+       
[…]

### 2018-02-14 tex/bvp_paper.tex
restructures AE method section. Done for today. more tomorrow, and making it sound pretty.

@@
 \end{equation}
+We hold Pr$ = 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.
 
@@
 \label{subsection:ae}
-Here we describe a method of Accelerated Evolution (AE), and compare it to Standard Evolution
-(SE).
-It is reasonable to assume that convection will evolve the mean temperature profile that
-drives it over the course of a thermal diffusion time, $t_\chi = \mathcal{P}^{-1}$. Thus, as Ra
-increases, the timescale for achieving a thermally converged mean temperature profile becomes intractable.
-This prohibitively long thermal timescale in an Initial Value Problem (IVP)
-can be skipped by coupling the IVP with a simple Boundary Value Problem
-(BVP) solve. By using information about the convecting dynamical state of an unconverged solution,
-a BVP can be used to solve for the evolved system state.
-A comparison of a simulation running for the thermal timescale, and another where a BVP is used
-to fast-forward atmospheric evolution, are shown in Fig \ref{fig:time_trace}a\&b.
+Here we describe a method of Accelerated Evolution (AE). We use this method to quickly evolve the
+thermodynamic state of our solutions.  We compare this method to Standard Evolution
+(SE), in which we naively evolve the atmosphere for one thermal diffusion time,
+$t_\kappa = \mathcal{P}^{-1}$. As Ra increases, SE solutions become intractable, 
+while the timeframe of convergence for an AE solution remains nearly constant
+(in units of freefall times).
+For an example of time saving achieved by using AE, we compare
+energy traces at $S = 10^5$ from a SE run in Fig \ref{fig:time_trace}a to an AE run
+in Fig. \ref{fig:time_trace}b.
 
@@
 
-The Boussinesq BVP in essence contains equations of hydrostatic balance and thermal equilibrium,
+The horizontally averaged profiles of the vertical conductive flux, 
+F$_{\text{cond}} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective flux,
+F$_{\text{conv}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method. We measure
+both of these quantities early in a simulation, as in Fig. \ref{fig:time_trace}c.
+At these early stages in the simulation, these flux profiles are highly asymmetric,
+with much more flux leaving through the upper boundary than entering through the
+lowe boundary as the atmosphere approaches the proper isotherm selected by the
+fixed temperature upper boundary.
+However, by calculating the total flux,
+F$_{\text{tot}} = $F$_{\text{conv}} +$ F$_{\text{cond}}$, and then calculating the profiles
+\begin{equation}
+f_{\text{conv}}(z) = \frac{F_{\text{conv}}}{F_{\text{tot}}},\qquad
+f_{\text{cond}}(z) = \frac{F_{\text{cond}}}{F_{\text{tot}}},
+\label{eqn:bvp_ratios}
+\end{equation}
+We presume that the early convection occupies roughly the same volume as the evolved
+convection, and thus that the early thermal boundary layers are roughly the proper
+width.  Where $f_{\text{conv}} = 1$, convection dominates all transport, and where
+$F_{\text{cond}} = 1$, conduction dominates all transport (in the boundary
+layers). Under this assumption, the proper evolved atmospheric flux profiles
+are F$_{\text{conv, ev}} = \text{F}_{\text{bot}}\cdot f_{\text{conv}}$
+and F$_{\text{cond, ev}} = \text{F}_{\text{bot}}\cdot f_{\text{cond}}$,
+where F$_{\text{bot}} = \mathcal{P}$ is the amount of flux entering the
+bottom of the atmosphere.
+
+In the evolved, time-stationary state, the horizontal- and time-average of
+Eqns. (\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms that
+vanish due to symmetry, are
 \begin{gather}
-\frac{\partial}{\partial z}\angles{\varpi} - \angles{T_1}\hat{z} = \angles{\bm{u}\times\bm{\omega}},
+\frac{\partial}{\partial z}\angles{\varpi}_{x,y} - \angles{T_1}_{x,y}\hat{z} = \angles{\bm{u}\times\bm{\omega}}_{x,y},
 	\label{eqn:bouss_BVP_momentum}
 \\
-\frac{\partial}{\partial z}\angles{wT_1} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1} = 0,
+\frac{\partial}{\partial z}\text{F}_{\text{conv, ev}} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1}_{x,y} = 0.
 	\label{eqn:bouss_BVP_energy}
 \end{gather}
-where $\angles{A}$ represents a time- and horizontally averaged profile of the quantity $A$.  
-These
-equations arise from assuming that the atmosphere is in a steady state ($\partial_t \rightarrow 0$),
-then taking time and horizontal averages of Eqns (\ref{eqn:bouss_momentum}\&\ref{eqn:bouss_energy}) and
-neglecting terms that vanish due to the symmetry of the problem.
 Convective flows
-are perturbations around a thermal profile defined by these equations in the proper evolved, statistically stationary state.
+are perturbations around a thermal profile defined by these equations in the proper evolved, 
+statistically stationary state. Furthermore, under the specification of
+F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y}$,
+\emph{the mean thermodynamic structure of the system} ($\angles{\varpi}_{x,y},\,\angles{T_1}_{x,y}$)
+\emph{is fully specified}.
 
-Under eqns (\ref{eqn:bouss_BVP_momentum}\&\ref{eqn:bouss_BVP_energy}), 
-the thermal structure ($\angles{T_1}$, $\angles{\varpi}$) of the atmosphere is fully determined by the specification
-of two profiles: the convective flux, $F_{conv} = \angles{w T_1}$, and the nonlinear advection, $\angles{\bm{u}\times\bm{\omega}}$.  
-If these profiles are known, then 
-solving for $\angles{T_1}$ and
-$\angles{\varpi}$ depends only upon the choice of boundary conditions.
-
-By definition, the profile of $F_{\text{conv}}$ is not in a time stationary state early in the IVP.  
-In fact, as the atmosphere approaches the
-isotherm specified by the upper (fixed $T$) boundary condition, the motions display an asymmetric flux as energy
-leaks through the upper boundary condition (Fig. \ref{fig:time_trace}c) in order to reach a lower temperature state.
-In order to construct the evolved convective flux from the current fluxes in the atmosphere,
-we assume that the atmospheric dynamics have properly developed the thickness of the boundary layers.
-In other words, if we know the quantities $F_{\text{conv}}$, $F_{\text{cond}} = \angles{-P \partial_z T}$,
-and $F_{\text{tot}} = F_{\text{conv}} + F_{\text{cond}}$, we assume that the profiles
-\begin{equation}
-f_{\text{conv}}(z) = \frac{F_{\text{conv}}}{F_{\text{tot}}},\qquad
-f_{\text{cond}}(z) = \frac{F_{\text{cond}}}{F_{\text{tot}}}
-\label{eqn:bvp_ratios}
-\end{equation}
-early in the evolution are the same as they will be in the final steady state solution. By definition, the
-evolved total flux through the atmosphere must be the same as the flux entering the atmosphere at the
-bottom boundary, $F_{\text{tot, steady}} = F_{\text{bot}}$.  The proper convective flux profile to use in
-Eqn. (\ref{eqn:bouss_BVP_energy}) is then 
-$\angles{w T_1}_{\text{steady}} = F_{\text{tot, steady}} \cdot f_{\text{conv}}$.
-
-In order to carry the converged amount of flux appropriately, 
-the velocity field and temperature fluctuations in the system must be scaled by a quantity
-$\xi(z) = \angles{w T_1}_{\text{steady}}/\angles{w T_1}$.  Thus, we multiply the velocities
+The AE method is thus simple: we construct F$_{\text{conv, ev}}$ as described above.
+Then we calculate a profile, 
+$\xi(z) = \text{F}_{\text{conv, ev}}/\text{F}_{\text{conv}}$, which is the amount that the
+flux in the system needs to be reduced by, as a function of height.
+We multiply the velocities
 and the thermal fluctuations, $T - \angles{T}$, by $\sqrt{\xi}$, such that the product of all fluctuations
-(which carry the convective flux) are diminished by a factor of $\xi$.  This also means that
-$\angles{\bm{u}\times\bm{\omega}}_{\text{steady}} = \xi \angles{\bm{u}\times\bm{\omega}}$. Once these profiles
-are appropriately adjusted, they can be used in the BVP solve to find $\angles{T}$ and $\angles{\varpi}$.
+(which carry the convective flux) are diminished by a factor of $\xi$.  We solve
+Eqns. (\ref{eqn:bouss_BVP_momentum}-\ref{eqn:bouss_BVP_energy}) with F$_{\text{conv, ev}}$
+and $\xi\cdot\angles{\bm{u}\times\bm{\omega}}_{x,y}$ for the mean thermodynamic state,
+and then continue evolving in time.  This adjustment of the mean profile and the
+diminishing of velocities and fluctuations is the AE method, and it can generally
+be applied tens of buoyancy times after the peak of convective transient.
 

### 2018-02-15 tex/bvp_paper.tex
some work on clobbering the results section (totally rewrote it, need to do fig captions / conclusion / appendices)

@@
 \label{sec:results}
-While Fig. \ref{fig:time_trace} shows us that the post-BVP and post-rundown solutions
-exhibit similar system energies and fluxes, it is important to examine other aspects of
-the evolved solution. The BVP mainly serves to adjust the thermodynamic state of the solution;
-in \RB convection, this means that the evolved temperature profile is a good measure of whether
-or not the BVP achieves the proper solution.
+We study evolved solutions achieved through the SE method from convective onset
+up to $S = 10^5$ in 2D and $S = 10^4$ in 3D.  These SE runs are compared to
+AE runs spanning from onset up to $S = 10^7$ in 2D and $S = 10^4$ in 3D.
+For a full list of simulations, we refer the reader to appendix \ref{appendix:run_table}.
 
-\begin{figure}[t]
-\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
-\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
-$S = 10^{4 + 2/3}$ are shown.  (a) Evolved temperature profiles, as a function of height.
-(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
-(c) Probability distributions of point-by-point measurements of $T$ throughout the two domains over the
-averaging windows are shown.  The cumulative distribution functions are overplotted and the maximum
-difference between them in 0.0407. This difference arises due to the imperfect alignment of the
-mean domain temperatures, but it is clear that otherwise the statistics are quite similar.
-\label{fig:temp_comparison} }
-\end{figure}
-
-The temperature profiles of a 2D run at $S = 10^{4 + 2/3}$ 
-for both the BVP solve and the long rundown are shown in
-Fig. \ref{fig:temp_comparison}a.  While they are not perfectly aligned they are within less than
-0.25\% of each other throughout the depth of the atmosphere, as shown in Fig. \ref{fig:temp_comparison}b.
-While the mean temperature profile is interesting, the point-by-point fluctuations in the
-temperature are what lead to convective transport, and thus examining the spread of temperature
-and the allowed values that it can take are important to characterizing the system.  As seen
-in Fig. \ref{fig:temp_comparison}c, aside from the noticeable difference in the mode of the
-temperatures, the two runs exhibit largely the same spread of temperatures.
-(AUTHOR NOTE: we aren't quite sure how to do a KS test properly here, but we can at least
-list the KS statistic -- currently this is in the caption.)
-
-In addition to examining the thermodynamics of the solutions, we are especially interested in
-determining if the post-BVP solution appropriately captures key features of the nonlinear dynamics.
-We show point-by-point probability distributions of the horizontal velocity, vertical velocity,
-and nonlinear transport in Fig. \ref{fig:pdf_comparison}.  All of these measures have a sharp
-peak at zero due to the no-slip, impenetrable boundary conditions and the denser grid sampling
-near the boundaries of our Chebyshev grid.  Regardless, we see that the velocities of the 
-two solutions are largely consistent.  The nonlinear transport in Fig. \ref{fig:pdf_comparison}c
-shows that the rundown solution experiences a larger number of energetic, extreme events,
-but the BVP displays a larger number of moderately energetic events than the IVP (as
-evidenced by the differences in the cumulative distribution functions).
-
-\begin{figure}[b]
-\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{Probability distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
-vertical transport (c) are shown for a 2D run at $S = 10^{4 + 2/3}$.  We sample flows every 0.1 time units for 500 freefall
-times, and include the flows at all points on the grid at each of these samples in these distributions.  All
-distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
-Chebyshev grids near the boundaries, so there is a large peak around zero. 
-The cumulative distribution function is overplotted on each plot, with a maximum difference of
-(a) 0.027, (b) 0.0061, and (c) 0.035. There is an excess of higher-flux carrying
-elements in the BVP solution than in the IVP rundown, despite the rundown's distribution
-having more powerful, rare events.
-\label{fig:pdf_comparison} }
-\end{figure}
-
-The goodness of this method has been tested across a broad range of supercriticality.  We have
-examined both Rundown and BVP solutions in the range $S = [10^{1/3}, 10^5]$ in 2D and
-$S = [10^1, 10^4]$ in 3D.  We have also further explored up to $S = 10^6$
-(AUTHOR NOTE: we're going up to $10^8$ in 2D right now, need to mention this is state of
-the art and give refs).
-We show the volume averaged Nusselt number, RMS Reynolds number, and mean temperature in
-the evolved BVP solutions in in Fig. \ref{fig:parameter_space_comparison}a-c.
-The relative error of the BVP measurements of these values is compared to the IVP
-measurements for these values in Fig. \ref{fig:parameter_space_comparison}d-f.
-
-In Fig. \ref{fig:parameter_space_comparison}a, we show the Nusselt number scaling in 2D and
-3D.  We use a classic definition of the Nusselt number
-to measure the heat transport in these systems, where
+We report the time- and volume-averaged values of select measurements of the
+evolved solutions in Fig. \ref{fig:parameter_space_comparison}.  We report
+the scaling of heat transport in the evolved solution, as quantified by the
+Nusselt number, in Fig. \ref{fig:parameter_space_comparison}a.
+The volume averaged Nusselt number is defined as
 \begin{equation}
 \text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
- = \frac{\angles{wT - (\text{Ra Pr})^{-1/2}\grad T}}{\angles{- (\text{Ra Pr})^{-1/2} \grad T}}.
+ = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}}.
 \end{equation}
-At small values of $S$, we achieve a steady state solution with a clear value of Nu.  Near
-$S \sim 10^3$, our simulations begin to achieve a horizontally oscillatory state.  Due to the
-use of no-slip boundaries, these states never give way to full scale shearing states, but they
-do reduce the overall heat transport through the system and cause the systems to oscillate between
-periods of high- and low- heat transport.  The vertical lines represent the standard deviation 
-of Nu associated with these oscillations, while the error bars show the drift of the mean
-value of Nu over the averaging window.  We find that $\text{Nu} \propto \text{Ra}^{1/5}$,
-a weaker scaling law than that seen in traditional \RB convection \cite{johnston&doering2009},
-but similar to that seen in shearing states [cite Goluskin].
-(AUTHOR NOTE: Ben, I think this is entirely because of the oscillatory states.  I wonder what
-would happen if we included viscous fluxes...)
+In 3D and in 2D when $S < 10^{3+2/3}$, the evolved system is defined by a clear
+value of Nu and the convection reaches a statistically stationary state.
+In 2D and at larger values of $S$, the value of Nu oscillates as a function of time
+as the plumes in the solution oscillate horizontally.  Our choice of no-slip
+boundary conditions prevent the fluid from entering a full-fledged shearing state
+\cite{goluskin&all2014}, but the oscillatory motions which do arise cause the
+system to vary between periods of low heat transport and high heat transport.
+The SE simulations which span up to $S = 10^5$ exhibit the same horizontally
+oscillatory motion as the AE solutions for the same initial conditions. The
+scaling of the mean value of Nu is roughly $\text{Nu} \propto \text{Ra}^{1/5}$,
+weaker than that reported in similar systems with fixed-T and fixed-flux boundary
+conditions \cite{johnston&doering2009}.  We attribute this weaker Nu scaling to
+the oscillatory nature of the plumes, which may have been avoided by previous studies
+using bootstrapping techniques as initial conditions.
 
-In Fig. \ref{fig:parameter_space_comparison}b, we measure the rms Reynolds number, where
-$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  We find that this scales roughly as
-$\text{Re} \propto \text{Ra}^{0.45}$.
+In Fig. \ref{fig:parameter_space_comparison}b, we report the rms Reynolds number
+in the AE solutions, where
+$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measure scales roughly as
+$\text{Re} \propto \text{Ra}^{0.45}$, and shows little variance with time.
 
-In Fig. \ref{fig:parameter_space_comparison}c, we measure the volume averaged 
-temperature of our solution, then subtract out the value at the upper (fixed $T$) boundary.
-If the atmosphere were perfectly isothermal, this value would be exactly zero.  Thus, this is
-a measure of the temperature jump across the boundary layers, and it provides insight both
-into whether or not the temperature profiles of two runs are the same and into whether
-the fluxes through the two systems are the same (it is in some ways an alternate measure of Nu
-[cite King 2009 supp materials]).
-We find that this measure is $\propto \text{Ra}^{-1/5}$, approaching zero, as expected.
+In Fig. \ref{fig:parameter_space_comparison}c, we report the volume averaged 
+temperature of the AE solutions, with the value at the upper (fixed $T$) boundary removed.
+This measurement probes the thickness of the boundary layers of the solutions, and
+should show scaling which is inversely proportional to Nu in converged solutions
+where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
+that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
+scaling of Nu, giving confidence that these solutions are in a converged state.
 
-For each of these measurements, the BVP achieves the same value as the IVP to
-within about 3\% (Fig. \ref{fig:parameter_space_comparison}d-f).  This is good agreement,
-and the residuals have a scattered distribution of positive and negative values, indicating
-that the method is not biased towards the wrong answer in a clear manner.
+In Fig. \ref{fig:parameter_space_comparison}d-f, we report the fractional difference
+between measurements from the AE solutions and measurements from the SE solutions.
+We find that the mean value of Nu from AE solutions is accurate to the values
+from SE solutions to within $\sim 1$\%, and the same is true for $\angles{T}$ measurements.
+Re measurements show slightly greater error, with AE measurements being on average
+$\leq 2$\% away from the SE measurements.
 
@@
 \end{figure}
+
+The measurements presented in Fig. \ref{fig:parameter_space_comparison} demonstrate
+that the AE method can be powerfully employed in parameter space studies in which
+large numbers of simulations are compared in a volume-averaged sense.  We now turn
+our examination to a more direct comparison of AE and SE for convection at
+$S = 10^5$, as has been introduced in Fig. \ref{fig:time_trace}.
+
+As the AE method primarily serves to adjust the thermodynamic structure of the
+solution, we compare the temperature profile attained by AE and SE in 
+Fig. \ref{fig:temp_comparison}.  We see that the boundary layer length scale is 
+nearly identical in the AE and SE solution (Fig. \ref{fig:temp_comparison}a), but that
+the mean temperature in the interior differs by about 0.5\% on average
+(Fig. \ref{fig:temp_comparison}b). The probability distribution function of point-by-point
+temperature values are compared in Fig. \ref{fig:temp_comparison}c.  We construct
+this PDF by interpolating our temperature field onto a regular grid, determing the
+frequency distribution of all $T$ values, and then properly normalizing such that
+the integral of the PDF is unity.  In addition to the
+difference in mode which can be seen in the mean vertical profile, the SE case
+has a broader spread of temperature values.  This can likely be attributed to the
+slight overstabilization of the temperature profile obtained by the AE method
+(as can be seen in Fig. \ref{fig:time_trace}a\&b).  One means of comparing two
+probability distributions to determine if they are drawn from the same underlying
+sample is through the use of a Kolmogorov-Smirnov (KS) \cite{wall&jenkins2012}.
+In general, a KS test must be conducted on independent, uncorrelated data, which
+poorly describes the point-by-point values of flow in a fluid simulation. Thus,
+we will merely use the KS statistic, the maximum difference
+between the cumulative distribution functions (CDFs) of the two sample distributions,
+as a numerical method of directly comparing the two PDFs.  For the distributions
+shown in Fig. \ref{fig:temp_comparison}c,
+we find a KS statistic of 0.113 near the modes, which is large, and implies that
+these two distributions are different.
+
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
+\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
+$S = 10^{5}$ are shown.  (a) Evolved temperature profiles, as a function of height.
+(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
+(c) Probability distributions of point-by-point measurements of $T$ throughout the two domains over the
+averaging windows are shown.  The cumulative distribution functions are overplotted and the maximum
+difference between them in 0.0407. This difference arises due to the imperfect alignment of the
+mean domain temperatures, but it is clear that otherwise the statistics are quite similar.
+\label{fig:temp_comparison} }
+\end{figure}
+
+In addition to comparing the thermodynamic state achieved by the SE and AE methods,
+we examine the velocities found in the evolved states.
+We compute PDFs in the same manner as in Fig. \ref{fig:temp_comparison}c for the
+vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
+and the nonlinear convective flux (Fig. \ref{fig:pdf_comparison}c). We report KS statistics
+of 0.0577, 0.858, and 0.0347, respectively.  Perhaps unsurpisingly, the nonlinear
+convective transport between the SE and AE methods are very similar, as is captured
+in a volume-averaged sense in the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d).
+In general, the velocity boundary conditions (Eqn. \ref{eqn:bcs}) more strongly dominate the flow
+fields for the SE cases than the AE cases in Fig. \ref{fig:pdf_comparison}a\&c. 
+This suggests that the velocity boundary layers are not yet fully formed in the
+AE solutions. However, aside from this difference, the two solutions show a similar
+distribution of realized velocity values.
+
+\begin{figure}[b]
+\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
+\caption{Probability distribution functions of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
+convective transport are shown for a 2D runs achieved through the SE and AE methods
+at $S = 10^{5}$.  Flows are sampled every 0.1 time units for 500 total time units,
+and flows are interpolated onto an evenly spaced grid before sampling.
+The cumulative distribution function is overplotted on each plot. 
+\label{fig:pdf_comparison} }
+\end{figure}
+
+Despite differences between the SE and AE solutiosn for the case studied in 
+Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
+the AE method is still extremely powerful.  The first application of the AE method
+($t \approx 70$ in Fig. \ref{time_trace}b) immediately increases the 
+average time step of our solver by a factor of 2-3. At higher supercriticality
+($S = 10^7$), the AE solve immediately boosts the timestep by nearly a factor of 4.
+Thus, not only does this method evolve the solution into nearly the correct state, 
+but further time evolution (either to achieve precisely the correct thermodynamic
+state or to take measurements of fluid quantities) happens more efficiently.
 

### 2018-02-15 code/plotting/parameter_space_comparison.py

@@ -208,11 +208,11 @@ gs_info = (((500,0), 400, 250), ((500, 370), 400, 250), ((500, 750), 400, 250))
 for i,k in enumerate(fields):
     ax = plt.subplot(gs.new_subplotspec(*gs_info[i]))
     if i == 0:
-        ax.annotate(r'$\mathrm{(d)}$', (2e3, 0.015), fontsize=10)
+        ax.annotate(r'$\mathrm{(d)}$', (1.3e3, 0.014), fontsize=10)
     if i == 1:
-        ax.annotate(r'$\mathrm{(e)}$', (2e3, 0.015), fontsize=10)
+        ax.annotate(r'$\mathrm{(e)}$', (1.3e3, 0.014), fontsize=10)
     if i == 2:
-        ax.annotate(r'$\mathrm{(f)}$', (2e3, 0.015), fontsize=10)
+        ax.annotate(r'$\mathrm{(f)}$', (1.3e3, 0.014), fontsize=10)
     mean_lists = []
     for j in range(len(base_dirs)):
         ra_list = []
@@ -262,11 +262,11 @@ for i,k in enumerate(fields):
     ax.set_xlim(1e3, 1e10)
     ax.set_xlabel('Ra')
     if i == 0:
-        ax.set_ylabel ('( BVP - IVP ) / IVP')
+        ax.set_ylabel ('( AE - SE ) / SE')
 
-    ax.set_ylim(-0.05, 0.03)
+    ax.set_ylim(-0.02, 0.02)
 
-    ax.set_yticks([-0.04, -0.02, 0, 0.02])
+    ax.set_yticks([-0.01, 0, 0.01])
 
     [t.set_fontsize(10) for t in ax.get_xticklabels()]
     [t.set_fontsize(10) for t in ax.get_yticklabels()]

### 2018-02-15 code/plotting/pdf_comparison.py

@@ -76,7 +76,8 @@ base_dirs_post = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
             ]
 ra_runs = '1.30e8'
-ra_runs = '6.01e7'
+#ra_runs = '6.01e7'
+
 
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_post):
@@ -95,7 +96,7 @@ for a, base_dir in enumerate(base_dirs_post):
         except:
             print('cannot find profile file in {:s}'.format(d))
         try:
-            with h5py.File('{:s}/new_pdfs/slice_pdf_data.h5'.format(d), 'r') as f:
+            with h5py.File('{:s}/slice_pdfs/slice_pdf_data.h5'.format(d), 'r') as f:
             #with h5py.File('{:s}/slice_pdfs/slice_pdf_data.h5'.format(d), 'r') as f:
                 for k in f.keys():
                     info[ra][k+'_pdf'] = f[k].value
@@ -103,7 +104,7 @@ for a, base_dir in enumerate(base_dirs_post):
             print('cannot find pdf file in {:s}'.format(d))
 
 
-
+print(info.keys())
 print(info['{}_0'.format(ra_runs)].keys())
 plt.figure(figsize=(8, 1.5))
 gs     = gridspec.GridSpec(*(1000,1000))
@@ -127,7 +128,7 @@ axes[-1].set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w
 axes[-1].set_xlabel('Vertical Velocity', labelpad=-1)
 axes[-1].set_ylabel('Probability')
 axes[-1].set_yscale('log')
-axes[-1].annotate(r'$\mathrm{(a)}$', (-0.17, 2e1), fontsize=10)
+axes[-1].annotate(r'$\mathrm{(a)}$', (-0.145, 2e1), fontsize=10)
 axes[-1].set_ylim(1e-3, 1e2)
 
 
@@ -171,11 +172,11 @@ axes[-1].plot(info[bvp_label]['u_xs_pdf'], info[bvp_label]['u_pdf_pdf'], c='red'
[…]

### 2018-02-15 code/plotting/temp_comparison.py

@@ -41,7 +41,7 @@ def calculate_CDF(x, pdf):
         cdf[i] = np.sum(d_cdf[:i+1])
     return new_x, cdf
 
-def ks_test(x1, y1, N1, x2, y2, N2, n=1000):
+def ks_test(x1, y1, N1, x2, y2, N2, n=10000):
     x_range = [np.min(x1), np.max(x1)]
     if np.min(x2) > x_range[0]:
         x_range[0] = np.min(x2)
@@ -52,13 +52,21 @@ def ks_test(x1, y1, N1, x2, y2, N2, n=1000):
 
     f1 = interp1d(x1, y1, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
     f2 = interp1d(x2, y2, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
-
+    
     y1_interp = f1(x_points)
     y2_interp = f2(x_points)
+    print(y1 - y2)
     print(y1_interp - y2_interp)
     diff = np.abs(y1_interp - y2_interp)
+
+#    plt.figure()
+#    plt.plot(x_points, diff)
+#    plt.plot(x1, np.abs(y1 - y2))
+#    plt.scatter(x1, np.abs(y1 - y2))
+#    plt.show()
     
     max_diff = np.max(diff)
+    print(max_diff, diff)
     return max_diff, np.sqrt((N1+N2)/(N1*N2))
 
 
@@ -79,7 +87,7 @@ base_dirs_post = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
             ]
 ra_runs = '1.30e8'
-ra_runs = '6.01e7'
+#ra_runs = '6.01e7'
 
 info = OrderedDict()
 for a, base_dir in enumerate(base_dirs_post):
@@ -120,11 +128,11 @@ gs_info = (((0,0), 1000, 267), ((0, 366), 1000, 267), ((0, 733), 1000, 267))
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[0])))
 base_label = '{}_0'.format(ra_runs)
 bvp_label = '{}_1'.format(ra_runs)
[…]

### 2018-02-15 code/plotting/time_trace.py

@@ -104,7 +104,7 @@ for i in range(4):
 axes[0].fill_between(np.linspace(-10, 70, 10), 1e-5, 1e15, color='orange', alpha=1)
 axes[1].fill_between(np.linspace(-10, 70, 10), 1e-5, 1e15, color='orange', alpha=1)
 
-axes[0].fill_between(np.linspace(1.14e4, 1e5, 10), 1e-5, 1e15, color='green', alpha=0.4)
+axes[0].fill_between(np.linspace(1.135e4, 1e5, 10), 1e-5, 1e15, color='green', alpha=0.4)
 axes[1].fill_between(np.linspace(410, 915, 10), 1e-5, 1e15, color='green', alpha=0.4)
 # Time traces
 for i in range(4):
@@ -116,17 +116,21 @@ for i in range(4):
         t_bvp_ind = np.argmax(df) + 1
         df[t_bvp_ind-1] = 0
         t_bvp_ind2 = np.argmax(df) + 1
+        df[t_bvp_ind2-1] = 0
+        t_bvp_ind3 = np.argmax(df) + 1
        
         axes[0].axvline(info['{}_1'.format(ra_runs)]['sim_time'][-1], ls='--', c='k')
         axes[i % 2].plot(info[this_label]['sim_time'][:t_bvp_ind], info[this_label]['KE_scalar'][:t_bvp_ind], c='k')
         axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind:t_bvp_ind2], info[this_label]['KE_scalar'][t_bvp_ind:t_bvp_ind2], c='k')
-        axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind2:], info[this_label]['KE_scalar'][t_bvp_ind2:], c='k')
+        axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind2:t_bvp_ind3], info[this_label]['KE_scalar'][t_bvp_ind2:t_bvp_ind3], c='k')
+        axes[i % 2].plot(info[this_label]['sim_time'][t_bvp_ind3:], info[this_label]['KE_scalar'][t_bvp_ind3:], c='k')
         axes[i % 2].set_yscale('log')
         axes[i % 2].set_ylim(1e-3, 1e-1)
 
[…]

### 2018-02-15 tex/bvp_paper.tex
rough draft of new words is in

@@
 \affiliation{Department of Physics and Astronomy, Bates College, Lewiston, ME 04240, USA}
-\title{Accelerated convergence of convective simulations using boundary value problems}
+\title{Accelerated evolution of convective simulations}
 
@@
 
-\begin{figure}[t]
-\includegraphics[width=\textwidth]{./figs/time_trace.png}
-\caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
-(b) are shown for $S = 10^{4 + 2/3}$.  The horizontal extent of the subplots is set
-such that one simulation time unit takes up an equal amount of paper space in (a) and (b). Volume averaged
-kinetic energy is shown in black, and the volume averaged temperature with the top value removed, is shown
-in red.
-The dashed vertical line on (a) represents the time at which averaging begins in the BVP solution in (b),
-and the horizontal dashed lines show the equilibrium value of the energies. The blue vertical lines represent
-the beginning of the time-averaging window.
-(c) System fluxes early in the run (the orange highlights in (a)) are shown.  
-Black is the sum of the flux, purple
-is the convective flux, and red is the conductive flux.
-(d) Fluxes in the converged rundown IVP compared to the converged BVP.  The sum of flux is shown in
-black \& grey, the convective flux is shown in purple \& pink, and the conductive flux is shown in red \& orange.
-(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, 
-the BVP fluxes deviate from the rundown fluxes by only a few percent of the total flux, and
-are much closer to the converged state than the initial fluxes, as in (c).
-\label{fig:time_trace} }
-\end{figure}
-
 The horizontally averaged profiles of the vertical conductive flux, 
@@
 bottom of the atmosphere.
+
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/time_trace.png}
+\caption{Traces of kinetic energy and mean temperature vs. time for a (a) SE and (b)
+AE run are shown at $S = 10^5$.
+The horizontal extent of the plots is set
+such that one simulation time unit takes up an equal amount of paper space in (a) and (b).
+The mean evolved values are shown as horizontal dashed lines.
+(c) System fluxes shortly after the convective transient are shown, at times corresponding
+to the orange highlighting in (a) and (b).  The sum of the flux is shown in black,
+the convective flux is shown in purple, and the conductive flux is shown in red.
+(d) Fluxes in the evolved AE state are shown, measured during the time highlighted
+in green in (b).  
+(e) The difference between the AE and SE fluxes, measured over the green highlighted
+regions in (a) and (b), are shown.
+Note that the black dashed vertical line in (a) denotes the simulation time at which
+averaging begins for the AE solution shown in (b).
+\label{fig:time_trace} }
+\end{figure}
 
@@
 be applied tens of buoyancy times after the peak of convective transient.
+
+The AE method specified here quickly converges the fluxes within the
+system to within a few percent of the fluxes in a system converged through
+SE (Fig. \ref{fig:time_trace}d \& e).
 
@@
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
-\caption{Scaling plots are shown for the Nusselt number (a), the
-Reynolds number (b), and the volume-averaged temperature (c).  
-Symbols represent the mean value of
-a measurement, vertical lines represent the standard deviation of the measurement over the
-time window, and error bars represent the shift in the mean value over the window.
-(a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
-simulations display horizontally oscillating plumes which have oscillating periods of high transport
-and low transport.  The mean value is marginally diminished as a result, and the variance of Nu with time
-is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
-Ra$^{0.45}$ in 2D and is not distinctly different in 3D. (c) The average temperature flucutation, minus the top
-temperature, which is a scalar measure of the final average thermodynamic state and should approach zero
-in the limit of infinitely large Ra.
-The temperature profile is slow to adjust, and differences between
-BVP solutions and rundown solutions are quite easy to pick out in this measure. (d-f)
-Relative error is shown between the BVP and IVP measurements of Nu (d), Re (e), and the
-mean temperature (f). The grey box indicates the region in which only BVP runs were
-carried out due to computational expense.
+\caption{Volume- and time-averaged measurements for AE runs are shown in (a)-(c).
+Symbols are located at the mean value of
+each measurement, while vertical lines represent the standard deviation of the measurement,
+showing natural variation over the
+averaging window, and error bars represent the change in the mean value over the window,
+such that large error bars would represent a poorly converged solution.
+(a) The Nusselt number scales as $Ra^{1/5}$, and above S$\geq 10^{3+2/3}$,
+simulations exhibit oscillating plume structures whose heat transport varies over time.  
+(b) The RMS Reynolds number, which measures the level of turbulence in the evolved solution, scales as
+Ra$^{0.45}$. (c) Temperature, with its value at the upper boundary removed, is shown.
+Relative error for (d) Nu, (e) Re, and (f) $T$ are shown between measurements 
+taken in AE solutions and SE solutions.
+The greyed area of the plot indicates the region in which only AE runs were
+carried out due to computational expense. The run at $S = 10^5$ marked as a
+black square is examined in more details in Figs. \ref{fig:time_trace},
+\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
 \label{fig:parameter_space_comparison} }
@@
 \includegraphics[width=\textwidth]{./figs/temp_comparison.png}
-\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
-$S = 10^{5}$ are shown.  (a) Evolved temperature profiles, as a function of height.
-(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
-(c) Probability distributions of point-by-point measurements of $T$ throughout the two domains over the
-averaging windows are shown.  The cumulative distribution functions are overplotted and the maximum
-difference between them in 0.0407. This difference arises due to the imperfect alignment of the
-mean domain temperatures, but it is clear that otherwise the statistics are quite similar.
+\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
+at $S = 10^{5}$ are shown.  (a) Evolved temperature profiles, as a function of height.
+(b) The percentage difference between the temperature profiles as a function of height.
+(c) Probability distributions of point-by-point measurements of the temperature field.
+$T$ is sampled every 0.1 time units for 500 total time units,
+and was interpolated onto an evenly spaced grid before sampling.
+The cumulative distribution function is overplotted on each plot. 
 \label{fig:temp_comparison} }
@@
 
-Despite differences between the SE and AE solutiosn for the case studied in 
+Despite differences between the SE and AE solutions for the case studied in 
 Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
@@
 
-\section{Discussion \& Conclusions}
+\section{Extensions of the AE method}
+\label{section:extensions}
+Here we have used \RB convection as a test case for the AE method, but we argue that
+the true power of this method is in its extensions to more complicated studies.
+Such extensions are beyond the scope of this work, but we will briefly describe
+avenues in which extensions to the AE method will be useful.
+For example, in studies of stratified convection where the thermal diffusivity
+is inversely proportional to the density \cite{anders&brown2017}, AE solutions
+will allow for the careful study of a broader range of parameter space. 
+Further, in studies where stable and convecting regions are paired
+\cite{hurlburt&all1986, couston&all2017}, the stable layers cannot rely on convective
+motions to restratify them and instead evolve on the order of the slow thermal
+timescale. In
+fully-convective domains, such as those studied here, the atmosphere evolves
+much more rapidly than the thermal diffusion time (see e.g., Fig. \ref{fig:time_trace}a).
+
+We note also that a further strength of the AE method is its generality.  One
+need only derive the steady-state, horizontally-averaged equations for a given
+equation set (e.g., Eqns. \ref{eqn:bouss_BVP_momentum} \& \ref{eqn:bouss_BVP_energy})
+and couple that information with knowledge of the current dynamics (Eqn. \ref{eqn:bvp_ratios})
+and the boundary conditions. Thus this method can be easily applied to more complex
+systems, and merely require that the experimenter understand the energy transport
+present in their systems.
+
+We have only studied solutions in which we use mixed thermal boundary conditions,
+as in Eqn. \ref{eqn:bcs}. However, this method can be easily applied to fixed-temperature
+boundary conditions, as well.  Rather than knowing the total final flux (F$_{\text{bot}}$)
+through the system a priori, it must be measured using the ratios in
+Eqn. \ref{eqn:bvp_ratios}.  We hesitate to use the AE method for systems in which
+both boundaries fix the flux, as such systems have degenerate solutions for the temperature.
+
+\section{Conclusion}
 \label{sec:discussion}
-The method presented here is a first step towards taking meaningful measurements
-of highly turbulent convection on manageable, human timescales.  As demonstrated in Figs.
-1-4, this BVP method quickly converges simulations to within a few percent of the true final
-state. Furthermore, the total simulation time required to use the BVPs does not change drastically from
-low $S$ to high $S$, so the main prohibition on high Ra states is the difficulty of timesteps becoming
-increasingly small as turbulence increases.  Additionally, post-BVP, we generally see an increase of the
-timestep size by nearly a factor of two due to the less intense driving of the near-converged state that
-is achieved quickly.
+Here we have described a method for converging convective simulations using
+a method of Accelerated Evolution (AE), and compared it to Standard
+Evolution (SE) achieved by running simulations for a thermal timescale.
+We have shown that the AE method produces dynamics that are similar to SE
+dynamics on much shorter timescales, and have discussed differences that arise
+between the two methods.
 
-It is important to note that the measurements made in
-this paper were generally done for short timescales (a few hundred buoyancy times) in
-order to show the precise differences between the BVP solutions and the IVP solutions.
-Where there are differences, the BVP solution is trending towards the IVP solution,
-and if measurements were taken over long timescales (e.g., a thermal time), the
-differences between the BVP solution and IVP solution would be negligible.
+We have shown that the AE method is valid at low values of $S$, in which solutions
+converge quickly, and at high values of $S$, at which SE solutions can take an
+intractable amount of time.  This shows that the AE method not only progresses
+solutions towards the correct evolved state (at high $S$), but it also does not
+throw the simulation out of the correct evolved state (at low $S$).  We have studied
+the AE method in both 2D and 3D, but since the method relies fundamentally on
+1D information from the transient flows, we have restricted most of our study
+to 2D and merely demonstrated the method's efficacy in 3D, too.
 
-One major benefit of the BVP method used here is that it preserves the natural behavior of 
-the convective solution (such as the horizontally oscillatory rolls
-of high-Ra 2D states in Fig. \ref{fig:parameter_space_comparison}).
-One frequently used method of measuring dynamics in high-Ra simulations is that of bootstrapping,
-in which the converged solution of a low-Ra state is used as initial conditions for a higher-Ra
-simulation.  While this method is powerful, it can be influenced by hysteresis effects,
-and the steady rolls achieved at low Ra can result in an artifically over-stable high-Ra
-roll solution.  The BVP method we present here uses random noise initial conditions which allows the
-convective solution to naturally choose the dynamics.
-
-Another benefit of our BVP method is that it can be easily extended to more complicated
-configurations.  For example, to use this method in simulations of stratified compressible convection,
-one need only adapt the BVP equations to the appropriate equations of hydrostatic equilibrium
-and thermal equilibrium obtained by averaging the fully compressible, ideal gas
-steady state momentum and energy equations \cite{anders&brown2017, lecoanet&all2014}.
-In compressible convection, where the density is allowed to change,
-it is also essential to conserve mass by adding boundary conditions on the integrated mas density at
-the upper and lower boundaries, much as stellar structure codes do \cite{paxton&all2011}.
-
-While we have not chosen to use them here, this BVP method can be extended to other boundary conditions.  
-To solve for fixed temperature boundary conditions, the 
-main difficulty is in finding the amount of flux through the system, $F_{\text{tot, steady}}$.
-However, by knowing the averaged value of the conductive flux (from the boundary conditions)
-and the ratios in Eqn. (\ref{eqn:bvp_ratios}), $F_{\text{tot, steady}}$ can be found.
-In the case of
-fixed flux boundary conditions, the temperature solution is degenerate.
-However, using knowledge about the system -- such as the initial symmetry of the
-RB state around $T = 0$, the final solution can be pegged onto the proper profile.
-
-Future work will aim to apply the methods presented here to compressible systems,
-internally heated systems, and systems with more complex forms of the conductive flux.
+This work serves as a first step towards creating robust methods for
+achieving evolved convective solutions at high Ra on short timescales.
+Future studies will extend this method to stratified, fully compressible
+convection \cite{anders&brown2017}, and to systems with internal heating.
 
@@
 \appendix
+\section{Accelerated Evolution Recipe}
+\label{appendix:recipe}
+In order to achieve Accelerated Evolution (AE), we solve a 1D Boundary Value Problem
+consisting of Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
+There are a steps required to properly advance the solution are as follows:
+\begin{enumerate}
+\item Update averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$
+every timestep.  Wait until that average converges. To ensure that an average is converged, at
+least some time $t_{\text{min}}$ must have passed since the average was started, and
+the profiles must change by no more than $P$\% on a given timestep.
+\item Construct F$_\text{conv, ev}$ and $\xi$ as specified in section \ref{subsection:ae}.
+\item Solve for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
+evolved state.  Adjust the profiles in the convecting simulation accordingly
+\item Multiply the velocity field and the fluctuations in $T - \angles{T}_{x,y}$ by $\sqrt{\xi}$ in the IVP. 
+\item Continue running the simulation.
+\end{enumerate}
+We refer to this process as an ``AE BVP solve.''
+
+In general, we find that repeating this method multiple times is the best way to
+ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
+waited for 50 time units after peak transient, completed an AE BVP solve
+with $t_{\text{min}} = 30$ and $P = 0.1$, waited 50 more time units, and then
+did a second AE BVP solve with the same parameters.
+For all 3D runs and 2D runs in the range $S \in [10^5, 10^6]$,
+we waited 20 time units after peak transient, completed an AE BVP solve
+with $t_{\text{min}} = 20$ and $P = 1$ in order to quickly reach a near-
+converged state and vastly increase our timestep.  After this, we completed
+two AE BVP solves, separated by 30 time units each, with $t_{\text{min}} = 30$
+and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}b).
+At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
+$P = 1$, waiting 20 time units after peak transient and 30 time units between
+the two solves.
+
 \section{Table of Runs}
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X X X X X X}
+\begin{tabularx}{\textwidth}{ X X X X X X X X X X }
 \hline																	
-$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{rundown}}$	&	Nu$_{\text{BVP}}$	\\
+$S$	&	Ra	&	nz	&	nx, ny	&	3D	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
 \hline																	
-$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	128	&	$52.8$	&	100	&	(TBD)	&	(TBD)	\\
-$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	128	&	$77.6$	&	100	&	--	&	--	\\
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	128	&	$114$	&	100	&	--	&	--	\\
-$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	128	&	$167$	&	100	&	--	&	--	\\
-$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	128	&	$245$	&	100	&	--	&	--	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	256	&	$360$	&	100	&	--	&	--	\\
-$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	256	&	$528$	&	100	&	--	&	--	\\
-$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	256	&	$776$	&	100	&	--	&	--	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	512	&	$1.14 \cdot 10^3$	&	200	&	--	&	--	\\
-$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	512	&	$1.67 \cdot 10^3$	&	500	&	--	&	--	\\
-$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	1024	&	$2.45 \cdot 10^3$	&	500	&	--	&	--	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	1024	&	$3.60 \cdot 10^3$	&	500	&	--	&	--	\\
-$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	1024	&	$5.28 \cdot 10^3$	&	500	&	--	&	--	\\
-$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	1024	&	$7.76 \cdot 10^3$	&	500	&	--	&	--	\\
-$10^5$	&	$1.30 \cdot 10^8$	&	512	&	2048	&	$1.14 \cdot 10^4$	&	500	&	--	&	--	\\
-$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	2048	&	$1.67 \cdot 10^4$	&	500	&	--	&	--	\\
-$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	2048	&	$2.45 \cdot 10^4$	&	500	&	--	&	--	\\
-$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	4096	&	$3.60 \cdot 10^4$	&	500	&	--	&	--	\\
+$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	FALSE	&	$52.8$	&	100	&	1.46	&	1.46	\\
+$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	FALSE	&	$77.6$	&	100	&	1.95	&	1.95	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	FALSE	&	$114$	&	100	&	2.43	&	2.42	\\
+$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	FALSE	&	$167$	&	100	&	2.54	&	2.54	\\
+$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	FALSE	&	$245$	&	100	&	3.14	&	3.14	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	FALSE	&	$360$	&	100	&	3.8	&	3.8	\\
+$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	FALSE	&	$528$	&	100	&	4.71	&	4.71	\\
+$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	FALSE	&	$776$	&	100	&	5.5	&	5.5	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	FALSE	&	$1.14 \cdot 10^3$	&	200	&	6.4	&	6.33	\\
+$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	FALSE	&	$1.67 \cdot 10^3$	&	500	&	6.87	&	6.95	\\
+$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	FALSE	&	$2.45 \cdot 10^3$	&	500	&	7.54	&	7.59	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	FALSE	&	$3.60 \cdot 10^3$	&	500	&	8.83	&	8.83	\\
+$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	FALSE	&	$5.28 \cdot 10^3$	&	500	&	10.13	&	10.14	\\
+$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	FALSE	&	$7.76 \cdot 10^3$	&	500	&	11.65	&	11.69	\\
+$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
+$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$1.67 \cdot 10^4$	&	500	&	N/A	&	16.21	\\
+$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$2.45 \cdot 10^4$	&	500	&	N/A	&	18.58	\\
+$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	FALSE	&	$3.60 \cdot 10^4$	&	500	&	N/A	&	22.132	\\
+$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	FALSE	&	$1.14 \cdot 10^5$	&	200	&	N/A	&	TBD	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64,64	&	TRUE	&	$114$	&	100	&	2.42	&	2.42	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128,128	&	TRUE	&	$360$	&	100	&	3.97	&	4	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256,256	&	TRUE	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512,512	&	TRUE	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
 \hline																	
@@
 
-\section{Accelerated Evolution Recipe}
-\label{appendix:recipe}
-In general, the BVP solve is completed in the following steps:
-\begin{enumerate}
-\item Run the convective IVP. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
-wait for 50 freefall time units.  
-\item Start taking the averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$, waiting either
-30 freefall time units or until the average profiles change by no more than 1 part in 1000 on a
-given timestep, whichever is a more difficult criterion. This ensures that
-the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
-\item Construct $\angles{w T_1}_{\text{steady}}$, $\xi$, and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
-from the flux profiles.
-\item Solve for $\angles{T_1}$ and \angles{\varpi} of the
-evolved state.  Adjust the mean profiles in the IVP.
-\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{\xi}$ in the IVP. 
-\item Continue running the IVP for freefall 50 time units to allow for the velocities to equilibrate to their new background state.
-\item Repeat steps 2-6 to complete a second BVP and get closer to the right solution now that we
-are far from the very unstable transient period.
-\item Take averages for the amount of time specified for the given run in Appendix \ref{section:appendix_table}.
-\end{enumerate}
-
 \bibliography{biblio.bib}

### 2018-02-15 code/plotting/parameter_space_comparison.py

@@ -52,6 +52,8 @@ for a, base_dir in enumerate(base_dirs):
             with h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(d), 'r') as f:
                 for k in fields:
                     info[ra][k] = f[k].value
+                    if 'Nu' in k:
+                        print(a, 'Nu', ra, np.mean(f[k].value))
                 info[ra]['sim_time'] = f['sim_time'].value
         except:
             print('cannot find file in {:s}'.format(d))
@@ -138,6 +140,8 @@ for i,k in enumerate(fields):
             ax.vlines(ra_list, ymin=min_list/ra_list**p, ymax=max_list/ra_list**(p), color=[color]*len(min_list), zorder=j)
             ax.scatter(ra_list, mean_list/ra_list**(p), s=s,  color=color, marker=mrkr, zorder=j)
             ax.errorbar(ra_list, mean_list/ra_list**p, yerr=np.array((mean_list-m_min_list, m_max_list-mean_list))/ra_list**p,  ecolor=color, fmt='none', zorder=j)
+            ind = ra_list == 1.30e8
+            ax.scatter(ra_list[ind], mean_list[ind]/ra_list[ind]**(p), s=s*1.5,  color='black', marker='s', zorder=1e10)
 
         elif k == 'Nu':
             p = pNu
@@ -145,12 +149,16 @@ for i,k in enumerate(fields):
             ax.vlines(ra_list, ymin=min_list/ra_list**p, ymax=max_list/ra_list**(p), color=[color]*len(min_list), zorder=j)
             ax.scatter(ra_list, mean_list/ra_list**(p), s=s,  color=color, marker=mrkr, zorder=j, label=label)
             ax.errorbar(ra_list, mean_list/ra_list**p, yerr=np.array((mean_list-m_min_list, m_max_list-mean_list))/ra_list**p,  ecolor=color, fmt='none', zorder=j)
+            ind = ra_list == 1.30e8
+            ax.scatter(ra_list[ind], mean_list[ind]/ra_list[ind]**(p), s=s*1.5,  color='black', marker='s', zorder=1e10)
         elif k == 'Re':
             p = pRe
[…]

### 2018-02-15 code/plotting/temp_comparison.py

@@ -141,7 +141,7 @@ axes[-1].set_yticks(y_ticks)
 #Plot 2
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[1])))
 
-axes[-1].plot(info[base_label]['z_profile'], 100*np.abs(info[base_label]['T_profile'][0,:] - info[bvp_label]['T_profile'][0,:])/np.abs(info[base_label]['T_profile'][0,:]))
+axes[-1].plot(info[base_label]['z_profile'], 100*np.abs(info[base_label]['T_profile'][0,:] - info[bvp_label]['T_profile'][0,:])/np.abs(info[base_label]['T_profile'][0,:]), c='k')
 y_ticks = np.array([0, 0.2, 0.40, 0.6])
 axes[-1].set_yticks(y_ticks)
 x_ticks = np.array([0, 0.5, 1])

### 2018-02-21 tex/bvp_paper.tex
figure overhauls

@@
 \begin{abstract}
-We present a method for coupling boundary value problems (BVPs) with initial value problems (IVPs)
-in order to achieve thermally converged convective solutions on dynamical timescales, rather than the
-long thermal timescale. We study this method in the context of \RB convection. 
-We demonstrate that the solution reached by BVP and the
-solution reached by a long thermal rundown of the IVP are similar, and demonstrate that this method works at a
-large range of supercriticalities.  The BVP method is used to achieve converged solutions at high supercriticality ($10^8$),
-and its extensions to more complex scenarios are discussed.
+We present a method for coupling boundary value problems with initial value problems 
+in order to achieve Accelerated Evolution (AE) of convective solutions on
+dynamical timescales, rather than the long thermal timescale. 
+We study this method in the context of \RB convection. 
+We demonstrate that the solution reached by AE and Standard Evolution (SE) are
+similar, and that this method works at a
+large range of supercriticalities.  The AE method is used to achieve converged 
+solutions at high supercriticality ($10^7$), and its extensions to more complex 
+systems are briefly discussed.
 \end{abstract}
@@
 prohibit numericists from studying realistic models of natural systems.  For example,
-flows in the Sun's convection zone range from a Mach number (Ma) of order unity
-near the solar surface to order $10^{-5}$ deep in the solar interior.
+flows in the convection zone of stars like the Sun are often at low Mach number
+(Ma) deep in the interior.
 Explicit methods which are bound by the Courant-Friedrich-Lewy
 (CFL) timestep limit must resolve the fastest motions (sound
-waves and surface convection), resulting in timesteps which are prohibitively
+waves), resulting in timesteps which are prohibitively
 small for studies of the deep, low-Ma motions. These systems are numerically
-stiff. Even in the absence of the fast surface motions, the disparity between
-the sound crossing time and the deep flows have made studies of low-Ma stellar
+stiff, and the disparity between
+the sound crossing time and the convective flows have made studies of low-Ma stellar
 convection difficult. Traditionally, approximations such as
@@
 
-While solutions to problem of disparate dynamical timescales have proven useful,
+While solutions to problem of disparate \emph{dynamical} timescales have proven useful,
 the difference between convective timescales and system relaxation timescales remains
@@
 by increasing into the high-Rayleigh-number (Ra) regime,
-the thermal diffusion timescale on which the system relaxes grows with respect
-to the dynamical timescale, which stays roughly constant across all Ra
-\cite{anders&brown2017}.
-Solar convection is, once again, a prime example of this phenomenon.
-Dynamical timescales in the Solar convective zone are relatively short 
+the ratio of the thermal diffusion timescale to dynamical timescales
+grows \cite{anders&brown2017}.
+Solar convection is a prime example of this phenomenon.
+Dynamical timescales in the solar convective zone are relatively short 
 (10 min overturn at solar surface, one month solar
@@
 Furthermore, as dynamical and diffusive timescales separate, 
-simulations become more turbulent. More turbulent motions 
+simulations become more turbulent. Increasingly turbulent motions 
 require finer grid meshes and smaller timesteps
@@
 low Ra solution imprint onto the dynamics of the new, high Ra solution. 
-In moderate-Ra simulations, a commonly-used tactic is to use 
+Another commonly-used tactic in
+moderate-Ra simulations is to use 
 a simple model of the full convective state as initial conditions.  
@@
 In certain systems, 
-the approximate state of the evolved solution can be estimated, and there an
+the approximate state of the evolved solution can be estimated. There, an
 appropriate set of initial conditions can either be solved for analytically
@@
 convective solution with knowledge about energy balances in the eventual solution
-to self-consistently adjust the mean thermodynamic profile towards. 
+to self-consistently adjust the mean thermodynamic profile towards its final state. 
 While such a method has been used previously \cite{hurlburt&all1986}, 
@@
 examine select simulations at very high Ra which have achieved accelerated evolution. Finally,
-in section \ref{sec:discussion}, we discuss extensions of the methods presented
-here to stratified, compressible systems.
+in section \ref{sec:extensions}, we discuss extensions of the methods presented here,
+and we offer concluding remarks in section \ref{sec:conclusion}.
 
@@
 In non-dimensional form, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
-are
+become
 \begin{gather}
-\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega}
+\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega},
 	\label{eqn:bouss_momentum}
@@
 whose dimensionless vertical extent is $z \in [-1/2, 1/2]$, 
-and which is horizontally period with an extent of $x, y \in [0, \Gamma]$ where $\Gamma = 2$ is the aspect
+and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$ where $\Gamma = 2$ is the aspect
 ratio. 
@@
 \begin{equation}
-u = v = w \, \, \text{at}\,\,z = \pm 1/2, \qquad T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
+u = v = w = 0 \, \, \text{at}\,\,z = \pm 1/2, \qquad T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
 \frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=-1/2.
@@
 F$_{\text{cond}} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective flux,
-F$_{\text{conv}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method. We measure
+F$_{\text{conv}} = \angles{w(T_0 + T_1)}_{x,y}$, where $\angles{}_{x,y}$ represent
+a horizontal average, are the basis of the AE method. We measure
 both of these quantities early in a simulation, as in Fig. \ref{fig:time_trace}c.
@@
 with much more flux leaving through the upper boundary than entering through the
-lowe boundary as the atmosphere approaches the proper isotherm selected by the
-fixed temperature upper boundary.
+lower boundary as the atmosphere approaches the proper isotherm selected by the
+fixed temperature upper boundary condition.
 However, by calculating the total flux,
@@
 \end{equation}
+we remove the asymmetry and examine which parts of the atmosphere are dominated
+by conduction, and which are not.
 We presume that the early convection occupies roughly the same volume as the evolved
@@
 width.  Where $f_{\text{conv}} = 1$, convection dominates all transport, and where
-$F_{\text{cond}} = 1$, conduction dominates all transport (in the boundary
+$f_{\text{cond}} = 1$, conduction dominates all transport (in the boundary
 layers). Under this assumption, the proper evolved atmospheric flux profiles
@@
 be applied tens of buoyancy times after the peak of convective transient.
+For specifics on the precise implementation of the AE method, we refer
+the reader to appendix \ref{appendix:recipe}.
 
@@
 shown in Fig. \ref{fig:temp_comparison}c,
-we find a KS statistic of 0.113 near the modes, which is large, and implies that
+we find a KS statistic of 0.185 near the modes, which is large, and implies that
 these two distributions are different.
@@
 and the nonlinear convective flux (Fig. \ref{fig:pdf_comparison}c). We report KS statistics
-of 0.0577, 0.858, and 0.0347, respectively.  Perhaps unsurpisingly, the nonlinear
+of 0.00615, 0.0349, and 0.0204, respectively.  Perhaps unsurpisingly, the nonlinear
 convective transport between the SE and AE methods are very similar, as is captured
@@
 the AE method is still extremely powerful.  The first application of the AE method
-($t \approx 70$ in Fig. \ref{time_trace}b) immediately increases the 
+($t \approx 70$ in Fig. \ref{fig:time_trace}b) immediately increases the 
 average time step of our solver by a factor of 2-3. At higher supercriticality
@@
 \section{Extensions of the AE method}
-\label{section:extensions}
+\label{sec:extensions}
 Here we have used \RB convection as a test case for the AE method, but we argue that
@@
 \section{Conclusion}
-\label{sec:discussion}
+\label{sec:conclusion}
 Here we have described a method for converging convective simulations using
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X X X X X X X }
+\begin{tabularx}{\textwidth}{ X X X X X X X X X }
 \hline															
-$S$	&	Ra	&	nz	&	nx, ny	&	3D	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
+$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
 \hline															
-$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	FALSE	&	$52.8$	&	100	&	1.46	&	1.46	\\
-$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	FALSE	&	$77.6$	&	100	&	1.95	&	1.95	\\
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	FALSE	&	$114$	&	100	&	2.43	&	2.42	\\
-$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	FALSE	&	$167$	&	100	&	2.54	&	2.54	\\
-$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	FALSE	&	$245$	&	100	&	3.14	&	3.14	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	FALSE	&	$360$	&	100	&	3.8	&	3.8	\\
-$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	FALSE	&	$528$	&	100	&	4.71	&	4.71	\\
-$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	FALSE	&	$776$	&	100	&	5.5	&	5.5	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	FALSE	&	$1.14 \cdot 10^3$	&	200	&	6.4	&	6.33	\\
-$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	FALSE	&	$1.67 \cdot 10^3$	&	500	&	6.87	&	6.95	\\
-$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	FALSE	&	$2.45 \cdot 10^3$	&	500	&	7.54	&	7.59	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	FALSE	&	$3.60 \cdot 10^3$	&	500	&	8.83	&	8.83	\\
-$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	FALSE	&	$5.28 \cdot 10^3$	&	500	&	10.13	&	10.14	\\
-$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	FALSE	&	$7.76 \cdot 10^3$	&	500	&	11.65	&	11.69	\\
-$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
-$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$1.67 \cdot 10^4$	&	500	&	N/A	&	16.21	\\
-$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$2.45 \cdot 10^4$	&	500	&	N/A	&	18.58	\\
-$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	FALSE	&	$3.60 \cdot 10^4$	&	500	&	N/A	&	22.132	\\
-$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	FALSE	&	$1.14 \cdot 10^5$	&	200	&	N/A	&	TBD	\\
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64,64	&	TRUE	&	$114$	&	100	&	2.42	&	2.42	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128,128	&	TRUE	&	$360$	&	100	&	3.97	&	4	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256,256	&	TRUE	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512,512	&	TRUE	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
+$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	100	&	1.46	&	1.46	\\
+$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	100	&	1.95	&	1.95	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	100	&	2.43	&	2.42	\\
+$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	100	&	2.54	&	2.54	\\
+$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	100	&	3.14	&	3.14	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	100	&	3.8	&	3.8	\\
+$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	$528$	&	100	&	4.71	&	4.71	\\
+$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	$776$	&	100	&	5.5	&	5.5	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	$1.14 \cdot 10^3$	&	200	&	6.4	&	6.33	\\
+$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	$1.67 \cdot 10^3$	&	500	&	6.87	&	6.95	\\
+$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	$2.45 \cdot 10^3$	&	500	&	7.54	&	7.59	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	$3.60 \cdot 10^3$	&	500	&	8.83	&	8.83	\\
+$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	$5.28 \cdot 10^3$	&	500	&	10.13	&	10.14	\\
+$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	$7.76 \cdot 10^3$	&	500	&	11.65	&	11.69	\\
+$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
+$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	500	&	N/A	&	16.21	\\
+$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	500	&	N/A	&	18.58	\\
+$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	500	&	N/A	&	22.132	\\
+$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	200	&	N/A	&	TBD	\\
+\\ \hline \hline								\\							
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64,64	&	$114$	&	100	&	2.42	&	2.42	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128,128	&	$360$	&	100	&	3.97	&	4	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256,256	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512,512	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
 \hline															

### 2018-02-21 code/plotting/parameter_space_comparison.py

@@ -73,7 +73,7 @@ for i,k in enumerate(fields):
     bx = ax.twiny()
     ax.axvline(2.79e8, ls='--', c='k')
     ax.fill_between(np.logspace(np.log10(2.79e8), 15, 2), 1e-5, 1e15, color='grey', alpha=0.4)
-    ax.set_xlim(1e3, 1e10)
+    ax.set_xlim(1e3, 2e10)
     for j in range(len(base_dirs)):
         if j == 0 or j == 2:
             continue
@@ -165,7 +165,7 @@ for i,k in enumerate(fields):
             ax.scatter(float(ra), mean, s=s, marker=mrkr, color=color, alpha=0.75)
     bx.set_xlabel('S')
     ax.legend(fontsize=8, loc='upper left', ncol=2, scatterpoints=1, handlelength=1, frameon=True)
-    ax.grid(which='major')
+#    ax.grid(which='major')
 
     if k == 'IE':
         ax.annotate(r'$\mathrm{(c)}$', (1e9, 3.5e-1), fontsize=10)
@@ -187,7 +187,7 @@ for i,k in enumerate(fields):
         label_end = '-{:.3g}'.format(pRe)
         label_end = '$\\langle\\mathrm{Re}\\rangle$'#\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end))
-        ax.set_ylim(1, 1e4)
+        ax.set_ylim(1, 2e4)
 #        ax.set_title(r'$\langle\mathrm{Re}\rangle \mathrm{Ra}^{-1/2}$', fontsize=10)
 #        ax.set_ylim(1e-1, 3e-1)
     else:
@@ -200,15 +200,15 @@ for i,k in enumerate(fields):
     for j,t in enumerate(ax.get_xticklabels()):
         t.set_visible(0)
 
-    for j,t in enumerate(bx.get_xticklabels()):
-        if j % 2 == 1:
-            t.set_visible(0)
-
     ax.set_xscale('log')
     bx.set_xscale('log')
     ax.set_yscale('log')
     bx.set_yscale('log')
 
+
+    bx.set_xlim(1e3/ra_crit, 2e10/ra_crit)
+    plt.axes(bx)
+    plt.xticks(np.array((1e1, 1e3, 1e5, 1e7)))
 
 
[…]

### 2018-02-21 code/plotting/pdf_comparison.py

@@ -128,8 +128,8 @@ axes[-1].set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w
 axes[-1].set_xlabel('Vertical Velocity', labelpad=-1)
 axes[-1].set_ylabel('Probability')
 axes[-1].set_yscale('log')
-axes[-1].annotate(r'$\mathrm{(a)}$', (-0.145, 2e1), fontsize=10)
-axes[-1].set_ylim(1e-3, 1e2)
+axes[-1].annotate(r'$\mathrm{(a)}$', (-0.145, 3e1), fontsize=10)
+axes[-1].set_ylim(1e-1, 1e2)
 
 
 w_cdf_x_bvp, w_cdf_y_bvp = calculate_CDF(info[bvp_label]['w_xs_pdf'], info[bvp_label]['w_pdf_pdf'])
@@ -138,8 +138,8 @@ w_cdf_x_base, w_cdf_y_base = calculate_CDF(info[base_label]['w_xs_pdf'], info[bv
 share = axes[-1].twinx()
 share.plot(w_cdf_x_bvp, w_cdf_y_bvp, c='darkred', dashes=(5,2), lw=2)
 share.plot(w_cdf_x_base, w_cdf_y_base, c='royalblue', dashes=(4,1.5), lw=2)
-share.set_ylim(0, 1)
-share.set_xlim(np.min(info[bvp_label]['w_xs_pdf']), np.max(info[bvp_label]['w_xs_pdf']))
+share.set_ylim(0, 1.05)
+share.set_xlim(-0.165, 0.165)
 
 for tick in axes[-1].get_xticklabels():
     tick.set_rotation(45)
@@ -172,8 +172,8 @@ axes[-1].plot(info[bvp_label]['u_xs_pdf'], info[bvp_label]['u_pdf_pdf'], c='red'
 axes[-1].set_xlim(np.min(info[bvp_label]['u_xs_pdf']), np.max(info[bvp_label]['u_xs_pdf']))
 axes[-1].set_xlabel('Horizontal Velocity', labelpad=-0.5)
 axes[-1].set_yscale('log')
-axes[-1].annotate(r'$\mathrm{(b)}$', (-0.17, 2e1), fontsize=10)
-axes[-1].set_ylim(1e-3, 1e2)
+axes[-1].annotate(r'$\mathrm{(b)}$', (-0.15, 1.4e1), fontsize=10)
[…]

### 2018-02-21 code/plotting/temp_comparison.py

@@ -161,8 +161,9 @@ axes[-1].set_xticks(x_ticks)
 axes[-1].set_xlabel(r'$T$')
 axes[-1].set_ylabel('Probability')
 axes[-1].set_yscale('log')
-axes[-1].set_xlim(-0.5, np.max(info[base_label]['T_xs_pdf']))
-axes[-1].annotate(r'$\mathrm{(c)}$', (-0.495, 1e2), fontsize=10)
+axes[-1].set_xlim(-0.5, -0.385)#np.max(info[base_label]['T_xs_pdf']))
+axes[-1].annotate(r'$\mathrm{(c)}$', (-0.495, 2e2), fontsize=10)
+axes[-1].set_ylim(1e-2, 1e3)
 
 T_cdf_x_bvp, T_cdf_y_bvp = calculate_CDF(info[bvp_label]['T_xs_pdf'], info[bvp_label]['T_pdf_pdf'])
 T_cdf_x_base, T_cdf_y_base = calculate_CDF(info[base_label]['T_xs_pdf'], info[bvp_label]['T_pdf_pdf'])
@@ -171,8 +172,8 @@ T_cdf_x_base, T_cdf_y_base = calculate_CDF(info[base_label]['T_xs_pdf'], info[bv
 share = axes[-1].twinx()
 share.plot(T_cdf_x_bvp, T_cdf_y_bvp, c='darkred', dashes=(5,2), lw=2)
 share.plot(T_cdf_x_base, T_cdf_y_base, c='royalblue', dashes=(4,1.5), lw=2)
-share.set_ylim(0, 1)
-axes[-1].set_xlim(-0.5, np.max(info[base_label]['T_xs_pdf']))
+axes[-1].set_xlim(-0.5, -0.385)#np.max(info[base_label]['T_xs_pdf']))
+share.set_ylim(0, 1.05)
 share.set_ylabel('CDF', rotation=270, labelpad=10)
 
 

### 2018-02-21 code/plotting/time_trace.py

@@ -29,10 +29,6 @@ import matplotlib.gridspec as gridspec
 import dedalus.public as de
 
 
-COLORS=['indigo', 'orange']
-MARKERS=['s', 'o', 'd', '*']
-MARKERSIZE=[5,4,5,7]
-
 base_dirs_pre = [
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_pre',
             '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_pre'
@@ -77,7 +73,7 @@ for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
             print('cannot find profile file in {:s}'.format(d))
 
 
-plt.figure(figsize=(8, 5))
+plt.figure(figsize=(8, 7.5))
 gs     = gridspec.GridSpec(*(1000,1000))
 
 #####################################
@@ -91,93 +87,130 @@ time_ratio = times[0]/(times[0]+times[1])
 size_1 = int(950 * time_ratio)
 size_2 = int(950 * (1 - time_ratio))
 
-gs_info = (((0,0), 450, size_1), ((0, 950-size_2),450, size_2))
+gs_info = (((30,0), 270, 660), ((30, 680), 270, 320), ((380, 500), 270, 500))
 print(size_1, size_2, gs_info)
 axes = []
 axes_share = []
 
-for i in range(4):
-    if i < 2:
-        axes.append(plt.subplot(gs.new_subplotspec(*gs_info[i])))
-        axes_share.append(axes[-1].twinx())
+for i in range(3):
+    axes.append(plt.subplot(gs.new_subplotspec(*gs_info[i])))
+    axes_share.append(axes[-1].twinx())
 #Overlaying bold areas on time traces
-axes[0].fill_between(np.linspace(-10, 70, 10), 1e-5, 1e15, color='orange', alpha=1)
-axes[1].fill_between(np.linspace(-10, 70, 10), 1e-5, 1e15, color='orange', alpha=1)
+axes[0].fill_between(np.linspace(50, 76, 10), 1e-5, 1e15, color='orange', alpha=1)
+axes[2].fill_between(np.linspace(50, 76, 10), 1e-5, 1e15, color='orange', alpha=1)
 
[…]

### 2018-02-21 tex/bvp_paper.tex
some text cleaning

@@
 
+%%%%%%%%%%%%
+%%%%%%%%%%%
+% INTRO
+%%%%%%%%%%%
+%%%%%%%%%%%%
+
 \section{Introduction}
@@
 prohibit numericists from studying realistic models of natural systems.  For example,
-flows in the convection zone of stars like the Sun are often at low Mach number
-(Ma) deep in the interior.
-Explicit methods which are bound by the Courant-Friedrich-Lewy
+flows in the convection zone of stars like the Sun are characteristically low Mach number
+(Ma) in the deep interior.
+Explicit timestepping methods which are bound by the Courant-Friedrich-Lewy
 (CFL) timestep limit must resolve the fastest motions (sound
@@
 small for studies of the deep, low-Ma motions. These systems are numerically
-stiff, and the disparity between
-the sound crossing time and the convective flows have made studies of low-Ma stellar
+stiff, and the difference between
+the sound crossing time and the convective overturn time have made studies of low-Ma stellar
 convection difficult. Traditionally, approximations such as
@@
 
-While solutions to problem of disparate \emph{dynamical} timescales have proven useful,
-the difference between convective timescales and system relaxation timescales remains
-a significant problem facing studies of convection. 
+While solutions to the problem of divergent \emph{dynamical} timescales have proven useful,
+the difference between convective timescales and thermal timescales, which
+characterize system relaxation, remain a significant problem facing studies of convection. 
+Solar convection is a prime example of this phenomenon;
+dynamical timescales in the solar convective zone are relatively short 
+(10 min overturn at solar surface, one month solar
+rotation rate) compared to the Kelvin-Helmholtz timescale of
+$3 \cdot 10^7$ years \cite{stix2003}.  
+In such a system, it is impossible to resolve the convective dynamics while also
+evolving the thermal structure of the system in a meaningful fashion.
 As modern simulations aim to model natural convection
@@
 grows \cite{anders&brown2017}.
-Solar convection is a prime example of this phenomenon.
-Dynamical timescales in the solar convective zone are relatively short 
-(10 min overturn at solar surface, one month solar
-rotation rate) compared to the Kelvin-Helmholtz timescale of
-$3 \cdot 10^7$ years \cite{stix2003}.  
-Furthermore, as dynamical and diffusive timescales separate, 
+Furthermore, as dynamical and thermal timescales separate, 
 simulations become more turbulent. Increasingly turbulent motions 
@@
 
-The vast difference between convective and diffusive timescales has long plagued
-numericists studying convection, and a plethora of approaches has been employed to
+The vast difference between convective and thermal timescales has long plagued
+numericists studying convection, and an abundance of approaches has been employed to
 study thermally converged solutions. One popular method for accelerating the convergence
-of high-Ra solutions is by ``Bootstrapping,'' or the process of using the flow
+of high-Ra solutions is by ``bootstrapping'' -- the process of using the flow
 fields in a converged solution at lower Ra as initial conditions for a simulation at a higher
@@
 
-Despite the plethora of methods that have been used,
+Despite the numerous methods that have been used,
 the most straightforward way to achieve a thermally converged solution
@@
 and we offer concluding remarks in section \ref{sec:conclusion}.
+
+%%%%%%%%%%%%
+%%%%%%%%%%%
+% EXPERIMENT
+%%%%%%%%%%%
+%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%
+%%%%%%%%%%%
+% AE METHOD
+%%%%%%%%%%%
+%%%%%%%%%%%%
+
 \subsection{The method of accelerated evolution}
@@
 SE (Fig. \ref{fig:time_trace}d \& e).
+
+%%%%%%%%%%%%
+%%%%%%%%%%%
+% RESULTS
+%%%%%%%%%%%
+%%%%%%%%%%%%
 
@@
 
-\section{Extensions of the AE method}
+%%%%%%%%%%%%
+%%%%%%%%%%%
+% CONCLUSION
+%%%%%%%%%%%
+%%%%%%%%%%%%
+
+\section{Extensions \& Conclusion}
 \label{sec:extensions}
-Here we have used \RB convection as a test case for the AE method, but we argue that
+In this work we have used \RB convection as a test case for the AE method, but we argue that
 the true power of this method is in its extensions to more complicated studies.
-Such extensions are beyond the scope of this work, but we will briefly describe
-avenues in which extensions to the AE method will be useful.
-For example, in studies of stratified convection where the thermal diffusivity
-is inversely proportional to the density \cite{anders&brown2017}, AE solutions
-will allow for the careful study of a broader range of parameter space. 
-Further, in studies where stable and convecting regions are paired
-\cite{hurlburt&all1986, couston&all2017}, the stable layers cannot rely on convective
-motions to restratify them and instead evolve on the order of the slow thermal
-timescale. In
-fully-convective domains, such as those studied here, the atmosphere evolves
-much more rapidly than the thermal diffusion time (see e.g., Fig. \ref{fig:time_trace}a).
+Such extensions are beyond the scope of this paper, but we will briefly describe
+areas in which extensions to the AE method should be explored.
+We note that a strength of the AE method is its generality.  One
+need only derive the steady-state, horizontally-averaged equations for a given
+equation set (e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
+and couple that information with knowledge of the current dynamics (Eqn. (\ref{eqn:bvp_ratios}))
+and the boundary conditions. Thus this method can be easily applied to more complex
+systems, so long as the experimenter understand the energy transport
+present in their systems.
 
-We note also that a further strength of the AE method is its generality.  One
-need only derive the steady-state, horizontally-averaged equations for a given
-equation set (e.g., Eqns. \ref{eqn:bouss_BVP_momentum} \& \ref{eqn:bouss_BVP_energy})
-and couple that information with knowledge of the current dynamics (Eqn. \ref{eqn:bvp_ratios})
-and the boundary conditions. Thus this method can be easily applied to more complex
-systems, and merely require that the experimenter understand the energy transport
-present in their systems.
+In studies of stratified convection where the thermal diffusivity
+is inversely proportional to the density \cite{anders&brown2017}, the
+thermal timescale deep in the atmosphere is much larger than the timescale
+near the surface.  Thus, the AE method can be a very important tool for studying
+highly stratified systems which aim to model realistic astrophysical atmospheres.
+Through carefully examining the flux in excess of the flux conducted along the
+adiabatic temperature gradient, the fractions of Eqn. (\ref{eqn:bvp_ratios})
+can be constructed for such a system.  In addition to solving for the average
+hydrostatic balance and thermal equilibrium, it is essential to simultaneously
+ensure that mass is conserved in truly stratified systems by adding a 
+mass-conservation equation, similar to those used in stellar structure models
+\cite{paxton&all2011}.
+
+It is common for studies to pair stable and convecting regions
+\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
+In such studies, particularly when the interface between the stable region
+and the convecting region is stiff and motions do not penetrate from the convecting
+region into the stable region, the stable region cannot rely on convective
+motions to assist in the restratification of the thermal profile.
+In fully-convective domains, such as those studied here, the atmosphere evolves
+much more rapidly than the thermal diffusion time (see e.g., Fig. \ref{fig:time_trace}a,
+where the SE solution is essentially fully converged after $4\cdot 10^3$ frefall units
+despite the thermal timescale being roughly $10^4$ frefall units).
 
@@
 through the system a priori, it must be measured using the ratios in
-Eqn. \ref{eqn:bvp_ratios}.  We hesitate to use the AE method for systems in which
+Eqn. \ref{eqn:bvp_ratios}.  The integrated conductive flux is known in these systems exactly thanks 
+to the fixed temperature jump across the domain.  The total flux through the system
+($F_{\text{bot}}$) can is thus $\mathcal{P} / \int f_{\text{cond}} dz$ (double-check).
+We hesitate to use the AE method for systems in which
 both boundaries fix the flux, as such systems have degenerate solutions for the temperature.
 
-\section{Conclusion}
-\label{sec:conclusion}
-Here we have described a method for converging convective simulations using
+In conclusion, here we have described a method for converging convective simulations using
 a method of Accelerated Evolution (AE), and compared it to Standard
@@
 $10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
-$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	500	&	N/A	&	16.21	\\
-$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	500	&	N/A	&	18.58	\\
-$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	500	&	N/A	&	22.132	\\
-$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	200	&	N/A	&	TBD	\\
+$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	500	&	--	&	16.21	\\
+$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	500	&	--	&	18.58	\\
+$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	500	&	--	&	22.13	\\
+$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	200	&	--	&	40.78	\\
 \\ \hline \hline \\															
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64,64	&	$114$	&	100	&	2.42	&	2.42	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128,128	&	$360$	&	100	&	3.97	&	4	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256,256	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512,512	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	100	&	2.42	&	2.42	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128$\times$128	&	$360$	&	100	&	3.97	&	4	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256$\times$256	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512$\times$512	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
 \hline															

### 2018-02-23 tex/bvp_paper.tex
overhaul of conclusionss

@@
 in section \ref{sec:extensions}, we discuss extensions of the methods presented here,
-and we offer concluding remarks in section \ref{sec:conclusion}.
+and we offer concluding remarks.
 
@@
 \includegraphics[width=\textwidth]{./figs/time_trace.png}
-\caption{Traces of kinetic energy and mean temperature vs. time for a (a) SE and (b)
-AE run are shown at $S = 10^5$.
-The horizontal extent of the plots is set
-such that one simulation time unit takes up an equal amount of paper space in (a) and (b).
-The mean evolved values are shown as horizontal dashed lines.
-(c) System fluxes shortly after the convective transient are shown, at times corresponding
-to the orange highlighting in (a) and (b).  The sum of the flux is shown in black,
-the convective flux is shown in purple, and the conductive flux is shown in red.
-(d) Fluxes in the evolved AE state are shown, measured during the time highlighted
-in green in (b).  
-(e) The difference between the AE and SE fluxes, measured over the green highlighted
-regions in (a) and (b), are shown.
-Note that the black dashed vertical line in (a) denotes the simulation time at which
-averaging begins for the AE solution shown in (b).
+\caption{A time trace is shown of kinetic energy (black) and mean temperature (blue)  vs. time 
+for an SE run at $S = 10^5$ (a). The mean evolved values of kinetic energy and mean temperature
+are denoted by the horizontal dashed black and blue lines. 
+By taking an average of the fluxes early in the
+simulation (b), and appropriately using the AE method described here, the evolution
+of these atmospheres can be greatly accelerated. The time trace of such an accelerated
+atmosphere, which uses these methods, is shown in (c).  The y-axes and x-axes are
+scaled identically as in (a).  Here, the AE method is used three times, marked by
+the numbered arrows. The fluxes averaged over the green region which begins at
+the vertical dashed line shortly after AE 3 are shown in (c) are shown
+in (d), and they are nearly in the fully evolved state, sampled over a similarly
+long region that occurs much later in the simulation in (a).  The difference between
+the fluxes in the AE and SE ssolutions is shown in (e), and it is small. The dashed
+vertical line in (a) denotes the simulation time at which evolved flux measurements
+begin to be taken in (c).
 \label{fig:time_trace} }
@@
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
-\caption{Volume- and time-averaged measurements for AE runs are shown in (a)-(c).
+\caption{Volume- and time-averaged measurements of the Nusselt number, the
+RMS Reynolds number, and the mean temperature for AE runs are shown in (a)-(c).
 Symbols are located at the mean value of
-each measurement, while vertical lines represent the standard deviation of the measurement,
-showing natural variation over the
-averaging window, and error bars represent the change in the mean value over the window,
-such that large error bars would represent a poorly converged solution.
-(a) The Nusselt number scales as $Ra^{1/5}$, and above S$\geq 10^{3+2/3}$,
+each measurement, vertical lines represent the standard deviation of the measurement,
+which shows natural variation over the
+averaging window, and error bars represent the change in the mean value over the averaging window,
+such that very large error bars represent solutions which are not fully converged when averaging
+begins.
+(a) The Nusselt number scales as Ra$^{1/5}$, and above S$\geq 10^{3+2/3}$,
 simulations exhibit oscillating plume structures whose heat transport varies over time.  
 (b) The RMS Reynolds number, which measures the level of turbulence in the evolved solution, scales as
-Ra$^{0.45}$. (c) Temperature, with its value at the upper boundary removed, is shown.
+Ra$^{0.45}$. (c) Temperature, with its value at the upper boundary removed, is shown,
+and scales as Ra$^{-1/5}$.
 Relative error for (d) Nu, (e) Re, and (f) $T$ are shown between measurements 
@@
 as a numerical method of directly comparing the two PDFs.  For the distributions
-shown in Fig. \ref{fig:temp_comparison}c,
-we find a KS statistic of 0.185 near the modes, which is large, and implies that
-these two distributions are different.
+shown in Fig. \ref{fig:temp_comparison}b,
+we find a KS statistic of 0.495 near the modes, which is very large, and implies that
+about half of the data points examined in the AE run are at lower temperature than 
+at the SE run. However, as shown in Fig. \ref{fig:temp_comparison}d, aside from the
+large difference near the modes, the two CDFs differ by less than one part in a hundred.
 
@@
 \caption{Comparisons of the evolved thermodynamic states of an AE and SE run
-at $S = 10^{5}$ are shown.  (a) Evolved temperature profiles, as a function of height.
-(b) The percentage difference between the temperature profiles as a function of height.
-(c) Probability distributions of point-by-point measurements of the temperature field.
+at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
+temperature profiles, as a function of height.
+(b) Probability Distribution Functions (PDFs) and their integrated
+Cumulative Distribution Functions (CDFs)
+of point-by-point measurements of the temperature field.
+(c) The percentage difference between the mean temperature profiles as a function of height.
+(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
+the AE and SE CDFs, as a function of temperature.
 $T$ is sampled every 0.1 time units for 500 total time units,
 and was interpolated onto an evenly spaced grid before sampling.
-The cumulative distribution function is overplotted on each plot. 
+The difference between the mean profiles is very small O(0.5\%), but this small
+difference results in a large difference between the two temperature CDFs near the values
+of the temperature mode.  The spread of temperature around the mode, or the fluctuations that
+drive convection, are nearly identical between the two runs.
 \label{fig:temp_comparison} }
@@
 equation set (e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
-and couple that information with knowledge of the current dynamics (Eqn. (\ref{eqn:bvp_ratios}))
-and the boundary conditions. Thus this method can be easily applied to more complex
-systems, so long as the experimenter understand the energy transport
-present in their systems.
+and couple that information with knowledge of the boundary conditions
+and current dynamics (as described in
+section \ref{subsection:ae} and appendix \ref{appendix:recipe}).
 
-In studies of stratified convection where the thermal diffusivity
-is inversely proportional to the density \cite{anders&brown2017}, the
-thermal timescale deep in the atmosphere is much larger than the timescale
-near the surface.  Thus, the AE method can be a very important tool for studying
-highly stratified systems which aim to model realistic astrophysical atmospheres.
-Through carefully examining the flux in excess of the flux conducted along the
-adiabatic temperature gradient, the fractions of Eqn. (\ref{eqn:bvp_ratios})
-can be constructed for such a system.  In addition to solving for the average
-hydrostatic balance and thermal equilibrium, it is essential to simultaneously
-ensure that mass is conserved in truly stratified systems by adding a 
-mass-conservation equation, similar to those used in stellar structure models
+One such area in which this method can be applied is to simple studies of
+internally heated convection \cite{goluskin2016}.  The simplest of these studies 
+examine the incompressible Boussinesq equations, as presented in this work,
+but include a constant source term in the energy equation. The evolved convective
+state in such internally heated systems includes a flux profile whose value linearly
+increases with height, as the volumetric heating requires the convection to carry
+more flux towards the top of the domain.  These systems can be straightforwardly
+studied using the methods that we examined here, but scaling the profiles derived
+in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux.
+
+Studies of stratified convection are likely to gain the most through
+developing and employing the AE method.
+In many studies of stratified convection, the thermal diffusivity
+is inversely proportional to the density \cite{anders&brown2017}. Thus, the
+thermal timescale is much larger deep in the atmosphere, where density is high and diffusivity
+is very low, than it is near the surface.  As such, runs at similar supercriticalities
+but with different degrees of stratification can have thermal timescales which
+differ by orders of magnitude.  Fortunately, the AE method is easily adapted to
+the simplest stratified, compressible systems.  Rather than studying the total
+flux through the system, one must only study the flux in excess of the adiabatic
+while constructing the fractions of Eqn. (\ref{eqn:bvp_ratios}).  
+Furthermore, in addition to solving for
+hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
+\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously
+ensure that mass is conserved.  Thus, additional equations and boundary conditions
+must be used to ensure that mass is not created or destroyed,
+in a manner similar to how mass appears in equations in stellar structure codes
 \cite{paxton&all2011}.
 
-It is common for studies to pair stable and convecting regions
+Studies of convection frequently examine paired stable and convecting regions
 \cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
-In such studies, particularly when the interface between the stable region
-and the convecting region is stiff and motions do not penetrate from the convecting
-region into the stable region, the stable region cannot rely on convective
-motions to assist in the restratification of the thermal profile.
-In fully-convective domains, such as those studied here, the atmosphere evolves
-much more rapidly than the thermal diffusion time (see e.g., Fig. \ref{fig:time_trace}a,
-where the SE solution is essentially fully converged after $4\cdot 10^3$ frefall units
-despite the thermal timescale being roughly $10^4$ frefall units).
+When the interface between the stable region
+and the convecting region is stiff and motions do not cross that interface,
+convective motions cannot accelerate the restratification of the stable region.
+In fully-convective domains, such as those studied in this work, the thermodynamics evolve
+at a more rapid rate than the thermal diffusion time across the domain due to
+the help of convective motions.  For example, in Fig. \ref{fig:time_trace}a,
+the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
+despite the thermal timescale being roughly $10^4$ frefall units.
 
-We have only studied solutions in which we use mixed thermal boundary conditions,
-as in Eqn. \ref{eqn:bcs}. However, this method can be easily applied to fixed-temperature
-boundary conditions, as well.  Rather than knowing the total final flux (F$_{\text{bot}}$)
-through the system a priori, it must be measured using the ratios in
-Eqn. \ref{eqn:bvp_ratios}.  The integrated conductive flux is known in these systems exactly thanks 
-to the fixed temperature jump across the domain.  The total flux through the system
-($F_{\text{bot}}$) can is thus $\mathcal{P} / \int f_{\text{cond}} dz$ (double-check).
-We hesitate to use the AE method for systems in which
-both boundaries fix the flux, as such systems have degenerate solutions for the temperature.
+A final area in which we encourage extensions of this method is in the study of systems
+operating in the presence of different thermal boundary conditionss.
+We have studied solutions in which we employ mixed thermal boundary conditions,
+as in Eqn. (\ref{eqn:bcs}). However, the AE method can be easily applied to fixed-temperature
+boundary conditions, as well.  The total evolved flux (F$_{\text{bot}}$)
+through the system is not known a priori, but it can be measured using the ratios in
+Eqn. (\ref{eqn:bvp_ratios}).  The integrated conductive flux is a constant which
+does not change with time due to the fixed temperature jump across the domain.  
+Thus, the total flux through the system can be calculated as 
+$F_{\text{bot}} = \mathcal{P} / \int f_{\text{cond}} dz$. While easily extensible
+to fixed-temperature boundary conditions, we hesitate to use the AE method for 
+fixed-flux boundary conditions.  In those systems, there are infinitely many degenerate
+solutions to the final temperature profile, and the AE method could advance the
+solution into an unrealistic state as a result of an arbitrary user choice on the
+temperature profile's offset.
 
@@
 Evolution (SE) achieved by running simulations for a thermal timescale.
-We have shown that the AE method produces dynamics that are similar to SE
-dynamics on much shorter timescales, and have discussed differences that arise
+We have shown that the AE method produces evolved solutions on short timescales
+whose dynamics are similar to SE solutions, and we have discussed differences that arise
 between the two methods.
@@
 We have shown that the AE method is valid at low values of $S$, in which solutions
-converge quickly, and at high values of $S$, at which SE solutions can take an
+converge quickly and the thermal timescale is short, but that it is also applicable
+at high values of $S$, where SE solutions can take an
 intractable amount of time. This shows that the AE method not only progresses
-solutions towards the correct evolved state (at high $S$), but it also does not
-throw the simulation out of the correct evolved state (at low $S$).  We have studied
-the AE method in both 2D and 3D, but since the method relies fundamentally on
-1D information from the transient flows, we have restricted most of our study
-to 2D and merely demonstrated the method's efficacy in 3D, too.
+solutions towards the correct evolved state (at high $S$), but that it also does not
+remove the simulation from the correct evolved state once such a state is achieved (at low $S$). 
+We have studied
+the AE method in both 2D and 3D, but have restricted most of our study to 2D flows.
+As a result of the AE method depending only on 1D information integrated across
+the horizontal dimensions of the atmosphere, we only examine a select small group
+of 3D simulations to demonstrate the method's efficacy there in addition to in 2D.
 
@@
 achieving evolved convective solutions at high Ra on short timescales.
-Future studies will extend this method to stratified, fully compressible
-convection \cite{anders&brown2017}, and to systems with internal heating.
+In order to study how astrophysical systems change over meaningful
+evolutionary timescales, there are two main approaches.  One-dimensional
+systems which parameterize dynamics can be quickly evolved over thermal timescales.
+However, if the experimenter wants to simultaneously study system evolution
+in the presence of realistic convective dynamics, we now know that it is
+impossible to avoid the constraints that advective dynamics place on
+timestep size \cite{viallet&all2011, viallet&all2013, viallet&all2016}
+in both implicit and explicit methods. We must explore other avenues
+of evolving the system forward on thermal timescales, and this work aims
+as a first step in these explorations.
 
@@
 \label{appendix:recipe}
-In order to achieve Accelerated Evolution (AE), we solve a 1D Boundary Value Problem
+In order to achieve Accelerated Evolution (AE), we pause the Direct Numerical Simulation (DNS)
+which is evolving the dynamics of the convection and solve a 1D Boundary Value Problem (BVP)
 consisting of Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
-There are a steps required to properly advance the solution are as follows:
+After solving this BVP, we adjust the fields being evolved in the DNS appropriately
+towards their evolved state, and then we continue running the now-evolved DNS.
+There specific steps taken in completing the AE method are as follows:
 \begin{enumerate}
-\item Update averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$
-every timestep.  Wait until that average converges. To ensure that an average is converged, at
-least some time $t_{\text{min}}$ must have passed since the average was started, and
+\item After the start of the DNS, we wait some time, $t_{\text{transient}}$ after
+the convective transient in which the dynamics vigorously break away from the hydrostatic
+state.
+\item Then, during the DNS, we calculate time averages of the 1D profiles of
+$F_{\text{conv}}$, $F_{\text{tot}}$, 
+and $\angles{\bm{u} \times \bm{\omega}}_{x,y}$, updating them every timestep.  
+To calculate these
+averages, we use a trapezoidal-rule integration in time, and then divide by the
+total time elapsed over which the average is taken. 
+\item We pause the DNS once the averages are sufficiently converged. 
+To ensure that an average is converged, at
+least some time $t_{\text{min}}$ must have passed since the average was started to
+ensure that the full range of convective dynamics are probed, and
 the profiles must change by no more than $P$\% on a given timestep.
-\item Construct F$_\text{conv, ev}$ and $\xi$ as specified in section \ref{subsection:ae}.
-\item Solve for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
-evolved state.  Adjust the profiles in the convecting simulation accordingly
-\item Multiply the velocity field and the fluctuations in $T - \angles{T}_{x,y}$ by $\sqrt{\xi}$ in the IVP. 
-\item Continue running the simulation.
+\item Construct F$_\text{conv, ev}$ and $\xi$ as specified in section \ref{subsection:ae}
+from the averaged profiles.
+\item Solve the BVP for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
+evolved state.  Set the horizontal average of the current DNS thermodynamic fields
+equal to the results of the BVP.
+\item Multiply the velocity field and the temperature fluctuations, $T - \angles{T}_{x,y}$,
+by $\sqrt{\xi}$ in the DNS to properly reduce the convective flux.
+\item Continue running the DNS
 \end{enumerate}
@@
 
-In general, we find that repeating this method multiple times is the best way to
+While the use of a single AE BVP solve rapidly advances the convecting state to
+one that is closer to the evolved state, we find that repeating this method 
+multiple times is the best way to
 ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
-waited for 50 time units after peak transient, completed an AE BVP solve
-with $t_{\text{min}} = 30$ and $P = 0.1$, waited 50 more time units, and then
-did a second AE BVP solve with the same parameters.
-For all 3D runs and 2D runs in the range $S \in [10^5, 10^6]$,
-we waited 20 time units after peak transient, completed an AE BVP solve
-with $t_{\text{min}} = 20$ and $P = 1$ in order to quickly reach a near-
-converged state and vastly increase our timestep.  After this, we completed
-two AE BVP solves, separated by 30 time units each, with $t_{\text{min}} = 30$
-and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}b).
+set $t_{\text{transient}} = 50$, completed an AE BVP solve
+with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure,
+including another wait of $t_{\text{transient}} = 50$ before beginning averages.
+For all 3D runs and 2D runs with $S \in [10^5, 10^6]$,
+we did a first AE BVP solve with $t_{\text{transient}} = 20$,
+$t_{\text{min}} = 20$, and $P = 1$ in order to quickly reach a near-
+converged state and vastly increase our timestep size.  After this first solve, 
+we completed two AE BVP solves, with $t_{\text{transient}} = 30$,
+$t_{\text{min}} = 30$, 
+and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}c).
 At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
-$P = 1$, waiting 20 time units after peak transient and 30 time units between
-the two solves.
+$P = 1$. For the first solve, we set $t_{\text{transient}} = 20$, and for the
+second we set $t_{\text{transient}} = 30$. We used fewer solves at this high
+value of $S$ in part to reduce the computational expense of the run, and in
+part because of how a third BVP generally did not modify the solution hugely
+(as in Fig. \ref{fig:time_trace}c).
 
@@
 \label{appendix:run_table}
+In Table \ref{table:run_parameters} we list key properties of all simulations
+conducted in this work.  The supercriticality, Rayleigh number, and resolution
+are reported.  We report the simulation run time of the SE solutions and AE
+solutions, as well as the amount of time over which average measurements
+were taken, in freefall time units.  The volume-averaged Nusselt number of the
+AE and SE solutions are shown.
+In the upper part of the table, information pertaining to 2D runs is reported,
+and below the double horizontal bars we report properties of all
+3D runs.
+
+\begin{table}
+\caption{Simulation parameters}
+\label{table:run_parameters}
 \begin{center}
@@
 \end{center}
+\end{table}
 

### 2018-02-23 code/plotting/temp_comparison.py

@@ -57,7 +57,8 @@ def ks_test(x1, y1, N1, x2, y2, N2, n=10000):
     y2_interp = f2(x_points)
     print(y1 - y2)
     print(y1_interp - y2_interp)
-    diff = np.abs(y1_interp - y2_interp)
+    diff_true = y1_interp - y2_interp
+    diff = np.abs(diff_true)
 
 #    plt.figure()
 #    plt.plot(x_points, diff)
@@ -67,7 +68,7 @@ def ks_test(x1, y1, N1, x2, y2, N2, n=10000):
     
     max_diff = np.max(diff)
     print(max_diff, diff)
-    return max_diff, np.sqrt((N1+N2)/(N1*N2))
+    return max_diff, np.sqrt((N1+N2)/(N1*N2)), x_points, diff_true
 
 
 
@@ -115,7 +116,7 @@ for a, base_dir in enumerate(base_dirs_post):
 
 
 print(info['{}_0'.format(ra_runs)].keys())
-plt.figure(figsize=(8, 1.5))
+plt.figure(figsize=(8, 3))
 gs     = gridspec.GridSpec(*(1000,1000))
 
 
@@ -124,49 +125,62 @@ axis_names   = ['x', 'y']
 # Bottom three plots
 #Plot 1
 axes = []
-gs_info = (((0,0), 1000, 267), ((0, 366), 1000, 267), ((0, 733), 1000, 267))
+#gs_info = (((0,0), 1000, 267), ((0, 366), 1000, 267), ((0, 733), 1000, 267))
+gs_info = (((0,0), 650, 450), ((725, 0), 275, 450), ((0, 550), 650, 450), ((725, 550), 275, 450))
 axes.append(plt.subplot(gs.new_subplotspec(*gs_info[0])))
 base_label = '{}_0'.format(ra_runs)
 bvp_label = '{}_1'.format(ra_runs)
-axes[-1].plot(info[base_label]['z_profile'], info[base_label]['T_profile'][0,:],  c='blue', lw=1, label='SE')
-axes[-1].plot(info[bvp_label]['z_profile'], info[bvp_label]['T_profile'][0,:], c='red', lw=1, dashes=(4,1.5), label='AE')
[…]

### 2018-02-23 code/plotting/time_trace.py

@@ -177,29 +177,27 @@ axes[1].set_xlim(1.183e4-590, 1.183e4)
 axes[2].set_xlim(0, 910.6)
 
 
-x_ticks = [0, 250, 500, 750, 1000]
+x_ticks = [250, 500, 750, 1000]
 axes[0].set_xticks(x_ticks)
 x_ticks = [1.133e4, 1.133e4+250, 1.183e4]
 axes[1].set_xticks(x_ticks)
-x_ticks = [0, 250, 500, 750]
+x_ticks = [250, 500, 750]
 axes[2].set_xticks(x_ticks)
 axes[0].set_ylabel(r'$\mathrm{Kinetic\,\, Energy}$', labelpad=-10)
 axes[2].set_ylabel(r'$\mathrm{Kinetic\,\, Energy}$', labelpad=-1)
-axes[0].set_xlabel('Simulation Time (freefall units)', labelpad=0)
-axes[0].xaxis.set_label_coords(0.70, -0.125)
+axes[0].set_xlabel(r'$t/t_{\mathrm{ff}}$ (freefall time)', labelpad=0)
+axes[0].xaxis.set_label_coords(0.24, -0.125)
 x, y = axes[0].xaxis.get_label().get_position()
 print(x, y)
 axes[0].xaxis.get_label().set_position((x/time_ratio, y))
 axes_share[1].set_ylabel(r'$\langle T_1\rangle - T_{\mathrm{top}}$', rotation=270, color='blue', labelpad=15)
-axes_share[2].set_ylabel(r'$\langle T_1\rangle - T_{\mathrm{top}}$', rotation=270, color='blue', labelpad=10)
+axes_share[2].set_ylabel(r'$\langle T_1\rangle - T_{\mathrm{top}}$', rotation=270, color='blue', labelpad=15)
 #for tick in axes[2].get_yticklabels():
 #    tick.set_size(0)
 #axes[2].yaxis.set_ticks_position('none')
 for tick in axes_share[0].get_yticklabels():
     tick.set_size(0)
 for tick in axes[2].get_yticklabels():
-    tick.set_size(0)
-for tick in axes_share[2].get_yticklabels():
     tick.set_size(0)
 axes_share[0].yaxis.set_ticks_position('none')
[…]

### 2018-02-23 tex/bvp_paper.tex
third draft

@@
 prohibit numericists from studying realistic models of natural systems.  For example,
-flows in the convection zone of stars like the Sun are characteristically low Mach number
+flows in the convection zones of stars like the Sun are characteristically low Mach number
 (Ma) in the deep interior.
@@
 
-While solutions to the problem of divergent \emph{dynamical} timescales have proven useful,
-the difference between convective timescales and thermal timescales, which
-characterize system relaxation, remain a significant problem facing studies of convection. 
-Solar convection is a prime example of this phenomenon;
-dynamical timescales in the solar convective zone are relatively short 
+Convective systems with divergent dynamical timescales can now be studied; however,
+thermal timescales, which characterize system relaxation, are often much larger than
+dynamical timescales, and resolving dynamics in atmospheres which are sufficiently
+thermally relaxed remains a challenging problem.
+Solar convection is a prime example of this phenomenon.
+Dynamical timescales in the solar convective zone are relatively short 
 (10 min overturn at solar surface, one month solar
-rotation rate) compared to the Kelvin-Helmholtz timescale of
+rotation rate) compared to the Sun's Kelvin-Helmholtz timescale of
 $3 \cdot 10^7$ years \cite{stix2003}.  
 In such a system, it is impossible to resolve the convective dynamics while also
-evolving the thermal structure of the system in a meaningful fashion.
+evolving the thermal structure of the system in a meaningful fashion using
+traditional timestepping techniques alone.
 As modern simulations aim to model natural convection
 by increasing into the high-Rayleigh-number (Ra) regime,
-the ratio of the thermal diffusion timescale to dynamical timescales
-grows \cite{anders&brown2017}.
+the thermal diffusion timescale becomes intractably large
+compared to dynamical timescales \cite{anders&brown2017}.
 Furthermore, as dynamical and thermal timescales separate, 
@@
 through a single convective overturn time becomes more computationally expensive
-while the number of overturn times required for systems to reach thermal equilibration
+and the number of overturn times required for systems to reach thermal equilibration
 grows.
@@
 of high-Ra solutions is by ``bootstrapping'' -- the process of using the flow
-fields in a converged solution at lower Ra as initial conditions for a simulation at a higher
+fields in a converged solution at low Ra as initial conditions for a simulation at high
 Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
@@
 as initial conditions for convection in a 3D cylinder \cite{verzicco&camussi1997}. 
-In certain systems, 
-the approximate state of the evolved solution can be estimated. There, an
-appropriate set of initial conditions can either be solved for analytically
-\cite{couston&all2017} or by using knowledge of Mixing Length Theory or other convective
-theories to adjust the initial profile towards the proper adiabatic state \cite{brandenburg&all2005}.
+In other systems, 
+the approximate state of the evolved solution can be estimated. There, a
+set of initial conditions which is close to the evolved state be 
+derived analytically \cite{couston&all2017, brandenburg&all2005}.
 
@@
 is to evolve a convective simulation through a thermal timescale. Some modern
-studies do just that \cite{featherstone&hindman2016}, but it is becoming
-increasingly difficult. Such evolution is
+studies do just that \cite{featherstone&hindman2016}.
+However, such evolution is
 \emph{expensive}, and state-of-the-art simulations at the highest values of Ra
-can only be reasonably run
+can only reasonably be run
 for tens to hundreds of buoyancy times \cite{stevens&all2011}, much less the
@@
 
-In this work, we study a method of achieving accelerated evolution of a
-convective simulation through adjusting the thermodynamic state using information 
-from resolved, convective dynamics. We couple measurements of the (non-converged)
-convective solution with knowledge about energy balances in the eventual solution
-to self-consistently adjust the mean thermodynamic profile towards its final state. 
+In this work, we study a method of achieving accelerated evolution of
+convective simulations. We couple measurements of the dynamics of non-converged
+convective simulations with knowledge about energy balances in the desired solution
+to self-consistently adjust the mean thermodynamic profile towards its evolved state. 
 While such a method has been used previously \cite{hurlburt&all1986}, 
@@
 method to those that have been evolved through a full diffusive timescale, and we
-examine select simulations at very high Ra which have achieved accelerated evolution. Finally,
+examine select simulations at high Ra which have achieved accelerated evolution. Finally,
 in section \ref{sec:extensions}, we discuss extensions of the methods presented here,
@@
 has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
-of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$, except on the
-term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, acts in the vertical momentum equation, 
-where $\rho = \rho_0(1  - \alpha T_1)$.  
-Under these constraints, the equations of motion are \cite{spiegel&veronis1960}
+of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$,
+except where it is $\rho = \rho_0(1  - \alpha T_1)$ on the term where
+the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, 
+acts in the vertical momentum equation.
+The equations of motion are \cite{spiegel&veronis1960}
 \begin{gather}
@@
 and $P$ is the pressure.
-We non-dimensionalize these equations such that the dimensionless unit of
-length is the layer height ($L_z$),
+We non-dimensionalize these equations such that the
+length is in units of the layer height ($L_z$),
 temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
 and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
-by these choices, one time unit is a freefall time ($L_z/v_{ff}$).
+by these choices, one time unit is a freefall time ($L_z/v_{\text{ff}}$).
 We introduce a reduced kinematic pressure,
@@
 \\
-\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1.
+\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
 	\label{eqn:bouss_energy}
@@
 whose dimensionless vertical extent is $z \in [-1/2, 1/2]$, 
-and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$ where $\Gamma = 2$ is the aspect
-ratio. 
-In the 2D cases, we set $v = \partial_y = 0$.
+and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$,
+where $\Gamma = 2$ is the aspect ratio. 
+In 2D simulations, we set $v = \partial_y = 0$.
 We specify no-slip, impenetrable boundary conditions at both the top and
@@
 as we do here; however, our choice of thermal boundary conditions here
-reflects the fact that the conditions in Eqn. \ref{eqn:bcs} are the simplest
+reflects the fact that the conditions in Eqn. (\ref{eqn:bcs}) are the simplest
 to implement in the process of accelerated evolution (see section \ref{subsection:ae})
@@
 
-\subsection{The method of accelerated evolution}
+\subsection{The method of Accelerated Evolution}
 \label{subsection:ae}
-Here we describe a method of Accelerated Evolution (AE). We use this method to quickly evolve the
-thermodynamic state of our solutions.  We compare this method to Standard Evolution
+Here we describe a method of Accelerated Evolution (AE), which we use 
+to rapidly evolve the thermodynamic state of convective simulations.  
+We compare this AE method to Standard Evolution
 (SE), in which we naively evolve the atmosphere for one thermal diffusion time,
@@
 while the timeframe of convergence for an AE solution remains nearly constant
-(in units of freefall times).
+in freefall time units.
 For an example of time saving achieved by using AE, we compare
-energy traces at $S = 10^5$ from a SE run in Fig \ref{fig:time_trace}a to an AE run
-in Fig. \ref{fig:time_trace}b.
+energy traces at $S = 10^5$ from a SE run in Fig. \ref{fig:time_trace}a to an AE run
+in Fig. \ref{fig:time_trace}c.
 
@@
 a horizontal average, are the basis of the AE method. We measure
-both of these quantities early in a simulation, as in Fig. \ref{fig:time_trace}c.
-At these early stages in the simulation, these flux profiles are highly asymmetric,
-with much more flux leaving through the upper boundary than entering through the
-lower boundary as the atmosphere approaches the proper isotherm selected by the
-fixed temperature upper boundary condition.
-However, by calculating the total flux,
-F$_{\text{tot}} = $F$_{\text{conv}} +$ F$_{\text{cond}}$, and then calculating the profiles
+both of these quantities early in a simulation, retrieving profiles similar to
+those shown in Fig. \ref{fig:time_trace}b.
+At early stages in the simulation, these flux profiles are highly asymmetric,
+with more flux exiting the atmosphere at the upper boundary than 
+the fixed-flux lower boundary is providing.
+By calculating the total flux,
+F$_{\text{tot}} =$ F$_{\text{conv}} +$ F$_{\text{cond}}$, we derive the profiles
 \begin{equation}
@@
 \end{equation}
-we remove the asymmetry and examine which parts of the atmosphere are dominated
-by conduction, and which are not.
+which have the systematic asymmetries removed. These profiles describe which
+parts of the atmosphere depend on convection to carry flux (where $f_{\text{conv}}(z) = 1$
+and $f_{\text{cond}}(z) = 0$).
 We presume that the early convection occupies roughly the same volume as the evolved
-convection, and thus that the early thermal boundary layers are roughly the proper
-width.  Where $f_{\text{conv}} = 1$, convection dominates all transport, and where
-$f_{\text{cond}} = 1$, conduction dominates all transport (in the boundary
-layers). Under this assumption, the proper evolved atmospheric flux profiles
+convection, and thus that the extent of the early thermal boundary layers 
+(where $f_{\text{cond}}(z) = 1$ and $f_{\text{conv}}(z) = 0$) 
+will not change significantly over the course of the atmosphere's evolution.
+Under this assumption, the proper evolved atmospheric flux profiles
 are F$_{\text{conv, ev}} = \text{F}_{\text{bot}}\cdot f_{\text{conv}}$
@@
 
-In the evolved, time-stationary state, the horizontal- and time-average of
-Eqns. (\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms that
+In a time-stationary state, the horizontal- and time-average of
+Eqns. (\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
 vanish due to symmetry, are
@@
 F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y}$,
-\emph{the mean thermodynamic structure of the system} ($\angles{\varpi}_{x,y},\,\angles{T_1}_{x,y}$)
-\emph{is fully specified}.
+\emph{the mean thermodynamic structure of the system is fully specified}.
 
-The AE method is thus simple: we construct F$_{\text{conv, ev}}$ as described above.
+Thus, the AE method is simple: we construct F$_{\text{conv, ev}}$ as described above.
 Then we calculate a profile, 
-$\xi(z) = \text{F}_{\text{conv, ev}}/\text{F}_{\text{conv}}$, which is the amount that the
-flux in the system needs to be reduced by, as a function of height.
+$\xi(z) = \text{F}_{\text{conv, ev}}/\text{F}_{\text{conv}}$, which is the fraction,
+as a function of height, by which the flux in the system must be reduced to go from
+an initial state (Fig. \ref{fig:time_trace}b) to an evolved state (Fig. \ref{fig:time_trace}d).
 We multiply the velocities
-and the thermal fluctuations, $T - \angles{T}$, by $\sqrt{\xi}$, such that the product of all fluctuations
-(which carry the convective flux) are diminished by a factor of $\xi$.  We solve
-Eqns. (\ref{eqn:bouss_BVP_momentum}-\ref{eqn:bouss_BVP_energy}) with F$_{\text{conv, ev}}$
-and $\xi\cdot\angles{\bm{u}\times\bm{\omega}}_{x,y}$ for the mean thermodynamic state,
-and then continue evolving in time.  This adjustment of the mean profile and the
-diminishing of velocities and fluctuations is the AE method, and it can generally
-be applied tens of buoyancy times after the peak of convective transient.
+and the thermal fluctuations, $T - \angles{T}_{x,y}$, by $\sqrt{\xi}$, such 
+that the advected, flux-carrying perturbations in the temperature are appropriately
+diminished.  We then solve a boundary value problem including
+Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}) using F$_{\text{conv, ev}}$
+and $\cdot\angles{\bm{u}\times\bm{\omega}}_{x,y}$, after diminishing it by a factor
+of $\xi$. We use mixed thermal boundary conditions, as in Eqn. (\ref{eqn:bcs}),
+because $F_{\text{bot}}$ is exactly specified, and the temperature profile is pegged
+at a reference value for the AE solve.
 For specifics on the precise implementation of the AE method, we refer
@@
 
-The AE method specified here quickly converges the fluxes within the
-system to within a few percent of the fluxes in a system converged through
-SE (Fig. \ref{fig:time_trace}d \& e).
+The AE method converges atmospheeres from extreme flux disequilibrium states 
+(Fig. \ref{fig:time_trace}b) on short dynamical timescales (Fig. \ref{fig:time_trace}c)
+to a converged state (Fig. \ref{fig:time_trace}d) whose flux balance is very
+close to the balance present in the corresponding SE solution (Fig. \ref{fig:time_trace}e).
+While the application of the AE method advances solutions toward the proper solution,
+we find that multiple applications of the method is the best means of achieving converged
+solutions quickly.
 
@@
 \label{sec:results}
-We study evolved solutions achieved through the SE method from convective onset
+We study evolved solutions achieved through the standard evolution (SE) method 
+from convective onset
 up to $S = 10^5$ in 2D and $S = 10^4$ in 3D.  These SE runs are compared to
-AE runs spanning from onset up to $S = 10^7$ in 2D and $S = 10^4$ in 3D.
+accelerated evolution (AE) runs spanning from onset up to $S = 10^7$ in 2D and $S = 10^4$ in 3D.
 For a full list of simulations, we refer the reader to appendix \ref{appendix:run_table}.
@@
 We report the time- and volume-averaged values of select measurements of the
-evolved solutions in Fig. \ref{fig:parameter_space_comparison}.  We report
-the scaling of heat transport in the evolved solution, as quantified by the
-Nusselt number, in Fig. \ref{fig:parameter_space_comparison}a.
+evolved solutions in Fig. \ref{fig:parameter_space_comparison}.
+The scaling of heat transport in the evolved solution, as quantified by the
+Nusselt number, is shown in Fig. \ref{fig:parameter_space_comparison}a.
 The volume averaged Nusselt number is defined as
@@
 \text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
- = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}}.
+ = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
 \end{equation}
-In 3D and in 2D when $S < 10^{3+2/3}$, the evolved system is defined by a clear
-value of Nu and the convection reaches a statistically stationary state.
+where $\angles{}$ represent a volume average.
+In 2D when $S < 10^{3+2/3}$ and in 3D, the evolved system is defined by a clear
+value of Nu and the convective heat transport reaches a temporally stationary state.
 In 2D and at larger values of $S$, the value of Nu oscillates as a function of time
-as the plumes in the solution oscillate horizontally.  Our choice of no-slip
-boundary conditions prevent the fluid from entering a full-fledged shearing state
+due to large horizontal oscillations in the convective plume structures.
+Our choice of no-slip
+boundary conditions prevent the fluid from entering a shearing state
 \cite{goluskin&all2014}, but the oscillatory motions which do arise cause the
@@
 using bootstrapping techniques as initial conditions.
-
-In Fig. \ref{fig:parameter_space_comparison}b, we report the rms Reynolds number
-in the AE solutions, where
-$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measure scales roughly as
-$\text{Re} \propto \text{Ra}^{0.45}$, and shows little variance with time.
-
-In Fig. \ref{fig:parameter_space_comparison}c, we report the volume averaged 
-temperature of the AE solutions, with the value at the upper (fixed $T$) boundary removed.
-This measurement probes the thickness of the boundary layers of the solutions, and
-should show scaling which is inversely proportional to Nu in converged solutions
-where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
-that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
-scaling of Nu, giving confidence that these solutions are in a converged state.
-
-In Fig. \ref{fig:parameter_space_comparison}d-f, we report the fractional difference
-between measurements from the AE solutions and measurements from the SE solutions.
-We find that the mean value of Nu from AE solutions is accurate to the values
-from SE solutions to within $\sim 1$\%, and the same is true for $\angles{T}$ measurements.
-Re measurements show slightly greater error, with AE measurements being on average
-$\leq 2$\% away from the SE measurements.
 
@@
 
+In Fig. \ref{fig:parameter_space_comparison}b, we report the volume-averaged
+RMS Reynolds number in the AE solutions, where
+$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measure scales roughly as
+$\text{Re} \propto \text{Ra}^{0.45}$, and shows little variance with time.
+
+In Fig. \ref{fig:parameter_space_comparison}c, we report the volume averaged 
+temperature of the AE solutions, with the value at the upper (fixed $T$) boundary removed.
+This measurement probes the thickness of the boundary layers of the solutions, and
+should show scaling which is inversely proportional to Nu in converged solutions
+where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
+that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
+scaling of Nu, giving confidence that these solutions are in a converged state.
+
+In Fig. \ref{fig:parameter_space_comparison}d-f, we report the fractional difference
+between measurements from the AE solutions and measurements from the SE solutions.
+We find that the mean value of Nu from AE solutions is accurate to the values
+from SE solutions to within $\sim 1$\%, and the same is true for $\angles{T}$ measurements.
+Re measurements show slightly greater error, with AE measurements being on average
+$\leq 2$\% away from the SE measurements.
+
 The measurements presented in Fig. \ref{fig:parameter_space_comparison} demonstrate
@@
 Fig. \ref{fig:temp_comparison}.  We see that the boundary layer length scale is 
-nearly identical in the AE and SE solution (Fig. \ref{fig:temp_comparison}a), but that
+nearly identical between the two solutions (Fig. \ref{fig:temp_comparison}a), but that
 the mean temperature in the interior differs by about 0.5\% on average
-(Fig. \ref{fig:temp_comparison}b). The probability distribution function of point-by-point
-temperature values are compared in Fig. \ref{fig:temp_comparison}c.  We construct
-this PDF by interpolating our temperature field onto a regular grid, determing the
-frequency distribution of all $T$ values, and then properly normalizing such that
-the integral of the PDF is unity.  In addition to the
-difference in mode which can be seen in the mean vertical profile, the SE case
-has a broader spread of temperature values.  This can likely be attributed to the
-slight overstabilization of the temperature profile obtained by the AE method
-(as can be seen in Fig. \ref{fig:time_trace}a\&b).  One means of comparing two
+(Fig. \ref{fig:temp_comparison}c).
+
+The probability distribution functions 
+of point-by-point temperature measurements are compared for the two runs
+in Fig. \ref{fig:temp_comparison}b.  We construct
+this PDF from snapshots of the temperature profile every 0.1 freefall time
+units over a duration of 500 total freefall time units, as shown by the green
+areas if Fig. \ref{fig:time_trace}a\&c.  We interpolate the temperature field
+of each of these snapshots onto an evenly spaced grid, determine the
+frequency distribution of all measured $T$ values, and then normalize the
+distribution such that its integral is unity.  The primary difference between
+the two PDFs is their modes, which is expected from Fig. \ref{fig:temp_comparison}a. 
+The fact that the the AE temperature
+profile is roughly 0.5\% off of the SE temperature profile (\ref{fig:temp_comparison}c), 
+the AE temperature
+field is still marginally evolving towards the SE temperature field, and this
+evolution appears as asymmetry of the AE PDF's peak.
+
+One means of comparing two
 probability distributions to determine if they are drawn from the same underlying
@@
 as a numerical method of directly comparing the two PDFs.  For the distributions
-shown in Fig. \ref{fig:temp_comparison}b,
-we find a KS statistic of 0.495 near the modes, which is very large, and implies that
-about half of the data points examined in the AE run are at lower temperature than 
-at the SE run. However, as shown in Fig. \ref{fig:temp_comparison}d, aside from the
-large difference near the modes, the two CDFs differ by less than one part in a hundred.
+shown in Fig. \ref{fig:temp_comparison}b, the difference between the CDFs is shown
+in Fig. \ref{fig:temp_comparison}d.  The maximum difiference, or the KS statistic,
+is 0.495 near the modes.  This difference is very large, but is not unexpected.
+While the temperature distributions near the modes are very different, their spread
+of perturbations is nearly identical.
 
@@
 we examine the velocities found in the evolved states.
-We compute PDFs in the same manner as in Fig. \ref{fig:temp_comparison}c for the
+We compute PDFs in the same manner as in Fig. \ref{fig:temp_comparison}b for the
 vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
@@
 convective transport between the SE and AE methods are very similar, as is captured
-in a volume-averaged sense in the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d).
-In general, the velocity boundary conditions (Eqn. \ref{eqn:bcs}) more strongly dominate the flow
-fields for the SE cases than the AE cases in Fig. \ref{fig:pdf_comparison}a\&c. 
-This suggests that the velocity boundary layers are not yet fully formed in the
-AE solutions. However, aside from this difference, the two solutions show a similar
-distribution of realized velocity values.
+in a volume-averaged sense in the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
+Each distribution shows a strong peak near zero due to the velocity boundary conditions
+(Eqn. (\ref{eqn:bcs})), but the distribution of flux transport elements and velocities
+is nearly identical in the AE and SE solutions.
 
-\begin{figure}[b]
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
@@
 
-Despite differences between the SE and AE solutions for the case studied in 
+The small differences between the SE and AE solutions for the case studied in 
 Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
-the AE method is still extremely powerful.  The first application of the AE method
+show that the AE method is extremely powerful.  The first application of the AE method
 ($t \approx 70$ in Fig. \ref{fig:time_trace}b) immediately increases the 
@@
 In this work we have used \RB convection as a test case for the AE method, but we argue that
-the true power of this method is in its extensions to more complicated studies.
-Such extensions are beyond the scope of this paper, but we will briefly describe
-areas in which extensions to the AE method should be explored.
-We note that a strength of the AE method is its generality.  One
-need only derive the steady-state, horizontally-averaged equations for a given
+the true power of this technique is in its extensions to more complicated studies.
+One need only derive the steady-state, horizontally-averaged equations for a given
 equation set (e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
@@
 and current dynamics (as described in
-section \ref{subsection:ae} and appendix \ref{appendix:recipe}).
+section \ref{subsection:ae} and appendix \ref{appendix:recipe}) to achieve a quickly
+converged solution. While in-depth studies of AE extensions are beyond the 
+scope of this paper, we will briefly describe
+areas in which the AE method should be explored.
 
-One such area in which this method can be applied is to simple studies of
-internally heated convection \cite{goluskin2016}.  The simplest of these studies 
+One area in which the AE approach can be applied is to simple studies of
+internally heated convection \cite{goluskin2016}.  The least complex of these studies 
 examine the incompressible Boussinesq equations, as presented in this work,
@@
 more flux towards the top of the domain.  These systems can be straightforwardly
-studied using the methods that we examined here, but scaling the profiles derived
+studied using the methods that we examined here, while scaling the profiles derived
 in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux.
@@
 the simplest stratified, compressible systems.  Rather than studying the total
-flux through the system, one must only study the flux in excess of the adiabatic
-while constructing the fractions of Eqn. (\ref{eqn:bvp_ratios}).  
+flux through the domain, it is essential to study only the flux in excess of 
+what is conducted along the adiabatic temperature gradient while constructing
+the profiles in Eqn. (\ref{eqn:bvp_ratios}).  
 Furthermore, in addition to solving for
@@
 must be used to ensure that mass is not created or destroyed,
-in a manner similar to how mass appears in equations in stellar structure codes
+in a manner similar to how mass is treated in stellar structure codes
 \cite{paxton&all2011}.
@@
 the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
-despite the thermal timescale being roughly $10^4$ frefall units.
+despite the thermal timescale being roughly $10^4$ freefall units.
 
 A final area in which we encourage extensions of this method is in the study of systems
-operating in the presence of different thermal boundary conditionss.
+operating in the presence of different thermal boundary conditions.
 We have studied solutions in which we employ mixed thermal boundary conditions,
@@
 
-In conclusion, here we have described a method for converging convective simulations using
+In conclusion, here we have described a procedure for converging convective simulations using
 a method of Accelerated Evolution (AE), and compared it to Standard
@@
 the AE method in both 2D and 3D, but have restricted most of our study to 2D flows.
-As a result of the AE method depending only on 1D information integrated across
-the horizontal dimensions of the atmosphere, we only examine a select small group
-of 3D simulations to demonstrate the method's efficacy there in addition to in 2D.
+Because the AE technique depends only on horizontally integrated information, 
+we examine a select small group
+of 3D simulations only to demonstrate the method's efficacy there.
 
@@
 In order to study how astrophysical systems change over meaningful
-evolutionary timescales, there are two main approaches.  One-dimensional
-systems which parameterize dynamics can be quickly evolved over thermal timescales.
-However, if the experimenter wants to simultaneously study system evolution
-in the presence of realistic convective dynamics, we now know that it is
+evolutionary timescales, most studies utilize one-dimensional
+systems which parameterize dynamics. However, 
+modern experimentalists aim to simultaneously study system evolution
+in the presence of realistic convective dynamics. We now know that it is
 impossible to avoid the constraints that advective dynamics place on
 timestep size \cite{viallet&all2011, viallet&all2013, viallet&all2016}
-in both implicit and explicit methods. We must explore other avenues
-of evolving the system forward on thermal timescales, and this work aims
-as a first step in these explorations.
+in both implicit and explicit methods. As a result, new, alternativie techniques
+for evolving systems forward on thermal timescales, such as the one explored
+here, must be examined in depth.
 

### 2018-02-27 tex/bvp_paper.tex
modified fig 4/ restructured [but did not edit, yet!] conclusions section

@@
 We introduce a reduced kinematic pressure,
-$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where the gravitational
+$\varpi \equiv (P / \rho_0 + \phi + |\bm{u}|^2 / 2) / v_{\text{ff}}^2$, where the gravitational
 potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. As $P$ is a
@@
 and the nonlinear convective flux (Fig. \ref{fig:pdf_comparison}c). We report KS statistics
-of 0.00615, 0.0349, and 0.0204, respectively.  Perhaps unsurpisingly, the nonlinear
+of 0.00615, 0.0349, and 0.0263, respectively.  Perhaps unsurpisingly, the nonlinear
 convective transport between the SE and AE methods are very similar, as is captured
@@
 
+In conclusion, here we have described a procedure for converging convective simulations using
+a method of Accelerated Evolution (AE), and compared it to Standard
+Evolution (SE) achieved by running simulations for a thermal timescale.
+We have shown that the AE method produces evolved solutions on short timescales
+whose dynamics are similar to SE solutions, and we have discussed differences that arise
+between the two methods.
+
+We have shown that the AE method is valid at low values of $S$, in which solutions
+converge quickly and the thermal timescale is short, but that it is also applicable
+at high values of $S$, where SE solutions can take an
+intractable amount of time. This shows that the AE method not only progresses
+solutions towards the correct evolved state (at high $S$), but that it also does not
+remove the simulation from the correct evolved state once such a state is achieved (at low $S$). 
+We have studied
+the AE method in both 2D and 3D, but have restricted most of our study to 2D flows.
+Because the AE technique depends only on horizontally integrated information, 
+we examine a select small group
+of 3D simulations only to demonstrate the method's efficacy there.
+
 One area in which the AE approach can be applied is to simple studies of
@@
 
-A final area in which we encourage extensions of this method is in the study of systems
-operating in the presence of different thermal boundary conditions.
-We have studied solutions in which we employ mixed thermal boundary conditions,
-as in Eqn. (\ref{eqn:bcs}). However, the AE method can be easily applied to fixed-temperature
-boundary conditions, as well.  The total evolved flux (F$_{\text{bot}}$)
-through the system is not known a priori, but it can be measured using the ratios in
-Eqn. (\ref{eqn:bvp_ratios}).  The integrated conductive flux is a constant which
-does not change with time due to the fixed temperature jump across the domain.  
-Thus, the total flux through the system can be calculated as 
-$F_{\text{bot}} = \mathcal{P} / \int f_{\text{cond}} dz$. While easily extensible
-to fixed-temperature boundary conditions, we hesitate to use the AE method for 
-fixed-flux boundary conditions.  In those systems, there are infinitely many degenerate
-solutions to the final temperature profile, and the AE method could advance the
-solution into an unrealistic state as a result of an arbitrary user choice on the
-temperature profile's offset.
-
-In conclusion, here we have described a procedure for converging convective simulations using
-a method of Accelerated Evolution (AE), and compared it to Standard
-Evolution (SE) achieved by running simulations for a thermal timescale.
-We have shown that the AE method produces evolved solutions on short timescales
-whose dynamics are similar to SE solutions, and we have discussed differences that arise
-between the two methods.
-
-We have shown that the AE method is valid at low values of $S$, in which solutions
-converge quickly and the thermal timescale is short, but that it is also applicable
-at high values of $S$, where SE solutions can take an
-intractable amount of time. This shows that the AE method not only progresses
-solutions towards the correct evolved state (at high $S$), but that it also does not
-remove the simulation from the correct evolved state once such a state is achieved (at low $S$). 
-We have studied
-the AE method in both 2D and 3D, but have restricted most of our study to 2D flows.
-Because the AE technique depends only on horizontally integrated information, 
-we examine a select small group
-of 3D simulations only to demonstrate the method's efficacy there.
-
-This work serves as a first step towards creating robust methods for
-achieving evolved convective solutions at high Ra on short timescales.
-In order to study how astrophysical systems change over meaningful
-evolutionary timescales, most studies utilize one-dimensional
-systems which parameterize dynamics. However, 
-modern experimentalists aim to simultaneously study system evolution
-in the presence of realistic convective dynamics. We now know that it is
-impossible to avoid the constraints that advective dynamics place on
-timestep size \cite{viallet&all2011, viallet&all2013, viallet&all2016}
-in both implicit and explicit methods. As a result, new, alternativie techniques
-for evolving systems forward on thermal timescales, such as the one explored
-here, must be examined in depth.
+Stellar structure + 3-2-1 D \cite{arnett&all2015, cristini&all2016}. The
+latter paper focuses on mixing on the boundaries of convective regions.
 

### 2018-02-27 code/plotting/pdf_comparison.py

@@ -37,7 +37,7 @@ def calculate_CDF(x, pdf):
         cdf[i] = np.sum(d_cdf[:i+1])
     return new_x, cdf
 
-def ks_test(x1, y1, N1, x2, y2, N2, n=1000):
+def ks_test(x1, y1, N1, x2, y2, N2, n=10000):
     x_range = [np.min(x1), np.max(x1)]
     if np.min(x2) > x_range[0]:
         x_range[0] = np.min(x2)
@@ -48,14 +48,15 @@ def ks_test(x1, y1, N1, x2, y2, N2, n=1000):
 
     f1 = interp1d(x1, y1, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
     f2 = interp1d(x2, y2, bounds_error=False, assume_sorted=True)#, fill_value='extrapolate')
-
+    
     y1_interp = f1(x_points)
     y2_interp = f2(x_points)
-    diff = np.abs(y1_interp - y2_interp)
-    
-    max_diff = np.max(diff)
-    return max_diff, np.sqrt((N1+N2)/(N1*N2))
+    diff_true = y1_interp - y2_interp
+    diff = np.abs(diff_true)
 
+    max_diff = np.max(diff)
+    print(max_diff, diff)
+    return max_diff, np.sqrt((N1+N2)/(N1*N2)), x_points, diff_true
 
 
 import dedalus.public as de
@@ -106,7 +107,7 @@ for a, base_dir in enumerate(base_dirs_post):
 
 print(info.keys())
 print(info['{}_0'.format(ra_runs)].keys())
-plt.figure(figsize=(8, 1.5))
+plt.figure(figsize=(8, 2.5))
 gs     = gridspec.GridSpec(*(1000,1000))
 
 
@@ -115,7 +116,8 @@ axis_names   = ['x', 'y']
 # Bottom three plots
 #Plot 1
 axes = []
-gs_info = (((0,0), 1000, 267), ((0, 366), 1000, 267), ((0, 733), 1000, 267))
+gs_info = (((0,0), 600, 267), ((0, 366), 600, 267), ((0, 733), 600, 267),
+           ((725,0), 275, 267), ((725, 366), 275, 267), ((725, 733), 275, 267))
[…]

### 2018-02-28 tex/bvp_paper.tex
updates to conclusion text

@@
 \label{sec:extensions}
-In this work we have used \RB convection as a test case for the AE method, but we argue that
+In this work, we have studied a method of Accelerated Evolution (AE) which can
+be employed to achieve rapid thermal convergence of convective simulations.  We compared
+this technique to the Standard Evolution (SE) of convection through a thermal diffusion timescale and
+showed that AE rapidly obtains solutions whose dynamics are similar to SE solutions.
+The AE method is not only valid at low values of $S$, where SE solutions
+converge quickly due to the short thermal timescale, but AE is also applicable
+at high values of $S$, where SE solutions are intractable.
+We have studied
+the AE method in both 2D and 3D, but restricted most of our study to 2D flows;
+AE depends only on the 1D horizontal average of quantities, and our inclusion of 3D
+simulations was merely to demonstrate the broadly useful nature of AE.
+
+Here we studied \RB convection as a test case for the AE method, but we argue that
 the true power of this technique is in its extensions to more complicated studies.
-One need only derive the steady-state, horizontally-averaged equations for a given
-equation set (e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
-and couple that information with knowledge of the boundary conditions
-and current dynamics (as described in
-section \ref{subsection:ae} and appendix \ref{appendix:recipe}) to achieve a quickly
-converged solution. While in-depth studies of AE extensions are beyond the 
-scope of this paper, we will briefly describe
-areas in which the AE method should be explored.
+To achieve AE in more complicated systems, one need only derive 
+the steady-state, horizontally-averaged equations governing
+the convective dynamics
+(e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
+and couple those equations with knowledge of the boundary conditions
+and current dynamics as described in
+section \ref{subsection:ae} and appendix \ref{appendix:recipe}.
+While in-depth studies of AE extensions are beyond the 
+scope of this paper, we will briefly discuss
+avenues in which the AE method should be explored and tested.
 
-In conclusion, here we have described a procedure for converging convective simulations using
-a method of Accelerated Evolution (AE), and compared it to Standard
-Evolution (SE) achieved by running simulations for a thermal timescale.
-We have shown that the AE method produces evolved solutions on short timescales
-whose dynamics are similar to SE solutions, and we have discussed differences that arise
-between the two methods.
+Convection in natural systems is often driven by internal heating processes
+rather than imposed, fixed boundary condditions. The AE procedure can be straightforwardly
+applied to Boussinesq studies of internally heated convection \cite{goluskin2016},
+where a constant source term in the energy equation causes 
+the vertical flux through the system to increase with height.
+These systems can be straightforwardly
+studied using exactly the methods that we examined here, but 
+scaling the flux profiles derived
+in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
+convection in natural system often employ height-dependent conductivities
+\cite{brandenburg2016}, leading
+to natural flux divergences that act as internal heating terms, and the study
+of this method in the simple internal heating context will be an important step
+towards achieving AE in simulations with astrophysically realistic conductivities.
 
-We have shown that the AE method is valid at low values of $S$, in which solutions
-converge quickly and the thermal timescale is short, but that it is also applicable
-at high values of $S$, where SE solutions can take an
-intractable amount of time. This shows that the AE method not only progresses
-solutions towards the correct evolved state (at high $S$), but that it also does not
-remove the simulation from the correct evolved state once such a state is achieved (at low $S$). 
-We have studied
-the AE method in both 2D and 3D, but have restricted most of our study to 2D flows.
-Because the AE technique depends only on horizontally integrated information, 
-we examine a select small group
-of 3D simulations only to demonstrate the method's efficacy there.
-
-One area in which the AE approach can be applied is to simple studies of
-internally heated convection \cite{goluskin2016}.  The least complex of these studies 
-examine the incompressible Boussinesq equations, as presented in this work,
-but include a constant source term in the energy equation. The evolved convective
-state in such internally heated systems includes a flux profile whose value linearly
-increases with height, as the volumetric heating requires the convection to carry
-more flux towards the top of the domain.  These systems can be straightforwardly
-studied using the methods that we examined here, while scaling the profiles derived
-in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux.
-
-Studies of stratified convection are likely to gain the most through
-developing and employing the AE method.
-In many studies of stratified convection, the thermal diffusivity
-is inversely proportional to the density \cite{anders&brown2017}. Thus, the
-thermal timescale is much larger deep in the atmosphere, where density is high and diffusivity
-is very low, than it is near the surface.  As such, runs at similar supercriticalities
-but with different degrees of stratification can have thermal timescales which
-differ by orders of magnitude.  Fortunately, the AE method is easily adapted to
-the simplest stratified, compressible systems.  Rather than studying the total
-flux through the domain, it is essential to study only the flux in excess of 
-what is conducted along the adiabatic temperature gradient while constructing
-the profiles in Eqn. (\ref{eqn:bvp_ratios}).  
-Furthermore, in addition to solving for
-hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
-\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously
-ensure that mass is conserved.  Thus, additional equations and boundary conditions
-must be used to ensure that mass is not created or destroyed,
-in a manner similar to how mass is treated in stellar structure codes
-\cite{paxton&all2011}.
-
-Studies of convection frequently examine paired stable and convecting regions
+In order to understand the influences of overshooting convection, some
+studies examine adjacent stable and convecting regions
 \cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
@@
 the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
-despite the thermal timescale being roughly $10^4$ freefall units.
+despite the thermal timescale being roughly $10^4$ freefall units. However, in 
+studies where there is a stable region which is not mixed by convection, the experimentalist
+must either wait through a thermal diffusion time for the region to restratify
+or employ methods such as the AE method to study evolved atmospheres.
 
-Stellar structure + 3-2-1 D \cite{arnett&all2015, cristini&all2016}. The
-latter paper focuses on mixing on the boundaries of convective regions.
+Studies of stratified, compressible convection have much to gain through
+developing and employing AE.
+In many studies of stratified convection, the thermal diffusivity
+is inversely proportional to the density \cite{anders&brown2017}. Thus, the
+thermal timescale grows with depth in the atmosphere, and
+the difficulty of achieving thermal convergence grows as simulators study more highly
+stratified domains.
+In order to extend AE into this regime, two additional pieces of information must be considered.
+First, rather than constructing the profiles in Eqn. (\ref{eqn:bvp_ratios})
+with the total flux through the domain, only the superadiabatic portion of
+the flux should be considered.
+Second, in addition to solving for
+hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
+\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
+profile in a manner which conserves mass.  In a 1D boundary value problem, such as
+is solved to achieve AE here, this implies the inclusion of an equation which tracks
+the vertically integrated mass, and sets boundary conditions on that mass to ensure
+that no mass enters or leaves the domain.
+
+A long-term goal would be to extend AE in a robust way such that it can be
+incorporated into stellar structure codes. Current state of the art stellar structure
+models are 1D solves that parameterize convection through widely accepted models
+like Mixing Length Theory \cite{paxton&all2011}. Recently, researches have begun
+efforts to couple evolution of stellar structure on significant thermal timescales
+while resolving convective dynamics.  A first attempt to do this was through the
+use of fully nonlinear implicit timestepping methods 
+\cite{viallet&all2011, viallet&all2013, viallet&all2016},
+but the emergence of unrealistic dynamics when timesteps are so large that they
+don't properly resolve advective motions has made this an unlikely means of
+evolving systems for long times. Other recent work, 
+such as 3-2-1D \cite{arnett&all2015} convection, which uses information in
+evolved 3D dynamical solutions to evolve the 1D underlying thermodynamic profile,
+and which is similar to the method we presented here, shows promise.  Some other
+work pairing 1D solves with fully nonlinear 3D solutions has been conducted
+\cite{cristini&all2016}, but often in more complicated systems than those we examine here. 
+Through small improvements and extensions, the AE method here can be improved
+and verified until it is capable of handling the full physics present in nonlinear
+stellar evolution.
 

### 2018-03-01 tex/bvp_paper.tex
updates final paragraph and all figure captions; finalizing edits tomorrow

@@
 
-\begin{figure}[t]
+\begin{figure*}[t!]
 \includegraphics[width=\textwidth]{./figs/time_trace.png}
-\caption{A time trace is shown of kinetic energy (black) and mean temperature (blue)  vs. time 
-for an SE run at $S = 10^5$ (a). The mean evolved values of kinetic energy and mean temperature
-are denoted by the horizontal dashed black and blue lines. 
-By taking an average of the fluxes early in the
-simulation (b), and appropriately using the AE method described here, the evolution
-of these atmospheres can be greatly accelerated. The time trace of such an accelerated
-atmosphere, which uses these methods, is shown in (c).  The y-axes and x-axes are
-scaled identically as in (a).  Here, the AE method is used three times, marked by
-the numbered arrows. The fluxes averaged over the green region which begins at
-the vertical dashed line shortly after AE 3 are shown in (c) are shown
-in (d), and they are nearly in the fully evolved state, sampled over a similarly
-long region that occurs much later in the simulation in (a).  The difference between
-the fluxes in the AE and SE ssolutions is shown in (e), and it is small. The dashed
-vertical line in (a) denotes the simulation time at which evolved flux measurements
-begin to be taken in (c).
+\caption{(a) Kinetic energy (black) and mean temperature (blue)  vs. time are shown
+for a SE run at $S = 10^5$. The mean evolved values of kinetic energy and mean temperature,
+averaged over the time shaded in green,
+are denoted by the horizontal dashed lines. (b) The time- and horizontally-averaged
+flux profiles are shown for the times highlighted in orange in (a).
+(c) The same quantities as in (a) are shown, but for AE at the same parameters.
+The axes are scaled identically in (a) and (c), and the AE method is used three times, marked by
+the numbered arrows in (c). The fluxes averaged over the green shaded region of (c)
+are shown in (d). The difference between
+the fluxes in the AE and SE solutions is shown in (e). The dashed
+vertical line in (a) and (c) denotes the simulation time at which evolved measurements
+are started for the AE case.
 \label{fig:time_trace} }
-\end{figure}
+\end{figure*}
 
@@
 
-The AE method converges atmospheeres from extreme flux disequilibrium states 
+The AE method converges atmospheres from extreme flux disequilibrium states 
 (Fig. \ref{fig:time_trace}b) on short dynamical timescales (Fig. \ref{fig:time_trace}c)
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
-\caption{Volume- and time-averaged measurements of the Nusselt number, the
-RMS Reynolds number, and the mean temperature for AE runs are shown in (a)-(c).
+\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
+RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
 Symbols are located at the mean value of
-each measurement, vertical lines represent the standard deviation of the measurement,
-which shows natural variation over the
-averaging window, and error bars represent the change in the mean value over the averaging window,
+each measurement.  Vertical lines represent the standard deviation of the measurement,
+and quantify natural variation over the
+averaging window. Error bars represent the change in the mean value over the averaging window,
 such that very large error bars represent solutions which are not fully converged when averaging
 begins.
-(a) The Nusselt number scales as Ra$^{1/5}$, and above S$\geq 10^{3+2/3}$,
-simulations exhibit oscillating plume structures whose heat transport varies over time.  
-(b) The RMS Reynolds number, which measures the level of turbulence in the evolved solution, scales as
-Ra$^{0.45}$. (c) Temperature, with its value at the upper boundary removed, is shown,
-and scales as Ra$^{-1/5}$.
-Relative error for (d) Nu, (e) Re, and (f) $T$ are shown between measurements 
-taken in AE solutions and SE solutions.
-The greyed area of the plot indicates the region in which only AE runs were
+(a) Nu scales as Ra$^{1/5}$; above S$\geq 10^{3+2/3}$,
+simulations exhibit oscillating plume structures whose heat transport fluctuates over time.  
+(b) Re, which measures the level of turbulence in the evolved solution, scales as
+Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at $z = +1/2$
+is shown, and this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
+Relative error for measurements of (d) Nu, (e) Re, and (f) $T$ between 
+AE solutions and SE solutions are shown.
+The greyed area of the plots indicates the region in which only AE runs were
 carried out due to computational expense. The run at $S = 10^5$ marked as a
@@
 
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
+\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
+at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
+temperature profiles, as a function of height.
+(b) Probability Distribution Functions (PDFs) and their integrated
+Cumulative Distribution Functions (CDFs)
+of point-by-point measurements of the temperature field.
+$T$ is sampled every 0.1 time units for 500 total time units,
+and was interpolated onto an evenly spaced grid before sampling.
+(c) The percentage difference between the mean temperature profiles as a function of height.
+The difference between the mean profiles is very small, O(0.5\%).
+(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
+the AE and SE CDFs, as a function of temperature.
+The small
+difference in the interior temperature 
+results in a large difference between the two temperature CDFs near the values
+of the temperature modes.  The spread of temperature around the modes, which includes the 
+fluctuations that drive convection, are nearly identical between the two runs.
+\label{fig:temp_comparison} }
+\end{figure}
+
 The probability distribution functions 
@@
 
-\begin{figure}[t]
-\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
-\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
-at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
-temperature profiles, as a function of height.
-(b) Probability Distribution Functions (PDFs) and their integrated
-Cumulative Distribution Functions (CDFs)
-of point-by-point measurements of the temperature field.
-(c) The percentage difference between the mean temperature profiles as a function of height.
-(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
-the AE and SE CDFs, as a function of temperature.
-$T$ is sampled every 0.1 time units for 500 total time units,
-and was interpolated onto an evenly spaced grid before sampling.
-The difference between the mean profiles is very small O(0.5\%), but this small
-difference results in a large difference between the two temperature CDFs near the values
-of the temperature mode.  The spread of temperature around the mode, or the fluctuations that
-drive convection, are nearly identical between the two runs.
-\label{fig:temp_comparison} }
-\end{figure}
-
 In addition to comparing the thermodynamic state achieved by the SE and AE methods,
@@
 \includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{Probability distribution functions of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
-convective transport are shown for a 2D runs achieved through the SE and AE methods
+\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
+convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
 at $S = 10^{5}$.  Flows are sampled every 0.1 time units for 500 total time units,
-and flows are interpolated onto an evenly spaced grid before sampling.
-The cumulative distribution function is overplotted on each plot. 
+and are first interpolated onto an evenly spaced grid.
+The cumulative distribution function (CDF) is overplotted for each PDF. 
+(d-f) The KS statistics, or the values of CDF$_{\text{AE}}$ - CDF$_{\text{SE}}$,
+are shown for the related distributions, and solid lines indicated positive values
+while dashed lines are negative values. Unlike the temperature distributions in
+Fig. \ref{fig:temp_comparison}, these distributions, particularly the vertical
+velocity and transport, show very good agreement and small values of the KS statistic.
 \label{fig:pdf_comparison} }
@@
 
-A long-term goal would be to extend AE in a robust way such that it can be
-incorporated into stellar structure codes. Current state of the art stellar structure
-models are 1D solves that parameterize convection through widely accepted models
-like Mixing Length Theory \cite{paxton&all2011}. Recently, researches have begun
-efforts to couple evolution of stellar structure on significant thermal timescales
-while resolving convective dynamics.  A first attempt to do this was through the
-use of fully nonlinear implicit timestepping methods 
-\cite{viallet&all2011, viallet&all2013, viallet&all2016},
-but the emergence of unrealistic dynamics when timesteps are so large that they
-don't properly resolve advective motions has made this an unlikely means of
-evolving systems for long times. Other recent work, 
-such as 3-2-1D \cite{arnett&all2015} convection, which uses information in
-evolved 3D dynamical solutions to evolve the 1D underlying thermodynamic profile,
-and which is similar to the method we presented here, shows promise.  Some other
-work pairing 1D solves with fully nonlinear 3D solutions has been conducted
-\cite{cristini&all2016}, but often in more complicated systems than those we examine here. 
-Through small improvements and extensions, the AE method here can be improved
-and verified until it is capable of handling the full physics present in nonlinear
-stellar evolution.
+An eventual use case of AE is in robustly replacing Mixing Length Theory (MLT)
+in stellar evolution codes. Current state of the art stellar structure
+models are the solutions of 1D simulations which parameterize convection 
+using MLT \cite{paxton&all2011}. Recent work has taken the first steps towards
+understanding how to simultaneously resolve convective motions while evolving
+systems through many thermal timescales, as is required in the evolution of stars.
+We now know that implicit timestepping methods, while not technically bound by
+CFL constraints, must resolve the convective motions for stability
+\cite{viallet&all2011, viallet&all2013, viallet&all2016}, and are thus
+not an ideal solution to achiving long-term system evolution.
+Recently, efforts have begun to improve 1D models of stellar
+convection by projecting the results of 3D simulations into 1D
+to more properly parameterize convection \cite{arnett&all2015, cristini&all2016}.
+This is precisely an extension of the AE that we present here,  and through the
+careful addition and testing of new physics, AE shows great potential for 
+improving our understanding of convection in general, and stellar evolution models
+in particular.
 

### 2018-03-01 code/plotting/pdf_comparison.py

@@ -173,10 +173,10 @@ axes[-1].plot(diff_x[diff_y > 0], diff_y[diff_y > 0],  c='k', lw=1)
 axes[-1].plot(diff_x[diff_y < 0], -diff_y[diff_y < 0], c='k', dashes=(3,1), lw=1)
 axes[-1].set_xlim(-0.165, 0.165)
 axes[-1].set_yscale('log')
-axes[-1].set_ylim(1e-4, 1e-2)
+axes[-1].set_ylim(1e-4, 1e-1)
 axes[-1].set_ylabel('CDF diff.')
 axes[-1].set_xlabel('Vertical Velocity', labelpad=-2)
-axes[-1].annotate(r'$\mathrm{(d)}$', (0.11, 3e-3), fontsize=10)
+axes[-1].annotate(r'$\mathrm{(d)}$', (-0.15, 1e-2), fontsize=10)
 for tick in axes[-1].get_xticklabels():
     tick.set_rotation(45)
 

### 2018-03-01 code/plotting/time_trace.py

@@ -73,7 +73,7 @@ for a, base_dir in enumerate(base_dirs_pre + base_dirs_post):
             print('cannot find profile file in {:s}'.format(d))
 
 
-plt.figure(figsize=(8, 7.5))
+plt.figure(figsize=(8, 9))
 gs     = gridspec.GridSpec(*(1000,1000))
 
 #####################################

### 2018-03-02 tex/bvp_paper.tex
pretty good draft

@@
 \begin{abstract}
-We present a method for coupling boundary value problems with initial value problems 
-in order to achieve Accelerated Evolution (AE) of convective solutions on
-dynamical timescales, rather than the long thermal timescale. 
+We present a method for achieving Accelerated Evolution (AE) of convective simulations.
+By probing the dynamics of convection early in simulations and adjusting the
+thermal profile of the simulation appropriately, we advance simulations to
+evolved states on timescales much shorter than the thermal diffusion timescale.
 We study this method in the context of \RB convection. 
-We demonstrate that the solution reached by AE and Standard Evolution (SE) are
-similar, and that this method works at a
-large range of supercriticalities.  The AE method is used to achieve converged 
-solutions at high supercriticality ($10^7$), and its extensions to more complex 
-systems are briefly discussed.
+The solutions reached by AE similar to those reached by a slow thermal evolution, 
+and AE is effective in 2D, 3D, and at low and high supercriticality.  
+Extensions to more complex systems are briefly discussed.
 \end{abstract}
@@
 Natural convection occurs in the presence of disparate timescales which
-prohibit numericists from studying realistic models of natural systems.  For example,
+prohibit numericists from studying realistic models of systems in nature.  For example,
 flows in the convection zones of stars like the Sun are characteristically low Mach number
@@
 
-Convective systems with divergent dynamical timescales can now be studied; however,
-thermal timescales, which characterize system relaxation, are often much larger than
-dynamical timescales, and resolving dynamics in atmospheres which are sufficiently
+Unfortunately, convective systems generally evolve over the course of thermal
+timescales, which are often much larger than
+dynamical timescales. Therefore resolving dynamics in atmospheres which are sufficiently
 thermally relaxed remains a challenging problem.
-Solar convection is a prime example of this phenomenon.
-Dynamical timescales in the solar convective zone are relatively short 
-(10 min overturn at solar surface, one month solar
-rotation rate) compared to the Sun's Kelvin-Helmholtz timescale of
+Solar convection is a prime example of this phenomenon, as
+dynamical timescales in the solar convective zone are relatively short 
+(convection overturns every $\sim 10$ minutes at the solar surface, 
+the Sun rotates roughly once every month)
+compared to the Sun's Kelvin-Helmholtz timescale of
 $3 \cdot 10^7$ years \cite{stix2003}.  
 In such a system, it is impossible to resolve the convective dynamics while also
-evolving the thermal structure of the system in a meaningful fashion using
+meaningfully evolving the thermal structure of the system using
 traditional timestepping techniques alone.
@@
 Furthermore, as dynamical and thermal timescales separate, 
-simulations become more turbulent. Increasingly turbulent motions 
-require finer grid meshes and smaller timesteps
-to capture advective dynamics. Thus, the progression of simulations into the high-Ra
+simulations become more turbulent. Capturing appropriately resolved
+turbulent motions requires finer grid meshes and smaller timesteps.
+Thus, the progression of simulations into the high-Ra
 regime of natural convection is slowed by two simultaneous effects: timestepping
@@
 the approximate state of the evolved solution can be estimated. There, a
-set of initial conditions which is close to the evolved state be 
+set of initial conditions which is close to the evolved state can be 
 derived analytically \cite{couston&all2017, brandenburg&all2005}.
@@
 can only reasonably be run
-for tens to hundreds of buoyancy times \cite{stevens&all2011}, much less the
-thousands of buoyancy timescales required for thermal convergence.
+for tens to hundreds of freefall timescales \cite{stevens&all2011}, much less the
+thousands of freefall times required for thermal convergence.
 
@@
 numerical methods, and our method for achieving accelerated evolution. In
-section \ref{sec:results}, we compare solutions reached through the accelerated evolution
-method to those that have been evolved through a full diffusive timescale, and we
-examine select simulations at high Ra which have achieved accelerated evolution. Finally,
-in section \ref{sec:extensions}, we discuss extensions of the methods presented here,
-and we offer concluding remarks.
+section \ref{sec:results}, we compare accelerated evolution solutions
+to solutions obtained from evolution through a full thermal diffusion timescale. Finally,
+in section \ref{sec:extensions}, we offer concluding remarks and
+discuss extensions of the methods presented here.
 
@@
 We study incompressible \RB convection under the Oberbeck-Boussinesq approximation,
-such that our fluid
+such that the fluid
 has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
@@
 and $P$ is the pressure.
-We non-dimensionalize these equations such that the
+We non-dimensionalize these equations such that
 length is in units of the layer height ($L_z$),
@@
 and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
-by these choices, one time unit is a freefall time ($L_z/v_{\text{ff}}$).
+By these choices, one time unit is a freefall time ($t_{\text{ff}} = L_z/v_{\text{ff}}$).
 We introduce a reduced kinematic pressure,
@@
 F$_{\text{cond}} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective flux,
-F$_{\text{conv}} = \angles{w(T_0 + T_1)}_{x,y}$, where $\angles{}_{x,y}$ represent
-a horizontal average, are the basis of the AE method. We measure
-both of these quantities early in a simulation, retrieving profiles similar to
+F$_{\text{conv}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method.
+Here we use $\angles{}_{x,y}$ to represent a horizontal average. We measure
+both of these fluxes early in a simulation, retrieving profiles such as
 those shown in Fig. \ref{fig:time_trace}b.
@@
 that the advected, flux-carrying perturbations in the temperature are appropriately
-diminished.  We then solve a boundary value problem including
+diminished.  We then solve a 1D boundary value problem including
 Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}) using F$_{\text{conv, ev}}$
-and $\cdot\angles{\bm{u}\times\bm{\omega}}_{x,y}$, after diminishing it by a factor
-of $\xi$. We use mixed thermal boundary conditions, as in Eqn. (\ref{eqn:bcs}),
-because $F_{\text{bot}}$ is exactly specified, and the temperature profile is pegged
+and $\angles{\bm{u}\times\bm{\omega}}_{x,y}$, after diminishing it by a factor
+of $\xi$. We use mixed thermal boundary conditions in this study, 
+as in Eqn. (\ref{eqn:bcs}),
+because $F_{\text{bot}}$ is exactly specified, and the temperature profile is fixed 
 at a reference value for the AE solve.
@@
 %%%%%%%%%%%%
-
+\vspace{-0.5cm}
 \section{Results}
 \label{sec:results}
-We study evolved solutions achieved through the standard evolution (SE) method 
-from convective onset
-up to $S = 10^5$ in 2D and $S = 10^4$ in 3D.  These SE runs are compared to
-accelerated evolution (AE) runs spanning from onset up to $S = 10^7$ in 2D and $S = 10^4$ in 3D.
-For a full list of simulations, we refer the reader to appendix \ref{appendix:run_table}.
+We study evolved SE solutions in $S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
+3D. We compare their properties to
+accelerated evolution (AE) runs in $S \in (1, 10^7]$ in 2D and
+$S \in (1, 10^4]$ in 3D.
+We refer the reader to appendix \ref{appendix:run_table} for a full list of
+simulations.
 
-We report the time- and volume-averaged values of select measurements of the
-evolved solutions in Fig. \ref{fig:parameter_space_comparison}.
-The scaling of heat transport in the evolved solution, as quantified by the
-Nusselt number, is shown in Fig. \ref{fig:parameter_space_comparison}a.
-The volume averaged Nusselt number is defined as
+\vspace{5cm}
+$\,$\newline
+The time- and volume-averaged values of the Nusselt number (Nu), the RMS
+Reynolds number (Re), and the mean temperature in AE solutions 
+are shown in Fig. \ref{fig:parameter_space_comparison}a-c.
+Nu, which quantifies the heat transport in evolved solutions,
+is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
+Nu is defined as
 \begin{equation}
@@
 \end{equation}
-where $\angles{}$ represent a volume average.
-In 2D when $S < 10^{3+2/3}$ and in 3D, the evolved system is defined by a clear
-value of Nu and the convective heat transport reaches a temporally stationary state.
-In 2D and at larger values of $S$, the value of Nu oscillates as a function of time
-due to large horizontal oscillations in the convective plume structures.
-Our choice of no-slip
-boundary conditions prevent the fluid from entering a shearing state
-\cite{goluskin&all2014}, but the oscillatory motions which do arise cause the
-system to vary between periods of low heat transport and high heat transport.
-The SE simulations which span up to $S = 10^5$ exhibit the same horizontally
-oscillatory motion as the AE solutions for the same initial conditions. The
-scaling of the mean value of Nu is roughly $\text{Nu} \propto \text{Ra}^{1/5}$,
-weaker than that reported in similar systems with fixed-T and fixed-flux boundary
-conditions \cite{johnston&doering2009}.  We attribute this weaker Nu scaling to
-the oscillatory nature of the plumes, which may have been avoided by previous studies
-using bootstrapping techniques as initial conditions.
+where the volume average of a quantity, $g$, is shown as $\angles{g}$.
+When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
+the evolved system is characterized by a specific
+value of Nu, as the convective heat transport reaches a temporally stationary state.
+At larger values of $S$ in 2D, the convective plumes consistently oscillate
+horizontally, leading to variations in Nu over time as the heat transport is alternately
+assisted and diminished by these oscillations.
+As a result of our choice of no-slip
+boundary conditions, the fluid never enters a full domain shearing state 
+\cite{goluskin&all2014}, and the
+oscillatory nature of the plumes is stable.
+The 2D SE simulations exhibit the same horizontally
+oscillatory behavior as the AE solutions for the same initial conditions. The
+dynamic nature of the plume structures diminishes the
+scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
+which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
+Previous studies in 2D convection may have avoided oscillatory plumes by using
+bootstrapping techniques as initial conditions for high $S$ runs.
 
@@
 
-In Fig. \ref{fig:parameter_space_comparison}b, we report the volume-averaged
-RMS Reynolds number in the AE solutions, where
-$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measure scales roughly as
-$\text{Re} \propto \text{Ra}^{0.45}$, and shows little variance with time.
+In Fig. \ref{fig:parameter_space_comparison}b, we report 
+$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measures the degree of
+turbulence in the solution, and scales roughly as
+$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
+the value of Re over time.
 
-In Fig. \ref{fig:parameter_space_comparison}c, we report the volume averaged 
-temperature of the AE solutions, with the value at the upper (fixed $T$) boundary removed.
-This measurement probes the thickness of the boundary layers of the solutions, and
-should show scaling which is inversely proportional to Nu in converged solutions
+Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$.
+The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
+so this measurements serves as a probe of the temperature jump across the boundary
+layers. As a result, we expect this measure to
+scaling inversely with Nu in converged solutions
 where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
 that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
-scaling of Nu, giving confidence that these solutions are in a converged state.
+scaling of Nu.
 
 In Fig. \ref{fig:parameter_space_comparison}d-f, we report the fractional difference
-between measurements from the AE solutions and measurements from the SE solutions.
-We find that the mean value of Nu from AE solutions is accurate to the values
-from SE solutions to within $\sim 1$\%, and the same is true for $\angles{T}$ measurements.
-Re measurements show slightly greater error, with AE measurements being on average
-$\leq 2$\% away from the SE measurements.
+between measurements in the AE and SE solutions.
+The mean values of Nu and $\angles{T} - T_{\text{top}}$ 
+measured in AE are accurate to SE values to within $\sim 1$\%.
+Re measurements show marginally greater error, with AE measurements being 
+$\leq 2$\% different from SE measurements.
 
 The measurements presented in Fig. \ref{fig:parameter_space_comparison} demonstrate
-that the AE method can be powerfully employed in parameter space studies in which
+that AE can be powerfully employed in parameter space studies in which
 large numbers of simulations are compared in a volume-averaged sense.  We now turn
 our examination to a more direct comparison of AE and SE for convection at
-$S = 10^5$, as has been introduced in Fig. \ref{fig:time_trace}.
+$S = 10^5$, the time and flux evolution of which was shown in Fig. \ref{fig:time_trace}.
+All comparisons that follow for these two runs occur over the times shaded in
+green in Fig. \ref{fig:time_trace}a\&c. Measurements are sampled every
+0.1 freefall time units for 500 total time units.
 
-As the AE method primarily serves to adjust the thermodynamic structure of the
-solution, we compare the temperature profile attained by AE and SE in 
-Fig. \ref{fig:temp_comparison}.  We see that the boundary layer length scale is 
-nearly identical between the two solutions (Fig. \ref{fig:temp_comparison}a), but that
-the mean temperature in the interior differs by about 0.5\% on average
+As AE is fundamentally a 1D adjustment to the thermodynamic structure of the
+solution, we compare the horizontally- and time-averaged temperature profiles 
+attained by AE and SE in Fig. \ref{fig:temp_comparison}a.  
+The boundary layer width and structure are  
+nearly identical between the two solutions, but the
+the mean temperature in the isothermal interior differs by roughly 0.5\%
 (Fig. \ref{fig:temp_comparison}c).
 
-\begin{figure}[t]
+\begin{figure}[b]
 \includegraphics[width=\textwidth]{./figs/temp_comparison.png}
@@
 
-The probability distribution functions 
+The probability distribution functions (PDFs)
 of point-by-point temperature measurements are compared for the two runs
-in Fig. \ref{fig:temp_comparison}b.  We construct
-this PDF from snapshots of the temperature profile every 0.1 freefall time
-units over a duration of 500 total freefall time units, as shown by the green
-areas if Fig. \ref{fig:time_trace}a\&c.  We interpolate the temperature field
+in Fig. \ref{fig:temp_comparison}b. To construct these PDFs, 
+we interpolate the temperature field
 of each of these snapshots onto an evenly spaced grid, determine the
 frequency distribution of all measured $T$ values, and then normalize the
-distribution such that its integral is unity.  The primary difference between
-the two PDFs is their modes, which is expected from Fig. \ref{fig:temp_comparison}a. 
-The fact that the the AE temperature
-profile is roughly 0.5\% off of the SE temperature profile (\ref{fig:temp_comparison}c), 
-the AE temperature
-field is still marginally evolving towards the SE temperature field, and this
-evolution appears as asymmetry of the AE PDF's peak.
+distribution such that its integral is unity.  The two PDFs have noticeably
+different modes, as is expected from Fig. \ref{fig:temp_comparison}a. 
+Over long timescales, the 0.5\% difference between the two profiles would
+disappear, as the AE solution evolves to be exactly the SE solution -- this
+is evident in the asymmetry of the AE PDF in Fig. \ref{fig:temp_comparison}b and also
+the trend of the mean temperature over time in Fig. \ref{fig:temp_comparison}c.
 
 One means of comparing two
-probability distributions to determine if they are drawn from the same underlying
-sample is through the use of a Kolmogorov-Smirnov (KS) \cite{wall&jenkins2012}.
+PDFs to determine if they are drawn from the same underlying
+sample distribution is through the use of a Kolmogorov-Smirnov (KS) \cite{wall&jenkins2012}.
 In general, a KS test must be conducted on independent, uncorrelated data, which
-poorly describes the point-by-point values of flow in a fluid simulation. Thus,
-we will merely use the KS statistic, the maximum difference
-between the cumulative distribution functions (CDFs) of the two sample distributions,
-as a numerical method of directly comparing the two PDFs.  For the distributions
-shown in Fig. \ref{fig:temp_comparison}b, the difference between the CDFs is shown
-in Fig. \ref{fig:temp_comparison}d.  The maximum difiference, or the KS statistic,
-is 0.495 near the modes.  This difference is very large, but is not unexpected.
-While the temperature distributions near the modes are very different, their spread
-of perturbations is nearly identical.
+poorly describes the point-by-point values of flows in a fluid simulation. Thus,
+we cannot directly use a KS test to determine if the two fluid samples are the same,
+but we can draw insight from the profile
+$\text{KS} = \text{CDF}_{\text{AE}} - \text{CDF}_{\text{SE}},$
+where CDF stands for cumulative distribution function, the integral of the PDF.
+A traditional Kolmogorov-Smirnov statistic is the maximum of the absolute value of
+the KS profile.  We show the KS profile in Fig. \ref{fig:temp_comparison}d, and the
+CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
+Near the modes of the temperature PDFs, the KS profile has a maximum value of
+0.495, which is very large and implies that roughly half of all temperature
+measurements in the SE case are greater than those in the AE case.
+This difference is significant, and shows that the two PDFs are distinctly different,
+but aside from this large value near the modes the KS profile has very small values,
+indicating that the temperature fluctuations away from the modes in the two cases are nearly identical.
 
@@
 we examine the velocities found in the evolved states.
-We compute PDFs in the same manner as in Fig. \ref{fig:temp_comparison}b for the
+Shown are the PDFs of 
 vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
-and the nonlinear convective flux (Fig. \ref{fig:pdf_comparison}c). We report KS statistics
-of 0.00615, 0.0349, and 0.0263, respectively.  Perhaps unsurpisingly, the nonlinear
-convective transport between the SE and AE methods are very similar, as is captured
-in a volume-averaged sense in the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
-Each distribution shows a strong peak near zero due to the velocity boundary conditions
-(Eqn. (\ref{eqn:bcs})), but the distribution of flux transport elements and velocities
-is nearly identical in the AE and SE solutions.
+and the nonlinear vertical convective flux (Fig. \ref{fig:pdf_comparison}c). 
+The CDFs of each profile are overplotted, and corresponding KS profiles are
+shown in Fig. \ref{fig:pdf_comparison}d-f.  The maximum absolute values of the
+KS profiles of vertical velocity, horizontal velocity, and nonlinear vertical convective flux
+are 0.00615, 0.0349, and 0.0263, respectively.  
+Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
+velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
+The difference in vertical velocity
+and heat transport is negligible, which is unsurprising in light of
+the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
+The horizontal velocity shows some small deviation between the two simulations, and this
+likely relates to the nature of the strength of the horizontally oscillatory motions
+as we previously described in the context of suppressed Nu scaling. Thus, while
+the temperature profiles are distinctly drawn from different distributions in
+Fig. \ref{fig:temp_comparison}b, the profiles are similar enough that they drive
+nearly identical nonlinear dynamics.
 
@@
 Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
-show that the AE method is extremely powerful.  The first application of the AE method
-($t \approx 70$ in Fig. \ref{fig:time_trace}b) immediately increases the 
-average time step of our solver by a factor of 2-3. At higher supercriticality
-($S = 10^7$), the AE solve immediately boosts the timestep by nearly a factor of 4.
-Thus, not only does this method evolve the solution into nearly the correct state, 
-but further time evolution (either to achieve precisely the correct thermodynamic
-state or to take measurements of fluid quantities) happens more efficiently.
+show the extreme power of AE.  In addition to the fact that AE runs require much
+less total simulation time (see e.g., Fig. \ref{fig:time_trace}a\&c and the time
+values in the green highlighted regions), the first application of AE in a given
+simulation (Fig. \ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
+increases the average timestep by immediately progressing the simulation into
+a more converged state. For the $S = 10^5$ case we examined in detail, the
+average time step size grew by a factor of 2-3 due to the decreased convective
+velocities from the transient state to the evolved state. 
+At $S = 10^7$, the AE solve immediately improved the timestep size 
+by nearly a factor of 4.
+Thus, AE achieves converged solutions in few simulation time units,
+while also taking less real world time per simulation time unit, when compared
+to the slowly converging SE state at the same simulation time.
 
@@
 \label{sec:extensions}
-In this work, we have studied a method of Accelerated Evolution (AE) which can
+In this work we have studied a method of Accelerated Evolution (AE) which can
 be employed to achieve rapid thermal convergence of convective simulations.  We compared
@@
 the AE method in both 2D and 3D, but restricted most of our study to 2D flows;
-AE depends only on the 1D horizontal average of quantities, and our inclusion of 3D
+AE depends only on 1D, horizontally averaged profiles of dynamics, and our inclusion of 3D
 simulations was merely to demonstrate the broadly useful nature of AE.
@@
 Convection in natural systems is often driven by internal heating processes
-rather than imposed, fixed boundary condditions. The AE procedure can be straightforwardly
+rather than imposed, fixed boundary conditions. The AE procedure can be straightforwardly
 applied to Boussinesq studies of internally heated convection \cite{goluskin2016},
@@
 the vertical flux through the system to increase with height.
-These systems can be straightforwardly
+These systems can be
 studied using exactly the methods that we examined here, but 
-scaling the flux profiles derived
+multiplying the flux profiles derived
 in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
 convection in natural system often employ height-dependent conductivities
-\cite{brandenburg2016}, leading
-to natural flux divergences that act as internal heating terms, and the study
-of this method in the simple internal heating context will be an important step
+\cite{brandenburg2016, kapyla&all2017}, leading
+to natural flux divergences that act as internal heating terms.
+The study
+of AE method in the context of simple internal heating simulations will be an important step
 towards achieving AE in simulations with astrophysically realistic conductivities.
 
-In order to understand the influences of overshooting convection, some
+A further area which could benefit from AE is overshooting convection, in which
 studies examine adjacent stable and convecting regions
@@
 must either wait through a thermal diffusion time for the region to restratify
-or employ methods such as the AE method to study evolved atmospheres.
+or employ other methods \cite{couston&all2017} to study evolved atmospheres.
 
@@
 
-An eventual use case of AE is in robustly replacing Mixing Length Theory (MLT)
+An eventual use case of AE is in robustly describing convection
 in stellar evolution codes. Current state of the art stellar structure
 models are the solutions of 1D simulations which parameterize convection 
-using MLT \cite{paxton&all2011}. Recent work has taken the first steps towards
+using Mixing Length Theory \cite{paxton&all2011}. Recent work has taken first steps towards
 understanding how to simultaneously resolve convective motions while evolving
-systems through many thermal timescales, as is required in the evolution of stars.
+systems through many thermal timescales, as is required when modeling the evolution of stars
+over the course of stellar lifetimes.
 We now know that implicit timestepping methods, while not technically bound by
@@
 not an ideal solution to achiving long-term system evolution.
-Recently, efforts have begun to improve 1D models of stellar
-convection by projecting the results of 3D simulations into 1D
-to more properly parameterize convection \cite{arnett&all2015, cristini&all2016}.
-This is precisely an extension of the AE that we present here,  and through the
-careful addition and testing of new physics, AE shows great potential for 
-improving our understanding of convection in general, and stellar evolution models
-in particular.
+Recently, efforts have begun to project the results of 3D simulations into 1D
+models to more properly parameterize convection for stellar evolution
+\cite{arnett&all2015, cristini&all2016}.
+Through the
+careful addition and testing of new physics, AE can be generally applied to
+very large complex problems such as stellar evolution, and
+shows great potential for improving our understanding of convection.
 
@@
 In order to achieve Accelerated Evolution (AE), we pause the Direct Numerical Simulation (DNS)
-which is evolving the dynamics of the convection and solve a 1D Boundary Value Problem (BVP)
+which is evolving the dynamics of convection and solve a 1D Boundary Value Problem (BVP)
 consisting of Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
-After solving this BVP, we adjust the fields being evolved in the DNS appropriately
+After solving this BVP, we appropriately adjust the fields being evolved in the DNS
 towards their evolved state, and then we continue running the now-evolved DNS.
-There specific steps taken in completing the AE method are as follows:
+The specific steps taken in completing the AE method are as follows:
 \begin{enumerate}
-\item After the start of the DNS, we wait some time, $t_{\text{transient}}$ after
-the convective transient in which the dynamics vigorously break away from the hydrostatic
-state.
-\item Then, during the DNS, we calculate time averages of the 1D profiles of
+\item Wait some time, $t_{\text{transient}}$, before beginning the AE process.
+\item During the DNS, calculate time averages of the 1D profiles of
 $F_{\text{conv}}$, $F_{\text{tot}}$, 
@@
 total time elapsed over which the average is taken. 
-\item We pause the DNS once the averages are sufficiently converged. 
+\item Pause the DNS once the averages are sufficiently converged. 
 To ensure that an average is converged, at
@@
 set $t_{\text{transient}} = 50$, completed an AE BVP solve
-with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure,
-including another wait of $t_{\text{transient}} = 50$ before beginning averages.
+with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure.
 For all 3D runs and 2D runs with $S \in [10^5, 10^6]$,
@@
 value of $S$ in part to reduce the computational expense of the run, and in
-part because of how a third BVP generally did not modify the solution hugely
-(as in Fig. \ref{fig:time_trace}c).
+part because a third BVP generally did not greatly alter the solution
+(as in Fig. \ref{fig:time_trace}c, arrow 3).
 
@@
 conducted in this work.  The supercriticality, Rayleigh number, and resolution
-are reported.  We report the simulation run time of the SE solutions and AE
-solutions, as well as the amount of time over which average measurements
-were taken, in freefall time units.  The volume-averaged Nusselt number of the
+are reported.  We report the simulation run time required to reach a converged
+state for the SE solutions (one thermal time)
+and AE solutions, as well as the amount of time over which average measurements
+were taken once the simulations were converged, in freefall time units.  The volume-averaged Nusselt number of the
 AE and SE solutions are shown.
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X X X X X X }
+\begin{tabularx}{\textwidth}{ X X X X | X X X | X X }
 \hline																	
-$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
+$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{AE}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
 \hline																	
-$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	100	&	1.46	&	1.46	\\
-$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	100	&	1.95	&	1.95	\\
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	100	&	2.43	&	2.42	\\
-$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	100	&	2.54	&	2.54	\\
-$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	100	&	3.14	&	3.14	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	100	&	3.8	&	3.8	\\
-$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	$528$	&	100	&	4.71	&	4.71	\\
-$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	$776$	&	100	&	5.5	&	5.5	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	$1.14 \cdot 10^3$	&	200	&	6.4	&	6.33	\\
-$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	$1.67 \cdot 10^3$	&	500	&	6.87	&	6.95	\\
-$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	$2.45 \cdot 10^3$	&	500	&	7.54	&	7.59	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	$3.60 \cdot 10^3$	&	500	&	8.83	&	8.83	\\
-$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	$5.28 \cdot 10^3$	&	500	&	10.13	&	10.14	\\
-$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	$7.76 \cdot 10^3$	&	500	&	11.65	&	11.69	\\
-$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
-$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	500	&	--	&	16.21	\\
-$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	500	&	--	&	18.58	\\
-$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	500	&	--	&	22.13	\\
-$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	200	&	--	&	40.78	\\
+$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	---	&	100	&	1.46	&	1.46	\\
+$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	---	&	100	&	1.95	&	1.95	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	---	&	100	&	2.43	&	2.42	\\
+$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	---	&	100	&	2.54	&	2.54	\\
+$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	---	&	100	&	3.14	&	3.14	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
+$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	$528$	&	$248$	&	100	&	4.71	&	4.71	\\
+$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	$776$	&	$251$	&	100	&	5.5	&	5.5	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	$1.14 \cdot 10^3$	&	$268$	&	200	&	6.4	&	6.33	\\
+$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	$1.67 \cdot 10^3$	&	$247$	&	500	&	6.87	&	6.95	\\
+$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	$2.45 \cdot 10^3$	&	$275$	&	500	&	7.54	&	7.59	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	$3.60 \cdot 10^3$	&	$301$	&	500	&	8.83	&	8.83	\\
+$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	$5.28 \cdot 10^3$	&	$317$	&	500	&	10.13	&	10.14	\\
+$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	$7.76 \cdot 10^3$	&	$326$	&	500	&	11.65	&	11.69	\\
+$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	$411$	&	500	&	14.02	&	14.18	\\
+$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	$391$	&	500	&	---	&	16.21	\\
+$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	$453$	&	500	&	---	&	18.58	\\
+$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
+$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	200	&	---	&	40.78	\\
 \\ \hline \hline \\																	
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	100	&	2.42	&	2.42	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128$\times$128	&	$360$	&	100	&	3.97	&	4	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256$\times$256	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512$\times$512	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	$261$	&	100	&	2.42	&	2.42	\\
+$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128$\times$128	&	$360$	&	$249$	&	100	&	3.97	&	4	\\
+$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256$\times$256	&	$1.14 \cdot 10^3$	&	$243$	&	500	&	6.27	&	6.27	\\
+$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512$\times$512	&	$3.60 \cdot 10^3$	&	$244$	&	500	&	9.92	&	9.88	\\
 \hline																	

### 2018-03-09 tex/bvp_paper.tex
adds new fig

@@
 \label{sec:intro}
-Natural convection occurs in the presence of disparate timescales which
+Astrophysical convection occurs in the presence of disparate timescales which
 prohibit numericists from studying realistic models of systems in nature.  For example,
@@
 have been used to study low-Ma flows \cite{brown&all2010, featherstone&hindman2016}.
-More recently, advanced numerical techniques which use implicit or mixed
-implicit-explicit timestepping mechanisms have made it feasible to study
-convection at low Mach numbers \cite{viallet&all2011, viallet&all2013, viallet&all2016, lecoanet&all2014,
-anders&brown2017, bordwell&all2018}, and careful studies of deep convection which
+More recently, advanced numerical techniques which use fully implicit 
+\cite{viallet&all2011, viallet&all2013, viallet&all2016} or mixed
+implicit-explicit \cite{lecoanet&all2014, anders&brown2017, bordwell&all2018} 
+timestepping mechanisms have made it feasible to study
+convection at low Mach numbers, and careful studies of deep convection which
 would have been impossible a decade ago are now widely accessible.
@@
 Unfortunately, convective systems generally evolve over the course of thermal
-timescales, which are often much larger than
+timescales, which are often much larger than all relevant
 dynamical timescales. Therefore resolving dynamics in atmospheres which are sufficiently
@@
 Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
-but it is not without its faults.  Bootstrapped solutions are succeptible to hysteresis
+but it is not without its faults.  Bootstrapped solutions are susceptible to hysteresis
 effects, in which large-scale convective structures present in the
@@
 can only reasonably be run
-for tens to hundreds of freefall timescales \cite{stevens&all2011}, much less the
-thousands of freefall times required for thermal convergence.
+for hundreds of freefall timescales \cite{stevens&all2011}, much less the
+thousands or millions freefall times required for thermal convergence.
 
 In this work, we study a method of achieving accelerated evolution of
-convective simulations. We couple measurements of the dynamics of non-converged
+convective simulations. We couple measurements of the dynamics of unequilibrated
 convective simulations with knowledge about energy balances in the desired solution
-to self-consistently adjust the mean thermodynamic profile towards its evolved state. 
-While such a method has been used previously \cite{hurlburt&all1986}, 
+to self-consistently adjust the mean vertical thermodynamic profile towards its evolved state. 
+While a technique of this kind has been used previously \cite{hurlburt&all1986}, 
 we find no explanation in the current literature of the steps involved in employing
-this method, nor any study into the accuracy of such a method.
+this method, nor do we find any study of its accuracy.
 In section \ref{sec:experiment}, we describe our convective simulations, our
-numerical methods, and our method for achieving accelerated evolution. In
+numerical methods, and the procedure for achieving accelerated evolution. In
 section \ref{sec:results}, we compare accelerated evolution solutions
@@
 where $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$ is the velocity, 
-$T = T_0 + T_1$ are the initial and fluctuating components of temperature, 
-and $P$ is the pressure.
+$T = T_0(z) + T_1(x, y, z, t)$ are the initial and fluctuating components of temperature, 
+and $P$ is the kinematic pressure.
 We non-dimensionalize these equations such that
@@
 $\varpi \equiv (P / \rho_0 + \phi + |\bm{u}|^2 / 2) / v_{\text{ff}}^2$, where the gravitational
-potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. As $P$ is a
-Langrange multiplier under the Oberbeck-Boussinesq approximation, $\varpi$
-can be treated straightforwardly as a linear variable. 
+potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. 
 In non-dimensional form, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
@@
 where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
-The dimensionless control parameters $\mathcal{P}$ and $\mathcal{R}$ 
-are set by the Rayleigh and Prandtl numbers,
+The dimensionless control parameters $\mathcal{R}$ and $\mathcal{P}$ 
+are set by the Rayleigh (Ra) and Prandtl (Pr) numbers,
 \begin{equation}
@@
 \end{equation}
-We hold Pr$ = 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.
+We hold Pr $= 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.
 
+In Eqns. (\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}),
+linear terms are grouped on the left-hand side of the equations, while nonlinear terms
+are found on the right-hand side. We timestep linear terms implicitly, and nonlinear
+terms explicitly.
+We utilize the 
+Dedalus\footnote{\url{http://dedalus-project.org/}} 
+pseudospectral framework \cite{burns&all2016} to evolve  
+Eqns. (\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}) 
+forward in time
+using an implicit-explicit (IMEX), third-order, four-stage 
+Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.
+
+Variables are time-evolved on a dealiased Chebyshev (vertical)
+and Fourier (horizontal, periodic) domain in which the
+physical grid dimensions are 3/2 the size of the coefficient grid.  
 We study 2D and 3D convection in which the domain is a cartesian box, 
@@
 reflects the fact that the conditions in Eqn. (\ref{eqn:bcs}) are the simplest
-to implement in the process of accelerated evolution (see section \ref{subsection:ae})
+to implement in the process of accelerated evolution (section \ref{subsection:ae})
 we study here.
 
-We utilize the 
-Dedalus\footnote{\url{http://dedalus-project.org/}} 
-pseudospectral framework \cite{burns&all2016} to evolve  
-Eqns. (\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}) 
-forward in time
-using an implicit-explicit (IMEX), third-order, four-step 
-Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
-The linear terms (on the LHS of the equations) are solved implicitly,
-while the nonlinear terms (RHS) are explicitly solved.
-Variables are time-evolved on a dealiased Chebyshev (vertical)
-and Fourier (horizontal, periodic) domain in which the
-physical grid dimensions are 3/2 the size of the coefficient grid.
-
-As initial conditions, we fill $T_1$ with
+The initial temperature profile is linearly unstable,
+$T_0(z) = -z$. On top of this profile, we fill $T_1$ with
 random white noise whose magnitude is $10^{-6}\mathcal{P}$.
@@
 (SE), in which we naively evolve the atmosphere for one thermal diffusion time,
-$t_\kappa = \mathcal{P}^{-1}$. As Ra increases, SE solutions become intractable, 
+$t_\kappa = \mathcal{P}^{-1}$. Both AE and SE simulatins begin with identical
+initial conditions, as described in section \ref{sec:experiment}.
+As Ra increases, and $\mathcal{P}$ decreases, SE solutions become intractable, 
 while the timeframe of convergence for an AE solution remains nearly constant
-in freefall time units.
+in simulation freefall time units (see table \ref{table:run_parameters}).
+
 For an example of time saving achieved by using AE, we compare
@@
 in Fig. \ref{fig:time_trace}c.
+In Fig. \ref{fig:time_trace}a, the time evolution of the SE simulation is shown.
+The solution grows exponentially from white noise during the
+first $\sim 25$ $t_{\text{ff}}$. The solution then saturates and begins to slowly
+equliibrate towards the proper isothermal profile in the interior of the domain.
+We find that the mean atmospheric temperature and
+kinetic energies are fully converged when $t = 4000$ $t_{\text{ff}}$ $= 0.35$ $t_{\kappa}$.
+We show roughly the first thousand freefall time
+units of evolution, as well as the evolved thermodynamic state reached after a full
+thermal time of evolution.  In Fig. \ref{fig:time_trace}c, we show an AE solution
+at the same parameters. The same linear growth phase occurs, but shortly after
+the peak of convective transient we accelerate the convergence of the atmosphere
+through the process which we describe below. We adjust the 1D vertical profile of
+the atmosphere three times, as denoted by the three labeled
+arrows in the graph numbered 1-3.  After the third profile adjustment, we find that
+the atmosphere is nearly in its converged state and we can begin to sample the evolved
+convective dynamics.
 
 The horizontally averaged profiles of the vertical conductive flux, 
-F$_{\text{cond}} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective flux,
-F$_{\text{conv}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method.
+F$_{\kappa} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective enthalpy flux,
+F$_{\text{E}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method.
 Here we use $\angles{}_{x,y}$ to represent a horizontal average. We measure
@@
 those shown in Fig. \ref{fig:time_trace}b.
-At early stages in the simulation, these flux profiles are highly asymmetric,
+At these early times, the flux profiles are highly asymmetric,
 with more flux exiting the atmosphere at the upper boundary than 
-the fixed-flux lower boundary is providing.
-By calculating the total flux,
-F$_{\text{tot}} =$ F$_{\text{conv}} +$ F$_{\text{cond}}$, we derive the profiles
-\begin{equation}
-f_{\text{conv}}(z) = \frac{F_{\text{conv}}}{F_{\text{tot}}},\qquad
-f_{\text{cond}}(z) = \frac{F_{\text{cond}}}{F_{\text{tot}}},
-\label{eqn:bvp_ratios}
-\end{equation}
-which have the systematic asymmetries removed. These profiles describe which
-parts of the atmosphere depend on convection to carry flux (where $f_{\text{conv}}(z) = 1$
-and $f_{\text{cond}}(z) = 0$).
-We presume that the early convection occupies roughly the same volume as the evolved
-convection, and thus that the extent of the early thermal boundary layers 
-(where $f_{\text{cond}}(z) = 1$ and $f_{\text{conv}}(z) = 0$) 
-will not change significantly over the course of the atmosphere's evolution.
-Under this assumption, the proper evolved atmospheric flux profiles
-are F$_{\text{conv, ev}} = \text{F}_{\text{bot}}\cdot f_{\text{conv}}$
-and F$_{\text{cond, ev}} = \text{F}_{\text{bot}}\cdot f_{\text{cond}}$,
-where F$_{\text{bot}} = \mathcal{P}$ is the amount of flux entering the
-bottom of the atmosphere.
+the fixed-flux lower boundary can provide. As the atmosphere evolves towards
+the isothermal profile specified by the upper (cold) boundary condition, excess
+temperature throughout the atmosphere must leave the domain, and this appears in
+the flux measurements in Fig. \ref{fig:time_trace}b where the flux exiting the upper
+boundary is nearly 2000\% the flux entering the bottom of the domain. Once the atmospheric
+temperature profile reaches its evolved state, the flux entering the bottom boundary
+is equal to the flux exiting the upper boundary.  In general, this takes very long time
+frames through SE (Fig. \ref{fig:time_trace}a), but AE (Fig. \ref{fig:time_trace}b)
+can take a system whose fluxes are in a strongly disequilibrium state (Fig. \ref{fig:time_trace}c),
+and quickly put them into a near-equilibrium state, as shown in Fig. \ref{fig:time_trace}d. In
+this final state, there is no conductive flux in the interior, both boundaries carry the
+same amount of flux, and convection carries that amount of flux through the interior.
+The converged state achieved through AE is at most 5\% different from the SE solution, as shown in
+Fig. \ref{fig:time_trace}e.
 
-\begin{figure*}[t!]
+\begin{figure}[p!]
 \includegraphics[width=\textwidth]{./figs/time_trace.png}
@@
 are denoted by the horizontal dashed lines. (b) The time- and horizontally-averaged
-flux profiles are shown for the times highlighted in orange in (a).
+flux profiles are shown for the times highlighted in orange.
 (c) The same quantities as in (a) are shown, but for AE at the same parameters.
@@
 are shown in (d). The difference between
-the fluxes in the AE and SE solutions is shown in (e). The dashed
-vertical line in (a) and (c) denotes the simulation time at which evolved measurements
-are started for the AE case.
-\label{fig:time_trace} }
-\end{figure*}
+the fluxes in the AE and SE solutions is shown in (e). \label{fig:time_trace} }
+\end{figure}
+
+In order to adjust the temperature profle to achieve AE, we calculate the total flux,
+F$_{\text{tot}} =$ F$_{\text{E}} +$ F$_{\kappa}$, and then derive the profiles
+\begin{equation}
+f_{\text{E}}(z) = \frac{\text{F}_{\text{E}}}{\text{F}_{\text{tot}}},\qquad
+f_{\kappa}(z) = \frac{\text{F}_{\kappa}}{\text{F}_{\text{tot}}},
+\label{eqn:bvp_ratios}
+\end{equation}
+which have the systematic asymmetries removed. These profiles describe which
+parts of the atmosphere depend on convection to carry flux (where $f_{\text{E}}(z) = 1$
+and $f_{\kappa}(z) = 0$).
+We presume that the early convection occupies roughly the same volume as the evolved
+convection, and thus that the extent of the early thermal boundary layers 
+(where $f_{\kappa}(z) = 1$ and $f_{\text{E}}(z) = 0$) 
+will not change significantly over the course of the atmosphere's evolution.
+Under this assumption, in order to reach the converged state, 
+the flux through the atmosphere must be decreased by some amount,
+\begin{equation}
+\xi(z) \equiv \frac{\text{F}_{\text{B}}}{\text{F}_{\text{tot}}},
+\label{eqn:xi}
+\end{equation}
+where $\text{F}_{\text{B}} = \mathcal{P}$ is the amount of flux that enters the
+bottom of the atmosphere.
 
@@
 \begin{gather}
-\frac{\partial}{\partial z}\angles{\varpi}_{x,y} - \angles{T_1}_{x,y}\hat{z} = \angles{\bm{u}\times\bm{\omega}}_{x,y},
+\frac{\partial}{\partial z}\angles{\varpi}_{x,y} - \angles{T_1}_{x,y}\hat{z} = \angles{\bm{u}\times\bm{\omega}}_{x,y, \text{ ev}},
 	\label{eqn:bouss_BVP_momentum}
 \\
-\frac{\partial}{\partial z}\text{F}_{\text{conv, ev}} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1}_{x,y} = 0.
+\frac{\partial}{\partial z}\text{F}_{\text{E, ev}} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1}_{x,y} = 0.
 	\label{eqn:bouss_BVP_energy}
 \end{gather}
+Here, we construct $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
+\xi(z) \angles{\bm{u}\times\bm{\omega}}_{x, y}$ and $\text{F}_{\text{E, ev}} = \xi(z) \text{F}_{\text{E}}$
+from our unevolved state, and solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
 Convective flows
@@
 
-Thus, the AE method is simple: we construct F$_{\text{conv, ev}}$ as described above.
-Then we calculate a profile, 
-$\xi(z) = \text{F}_{\text{conv, ev}}/\text{F}_{\text{conv}}$, which is the fraction,
-as a function of height, by which the flux in the system must be reduced to go from
-an initial state (Fig. \ref{fig:time_trace}b) to an evolved state (Fig. \ref{fig:time_trace}d).
-We multiply the velocities
-and the thermal fluctuations, $T - \angles{T}_{x,y}$, by $\sqrt{\xi}$, such 
-that the advected, flux-carrying perturbations in the temperature are appropriately
-diminished.  We then solve a 1D boundary value problem including
-Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}) using F$_{\text{conv, ev}}$
-and $\angles{\bm{u}\times\bm{\omega}}_{x,y}$, after diminishing it by a factor
-of $\xi$. We use mixed thermal boundary conditions in this study, 
-as in Eqn. (\ref{eqn:bcs}),
-because $F_{\text{bot}}$ is exactly specified, and the temperature profile is fixed 
-at a reference value for the AE solve.
+Thus, the AE method is simple: we construct $\xi(z)$ from measured information about
+the convective dynamics. We solve a 1D boundary value problem consisting of
+Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
+to obtain the proper evolved thermodynamic profile, and proper conductive flux.
+To obtain the proper convective enthalpy flux, we multiply both the velocity field,
+$\bm{u}$, and the temperature perturbations around the mean, $T - \angles{T}_{x,y}$,
+by $\sqrt{\xi}$, thus diminishing the magnitude of these perturbations appropriately.
+After adjusing the fields of a simulation in this manner, we continue timestepping forward.
 For specifics on the precise implementation of the AE method, we refer
 the reader to appendix \ref{appendix:recipe}.
-
-The AE method converges atmospheres from extreme flux disequilibrium states 
-(Fig. \ref{fig:time_trace}b) on short dynamical timescales (Fig. \ref{fig:time_trace}c)
-to a converged state (Fig. \ref{fig:time_trace}d) whose flux balance is very
-close to the balance present in the corresponding SE solution (Fig. \ref{fig:time_trace}e).
-While the application of the AE method advances solutions toward the proper solution,
-we find that multiple applications of the method is the best means of achieving converged
-solutions quickly.
 
@@
 \label{sec:results}
-We study evolved SE solutions in $S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
+We study evolved SE solutions whose supercriticalities ($S$) are 
+$S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
 3D. We compare their properties to
@@
 carried out due to computational expense. The run at $S = 10^5$ marked as a
-black square is examined in more details in Figs. \ref{fig:time_trace},
+black square is examined in more detail in Figs. \ref{fig:time_trace},
 \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
@@
 In Table \ref{table:run_parameters} we list key properties of all simulations
-conducted in this work.  The supercriticality, Rayleigh number, and resolution
-are reported.  We report the simulation run time required to reach a converged
-state for the SE solutions (one thermal time)
-and AE solutions, as well as the amount of time over which average measurements
-were taken once the simulations were converged, in freefall time units.  The volume-averaged Nusselt number of the
+conducted in this work.  
+\begin{table}
+\caption{Simulation parameters. We report the supercriticality ($S$), Rayleigh number (Ra), 
+and coefficient resolution (nz, nx, and ny are the number of coefficients in the
+z, x, and y directions respectively).
+Simulation run times required to reach convergence
+are reported for the SE solutions ($t_{\text{therm}}$) and the AE solutions ($t_{\text{AE}}$).
+The amount of time over which simulations measurements were taken in the evolved
+state is listed ($t_{\text{avg}}$). All times are in freefall time units.  
+The volume-averaged Nusselt number (Nu) of the
 AE and SE solutions are shown.
@@
 3D runs.
-
-\begin{table}
-\caption{Simulation parameters}
+}
 \label{table:run_parameters}
@@
 \hline																	
-$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	---	&	100	&	1.46	&	1.46	\\
-$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	---	&	100	&	1.95	&	1.95	\\
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	---	&	100	&	2.43	&	2.42	\\
-$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	---	&	100	&	2.54	&	2.54	\\
-$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	---	&	100	&	3.14	&	3.14	\\
+$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	$340$	&	100	&	1.46	&	1.46	\\
+$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	$282$	&	100	&	1.95	&	1.95	\\
+$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	$265$	&	100	&	2.43	&	2.42	\\
+$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	$251$	&	100	&	2.54	&	2.54	\\
+$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	$245$	&	100	&	3.14	&	3.14	\\
 $10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
@@
 $10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
-$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	200	&	---	&	40.78	\\
+$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	40.78	\\
 \\ \hline \hline \\																	

### 2018-03-09 code/plotting/oscillating_plumes.py

@@ -1,0 +1,121 @@
+import matplotlib.style
+import matplotlib
+matplotlib.use('Agg')
+matplotlib.style.use('classic')
+matplotlib.rcParams.update({'font.size': 11})
+import matplotlib.pyplot as plt
+plt.rc('font',family='Times New Roman')
+from matplotlib.colors import ColorConverter
+import os
+import numpy as np
+import glob
+from docopt import docopt
+from mpi4py import MPI
+comm_world = MPI.COMM_WORLD
+from collections import OrderedDict
+import h5py
+import matplotlib.gridspec as gridspec
+
+
+import dedalus.public as de
+from scipy.interpolate import interp1d
+
+
+
+
+
+base_dir = '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+subdir = 'rayleigh_benard_2D_mixed_noSlip_Ra1.30e8_Pr1_a2/'
+subdir2 = 'rayleigh_benard_2D_mixed_noSlip_Ra1.30e10_Pr1_a2/'
+full_dir = base_dir + '/' + subdir
+full_dir2 = base_dir + '/' + subdir2
+
+
+plt.figure(figsize=(8, 3))
+gs     = gridspec.GridSpec(*(1000,1000))
+
+slices1 = h5py.File('{:s}/slices/slices_s81.h5' .format(full_dir), 'r')
+slices2 = h5py.File('{:s}/slices/slices_s134.h5'.format(full_dir), 'r')
+slices3 = h5py.File('{:s}/slices/slices_s75.h5'.format(full_dir2), 'r')
+slices4 = h5py.File('{:s}/slices/slices_s81.h5'.format(full_dir2), 'r')
+scalars = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir), 'r')
+scalars2 = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir2), 'r')
+
+temp1 = slices1['tasks']['T'][5,:,:]
+temp2 = slices2['tasks']['T'][10,:,:]
+temp3 = slices3['tasks']['T'][0,:,:]
+temp4 = slices4['tasks']['T'][0,:,:]
+x     = slices1['scales']['x']['1.0'].value
+z     = slices1['scales']['z']['1.0'].value
[…]

### 2018-03-09 code/plotting/parameter_space_comparison.py

@@ -45,6 +45,9 @@ for a, base_dir in enumerate(base_dirs):
 
     for i, d in enumerate(glob.glob('{:s}/*/'.format(base_dir))):
         ra = d.split('_Ra')[-1].split('_')[0]
+        fancy = False
+        if ra == '1.30e10':
+            fancy = True
         ra += '_{}'.format(a)
 
         info[ra] = OrderedDict()
@@ -55,6 +58,10 @@ for a, base_dir in enumerate(base_dirs):
                     if 'Nu' in k:
                         print(a, 'Nu', ra, np.mean(f[k].value))
                 info[ra]['sim_time'] = f['sim_time'].value
+                if fancy:
+                    where = info[ra]['sim_time'] > 209.8
+                    for k in info[ra].keys():
+                        info[ra][k] = info[ra][k][where]
         except:
             print('cannot find file in {:s}'.format(d))
 
@@ -164,7 +171,7 @@ for i,k in enumerate(fields):
             ax.errorbar(float(ra), mean, yerr=std,  color=color)
             ax.scatter(float(ra), mean, s=s, marker=mrkr, color=color, alpha=0.75)
     bx.set_xlabel('S')
-    ax.legend(fontsize=8, loc='upper left', ncol=2, scatterpoints=1, handlelength=1, frameon=True)
+    ax.legend(fontsize=8, loc='lower right', ncol=2, scatterpoints=1, handlelength=1, frameon=True)
 #    ax.grid(which='major')
 
     if k == 'IE':
@@ -176,14 +183,14 @@ for i,k in enumerate(fields):
 #        ax.set_ylabel(r'$\langle T_1 \rangle - T_{\mathrm{top}}$', fontsize=10, labelpad=4)
 #        ax.set_ylim(1, 2)
     elif k == 'Nu':
-        ax.annotate(r'$\mathrm{(a)}$', (1e9, 1.5e0), fontsize=10)
+        ax.annotate(r'$\mathrm{(a)}$', (2e3, 5e1), fontsize=10)
         label_end = '-{:.2g}'.format(pNu)
         label_end = '$\\langle\\mathrm{Nu}\\rangle$'#\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end))
         ax.set_ylim(1, 1e2)
[…]

### 2018-03-09 code/plotting/time_trace.py

@@ -305,8 +305,8 @@ z = pre_flux_file['z'].value
 
 axes[-1].axhline(1, c='k', ls=':')
 axes[-1].axhline(0, c='k')
-axes[-1].plot(z, enth,  c=f_conv_color, label=r'$\mathrm{F}_{\mathrm{conv}}$', lw=2)
-axes[-1].plot(z, kappa, c=f_cond_color, label=r'$\mathrm{F}_{\mathrm{cond}}$', lw=2)
+axes[-1].plot(z, enth,  c=f_conv_color, label=r'$\mathrm{F}_{\mathrm{E}}$', lw=2)
+axes[-1].plot(z, kappa, c=f_cond_color, label=r'$\mathrm{F}_{\kappa}$', lw=2)
 axes[-1].plot(z, sum_f, c=f_sum_color, label=r'$\mathrm{F}_{\mathrm{tot}}$', lw=2)
 y_ticks = np.array([0, 5, 10, 15, np.ceil(np.max(sum_f))])
 axes[-1].set_yticks(y_ticks)

### 2018-03-09 code/run_scripts/2d/bvp_pre/local_runs.sh

@@ -1,5 +1,5 @@
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e3   --do_bvp --num_bvps=2 --bvp_final_equil_time=50  
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e3   --do_bvp --num_bvps=2 --bvp_final_equil_time=50 
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=1.30e4   --do_bvp --num_bvps=2 --bvp_final_equil_time=50 
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e4   --do_bvp --num_bvps=2 --bvp_final_equil_time=50 
-mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=6.01e4   --do_bvp --num_bvps=2 --bvp_final_equil_time=50
+mpirun -n 2 python3 rayleigh_benard.py --aspect=2 --nx=64 --nz=32 --root_dir=runs/bvp_pre --run_time_therm=15 --mixed_flux_T --no_slip --Rayleigh=2.79e3   --do_bvp --num_bvps=2 --bvp_final_equil_time=50 --first_bvp_time=30 --first_bvp_convergence_factor=1e-3 --bvp_transient_time=50 --bvp_equil_time=50 --bvp_convergence_factor=1e-3 --min_bvp_time=30   
[…]

### 2018-03-14 tex/bvp_paper.tex
updates to figures, need to finalize text

@@
 \newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
+\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
+\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
 \newcommand{\grad}{\ensuremath{\nabla}}
@@
 
-\vspace{5cm}
-$\,$\newline
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
+\caption{. \label{fig:oscillating_plumes} }
+\end{figure}
+
+The Nusselt number (Nu) quantifies the efficiency of convective heat transport
+and is defined as
+\begin{equation}
+\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
+ = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
+\end{equation}
+where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
+When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
+the evolved system is characterized by a specific
+value of Nu, as the convective heat transport reaches a temporally stationary state.
+At larger values of $S$ in 2D, the value of Nu varies significantly over time,
+as shown by the time traces for $S = 10^5$ (top) and $S = 10^7$ (bottom) for two
+AE runs in Fig. \ref{fig:oscillating_plumes}. We find that these systems go between
+states in which temperature fluctuations primarily travel in their natural buoyant
+direction (as in Ia and IIa, where cold elements are falling and hot elements rise),
+and states in which temperature perturbations are entrained in an upflow or downflow
+with oppositely signed fluid (as in Ib and IIb, where warm fluid is pulled down by the downflow
+lane, and cool fluid is pulled up by the upflow lane).  The fluid from the oppositely
+signed plume pushes on the other plume such that the system goes between states in which
+the fluid primarily serves to enhance convective transport (Ia and IIa), states in which
+there is counterclockwise entrainment (IIa and IIb), then back to enhanced transport states
+followed by clockwise entrainment.  This horizontally oscillatory motion that characterizes the
+plumes provides, and the resultant time-dependent entrainment, leads to large variations in Nu over time 
+As a result of our choice of no-slip
+boundary conditions, the fluid never enters a full domain shearing state 
+\cite{goluskin&all2014}, and the
+oscillatory nature of the plumes is stable.
+The 2D SE simulations exhibit the same horizontally
+oscillatory behavior as the AE solutions for the same initial conditions. 
+This time-dependent behavior or Nu is not seen strongly in our 3D solutions,
+likely as a result of the extra degrees of freedom in which rising and falling
+fluid elements can expand, reducing entrainment.
+
 The time- and volume-averaged values of the Nusselt number (Nu), the RMS
@@
 is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
-Nu is defined as
-\begin{equation}
-\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
- = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
-\end{equation}
-where the volume average of a quantity, $g$, is shown as $\angles{g}$.
-When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
-the evolved system is characterized by a specific
-value of Nu, as the convective heat transport reaches a temporally stationary state.
-At larger values of $S$ in 2D, the convective plumes consistently oscillate
-horizontally, leading to variations in Nu over time as the heat transport is alternately
-assisted and diminished by these oscillations.
-As a result of our choice of no-slip
-boundary conditions, the fluid never enters a full domain shearing state 
-\cite{goluskin&all2014}, and the
-oscillatory nature of the plumes is stable.
-The 2D SE simulations exhibit the same horizontally
-oscillatory behavior as the AE solutions for the same initial conditions. The
+The
 dynamic nature of the plume structures diminishes the
@@
 bootstrapping techniques as initial conditions for high $S$ runs.
+In Fig. \ref{fig:parameter_space_comparison}b, we report 
+$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measures the degree of
+turbulence in the solution, and scales roughly as
+$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
+the value of Re over time.
+Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$.
+The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
+so this measurements serves as a probe of the temperature jump across the boundary
+layers. As a result, we expect this measure to
+scale inversely with Nu in converged solutions
+where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
+that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
+scaling of Nu.
 
@@
 Symbols are located at the mean value of
-each measurement.  Vertical lines represent the standard deviation of the measurement,
-and quantify natural variation over the
-averaging window. Error bars represent the change in the mean value over the averaging window,
-such that very large error bars represent solutions which are not fully converged when averaging
-begins.
+each measurement and denote 2D (purple circles) and 3D (red stars). 
+The run at $S = 10^5$ marked as a
+black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
+\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
+Vertical lines represent the standard deviation of the measurement,
+and quantify natural variation over the averaging window. 
 (a) Nu scales as Ra$^{1/5}$; above S$\geq 10^{3+2/3}$,
-simulations exhibit oscillating plume structures whose heat transport fluctuates over time.  
+simulations exhibit oscillating plume structures whose heat transport fluctuates over time
+as a result of temporally-varying entrainment of wrongly signed temperature perturbations
+(see Fig. \ref{fig:oscillating_plumes}).  
 (b) Re, which measures the level of turbulence in the evolved solution, scales as
@@
 The greyed area of the plots indicates the region in which only AE runs were
-carried out due to computational expense. The run at $S = 10^5$ marked as a
-black square is examined in more detail in Figs. \ref{fig:time_trace},
-\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
-\label{fig:parameter_space_comparison} }
+carried out due to computational expense. \label{fig:parameter_space_comparison} }
 \end{figure}
 
-In Fig. \ref{fig:parameter_space_comparison}b, we report 
-$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measures the degree of
-turbulence in the solution, and scales roughly as
-$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
-the value of Re over time.
-
-Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$.
-The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
-so this measurements serves as a probe of the temperature jump across the boundary
-layers. As a result, we expect this measure to
-scaling inversely with Nu in converged solutions
-where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
-that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
-scaling of Nu.
+This is a short paragraph which says 2D and 3D are the same, here.
 
@@
 of point-by-point measurements of the temperature field.
-$T$ is sampled every 0.1 time units for 500 total time units,
-and was interpolated onto an evenly spaced grid before sampling.
 (c) The percentage difference between the mean temperature profiles as a function of height.
@@
 disappear, as the AE solution evolves to be exactly the SE solution -- this
-is evident in the asymmetry of the AE PDF in Fig. \ref{fig:temp_comparison}b and also
-the trend of the mean temperature over time in Fig. \ref{fig:temp_comparison}c.
+is evident in the asymmetry of the AE PDF near the mode
+in Fig. \ref{fig:temp_comparison}b and also
+the trend of the mean temperature over time in Fig. \ref{fig:time_trace}c.
 
@@
 PDFs to determine if they are drawn from the same underlying
-sample distribution is through the use of a Kolmogorov-Smirnov (KS) \cite{wall&jenkins2012}.
-In general, a KS test must be conducted on independent, uncorrelated data, which
-poorly describes the point-by-point values of flows in a fluid simulation. Thus,
-we cannot directly use a KS test to determine if the two fluid samples are the same,
-but we can draw insight from the profile
-$\text{KS} = \text{CDF}_{\text{AE}} - \text{CDF}_{\text{SE}},$
+sample distribution is through the use of a Kolmogorov-Smirnov (KS) test \cite{wall&jenkins2012}.
+We calculate the KS statistic for a PDF of some value, $q$, as
+\begin{equation}
+\KS{q} = \text{CDF}_{\text{AE}}(q) - \text{CDF}_{\text{SE}}(q),
+\label{eqn:ks_profile}
+\end{equation}
 where CDF stands for cumulative distribution function, the integral of the PDF.
-A traditional Kolmogorov-Smirnov statistic is the maximum of the absolute value of
-the KS profile.  We show the KS profile in Fig. \ref{fig:temp_comparison}d, and the
+A traditional Kolmogorov-Smirnov statistic is just a single value,
+$\KSstat{q} = |\KS{q}|_\infty =
+\text{max} |\KS{q}|$, and we use both the profile KS$(q)$ and
+$\KSstat{q}$ to gain insight into the likeness of two PDFs. 
+We show the KS profile in Fig. \ref{fig:temp_comparison}d, and the
 CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
-Near the modes of the temperature PDFs, the KS profile has a maximum value of
-0.495, which is very large and implies that roughly half of all temperature
+Near the modes of the temperature PDFs, the $\KSstat{T} = 0.495$, 
+which is very large and implies that roughly half of all temperature
 measurements in the SE case are greater than those in the AE case.
@@
 The CDFs of each profile are overplotted, and corresponding KS profiles are
-shown in Fig. \ref{fig:pdf_comparison}d-f.  The maximum absolute values of the
-KS profiles of vertical velocity, horizontal velocity, and nonlinear vertical convective flux
-are 0.00615, 0.0349, and 0.0263, respectively.  
+shown in Fig. \ref{fig:pdf_comparison}d-f.  We report
+$\KSstat{w} = 0.00615$ (vertical velocity), $\KSstat{u} = 0.0349$ (horizontal velocity),
+and $\KSstat{w(T - \angles{T}_{x,y})} = 0.0263$.
 Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
@@
 The difference in vertical velocity
-and heat transport is negligible, which is unsurprising in light of
+and heat transport between AE and SE is negligible, which is unsurprising in light of
 the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
@@
 convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
-at $S = 10^{5}$.  Flows are sampled every 0.1 time units for 500 total time units,
-and are first interpolated onto an evenly spaced grid.
-The cumulative distribution function (CDF) is overplotted for each PDF. 
+at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
 (d-f) The KS statistics, or the values of CDF$_{\text{AE}}$ - CDF$_{\text{SE}}$,
@@
 
-\section{Extensions \& Conclusion}
+\section{Extensions \& Conclusions}
 \label{sec:extensions}
@@
 at high values of $S$, where SE solutions are intractable.
-We have studied
-the AE method in both 2D and 3D, but restricted most of our study to 2D flows;
-AE depends only on 1D, horizontally averaged profiles of dynamics, and our inclusion of 3D
-simulations was merely to demonstrate the broadly useful nature of AE.
+As discussed, 2D and 3D are identical short of the time-varying entrainment states
+(Fig. \ref{fig:oscillating_plumes}), so we have restricted most of our study to 2D.
+However, due to the greater computational expense of 3D runs, they stand to gain more
+time savings from AE. This is a sentence about the magnitude of savings involved for
+AE vs. SE (wall time + cpu hours, 2d: $10^5$, 3d: $10^4$).
 
@@
 The study
-of AE method in the context of simple internal heating simulations will be an important step
+of AE in the context of simple internal heating simulations will be an important step
 towards achieving AE in simulations with astrophysically realistic conductivities.
@@
 at a more rapid rate than the thermal diffusion time across the domain due to
-the help of convective motions.  For example, in Fig. \ref{fig:time_trace}a,
+convective mixing.  For example, in Fig. \ref{fig:time_trace}a,
 the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
@@
 the vertically integrated mass, and sets boundary conditions on that mass to ensure
-that no mass enters or leaves the domain.
+that no mass enters or leaves the domain. [GIVE NUMBERS]
 
@@
 part because a third BVP generally did not greatly alter the solution
-(as in Fig. \ref{fig:time_trace}c, arrow 3).
+(as in Fig. \ref{fig:time_trace}c, arrow 3). We wait 50 freefall times after
+the final AE BVP solve of each run before beginning to take measurements.
 
@@
 $S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{AE}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
+\hline \hline \\
+\multicolumn{9}{c}{2D Runs} \\
 \hline
@@
 $10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
-$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	40.78	\\
+$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	38.29	\\
 \\ \hline \hline \\																	
+\multicolumn{9}{c}{3D Runs} \\
+\hline
 $10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	$261$	&	100	&	2.42	&	2.42	\\

### 2018-03-14 code/plotting/oscillating_plumes.py

@@ -35,16 +35,25 @@ plt.figure(figsize=(8, 3))
 gs     = gridspec.GridSpec(*(1000,1000))
 
 slices1 = h5py.File('{:s}/slices/slices_s81.h5' .format(full_dir), 'r')
-slices2 = h5py.File('{:s}/slices/slices_s134.h5'.format(full_dir), 'r')
+slices2 = h5py.File('{:s}/slices/slices_s86.h5'.format(full_dir), 'r')
 slices3 = h5py.File('{:s}/slices/slices_s75.h5'.format(full_dir2), 'r')
-slices4 = h5py.File('{:s}/slices/slices_s81.h5'.format(full_dir2), 'r')
+slices4 = h5py.File('{:s}/slices/slices_s80.h5'.format(full_dir2), 'r')
+#slices4 = h5py.File('{:s}/slices/slices_s81.h5'.format(full_dir2), 'r')
 scalars = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir), 'r')
 scalars2 = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir2), 'r')
 
-temp1 = slices1['tasks']['T'][5,:,:]
-temp2 = slices2['tasks']['T'][10,:,:]
-temp3 = slices3['tasks']['T'][0,:,:]
-temp4 = slices4['tasks']['T'][0,:,:]
+temp1 = slices1['tasks']['T'][10,:,:]
+w1 = slices1['tasks']['w'][10,:,:]
+u1 = slices1['tasks']['u'][10,:,:]
+temp2 = slices2['tasks']['T'][19,:,:]
+w2 = slices2['tasks']['w'][19,:,:]
+u2 = slices2['tasks']['u'][19,:,:]
+temp3 = slices3['tasks']['T'][4,:,:]
+w3 = slices3['tasks']['w'][4,:,:]
+u3 = slices3['tasks']['u'][4,:,:]
+temp4 = slices4['tasks']['T'][5,:,:]
+w4 = slices4['tasks']['w'][5,:,:]
+u4 = slices4['tasks']['u'][5,:,:]
 x     = slices1['scales']['x']['1.0'].value
 z     = slices1['scales']['z']['1.0'].value
 x2     = slices3['scales']['x']['1.0'].value
@@ -61,12 +70,12 @@ time2  = scalars2['sim_time'].value
 nu2  = scalars2['Nu'].value
[…]

### 2018-03-14 code/plotting/parameter_space_comparison.py

@@ -10,7 +10,10 @@ Options:
 """
 
 
-import matplotlib   
+import matplotlib.style
+import matplotlib
+matplotlib.use('Agg')
+matplotlib.style.use('classic')
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
 from matplotlib.colors import ColorConverter
@@ -62,6 +65,9 @@ for a, base_dir in enumerate(base_dirs):
                     where = info[ra]['sim_time'] > 209.8
                     for k in info[ra].keys():
                         info[ra][k] = info[ra][k][where]
+                        if 'Nu' in k:
+                            print(a, 'Nu', ra, np.mean(info[ra][k]))
+
         except:
             print('cannot find file in {:s}'.format(d))
 
@@ -146,7 +152,7 @@ for i,k in enumerate(fields):
             bx.scatter(ra_list/ra_crit, mean_list/ra_list**(p), s=0, alpha=0)
             ax.vlines(ra_list, ymin=min_list/ra_list**p, ymax=max_list/ra_list**(p), color=[color]*len(min_list), zorder=j)
             ax.scatter(ra_list, mean_list/ra_list**(p), s=s,  color=color, marker=mrkr, zorder=j)
-            ax.errorbar(ra_list, mean_list/ra_list**p, yerr=np.array((mean_list-m_min_list, m_max_list-mean_list))/ra_list**p,  ecolor=color, fmt='none', zorder=j)
+#            ax.errorbar(ra_list, mean_list/ra_list**p, yerr=np.array((mean_list-m_min_list, m_max_list-mean_list))/ra_list**p,  ecolor=color, fmt='none', zorder=j)
             ind = ra_list == 1.30e8
             ax.scatter(ra_list[ind], mean_list[ind]/ra_list[ind]**(p), s=s*1.5,  color='black', marker='s', zorder=1e10)
 
@@ -155,7 +161,7 @@ for i,k in enumerate(fields):
             bx.scatter(ra_list/ra_crit, mean_list/ra_list**(p), s=0, alpha=0)
             ax.vlines(ra_list, ymin=min_list/ra_list**p, ymax=max_list/ra_list**(p), color=[color]*len(min_list), zorder=j)
[…]

### 2018-03-14 code/plotting/pdf_comparison.py

@@ -10,7 +10,10 @@ Options:
 """
 
 
-import matplotlib   
+import matplotlib.style
+import matplotlib
+matplotlib.use('Agg')
+matplotlib.style.use('classic')
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
 plt.rc('font',family='Times New Roman')
@@ -174,7 +177,7 @@ axes[-1].plot(diff_x[diff_y < 0], -diff_y[diff_y < 0], c='k', dashes=(3,1), lw=1
 axes[-1].set_xlim(-0.165, 0.165)
 axes[-1].set_yscale('log')
 axes[-1].set_ylim(1e-4, 1e-1)
-axes[-1].set_ylabel('CDF diff.')
+axes[-1].set_ylabel(r'KS$(q)$')
 axes[-1].set_xlabel('Vertical Velocity', labelpad=-2)
 axes[-1].annotate(r'$\mathrm{(d)}$', (-0.15, 1e-2), fontsize=10)
 for tick in axes[-1].get_xticklabels():

### 2018-03-14 code/plotting/temp_comparison.py

@@ -10,7 +10,10 @@ Options:
 """
 
 
-import matplotlib   
+import matplotlib.style
+import matplotlib
+matplotlib.use('Agg')
+matplotlib.style.use('classic')
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
 plt.rc('font',family='Times New Roman')
@@ -169,7 +172,7 @@ x_ticks = np.array([-0.5, -0.45, -0.40])
 axes[-1].set_xticks(x_ticks)
 minor_x_ticks = np.array([-0.475, -0.425])
 axes[-1].set_xticks(minor_x_ticks, minor=True)
-axes[-1].set_ylabel('PDF')
+axes[-1].set_ylabel('PDF', labelpad=2)
 axes[-1].set_yscale('log')
 axes[-1].set_xlim(-0.5, -0.385)#np.max(info[base_label]['T_xs_pdf']))
 axes[-1].annotate(r'$\mathrm{(b)}$', (-0.497, 3e2), fontsize=10)
@@ -210,7 +213,7 @@ axes[-1].set_xticks(x_ticks)
 axes[-1].set_xticks(minor_x_ticks, minor=True)
 #y_ticks = np.array([1e-3, 1e-1])
 #axes[-1].set_yticks(y_ticks)
-axes[-1].set_ylabel('CDF diff.')
+axes[-1].set_ylabel(r'KS$(\,T\,)$', labelpad=2)
 axes[-1].set_xlabel(r'$T$')
 axes[-1].annotate(r'$\mathrm{(d)}$', (-0.497, 1.5e-1), fontsize=10)
 

### 2018-03-15 tex/bvp_paper.tex
lots of edits

@@
 \begin{abstract}
-We present a method for achieving Accelerated Evolution (AE) of convective simulations.
-By probing the dynamics of convection early in simulations and adjusting the
-thermal profile of the simulation appropriately, we advance simulations to
-evolved states on timescales much shorter than the thermal diffusion timescale.
-We study this method in the context of \RB convection. 
-The solutions reached by AE similar to those reached by a slow thermal evolution, 
-and AE is effective in 2D, 3D, and at low and high supercriticality.  
-Extensions to more complex systems are briefly discussed.
+Modern, turbulent simulations of convection suffer from a large discrepancy between
+short dynamical convective timescales and long thermal timescales of system evolution.
+In this paper, we present a method of achieving Accelerated Evolution (AE) of convective simulations which
+fast-forwards through the long thermal evolution of these systems, and we test the
+validity of this method. The AE procedure involves measuring the dynamics of convection
+early in a simulation and using its characteristics to adjust the mean thermodynamic
+profile within the domain towards its evolved state. We study \RB convection as a test case for AE.  
+Key evolved properties of AE solutions are measured to be within a few percent
+of measurements of the same quantities in solutions which are reached through 
+evolution over a full thermal timescale. We conclude with a brief discussion of useful extensions
+of AE, such as to studies of stratified, compressible convection.
 \end{abstract}
@@
 %%%%%%%%%%%%
-\vspace{-0.5cm}
 \section{Results}
 \label{sec:results}
-We study evolved SE solutions whose supercriticalities ($S$) are 
+We study evolved standard evolution (SE) solutions whose supercriticalities ($S$) are 
 $S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
 3D. We compare their properties to
-accelerated evolution (AE) runs in $S \in (1, 10^7]$ in 2D and
+accelerated evolution (AE) runs at $S \in (1, 10^7]$ in 2D and
 $S \in (1, 10^4]$ in 3D.
@@
 simulations.
-
-\begin{figure}[t!]
-\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
-\caption{. \label{fig:oscillating_plumes} }
-\end{figure}
 
@@
 When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
-the evolved system is characterized by a specific
-value of Nu, as the convective heat transport reaches a temporally stationary state.
-At larger values of $S$ in 2D, the value of Nu varies significantly over time,
-as shown by the time traces for $S = 10^5$ (top) and $S = 10^7$ (bottom) for two
-AE runs in Fig. \ref{fig:oscillating_plumes}. We find that these systems go between
-states in which temperature fluctuations primarily travel in their natural buoyant
-direction (as in Ia and IIa, where cold elements are falling and hot elements rise),
-and states in which temperature perturbations are entrained in an upflow or downflow
-with oppositely signed fluid (as in Ib and IIb, where warm fluid is pulled down by the downflow
-lane, and cool fluid is pulled up by the upflow lane).  The fluid from the oppositely
-signed plume pushes on the other plume such that the system goes between states in which
-the fluid primarily serves to enhance convective transport (Ia and IIa), states in which
-there is counterclockwise entrainment (IIa and IIb), then back to enhanced transport states
-followed by clockwise entrainment.  This horizontally oscillatory motion that characterizes the
-plumes provides, and the resultant time-dependent entrainment, leads to large variations in Nu over time 
-As a result of our choice of no-slip
-boundary conditions, the fluid never enters a full domain shearing state 
+the evolved system is characterized by a time-stationary value of Nu, and is thus
+in a state of constant convective heat transport.
+At larger $S$ in 2D, the value of Nu varies significantly over time,
+as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
+AE runs in Fig. \ref{fig:oscillating_plumes}. We find that these systems exhibit
+large Nu during
+states in which temperature fluctuations travel in their natural buoyant
+direction (Fig. \ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
+However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
+with oppositely signed fluid, Nu is suppressed (Fig. \ref{fig:oscillating_plumes}, Ib and IIb, 
+where warm fluid is pulled down by the downflow
+lane, and cool fluid is drawn up by the upflow lane). The plumes in these
+systems naturally oscillate over time, switching between transport being dominated
+by a counterclockwise cell, as pictured in Fig. \ref{fig:oscillatin_plumes}, and
+a counter-clockwise cell. Our choice of no-slip
+boundary conditions prevents the fluid from entering a full domain shearing state 
 \cite{goluskin&all2014}, and the
@@
 oscillatory behavior as the AE solutions for the same initial conditions. 
-This time-dependent behavior or Nu is not seen strongly in our 3D solutions,
-likely as a result of the extra degrees of freedom in which rising and falling
-fluid elements can expand, reducing entrainment.
+This time-dependent behavior of Nu is not seen strongly in our 3D solutions,
+however most 3D simulations we conducted were at low $S$ compared to the runs in
+which this behavior was observed in 2D.
 
-The time- and volume-averaged values of the Nusselt number (Nu), the RMS
-Reynolds number (Re), and the mean temperature in AE solutions 
-are shown in Fig. \ref{fig:parameter_space_comparison}a-c.
-Nu, which quantifies the heat transport in evolved solutions,
-is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
-The
-dynamic nature of the plume structures diminishes the
-scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
-which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
-Previous studies in 2D convection may have avoided oscillatory plumes by using
-bootstrapping techniques as initial conditions for high $S$ runs.
-In Fig. \ref{fig:parameter_space_comparison}b, we report 
-$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measures the degree of
-turbulence in the solution, and scales roughly as
-$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
-the value of Re over time.
-Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$.
-The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
-so this measurements serves as a probe of the temperature jump across the boundary
-layers. As a result, we expect this measure to
-scale inversely with Nu in converged solutions
-where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
-that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
-scaling of Nu.
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
+\caption{The time variation of the Nusselt number is shown for two AE cases at
+$S = 10^5$ (top) and $S = 10^7$ (bottom). On the left, the instantaneous value of Nu
+is shown as a function of time. On the right, temperature snapshots are shown for
+Nu maxima (Ia \& IIa) and minima (Ib \& IIb). The suppressed value of Nu at the
+minma arises from entrainment of fluid elements whose temperature perturbations
+are wrongly signed (e.g., hot material going downwards and cold material going
+upwards in Ib \& IIb).\vspace{-1cm} \label{fig:oscillating_plumes} }
+\end{figure}
 
-\begin{figure}[b]
+\begin{figure}[b!]
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
@@
 and quantify natural variation over the averaging window. 
-(a) Nu scales as Ra$^{1/5}$; above S$\geq 10^{3+2/3}$,
-simulations exhibit oscillating plume structures whose heat transport fluctuates over time
-as a result of temporally-varying entrainment of wrongly signed temperature perturbations
+(a) Nu scales as Ra$^{1/5}$; at high $S$ in 2D the value of Nu fluctuates over time
 (see Fig. \ref{fig:oscillating_plumes}).  
-(b) Re, which measures the level of turbulence in the evolved solution, scales as
-Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at $z = +1/2$
-is shown, and this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
-Relative error for measurements of (d) Nu, (e) Re, and (f) $T$ between 
+(b) Re, which measures turbulence in the solution, scales as
+Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at the fixed-temperature
+top boundary is shown; this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
+Relative error for measurements of (d) Nu, (e) Re, and (f) $\angles{T} - T_{\text{top}}$ between 
 AE solutions and SE solutions are shown.
@@
 
-This is a short paragraph which says 2D and 3D are the same, here.
+The time- and volume-averaged values of Nu, the RMS
+Reynolds number (Re), and the mean temperature 
+are shown for AE solutions in Fig. \ref{fig:parameter_space_comparison}a-c.
+Mean values are shown by the symbols (purple circles and red stars), and 
+the vertical lines represent the standard deviation of the measurement over time.
+Nu is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
+The dynamic nature of the plume structures (e.g., Fig. \ref{fig:oscillating_plumes})
+diminishes the mean
+scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
+which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
+Previous studies in 2D convection may have avoided these time-varying Nu states by using
+bootstrapping techniques as initial conditions for high $S$ runs.
+In Fig. \ref{fig:parameter_space_comparison}b, we report 
+$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$ as a function of Ra and $S$.  
+Re measures the degree of
+turbulence in the solution, and scales roughly as
+$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
+the value of Re over time.
+Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$,
+the mean value of the temperature minus its value at the upper (fixed temperature) boundary.
+The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
+so this measurements serves as a probe of the temperature jump across the boundary
+layers. As a result, we expect this measure to
+scale inversely with Nu in converged solutions
+where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
+that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
+scaling of Nu.
 
@@
 
+For the select 3D runs conducted in this study, the scaling of Nu, Re, and $\angles{T} - T_{\text{top}}$
+reported in Fig. \ref{fig:parameter_space_comparison}a-c is nearly identical to the
+2D simulations. Errors between AE and SE solutions in 3D fall within the same range as
+errors in 2D in Fig. \ref{fig:parameter_space_comparison}d-f. AE is therefore
+equally effective in both 2D and 3D, and we restrict much of our study to 2D here.
+
 The measurements presented in Fig. \ref{fig:parameter_space_comparison} demonstrate
@@
 large numbers of simulations are compared in a volume-averaged sense.  We now turn
-our examination to a more direct comparison of AE and SE for convection at
+our examination to a more direct comparison of AE and SE for 2D convection at
 $S = 10^5$, the time and flux evolution of which was shown in Fig. \ref{fig:time_trace}.
@@
 
-\begin{figure}[b]
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{./figs/temp_comparison.png}
@@
 in Fig. \ref{fig:temp_comparison}b. To construct these PDFs, 
-we interpolate the temperature field
-of each of these snapshots onto an evenly spaced grid, determine the
-frequency distribution of all measured $T$ values, and then normalize the
+we interpolate the full temperature field
+at each measurement time onto an evenly spaced grid, determine the
+frequency distribution of all $T$ values over the duration of the 500 $t_{\text{ff}}$
+measurement window, and then normalize the
 distribution such that its integral is unity.  The two PDFs have noticeably
@@
 $\KSstat{q}$ to gain insight into the likeness of two PDFs. 
-We show the KS profile in Fig. \ref{fig:temp_comparison}d, and the
+We show the $\KS{T}$ in Fig. \ref{fig:temp_comparison}d, and the
 CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
-Near the modes of the temperature PDFs, the $\KSstat{T} = 0.495$, 
-which is very large and implies that roughly half of all temperature
-measurements in the SE case are greater than those in the AE case.
-This difference is significant, and shows that the two PDFs are distinctly different,
-but aside from this large value near the modes the KS profile has very small values,
-indicating that the temperature fluctuations away from the modes in the two cases are nearly identical.
+Near the modes of the temperature PDFs, $\KSstat{T} = 0.495$, 
+which is very large and implies that roughly half of all
+measurements in the AE case are at a lower $T$ than those in the SE case.
+While this difference is significant, it is also expected from Fig. \ref{fig:temp_comparison}a.
+Fortunately, $\KS{T}$ is very small away from the modes, 
+indicating that the temperature fluctuations off of the modes, which are the primary
+drivers of convective transport, are nearly identical.
 
 In addition to comparing the thermodynamic state achieved by the SE and AE methods,
-we examine the velocities found in the evolved states.
+we examine the velocities and heat transport found in the evolved states.
 Shown are the PDFs of 
-vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
-and the nonlinear vertical convective flux (Fig. \ref{fig:pdf_comparison}c). 
+vertical velocity ($w$, Fig. \ref{fig:pdf_comparison}a), horizontal velocity ($u$, Fig. \ref{fig:pdf_comparison}b),
+and the nonlinear vertical convective flux ($w(T - \angles{T}_{x,y})$, Fig. \ref{fig:pdf_comparison}c). 
+Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
+velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
 The CDFs of each profile are overplotted, and corresponding KS profiles are
 shown in Fig. \ref{fig:pdf_comparison}d-f.  We report
-$\KSstat{w} = 0.00615$ (vertical velocity), $\KSstat{u} = 0.0349$ (horizontal velocity),
+$\KSstat{w} = 0.00615$, $\KSstat{u} = 0.0349$,
 and $\KSstat{w(T - \angles{T}_{x,y})} = 0.0263$.
-Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
-velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
 The difference in vertical velocity
@@
 the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
+this also confirms that the large $\KSstat{T}$ in Fig. \ref{fig:temp_comparison}d is
+not of concern, and that the AE run achieves the proper convective solution.
 The horizontal velocity shows some small deviation between the two simulations, and this
-likely relates to the nature of the strength of the horizontally oscillatory motions
-as we previously described in the context of suppressed Nu scaling. Thus, while
-the temperature profiles are distinctly drawn from different distributions in
-Fig. \ref{fig:temp_comparison}b, the profiles are similar enough that they drive
-nearly identical nonlinear dynamics.
+likely relates to the precise configuration of the convective plumes (e.g., Fig. \ref{fig:oscillating_plumes}).
+We find that despite our no-slip boundary conditions, the full convective roll systems
+migrate slowly to the left or the right over time, and the difference in $\KS{u}$
+appears to be caused by a more prominent migration in the -x direction in the AE run
+than in the SE run.
 
@@
 at high values of $S$, where SE solutions are intractable.
-As discussed, 2D and 3D are identical short of the time-varying entrainment states
-(Fig. \ref{fig:oscillating_plumes}), so we have restricted most of our study to 2D.
-However, due to the greater computational expense of 3D runs, they stand to gain more
-time savings from AE. This is a sentence about the magnitude of savings involved for
-AE vs. SE (wall time + cpu hours, 2d: $10^5$, 3d: $10^4$).
+As discussed, AE is equally applicable in 2D and 3D, so we have restricted most of our study to 2D.
+At the largest values of $S$ in which AE and SE are compared in this work, we find
+time savings of nearly an order of magnitude. 
+For example, in 2D and at $S = 10^5$, the
+AE run took 10.78 wall hours on 256 cores ($2.8\cdot 10^3$ cpu-hours) while the 
+SE run took 94 wall hours ($2.4\cdot 10^4$ cpu-hours). In 3D and at $S = 10^4$,
+the AE run took 2.81 wall hours on 8192 cores ($2.3 \cdot 10^4$ cpu-hours),
+while the SE run took 37.9 wall hours, or ($3.1 \cdot 10^5$ cpu-hours). As $S$ increases,
+and the thermal time, $t_{\kappa}$ simultaneously increases, we anticipate the time
+savings to further increase.  The increased computational expense of 3D runs compared
+to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.
 
@@
 When the interface between the stable region
-and the convecting region is stiff and motions do not cross that interface,
+and the convecting region is stiff,
 convective motions cannot accelerate the restratification of the stable region.
@@
 the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
-despite the thermal timescale being roughly $10^4$ freefall units. However, in 
+which is roughly 40\% of a thermal timescale. However, in 
 studies where there is a stable region which is not mixed by convection, the experimentalist
 must either wait through a thermal diffusion time for the region to restratify
-or employ other methods \cite{couston&all2017} to study evolved atmospheres.
+or otherwise adjust the mean profile to study evolved atmospheres \cite{couston&all2017}.
 
@@
 the difficulty of achieving thermal convergence grows as simulators study more highly
-stratified domains.
+stratified domains. For example, in a modestly stratified atmosphere which spans three
+density scale heights, the density at the bottom, and thus the thermal timescale, is a
+factor of 20 greater than at the top of the domain.
 In order to extend AE into this regime, two additional pieces of information must be considered.
@@
 with the total flux through the domain, only the superadiabatic portion of
-the flux should be considered.
+the flux should be considered \cite{anders&brown2017}.
 Second, in addition to solving for
@@
 the vertically integrated mass, and sets boundary conditions on that mass to ensure
-that no mass enters or leaves the domain. [GIVE NUMBERS]
+that no mass enters or leaves the domain.
 
-An eventual use case of AE is in robustly describing convection
+Ideally, AE can eventually be used in robustly describing convection
 in stellar evolution codes. Current state of the art stellar structure
 models are the solutions of 1D simulations which parameterize convection 
-using Mixing Length Theory \cite{paxton&all2011}. Recent work has taken first steps towards
-understanding how to simultaneously resolve convective motions while evolving
-systems through many thermal timescales, as is required when modeling the evolution of stars
-over the course of stellar lifetimes.
-We now know that implicit timestepping methods, while not technically bound by
-CFL constraints, must resolve the convective motions for stability
-\cite{viallet&all2011, viallet&all2013, viallet&all2016}, and are thus
-not an ideal solution to achiving long-term system evolution.
+using Mixing Length Theory \cite{paxton&all2011}. Recent studies have tried
+to understand how to simultaneously resolve convective motions and evolve
+systems through many thermal timescales, as is required when determining the
+interior structure of stars over their evolving lifetimes.
+We now know that implicit timestepping methods
+must resolve convective motions in order to timestep with stability
+\cite{viallet&all2011, viallet&all2013, viallet&all2016}, and thus
+cannot achieve fast, meaningful system evolution.
 Recently, efforts have begun to project the results of 3D simulations into 1D
 models to more properly parameterize convection for stellar evolution
-\cite{arnett&all2015, cristini&all2016}.
-Through the
-careful addition and testing of new physics, AE can be generally applied to
-very large complex problems such as stellar evolution, and
-shows great potential for improving our understanding of convection.
+\cite{arnett&all2015, cristini&all2016}. This is precisely the technology
+employed in the AE method we present here. Through the careful expansion
+of AE from \RB convection to fully stratified, compressible convection with realistic
+opacities, it is possible that carefully evolved stellar structure models which
+use statistics from resolved convective motions, rather than parameterized 1D models,
+are well within reach of modern computing tools.
 
@@
 \item Wait some time, $t_{\text{transient}}$, before beginning the AE process.
-\item During the DNS, calculate time averages of the 1D profiles of
-$F_{\text{conv}}$, $F_{\text{tot}}$, 
+\item During the DNS, calculate time averages of the 1D vertical profiles of
+F$_{\text{E}}$, F$_{\text{tot}}$, 
 and $\angles{\bm{u} \times \bm{\omega}}_{x,y}$, updating them every timestep.  
@@
 the profiles must change by no more than $P$\% on a given timestep.
-\item Construct F$_\text{conv, ev}$ and $\xi$ as specified in section \ref{subsection:ae}
+\item Construct $\xi$, F$_{\text{E, ev}}$, and $\angles{\bm{u} \times \bm{\omega}}_{x,y\text{, ev}}$,
+as specified in section \ref{subsection:ae}
 from the averaged profiles.
@@
 equal to the results of the BVP.
-\item Multiply the velocity field and the temperature fluctuations, $T - \angles{T}_{x,y}$,
+\item Multiply the velocity field, $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$,
+and the temperature fluctuations, $T - \angles{T}_{x,y}$,
 by $\sqrt{\xi}$ in the DNS to properly reduce the convective flux.
-\item Continue running the DNS
+\item Continue running the DNS.
 \end{enumerate}
@@
 In the upper part of the table, information pertaining to 2D runs is reported,
-and below the double horizontal bars we report properties of all
-3D runs.
+while information pertaining to 3D runs is in the lower part of the table.
 }
@@
 $S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{AE}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
-\hline \hline \\
-\multicolumn{9}{c}{2D Runs} \\
+\hline \hline \multicolumn{9}{c}{\vspace{-0.2cm}}\\
+\multicolumn{9}{c}{\vspace{0.1cm}2D Runs} \\
 \hline
@@
 $10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	38.29	\\
-\\ \hline \hline \\																	
-\multicolumn{9}{c}{3D Runs} \\
+\\ \hline \hline \multicolumn{9}{c}{\vspace{-0.2cm}}\\
+\multicolumn{9}{c}{\vspace{0.1cm}3D Runs} \\
 \hline

### 2018-03-15 tex/bvp_paper.tex
near-submission draft

@@
 \begin{abstract}
-Modern, turbulent simulations of convection suffer from a large discrepancy between
-short dynamical convective timescales and long thermal timescales of system evolution.
+High Rayleigh number, turbulent convection is a classic system with a large timescale
+separation between flow speeds and equilibration time.
 In this paper, we present a method of achieving Accelerated Evolution (AE) of convective simulations which
@@
 Astrophysical convection occurs in the presence of disparate timescales which
-prohibit numericists from studying realistic models of systems in nature.  For example,
+make direct numerical simulations of realistic models of systems in nature infeasible.  
+Stiffness in astrophysical systems can manifest in multiple ways, some of which can
+be handled by clever choices of numerical algorithms, and some which cannot.
+For example,
 flows in the convection zones of stars like the Sun are characteristically low Mach number
-(Ma) in the deep interior.
-Explicit timestepping methods which are bound by the Courant-Friedrich-Lewy
-(CFL) timestep limit must resolve the fastest motions (sound
+(Ma) in the deep interior. Initial value problems solved using
+explicit timestepping methods are bound by the Courant-Friedrich-Lewy
+(CFL) timestep limit corresponding to the fastest motions (sound
 waves), resulting in timesteps which are prohibitively
@@
 the sound crossing time and the convective overturn time have made studies of low-Ma stellar
-convection difficult. Traditionally, approximations such as
+convection difficult. This stiffness can be avoided using approximations such as
 the anelastic approximation, in which sound waves are explicitly filtered out,
 have been used to study low-Ma flows \cite{brown&all2010, featherstone&hindman2016}.
-More recently, advanced numerical techniques which use fully implicit 
+Recently, advanced numerical techniques which use fully implicit 
 \cite{viallet&all2011, viallet&all2013, viallet&all2016} or mixed
@@
 timestepping mechanisms have made it feasible to study
-convection at low Mach numbers, and careful studies of deep convection which
+convection in the fully compressible equations at low Mach numbers, 
+and careful studies of deep convection which
 would have been impossible a decade ago are now widely accessible.
 
-Unfortunately, convective systems generally evolve over the course of thermal
+Unfortunately, convective systems are stiff in more than one timescale and
+generally evolve over the course of thermal
 timescales, which are often much larger than all relevant
-dynamical timescales. Therefore resolving dynamics in atmospheres which are sufficiently
+dynamical timescales. Transport by convection is a highly nonlinear process,
+and this makes addressing the stiffness much more challenging; even fully
+implicit  methods remain bound by the nonlinear flow timescales
+\cite{viallet&all2011, viallet&all2013, viallet&all2016}. 
+Resolving dynamics in atmospheres which are sufficiently
 thermally relaxed remains a challenging problem.
@@
 dynamical timescales in the solar convective zone are relatively short 
-(convection overturns every $\sim 10$ minutes at the solar surface, 
-the Sun rotates roughly once every month)
+(convection overturns every $\sim 5$ minutes at the solar surface)
 compared to the Sun's Kelvin-Helmholtz timescale of
@@
 As modern simulations aim to model natural convection
-by increasing into the high-Rayleigh-number (Ra) regime,
+by in the high-Rayleigh-number (Ra) regime,
 the thermal diffusion timescale becomes intractably large
-compared to dynamical timescales \cite{anders&brown2017}.
+compared to dynamical timescales \cite{anders&brown2017}, 
+\begin{equation}
+\frac{t_{\kappa}}{t_{\text{ff}}} = (\text{Ra Pr})^{1/2},
+\end{equation}
+where the thermal timescale is $t_{\kappa} = L_z^2 / \kappa$,
+$L_z$ is the depth of the convective domain, $\kappa$ is
+the thermal diffusivity, and
+the freefall timescale is defined in Section \ref{sec:experiment}.
 Furthermore, as dynamical and thermal timescales separate, 
@@
 Another commonly-used tactic in
-moderate-Ra simulations is to use 
-a simple model of the full convective state as initial conditions.  
-For example, past studies have used a linear eigenvalue solve to set the initial
-convective state \cite{hurlburt&all1984} or used an axisymmetric solution 
-as initial conditions for convection in a 3D cylinder \cite{verzicco&camussi1997}. 
-In other systems, 
-the approximate state of the evolved solution can be estimated. There, a
-set of initial conditions which is close to the evolved state can be 
-derived analytically \cite{couston&all2017, brandenburg&all2005}.
+moderate-Ra simulations is to use a simplified system model to construct initial
+conditions, such as the solution of a linear eigenvalue solve \cite{hurlburt&all1984} 
+or an axisymmetric solution for convection in a 3D cylinder \cite{verzicco&camussi1997}. 
+In other systems, a set of initial conditions closer to the evolved state than a standard
+conductive state can be analytically derived \cite{couston&all2017, brandenburg&all2005};
+these experiments all have slowly-evolving stable regions, and so a combination of
+intuition from low-Ra solutions and established convective theory inform an
+initial state which is closer to the evolved state than the standard conductive,
+hydrostatic state often used.
 
@@
 studies do just that \cite{featherstone&hindman2016}.
-However, such evolution is
+Such evolution is computationally 
 \emph{expensive}, and state-of-the-art simulations at the highest values of Ra
@@
 to self-consistently adjust the mean vertical thermodynamic profile towards its evolved state. 
-While a technique of this kind has been used previously \cite{hurlburt&all1986}, 
-we find no explanation in the current literature of the steps involved in employing
-this method, nor do we find any study of its accuracy.
+While a technique of this kind has been used previously \cite{hurlburt&all1986}.
+The details of implementation, the convergence properties, and whether or not the
+accelerated evolution state corresponds to a standard evolution state are not documented.
 In section \ref{sec:experiment}, we describe our convective simulations, our
@@
 section \ref{sec:results}, we compare accelerated evolution solutions
-to solutions obtained from evolution through a full thermal diffusion timescale. Finally,
+to solutions obtained from standard evolution through a full thermal diffusion timescale. Finally,
 in section \ref{sec:extensions}, we offer concluding remarks and
@@
 \label{sec:experiment}
-We study incompressible \RB convection under the Oberbeck-Boussinesq approximation,
+In this work we study a simple form of thermal convection:
+incompressible \RB convection under the Oberbeck-Boussinesq approximation,
 such that the fluid
@@
 of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$,
-except where it is $\rho = \rho_0(1  - \alpha T_1)$ on the term where
-the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, 
-acts in the vertical momentum equation.
-The equations of motion are \cite{spiegel&veronis1960}
+except in the buoyancy term, where it is $\rho = \rho_0(1  - \alpha T_1)$.
+The gravitational acceleration, $\bm{g} = - g\hat{z}$, is constant.
+The equations of motion are \cite{spiegel&veronis1960}:
 \begin{gather}
@@
 \end{gather}
-where $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$ is the velocity, 
+where $\bm{u} = u\bm{\hat{x}} + v\bm{\hat{y}} + w\bm{\hat{z}}$ is the velocity, 
 $T = T_0(z) + T_1(x, y, z, t)$ are the initial and fluctuating components of temperature, 
@@
 potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. 
-In non-dimensional form, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
+In non-dimensional form, and substituting 
+$\bm{u}\cdot\grad\bm{u} = \grad(|\bm{u}|^2/2) - \bm{u}\times(\grad\times\bm{u})$
+and $\grad^2\bm{u} = -\grad\times\grad\times\bm{u}$, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
 become
-\begin{gather}
-\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega},
+\begin{align}
+\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} &= \bm{u}\times\bm{\omega},
 	\label{eqn:bouss_momentum}
 \\
-\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
+\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} &= - \bm{u}\cdot\grad T_1,
 	\label{eqn:bouss_energy}
-\end{gather}
+\end{align}
 where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
@@
 We hold Pr $= 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.
+$\mathcal{P}$ and $\mathcal{R}$ are related to the inverse Reynolds and Peclet numbers of the
+evolved flows.
 
-In Eqns. (\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}),
+In Eqns.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}),
 linear terms are grouped on the left-hand side of the equations, while nonlinear terms
@@
 pseudospectral framework \cite{burns&all2016} to evolve  
-Eqns. (\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}) 
+Eqns.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}) 
 forward in time
@@
 and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$,
-where $\Gamma = 2$ is the aspect ratio. 
+where $\Gamma = 2$ is the aspect ratio, as has been previously studied
+\cite{goluskin&all2014, johnston&doering2009}. 
 In 2D simulations, we set $v = \partial_y = 0$.
 We specify no-slip, impenetrable boundary conditions at both the top and
-bottom boundary and we use mixed thermal boundary conditions, such that
+bottom boundary,
 \begin{equation}
-u = v = w = 0 \, \, \text{at}\,\,z = \pm 1/2, \qquad T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
+u = v = w = 0 \, \, \text{at}\,\,z = \pm 1/2,
+\label{eqn:vel_bcs}
+\end{equation}
+and we use mixed thermal boundary conditions, such that
+\begin{equation}
+T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
 \frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=-1/2.
-\label{eqn:bcs}
+\label{eqn:temp_bcs}
 \end{equation}
 For this choice of boundary conditions, the critical value of Ra at which
-the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$, and the
+the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$ \cite{goluskin2016}, and the
 supercriticality of a run is defined as $S \equiv \text{Ra}/\text{Ra}_{\text{crit}}$.
@@
 astrophysical systems such as stars often employ mixed thermal
-boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017},
-as we do here; however, our choice of thermal boundary conditions here
-reflects the fact that the conditions in Eqn. (\ref{eqn:bcs}) are the simplest
-to implement in the process of accelerated evolution (section \ref{subsection:ae})
-we study here.
+boundary conditions, as we do here \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.
+Our choice of the thermal boundary conditions in Eqn.~(\ref{eqn:temp_bcs}) 
+was motivated by the fact that accelerated evolution is simpler when both the
+thermal profile and the flux through the domain are fixed at some point in the domain.
 
@@
 $T_0(z) = -z$. On top of this profile, we fill $T_1$ with
-random white noise whose magnitude is $10^{-6}\mathcal{P}$.
+random white noise whose magnitude is $10^{-6}\mathcal{P}$, and which is
+vertically tapered so as to match the thermal boundary conditions.
 This ensures that the initial perturbations are much smaller than the
@@
 such that only the lower 25\% of the coefficients
-have power.
+have power; this low-pass filter is used to avoid populating the
+highest wavenumbers with noise in order to improve the stability of our
+spectral timestepping methods.
 
@@
 
-\subsection{The method of Accelerated Evolution}
-\label{subsection:ae}
+\section{The method of Accelerated Evolution}
+\label{sec:ae}
 Here we describe a method of Accelerated Evolution (AE), which we use 
@@
 We compare this AE method to Standard Evolution
-(SE), in which we naively evolve the atmosphere for one thermal diffusion time,
-$t_\kappa = \mathcal{P}^{-1}$. Both AE and SE simulatins begin with identical
+(SE), in which we evolve the atmosphere from noise initial conditions
+for one thermal diffusion time,
+$t_\kappa = \mathcal{P}^{-1}$. Both AE and SE simulations begin with identical
 initial conditions, as described in section \ref{sec:experiment}.
@@
 
-For an example of time saving achieved by using AE, we compare
-energy traces at $S = 10^5$ from a SE run in Fig. \ref{fig:time_trace}a to an AE run
-in Fig. \ref{fig:time_trace}c.
-In Fig. \ref{fig:time_trace}a, the time evolution of the SE simulation is shown.
-The solution grows exponentially from white noise during the
+We study in depth a 2D simulation at $S = 10^5$ to demonstrate the power of AE.
+We compare kinetic energy (KE, black line) and mean temperature (blue line)
+traces from a SE run in Fig.~\ref{fig:time_trace}a to an AE run
+in Fig.~\ref{fig:time_trace}c.
+In Fig.~\ref{fig:time_trace}a, the time evolution of the SE simulation is shown.
+The KE grows exponentially from white noise during the
 first $\sim 25$ $t_{\text{ff}}$. The solution then saturates and begins to slowly
-equliibrate towards the proper isothermal profile in the interior of the domain.
-We find that the mean atmospheric temperature and
+equilibrate towards the proper isothermal profile in the interior of the domain.
+This slow equilibration is evident in the behavior of the blue line, which measures
+$\angles{T} - T_{\text{top}}$, where \angles{T} is the volume-average of $T$, and
+$T_{\text{top}} = -0.5$ is the temperature at the upper boundary.
+The mean atmospheric temperature and
 kinetic energies are fully converged when $t = 4000$ $t_{\text{ff}}$ $= 0.35$ $t_{\kappa}$.
@@
 units of evolution, as well as the evolved thermodynamic state reached after a full
-thermal time of evolution.  In Fig. \ref{fig:time_trace}c, we show an AE solution
+thermal time of evolution.  In Fig.~\ref{fig:time_trace}c, similar traces are
+shown for the corresponding AE solution
 at the same parameters. The same linear growth phase occurs, but shortly after
@@
 arrows in the graph numbered 1-3.  After the third profile adjustment, we find that
-the atmosphere is nearly in its converged state and we can begin to sample the evolved
+the atmosphere is nearly in its converged state and we begin to sample the evolved
 convective dynamics.
@@
 both of these fluxes early in a simulation, retrieving profiles such as
-those shown in Fig. \ref{fig:time_trace}b.
-At these early times, the flux profiles are highly asymmetric,
-with more flux exiting the atmosphere at the upper boundary than 
-the fixed-flux lower boundary can provide. As the atmosphere evolves towards
+those shown in Fig.~\ref{fig:time_trace}b.
+As the atmosphere evolves towards
 the isothermal profile specified by the upper (cold) boundary condition, excess
-temperature throughout the atmosphere must leave the domain, and this appears in
-the flux measurements in Fig. \ref{fig:time_trace}b where the flux exiting the upper
-boundary is nearly 2000\% the flux entering the bottom of the domain. Once the atmospheric
+temperature throughout the atmosphere must leave the domain. This excess thermal
+energy leaves through the upper boundary, as seen in 
+Fig.~\ref{fig:time_trace}b, where the amount of flux exiting at the top of the domain
+is nearly 20 times larger the flux entering the bottom of the domain. Once the atmospheric
 temperature profile reaches its evolved state, the flux entering the bottom boundary
-is equal to the flux exiting the upper boundary.  In general, this takes very long time
-frames through SE (Fig. \ref{fig:time_trace}a), but AE (Fig. \ref{fig:time_trace}b)
-can take a system whose fluxes are in a strongly disequilibrium state (Fig. \ref{fig:time_trace}c),
-and quickly put them into a near-equilibrium state, as shown in Fig. \ref{fig:time_trace}d. In
-this final state, there is no conductive flux in the interior, both boundaries carry the
-same amount of flux, and convection carries that amount of flux through the interior.
-The converged state achieved through AE is at most 5\% different from the SE solution, as shown in
-Fig. \ref{fig:time_trace}e.
+is equal to the flux exiting through the upper boundary.  In general, this 
+evolution is slow in SE (Fig.~\ref{fig:time_trace}a), but AE (Fig. \ref{fig:time_trace}c)
+can take a system whose fluxes are in a strongly disequilibrium state (Fig.~\ref{fig:time_trace}b),
+and quickly put them into a near-equilibrium state, as shown in Fig.~\ref{fig:time_trace}d. In
+this final state both boundaries conduct the same amount of flux.
+The converged state achieved through AE is at most 5\% different from the SE solution, 
+as shown in Fig.~\ref{fig:time_trace}e. 
+This is a very small difference considering the short timescales on which convergence
+is reached and the strongly disequilibrium state used to inform the AE process.
 
@@
 In order to adjust the temperature profle to achieve AE, we calculate the total flux,
-F$_{\text{tot}} =$ F$_{\text{E}} +$ F$_{\kappa}$, and then derive the profiles
+F$_{\text{tot}} =$ F$_{\text{E}}$ + F$_{\kappa}$, and then derive the profiles
 \begin{equation}
@@
 \end{equation}
-which have the systematic asymmetries removed. These profiles describe which
+which have the systematic asymmetries (Fig.~\ref{fig:time_trace}b) removed. These profiles describe which
 parts of the atmosphere depend on convection to carry flux (where $f_{\text{E}}(z) = 1$
@@
 In a time-stationary state, the horizontal- and time-average of
-Eqns. (\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
+Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
 vanish due to symmetry, are
@@
 statistically stationary state. Furthermore, under the specification of
-F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y}$,
+F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
 \emph{the mean thermodynamic structure of the system is fully specified}.
 
-Thus, the AE method is simple: we construct $\xi(z)$ from measured information about
-the convective dynamics. We solve a 1D boundary value problem consisting of
-Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
+Thus, the AE method is simple: we pause a convective simulation and
+construct $\xi(z)$ from measured flux profiles in the convective domain.
+We solve a 1D boundary value problem consisting of
+Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
 to obtain the proper evolved thermodynamic profile, and proper conductive flux.
 To obtain the proper convective enthalpy flux, we multiply both the velocity field,
-$\bm{u}$, and the temperature perturbations around the mean, $T - \angles{T}_{x,y}$,
+$\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
 by $\sqrt{\xi}$, thus diminishing the magnitude of these perturbations appropriately.
@@
 as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
-AE runs in Fig. \ref{fig:oscillating_plumes}. We find that these systems exhibit
+AE runs in Fig.~\ref{fig:oscillating_plumes}. We find that these systems exhibit
 large Nu during
 states in which temperature fluctuations travel in their natural buoyant
-direction (Fig. \ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
+direction (Fig.~\ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
 However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
-with oppositely signed fluid, Nu is suppressed (Fig. \ref{fig:oscillating_plumes}, Ib and IIb, 
+with oppositely signed fluid, Nu is suppressed (Fig.~\ref{fig:oscillating_plumes}, Ib and IIb, 
 where warm fluid is pulled down by the downflow
@@
 systems naturally oscillate over time, switching between transport being dominated
-by a counterclockwise cell, as pictured in Fig. \ref{fig:oscillatin_plumes}, and
+by a counterclockwise cell, as pictured in Fig.~\ref{fig:oscillating_plumes}, and
 a counter-clockwise cell. Our choice of no-slip
@@
 are wrongly signed (e.g., hot material going downwards and cold material going
-upwards in Ib \& IIb).\vspace{-1cm} \label{fig:oscillating_plumes} }
+upwards in Ib \& IIb). The colorbar scaling of panels Ia\&b are the same, as
+are the scalings of panels IIa\&b. 
+The minimum temperature is chosen by the fixed-temperature
+boundary condition at the top, $T_{\text{top}} = -0.5$. The decreased range of
+the colorbar scaling for
+for IIa\&b was chosen to better display the convective dynamics.
+\label{fig:oscillating_plumes} }
 \end{figure}
@@
 (a) Nu scales as Ra$^{1/5}$; at high $S$ in 2D the value of Nu fluctuates over time
-(see Fig. \ref{fig:oscillating_plumes}).  
+(see Fig.~\ref{fig:oscillating_plumes}).  
 (b) Re, which measures turbulence in the solution, scales as
@@
 Reynolds number (Re), and the mean temperature 
-are shown for AE solutions in Fig. \ref{fig:parameter_space_comparison}a-c.
+are shown for AE solutions in Fig.~\ref{fig:parameter_space_comparison}a-c.
 Mean values are shown by the symbols (purple circles and red stars), and 
 the vertical lines represent the standard deviation of the measurement over time.
-Nu is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
-The dynamic nature of the plume structures (e.g., Fig. \ref{fig:oscillating_plumes})
+Nu is shown as a function of Ra and $S$ in Fig.~\ref{fig:parameter_space_comparison}a.
+The dynamic nature of the plume structures (e.g., Fig.~\ref{fig:oscillating_plumes})
 diminishes the mean
@@
 bootstrapping techniques as initial conditions for high $S$ runs.
-In Fig. \ref{fig:parameter_space_comparison}b, we report 
+In Fig.~\ref{fig:parameter_space_comparison}b, we report 
 $\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$ as a function of Ra and $S$.  
@@
 the value of Re over time.
-Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$,
+Fig.~\ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$,
 the mean value of the temperature minus its value at the upper (fixed temperature) boundary.
@@
 
-In Fig. \ref{fig:parameter_space_comparison}d-f, we report the fractional difference
+In Fig.~\ref{fig:parameter_space_comparison}d-f, we report the fractional difference
 between measurements in the AE and SE solutions.
@@
 For the select 3D runs conducted in this study, the scaling of Nu, Re, and $\angles{T} - T_{\text{top}}$
-reported in Fig. \ref{fig:parameter_space_comparison}a-c is nearly identical to the
+reported in Fig.~\ref{fig:parameter_space_comparison}a-c is nearly identical to the
 2D simulations. Errors between AE and SE solutions in 3D fall within the same range as
-errors in 2D in Fig. \ref{fig:parameter_space_comparison}d-f. AE is therefore
+errors in 2D in Fig.~\ref{fig:parameter_space_comparison}d-f. AE is therefore
 equally effective in both 2D and 3D, and we restrict much of our study to 2D here.
 
-The measurements presented in Fig. \ref{fig:parameter_space_comparison} demonstrate
+The measurements presented in Fig.~\ref{fig:parameter_space_comparison} demonstrate
 that AE can be powerfully employed in parameter space studies in which
@@
 our examination to a more direct comparison of AE and SE for 2D convection at
-$S = 10^5$, the time and flux evolution of which was shown in Fig. \ref{fig:time_trace}.
+$S = 10^5$, the time and flux evolution of which was shown in Fig.~\ref{fig:time_trace}.
 All comparisons that follow for these two runs occur over the times shaded in
-green in Fig. \ref{fig:time_trace}a\&c. Measurements are sampled every
+green in Fig.~\ref{fig:time_trace}a\&c. Measurements are sampled every
 0.1 freefall time units for 500 total time units.
@@
 solution, we compare the horizontally- and time-averaged temperature profiles 
-attained by AE and SE in Fig. \ref{fig:temp_comparison}a.  
+attained by AE and SE in Fig.~\ref{fig:temp_comparison}a.  
 The boundary layer width and structure are  
@@
 the mean temperature in the isothermal interior differs by roughly 0.5\%
-(Fig. \ref{fig:temp_comparison}c).
+(Fig.~\ref{fig:temp_comparison}c).
 
@@
 of point-by-point temperature measurements are compared for the two runs
-in Fig. \ref{fig:temp_comparison}b. To construct these PDFs, 
+in Fig.~\ref{fig:temp_comparison}b. To construct these PDFs, 
 we interpolate the full temperature field
@@
 distribution such that its integral is unity.  The two PDFs have noticeably
-different modes, as is expected from Fig. \ref{fig:temp_comparison}a. 
+different modes, as is expected from Fig.~\ref{fig:temp_comparison}a. 
 Over long timescales, the 0.5\% difference between the two profiles would
@@
 is evident in the asymmetry of the AE PDF near the mode
-in Fig. \ref{fig:temp_comparison}b and also
-the trend of the mean temperature over time in Fig. \ref{fig:time_trace}c.
+in Fig.~\ref{fig:temp_comparison}b and also
+the trend of the mean temperature over time in Fig.~\ref{fig:time_trace}c.
 
@@
 $\KSstat{q}$ to gain insight into the likeness of two PDFs. 
-We show the $\KS{T}$ in Fig. \ref{fig:temp_comparison}d, and the
-CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
+We show the $\KS{T}$ in Fig.~\ref{fig:temp_comparison}d, and the
+CDFs used to construct it overlay the PDFs in Fig.~\ref{fig:temp_comparison}b.
 Near the modes of the temperature PDFs, $\KSstat{T} = 0.495$, 
@@
 measurements in the AE case are at a lower $T$ than those in the SE case.
-While this difference is significant, it is also expected from Fig. \ref{fig:temp_comparison}a.
+While this difference is significant, it is also expected from Fig.~\ref{fig:temp_comparison}a.
 Fortunately, $\KS{T}$ is very small away from the modes, 
@@
 Shown are the PDFs of 
-vertical velocity ($w$, Fig. \ref{fig:pdf_comparison}a), horizontal velocity ($u$, Fig. \ref{fig:pdf_comparison}b),
-and the nonlinear vertical convective flux ($w(T - \angles{T}_{x,y})$, Fig. \ref{fig:pdf_comparison}c). 
+vertical velocity ($w$, Fig.~\ref{fig:pdf_comparison}a), horizontal velocity ($u$, Fig. \ref{fig:pdf_comparison}b),
+and the nonlinear vertical convective flux ($w(T - \angles{T}_{x,y})$, Fig.~\ref{fig:pdf_comparison}c). 
 Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
@@
 The CDFs of each profile are overplotted, and corresponding KS profiles are
-shown in Fig. \ref{fig:pdf_comparison}d-f.  We report
+shown in Fig.~\ref{fig:pdf_comparison}d-f.  We report
 $\KSstat{w} = 0.00615$, $\KSstat{u} = 0.0349$,
@@
 and heat transport between AE and SE is negligible, which is unsurprising in light of
-the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
-this also confirms that the large $\KSstat{T}$ in Fig. \ref{fig:temp_comparison}d is
+the Nu measurements of Fig.~\ref{fig:parameter_space_comparison}a\&d.
+this also confirms that the large $\KSstat{T}$ in Fig.~\ref{fig:temp_comparison}d is
 not of concern, and that the AE run achieves the proper convective solution.
 The horizontal velocity shows some small deviation between the two simulations, and this
-likely relates to the precise configuration of the convective plumes (e.g., Fig. \ref{fig:oscillating_plumes}).
+likely relates to the precise configuration of the convective plumes (e.g., Fig.~\ref{fig:oscillating_plumes}).
 We find that despite our no-slip boundary conditions, the full convective roll systems
@@
 at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
-(d-f) The KS statistics, or the values of CDF$_{\text{AE}}$ - CDF$_{\text{SE}}$,
-are shown for the related distributions, and solid lines indicated positive values
+(d-f) The KS profiles, as defined in Eqn. (\ref{eqn:ks_profile}),
+are shown for the related distributions; solid lines indicate positive values
 while dashed lines are negative values. Unlike the temperature distributions in
-Fig. \ref{fig:temp_comparison}, these distributions, particularly the vertical
-velocity and transport, show very good agreement and small values of the KS statistic.
+Fig.~\ref{fig:temp_comparison}, these distributions
+show very good agreement and small values of the KS statistic.
 \label{fig:pdf_comparison} }
@@
 show the extreme power of AE.  In addition to the fact that AE runs require much
-less total simulation time (see e.g., Fig. \ref{fig:time_trace}a\&c and the time
+less total simulation time (see e.g., Fig.~\ref{fig:time_trace}a\&c and the time
 values in the green highlighted regions), the first application of AE in a given
-simulation (Fig. \ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
+simulation (Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
 increases the average timestep by immediately progressing the simulation into
@@
 be employed to achieve rapid thermal convergence of convective simulations.  We compared
-this technique to the Standard Evolution (SE) of convection through a thermal diffusion timescale and
-showed that AE rapidly obtains solutions whose dynamics are similar to SE solutions.
-The AE method is not only valid at low values of $S$, where SE solutions
-converge quickly due to the short thermal timescale, but AE is also applicable
+this technique to the Standard Evolution (SE) of convection through a full thermal diffusion timescale,
+and we
+showed that AE rapidly obtains solutions whose dynamics are statistically similar to SE solutions.
+The AE method is valid at low values of $S$, where SE solutions
+converge quickly due to the short thermal timescale, and AE remains applicable
 at high values of $S$, where SE solutions are intractable.
-As discussed, AE is equally applicable in 2D and 3D, so we have restricted most of our study to 2D.
+As discussed, AE is equally applicable in 2D and 3D; here we have restricted most of our study to 2D
+to extend our parameter space coverage.
 At the largest values of $S$ in which AE and SE are compared in this work, we find
@@
 while the SE run took 37.9 wall hours, or ($3.1 \cdot 10^5$ cpu-hours). As $S$ increases,
-and the thermal time, $t_{\kappa}$ simultaneously increases, we anticipate the time
+and the thermal time, $t_{\kappa}$, simultaneously increases, we anticipate the 
+computational and wall hour time
 savings to further increase.  The increased computational expense of 3D runs compared
@@
 the convective dynamics
-(e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
+(e.g., the analogs to Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
 and couple those equations with knowledge of the boundary conditions
 and current dynamics as described in
-section \ref{subsection:ae} and appendix \ref{appendix:recipe}.
+section \ref{sec:ae} and appendix \ref{appendix:recipe}.
 While in-depth studies of AE extensions are beyond the 
 scope of this paper, we will briefly discuss
-avenues in which the AE method should be explored and tested.
+avenues in which the AE method should be explored and tested in order
+to push these studies of different convective phenomena further into
+the high-Ra regime.
 
@@
 the vertical flux through the system to increase with height.
+In these systems, the thermal evolution is very slow compared to convective
+dynamical timescales, just as it is in classic \RB convection.
 These systems can be
@@
 towards achieving AE in simulations with astrophysically realistic conductivities.
+In these systems, the fluxes at the upper and lower boundaries are naturally different,
+even in the evolved state. AE can rapidly adjust the thermal profile to carry the proper
+amount of flux in and out of the domain, while achieving the proper interior isotherm.
 
@@
 at a more rapid rate than the thermal diffusion time across the domain due to
-convective mixing.  For example, in Fig. \ref{fig:time_trace}a,
+convective mixing.  For example, in Fig.~\ref{fig:time_trace}a,
 the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
@@
 or otherwise adjust the mean profile to study evolved atmospheres \cite{couston&all2017}.
+In these systems, AE can instantaneously adjust the thermal profile in the
+stable region from a far-disequilibrium state to the properly converged solution,
+skipping the slow thermal evolution.
 
@@
 In many studies of stratified convection, the thermal diffusivity
-is inversely proportional to the density \cite{anders&brown2017}. Thus, the
+is a non-constant coefficient and varies
+inversely proportional to the density \cite{anders&brown2017}. Thus, the
 thermal timescale grows with depth in the atmosphere, and
@@
 
-Ideally, AE can eventually be used in robustly describing convection
+AE techniques can contribute to improving the description of convection
 in stellar evolution codes. Current state of the art stellar structure
 models are the solutions of 1D simulations which parameterize convection 
-using Mixing Length Theory \cite{paxton&all2011}. Recent studies have tried
+using Mixing Length Theory and its variants
+\cite{paxton&all2011, paxton&all2013, paxton&all2015, paxton&all2018}. 
+Recent studies \cite{viallet&all2011, viallet&all2013, viallet&all2016, arnett&all2015, cristini&all2016}
+have tried
 to understand how to simultaneously resolve convective motions and evolve
@@
 cannot achieve fast, meaningful system evolution.
-Recently, efforts have begun to project the results of 3D simulations into 1D
+Other efforts have begun to project the results of 3D simulations into 1D
 models to more properly parameterize convection for stellar evolution
-\cite{arnett&all2015, cristini&all2016}. This is precisely the technology
-employed in the AE method we present here. Through the careful expansion
+\cite{arnett&all2015, cristini&all2016}, but the validity of these 321D techniques
+has not been hitherto thoroughly tested. This is precisely the technology
+employed in the tested AE method we present here. Through the careful expansion
 of AE from \RB convection to fully stratified, compressible convection with realistic
@@
 \item Construct $\xi$, F$_{\text{E, ev}}$, and $\angles{\bm{u} \times \bm{\omega}}_{x,y\text{, ev}}$,
-as specified in section \ref{subsection:ae}
+as specified in section \ref{sec:ae}
 from the averaged profiles.
@@
 $t_{\text{min}} = 30$, 
-and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}c).
+and $P = 0.1$ to get very close to the solution (as in Fig.~\ref{fig:time_trace}c).
 At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
@@
 part because a third BVP generally did not greatly alter the solution
-(as in Fig. \ref{fig:time_trace}c, arrow 3). We wait 50 freefall times after
+(as in Fig.~\ref{fig:time_trace}c, arrow 3). We wait 50 freefall times after
 the final AE BVP solve of each run before beginning to take measurements.

### 2018-03-16 tex/bvp_paper.tex
near-submission-ready

@@
 profile within the domain towards its evolved state. We study \RB convection as a test case for AE.  
-Key evolved properties of AE solutions are measured to be within a few percent
-of measurements of the same quantities in solutions which are reached through 
-evolution over a full thermal timescale. We conclude with a brief discussion of useful extensions
-of AE, such as to studies of stratified, compressible convection.
+Evolved flow properties of AE solutions are measured to be within a few percent
+of solutions which are reached through standard evolution over a full thermal timescale. 
+We conclude with a discussion of useful extensions of AE, including 
+stratified, compressible convection or stellar structure models.
 \end{abstract}
@@
 \label{sec:intro}
-Astrophysical convection occurs in the presence of disparate timescales which
-make direct numerical simulations of realistic models of systems in nature infeasible.  
+Astrophysical convection occurs in the presence of disparate timescales. 
+Studying realistic models of natural systems through direct numerical
+simulations is infeasible due to the
+large separation between various flow timescales and equilibration times.
 Stiffness in astrophysical systems can manifest in multiple ways, some of which can
@@
 stiff, and the difference between
-the sound crossing time and the convective overturn time have made studies of low-Ma stellar
+the sound crossing time and the convective overturn time has made studies of low-Ma stellar
 convection difficult. This stiffness can be avoided using approximations such as
-the anelastic approximation, in which sound waves are explicitly filtered out,
-have been used to study low-Ma flows \cite{brown&all2010, featherstone&hindman2016}.
+the anelastic approximation, in which sound waves are explicitly filtered out
+\cite{brown&all2010, featherstone&hindman2016}.
 Recently, advanced numerical techniques which use fully implicit 
@@
 implicit-explicit \cite{lecoanet&all2014, anders&brown2017, bordwell&all2018} 
-timestepping mechanisms have made it feasible to study
+timestepping mechanisms have made it possible to study
 convection in the fully compressible equations at low Mach numbers, 
@@
 As modern simulations aim to model natural convection
-by in the high-Rayleigh-number (Ra) regime,
-the thermal diffusion timescale becomes intractably large
-compared to dynamical timescales \cite{anders&brown2017}, 
+in the high-Rayleigh-number (Ra) regime,
+the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
+becomes intractably large compared to dynamical timescales 
+such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
+\cite{anders&brown2017}, 
 \begin{equation}
-\frac{t_{\kappa}}{t_{\text{ff}}} = (\text{Ra Pr})^{1/2},
+\frac{t_{\kappa}}{t_{\text{ff}}} \propto (\text{Ra})^{1/2}.
 \end{equation}
-where the thermal timescale is $t_{\kappa} = L_z^2 / \kappa$,
-$L_z$ is the depth of the convective domain, $\kappa$ is
-the thermal diffusivity, and
-the freefall timescale is defined in Section \ref{sec:experiment}.
 Furthermore, as dynamical and thermal timescales separate, 
@@
 Another commonly-used tactic in
-moderate-Ra simulations is to use a simplified system model to construct initial
-conditions, such as the solution of a linear eigenvalue solve \cite{hurlburt&all1984} 
-or an axisymmetric solution for convection in a 3D cylinder \cite{verzicco&camussi1997}. 
-In other systems, a set of initial conditions closer to the evolved state than a standard
-conductive state can be analytically derived \cite{couston&all2017, brandenburg&all2005};
-these experiments all have slowly-evolving stable regions, and so a combination of
-intuition from low-Ra solutions and established convective theory inform an
-initial state which is closer to the evolved state than the standard conductive,
-hydrostatic state often used.
+moderate-Ra simulations is to first solve a simple model of the system in question,
+and then use the solution of that model as initial conditions for full nonlinear
+direct numerical simulations. For example, past studies have used initial conditions from
+a linear eigenvalue solve \cite{hurlburt&all1984} in plane-parallel studies, or
+axisymmetric solutions in studies of convection in 3D cylinders \cite{verzicco&camussi1997}. 
+In other systems, particularly when convective zones are adjacent to stable regions,
+authors often choose initial conditions which are not in a classic, hydrostatic,
+conductive state. Rather, either through knowledge of low-Ra solutions \cite{couston&all2017}
+or broader convective theories such as Mixing Length Theory
+\cite{brandenburg&all2005}, initial conditions can be adjusted such that the stratification
+within the convective domain is closer to an equilibrium state than the largely
+unstable hydrostatic state.
 
@@
 for hundreds of freefall timescales \cite{stevens&all2011}, much less the
-thousands or millions freefall times required for thermal convergence.
+thousands or millions of freefall times required for thermal convergence.
 
@@
 to self-consistently adjust the mean vertical thermodynamic profile towards its evolved state. 
-While a technique of this kind has been used previously \cite{hurlburt&all1986}.
-The details of implementation, the convergence properties, and whether or not the
+While a technique of this kind has been used previously \cite{hurlburt&all1986},
+the details of implementation, the convergence properties, and whether or not the
 accelerated evolution state corresponds to a standard evolution state are not documented.
-In section \ref{sec:experiment}, we describe our convective simulations, our
-numerical methods, and the procedure for achieving accelerated evolution. In
+In section \ref{sec:experiment}, we describe our convective simulations and
+numerical methods. In section \ref{sec:ae}, we describe the procedure for 
+achieving accelerated evolution. In
 section \ref{sec:results}, we compare accelerated evolution solutions
@@
 except in the buoyancy term, where it is $\rho = \rho_0(1  - \alpha T_1)$.
-The gravitational acceleration, $\bm{g} = - g\hat{z}$, is constant.
+The gravitational acceleration, $\bm{g} = - g\bm{\hat{z}}$, is constant.
 The equations of motion are \cite{spiegel&veronis1960}:
@@
 length is in units of the layer height ($L_z$),
-temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
-and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
+temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \partial_z T_0$), 
+and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \partial_z T_0}$).
 By these choices, one time unit is a freefall time ($t_{\text{ff}} = L_z/v_{\text{ff}}$).
@@
 $\bm{u}\cdot\grad\bm{u} = \grad(|\bm{u}|^2/2) - \bm{u}\times(\grad\times\bm{u})$
-and $\grad^2\bm{u} = -\grad\times\grad\times\bm{u}$, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
+and $\grad^2\bm{u} = -\grad\times(\grad\times\bm{u})$, Eqns.~\ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
 become
@@
 \mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
-\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
+\text{Ra} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
 \end{equation}
@@
 was motivated by the fact that accelerated evolution is simpler when both the
-thermal profile and the flux through the domain are fixed at some point in the domain.
+thermal profile and the flux through the domain are fixed at a boundary.
 
@@
 while the timeframe of convergence for an AE solution remains nearly constant
-in simulation freefall time units (see table \ref{table:run_parameters}).
+in simulation freefall time units (see table \ref{table:run_parameters} in
+appendix \ref{appendix:run_table}).
 
@@
 is equal to the flux exiting through the upper boundary.  In general, this 
-evolution is slow in SE (Fig.~\ref{fig:time_trace}a), but AE (Fig. \ref{fig:time_trace}c)
-can take a system whose fluxes are in a strongly disequilibrium state (Fig.~\ref{fig:time_trace}b),
-and quickly put them into a near-equilibrium state, as shown in Fig.~\ref{fig:time_trace}d. In
+evolution is slow in SE (Fig.~\ref{fig:time_trace}a), but AE (Fig.~\ref{fig:time_trace}c)
+can rapidly advance a system whose fluxes are in a strongly disequilibrium state (Fig.~\ref{fig:time_trace}b),
+into a near-equilibrium state, as shown in Fig.~\ref{fig:time_trace}d. In
 this final state both boundaries conduct the same amount of flux.
@@
 \includegraphics[width=\textwidth]{./figs/time_trace.png}
-\caption{(a) Kinetic energy (black) and mean temperature (blue)  vs. time are shown
+\caption{(a) Kinetic energy (black) and $\angles{T} - T_{\text{top}}$ (blue)  vs. time are shown
 for a SE run at $S = 10^5$. The mean evolved values of kinetic energy and mean temperature,
@@
 are denoted by the horizontal dashed lines. (b) The time- and horizontally-averaged
-flux profiles are shown for the times highlighted in orange.
+flux profiles are shown for the times highlighted in orange in (a).
 (c) The same quantities as in (a) are shown, but for AE at the same parameters.
 The axes are scaled identically in (a) and (c), and the AE method is used three times, marked by
-the numbered arrows in (c). The fluxes averaged over the green shaded region of (c)
+the numbered arrows. The fluxes averaged over the green shaded region of (c)
 are shown in (d). The difference between
@@
 are perturbations around a thermal profile defined by these equations in the proper evolved, 
-statistically stationary state. Furthermore, under the specification of
+statistically stationary state. Furthermore, under the proper specification of
 F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
@@
 
-Thus, the AE method is simple: we pause a convective simulation and
+Thus, the AE method occurs in the following steps. First, we pause a convective simulation and
 construct $\xi(z)$ from measured flux profiles in the convective domain.
@@
 $\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
-by $\sqrt{\xi}$, thus diminishing the magnitude of these perturbations appropriately.
+by $\sqrt{\xi}$; this diminishes the magnitude of these perturbations, and the
+flux they carry, appropriately.
 After adjusing the fields of a simulation in this manner, we continue timestepping forward.
@@
 lane, and cool fluid is drawn up by the upflow lane). The plumes in these
-systems naturally oscillate over time, switching between transport being dominated
+systems naturally oscillate horizontally over time, switching between transport being dominated
 by a counterclockwise cell, as pictured in Fig.~\ref{fig:oscillating_plumes}, and
-a counter-clockwise cell. Our choice of no-slip
+a clockwise cell. Our choice of no-slip
 boundary conditions prevents the fluid from entering a full domain shearing state 
 \cite{goluskin&all2014}, and the
-oscillatory nature of the plumes is stable.
+oscillatory nature of the plumes is stable. However, thanks to our choice of periodic
+boundary conditions and despite the no-slip conditions, the full system of the
+upflow and downflow plumes is free to slowly migrate to the left or right over time,
+and we observe this phenomenon in our solutions.
 The 2D SE simulations exhibit the same horizontally
@@
 errors in 2D in Fig.~\ref{fig:parameter_space_comparison}d-f. AE is therefore
-equally effective in both 2D and 3D, and we restrict much of our study to 2D here.
+equally effective in both 2D and 3D, and we restrict much of our study to 2D here
+in order to more thoroughly sample paramtere space.
 
@@
 green in Fig.~\ref{fig:time_trace}a\&c. Measurements are sampled every
-0.1 freefall time units for 500 total time units.
+0.1 freefall time units for 500 total freefall time units.
 
@@
 The difference between the mean profiles is very small, O(0.5\%).
-(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
-the AE and SE CDFs, as a function of temperature.
-The small
-difference in the interior temperature 
-results in a large difference between the two temperature CDFs near the values
+(d) $\KS{T}$, as defined in Eqn.~\ref{eqnks_profile}, is shown. The small
+difference in the mean interior temperature between AE and SE
+results in a large difference between the two temperature distributions near the values
 of the temperature modes.  The spread of temperature around the modes, which includes the 
@@
 Over long timescales, the 0.5\% difference between the two profiles would
-disappear, as the AE solution evolves to be exactly the SE solution -- this
+disappear, as the AE solution evolves to be exactly the SE solution; this
 is evident in the asymmetry of the AE PDF near the mode
@@
 $\KSstat{q}$ to gain insight into the likeness of two PDFs. 
-We show the $\KS{T}$ in Fig.~\ref{fig:temp_comparison}d, and the
+We show $\KS{T}$ in Fig.~\ref{fig:temp_comparison}d, and the
 CDFs used to construct it overlay the PDFs in Fig.~\ref{fig:temp_comparison}b.
@@
 Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
-velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
+velocity boundary conditions (Eqn.~(\ref{eqn:vel_bcs})).
 The CDFs of each profile are overplotted, and corresponding KS profiles are
@@
 likely relates to the precise configuration of the convective plumes (e.g., Fig.~\ref{fig:oscillating_plumes}).
-We find that despite our no-slip boundary conditions, the full convective roll systems
-migrate slowly to the left or the right over time, and the difference in $\KS{u}$
-appears to be caused by a more prominent migration in the -x direction in the AE run
-than in the SE run.
+We find that the difference in $\KS{u}$, which consistently has more probability
+of flows moving left (in the -$x$ direction), appears to be caused by a more prominent migration 
+of the full roll system in the -$x$ direction in the AE run than in the SE run. 
+This migration does not appear to affect the vertical transport appreciably.
 
@@
 at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
-(d-f) The KS profiles, as defined in Eqn. (\ref{eqn:ks_profile}),
+(d-f) The KS profiles, as defined in Eqn.~(\ref{eqn:ks_profile}),
 are shown for the related distributions; solid lines indicate positive values
@@
 a more converged state. For the $S = 10^5$ case we examined in detail, the
-average time step size grew by a factor of 2-3 due to the decreased convective
+average time step grew by a factor of 2-3 due to the decreased convective
 velocities from the transient state to the evolved state. 
@@
 computational and wall hour time
-savings to further increase.  The increased computational expense of 3D runs compared
+savings to further increase.  The additional computational expense of 3D runs compared
 to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.
@@
 scope of this paper, we will briefly discuss
-avenues in which the AE method should be explored and tested in order
-to push these studies of different convective phenomena further into
-the high-Ra regime.
+avenues in which AE should be explored and tested in order
+to push interesting studies of various convective phenomena into
+the astrophysically-interesting, high-Ra regime.
 
@@
 multiplying the flux profiles derived
-in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
-convection in natural system often employ height-dependent conductivities
+in Eqn.~(\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
+convection in natural systems often employ height-dependent conductivities
 \cite{brandenburg2016, kapyla&all2017}, leading
@@
 towards achieving AE in simulations with astrophysically realistic conductivities.
-In these systems, the fluxes at the upper and lower boundaries are naturally different,
-even in the evolved state. AE can rapidly adjust the thermal profile to carry the proper
-amount of flux in and out of the domain, while achieving the proper interior isotherm.
+As such studies (e.g., \cite{kapyla&all2017}) are currently very limited in the
+span of Ra that can be examined, AE could be key in studying the scaling of convective
+properties in such systems, and gaining knowledge about the eventual, very-high-Ra,
+ultimate regime of such systems.
 
@@
 the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
-which is roughly 40\% of a thermal timescale. However, in 
+which is roughly 35\% of a thermal timescale. However, in 
 studies where there is a stable region which is not mixed by convection, the experimentalist
-must either wait through a thermal diffusion time for the region to restratify
-or otherwise adjust the mean profile to study evolved atmospheres \cite{couston&all2017}.
+must either wait through a thermal diffusion time 
+or otherwise manually adjust the initial profile to study converged dynamics \cite{couston&all2017}.
 In these systems, AE can instantaneously adjust the thermal profile in the
@@
 is a non-constant coefficient and varies
-inversely proportional to the density \cite{anders&brown2017}. Thus, the
-thermal timescale grows with depth in the atmosphere, and
+inversely with density \cite{anders&brown2017}. Thus, the
+thermal timescale increases with depth in the atmosphere, and
 the difficulty of achieving thermal convergence grows as simulators study more highly
@@
 In order to extend AE into this regime, two additional pieces of information must be considered.
-First, rather than constructing the profiles in Eqn. (\ref{eqn:bvp_ratios})
+First, rather than constructing the profiles in Eqn.~(\ref{eqn:bvp_ratios})
 with the total flux through the domain, only the superadiabatic portion of
@@
 Second, in addition to solving for
-hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
+hydrostatic balance and thermal equilibrium, as in Eqns.~(\ref{eqn:bouss_BVP_momentum})
 \& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
@@
 in stellar evolution codes. Current state of the art stellar structure
-models are the solutions of 1D simulations which parameterize convection 
+models are solutions of 1D simulations which parameterize convection 
 using Mixing Length Theory and its variants
@@
 opacities, it is possible that carefully evolved stellar structure models which
-use statistics from resolved convective motions, rather than parameterized 1D models,
-are well within reach of modern computing tools.
+use statistics from resolved convective motions are well within reach of modern computing resources.
 
@@
 \appendix
-\section{Accelerated Evolution Recipe}
-\label{appendix:recipe}
-In order to achieve Accelerated Evolution (AE), we pause the Direct Numerical Simulation (DNS)
-which is evolving the dynamics of convection and solve a 1D Boundary Value Problem (BVP)
-consisting of Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
-After solving this BVP, we appropriately adjust the fields being evolved in the DNS
-towards their evolved state, and then we continue running the now-evolved DNS.
-The specific steps taken in completing the AE method are as follows:
-\begin{enumerate}
-\item Wait some time, $t_{\text{transient}}$, before beginning the AE process.
-\item During the DNS, calculate time averages of the 1D vertical profiles of
-F$_{\text{E}}$, F$_{\text{tot}}$, 
-and $\angles{\bm{u} \times \bm{\omega}}_{x,y}$, updating them every timestep.  
-To calculate these
-averages, we use a trapezoidal-rule integration in time, and then divide by the
-total time elapsed over which the average is taken. 
-\item Pause the DNS once the averages are sufficiently converged. 
-To ensure that an average is converged, at
-least some time $t_{\text{min}}$ must have passed since the average was started to
-ensure that the full range of convective dynamics are probed, and
-the profiles must change by no more than $P$\% on a given timestep.
-\item Construct $\xi$, F$_{\text{E, ev}}$, and $\angles{\bm{u} \times \bm{\omega}}_{x,y\text{, ev}}$,
-as specified in section \ref{sec:ae}
-from the averaged profiles.
-\item Solve the BVP for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
-evolved state.  Set the horizontal average of the current DNS thermodynamic fields
-equal to the results of the BVP.
-\item Multiply the velocity field, $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$,
-and the temperature fluctuations, $T - \angles{T}_{x,y}$,
-by $\sqrt{\xi}$ in the DNS to properly reduce the convective flux.
-\item Continue running the DNS.
-\end{enumerate}
-We refer to this process as an ``AE BVP solve.''
-
-While the use of a single AE BVP solve rapidly advances the convecting state to
-one that is closer to the evolved state, we find that repeating this method 
-multiple times is the best way to
-ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
-set $t_{\text{transient}} = 50$, completed an AE BVP solve
-with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure.
-For all 3D runs and 2D runs with $S \in [10^5, 10^6]$,
-we did a first AE BVP solve with $t_{\text{transient}} = 20$,
-$t_{\text{min}} = 20$, and $P = 1$ in order to quickly reach a near-
-converged state and vastly increase our timestep size.  After this first solve, 
-we completed two AE BVP solves, with $t_{\text{transient}} = 30$,
-$t_{\text{min}} = 30$, 
-and $P = 0.1$ to get very close to the solution (as in Fig.~\ref{fig:time_trace}c).
-At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
-$P = 1$. For the first solve, we set $t_{\text{transient}} = 20$, and for the
-second we set $t_{\text{transient}} = 30$. We used fewer solves at this high
-value of $S$ in part to reduce the computational expense of the run, and in
-part because a third BVP generally did not greatly alter the solution
-(as in Fig.~\ref{fig:time_trace}c, arrow 3). We wait 50 freefall times after
-the final AE BVP solve of each run before beginning to take measurements.
-
 \section{Table of Runs}
@@
 
+\newpage
+\section{Accelerated Evolution Recipe}
+\label{appendix:recipe}
+In order to achieve Accelerated Evolution (AE), we pause the Direct Numerical Simulation (DNS)
+which is evolving the dynamics of convection and solve a 1D Boundary Value Problem (BVP)
+consisting of Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
+After solving this BVP, we appropriately adjust the fields being evolved in the DNS
+towards their evolved state, and then we continue running the now-evolved DNS.
+The specific steps taken in completing the AE method are as follows:
+\begin{enumerate}
+\item Wait some time, $t_{\text{transient}}$, before beginning the AE process.
+\item During the DNS, calculate time averages of the 1D vertical profiles of
+F$_{\text{E}}$, F$_{\text{tot}}$, 
+and $\angles{\bm{u} \times \bm{\omega}}_{x,y}$, updating them every timestep.  
+To calculate these
+averages, we use a trapezoidal-rule integration in time, and then divide by the
+total time elapsed over which the average is taken. 
+\item Pause the DNS once the averages are sufficiently converged. 
+To ensure that an average is converged, at
+least some time $t_{\text{min}}$ must have passed since the average was started to
+ensure that the full range of convective dynamics are probed, and
+the profiles must change by no more than $P$\% on a given timestep.
+\item Construct $\xi$, F$_{\text{E, ev}}$, and $\angles{\bm{u} \times \bm{\omega}}_{x,y\text{, ev}}$,
+as specified in section \ref{sec:ae}
+from the averaged profiles.
+\item Solve the BVP for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
+evolved state.  Set the horizontal average of the current DNS thermodynamic fields
+equal to the results of the BVP.
+\item Multiply the velocity field, $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$,
+and the temperature fluctuations, $T - \angles{T}_{x,y}$,
+by $\sqrt{\xi}$ in the DNS to properly reduce the convective flux.
+\item Continue running the DNS.
+\end{enumerate}
+We refer to this process as an ``AE BVP solve.''
+
+While the use of a single AE BVP solve rapidly advances the convecting state to
+one that is closer to the evolved state, we find that repeating this method 
+multiple times is the best way to
+ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
+set $t_{\text{transient}} = 50$, completed an AE BVP solve
+with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure.
+For all 3D runs and 2D runs with $S \in [10^5, 10^6]$,
+we did a first AE BVP solve with $t_{\text{transient}} = 20$,
+$t_{\text{min}} = 20$, and $P = 1$ in order to quickly reach a near-
+converged state and vastly increase our timestep size.  After this first solve, 
+we completed two AE BVP solves, with $t_{\text{transient}} = 30$,
+$t_{\text{min}} = 30$, 
+and $P = 0.1$ to get very close to the solution (as in Fig.~\ref{fig:time_trace}c).
+At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
+$P = 1$. For the first solve, we set $t_{\text{transient}} = 20$, and for the
+second we set $t_{\text{transient}} = 30$. We used fewer solves at this high
+value of $S$ in part to reduce the computational expense of the run, and in
+part because a third BVP generally did not greatly alter the solution
+(as in Fig.~\ref{fig:time_trace}c, arrow 3). We wait 50 freefall times after
+the final AE BVP solve of each run before beginning to take measurements.
+
 \bibliography{biblio.bib}

### 2018-05-30 referee_process/first_submission/referee_response.tex
adds referee reponse files

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Editor,
$\,$\newline

\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}

\begin{singlespace}
Short cover letter blah blah.

$\,$\newline
\noindent
Sincerely,

Evan H. Anders, Benjamin P. Brown, \& Jeffrey S. Oishi

%\end{singlespace}

$\,$
\newline
$\,$
\newline
\noindent
\Large{\textbf{Response to first referee:}}\newline$\,$\newline\indent

\begin{myquotation}
This paper describes a technique for accelerating the convergence to
thermal equilibrium in convective DNS simulations where such
convergence from an initial conductive state would be long. The
technique is essentially to evolve a DNS for for a while, collect the
background state non-equilibrium fluxes, and then solve a mean field
boundary value problem with scaled version of these fluxes for a new
background state in thermal equilibrium, then use this to restart the
DNS. These, or very similar techniques, have been used by many in the
past, although to my knowledge, as the authors here also claim, they
have not been explicitly written down in a paper. The authors have
gone to the trouble of doing this, not only providing a fairly
detailed prescription of the technique, but also some evidence of its
usefulness, albeit in a very simple case where it will definitely work
which is perhaps not totally representative. I guess I think this
paper is overall worthwhile, since it provides a place for newcomers
to the business to find some potentially time-saving help, even though
the ideas are not original. I think the most important issue with this
paper is that its claims of more universal applicability are somewhat
naive. I would suggest they temper these assertions substantially.
\end{myquotation}
So this is the summary / takeaway paragraph. I think we need to
in some way \emph{prove} that such a prescription can be useful in
more complex situations. This is one of the biggest points we need to
address from this referee report: either temper our claims or prove them.

\begin{myquotation}
Basic questions:

How confident can one be that the BVP puts you closer to a nonlinear
saturated state that where you were? For example, in highly nonlinear
(turbulent) problems, there may be multiple states, maybe even
multiple stable states, with different background properties. Is it
possible to guarantee that you are not putting the system into an
equilibrium but unstable state, from which an equally long evolution
to a stable state is required? For the simple problems shown here,
this is perhaps not likely, but for very high degrees of turbulence,
or situations where unknown instabilities may exist, this process may
not be so successful perhaps? This is again a factor in my hesitation
about the total applicability of this technique across many problems
beyond the one the authors present.
\end{myquotation}
Yeah, this is a good question. I don't know the answer to this immediately.
I think we need to make some sort of clear distinction between ``AE works
perfectly always'' and ``AE is better than running from initial conditions.''

\begin{myquotation}
Here are some more comments in chronological order, not order of
importance.

Abstract and Intro:

The authors come from an astrophysical convection background where the
Peclet number is generally high and where these techniques are useful.
They need to be careful to be clear that the convection they are
talking about is high Pe, the parameter that describes the separation
of overturning and thermal diffusion timescales. These techniques will
not be useful (or required) for low Pe number situations.
\end{myquotation}

Yeah, that's fair. Peclet number is actually what matters, not Re, for
this problem. We should say that, and perhaps we should report Pe if we
ever report one or the other.

\begin{myquotation}
Section II.

After (4): The expression for delta T\_0 assumes that the background
temperature gradient is constant, which has not been introduced yet.

The sentence “ Our choice of the thermal boundary conditions in Eqn.
(9 ) was motivated by the fact that accelerated evolution is simpler
when both the thermal profile and the flux through the domain are
fixed at a boundary” is never revisited or explained, unless I missed
it?
\end{myquotation}
Two small fixes.

\begin{myquotation}
Section III.

The assumption after equation (10) that the convective region will NOT
change substantially is a BIG assumption that allows this technique to
work. In a situation where nonlinearities affect the extent of the
convective region (e.g. penetrative convection), our anywhere else
where the active region varies (e.g. an instability), this technique
will have problems. More on this later.

Equations (12-13): These are essentially steady state, mean field
equations, with approximated fluxes for the later (solved) state. Is
the prescription for the approximated fluxes in (11) going to work for
all problems? It does so for the case examined, but this case has a
simple background temperature gradient. Would this work for more
complicated problems, for example, with a non-constant DT\_0/dz? What
about the cases that are NOT symmetric (i.e. periodic in the
horizontal where the mean field equations contain some other terms?
\end{myquotation}
Yeah, this should work for non-constant DT/Dz. I designed the layout of the
paper with internally heated systems in mind, where the background temperature
gradient is linear. This is the reason for the generality of the $\xi$
and $F_{tot}$ construction. Should say so explicitly, maybe?

\begin{myquotation}
Last para: the authors say “proper” profile, but this is an
approximate thermodynamic background profile, essentially the first
iterate in an iteration scheme. Perhaps proper is not the right word?
\end{myquotation}
Proper probably isn't the right word.

\begin{myquotation}
IV:

I don’t understand ``$10^{3+2/3}$''? Why is written like this?
\end{myquotation}
I think that's a typo from a previous draft.

\begin{myquotation}
I am not convinced that the whole ``2D and 3D scaling laws'' section
adds anything at all to this paper. It shows that this technique can
be used but so does the single example that is interrupted by this
piece. It is somewhat interesting for the scaling laws found
themselves, but it sounds like this should be in a different paper
because there is not enough explanation to understand things totally
here. I feel like the examples before and after this section are
sufficient to make the point about the AE scheme.
\end{myquotation}
Fair. It's sort of off-topic. The purpose of that figure is to show that
AE works across Ra, not to show that we get correct scaling laws. We
should address this.

\begin{myquotation}
When discussing the PDFs, the author refer to the “modes” of the PDF?
This sounds a bit odd to me. Do they mean the peaks? The phrase
“temperature fluctuations off of the modes” is particularly baffling!
\end{myquotation}
Yeah, I mean mode as in ``the mode of the PDF'', so the max. I can say max
or peak.

\begin{myquotation}
The fact that the mean temperature profile is off by a constant factor
almost everywhere is a bit disturbing, even if the factor is small.
Does continued iteration of AE not get rid of this? If not, then this
is significant, because it would take a thermal relaxation time again
to correct this issue.
\end{myquotation}
This is the second biggest point in this referee report. We need to talk about this
and figure out how to address it.

\begin{myquotation}
I felt like I wanted a section at the end of this section that
described how much the AE saved in computational time and wall time
over SE. There is a bit of it here, and some of it in the discussion,
and some more details in the appendix, which seems a bit scattered. I
would be tempted to agglomerate it all here in a separate section.
\end{myquotation}
Fair, let's figure out how to consolidate this and present it in a meaningful way.

\begin{myquotation}
V.

This is the section I have most issues with.

The example performed was the most likely to succeed. The 2D cases
were essentially rolls. Were the 3D cases still essentially 2D rolls
too (since the scalings came out the same)? What about larger aspect
ratio and more turbulence cases where the dynamics would be more
complex? Keeping things smooth certainly enhances the likelihood of a
simple scaling of the nonlinear fluxes working.

I think the projections for more complicated problems mentioned are
naive. If there is any nonlinear adjustment to the convective region,
e.g. penetrative convection, then the technique is far less likely to
be simply successful in the current form. The assumption of fully
convective and thermal boundary layers remaining in place is a big
one, and this is not really acknowledged. The authors do mention
penetrative convection and do indeed say that only a stiff case would
work under these premises, but this is a bit hidden, I think, and
needs to be emphasized more. For example, the penetrative ice-water
problem even in Boussinesq would not work well with this technique I
think, since the penetrative region can deepen dramatically, and
adjust the radiative flux to match the substantially changed
convective flux.

Furthermore, the compressible case is much more danger prone than
envisioned here. I suspect that in the iteration to accelerate, any
mismatch in the fluctuations and the estimated means in the DNS will
lead to major transients in the form of sound waves, which can totally
destroy a compressible evolution by reducing the tilmestep
substantially, so this technique may have drawbacks if there is not
filtering of sound waves somehow. The authors have glossed over these
problems in their eagerness to extol the virtues of their scheme.

I think the claims of this method working in many more situations need
to be examined more thoroughly before being made so boldly here.
\end{myquotation}
We either need to back off on some of these claims, show that AE works
in a more complex situation, or temper these claims with warnings of
possible complications.

\noindent
\Large{\textbf{Response to second referee:}}\newline$\,$\newline\indent
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\item The authors should provide clarification on what the following terms mean: ``thermal equilibration'', ``thermally relaxed'', and ``thermal convergence''. Also, are these terms related to statistically steady state?
\item What is the ``Kelvin-Helmholtz timescale''?
\end{enumerate}
\end{myquotation}
We need to define these
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{2}
\item The authors note that the bootstrapping method is susceptible to hysteresis effects. They should provide examples of where such effects have been observed.
\end{enumerate}
\end{myquotation}
I know this from my own work. Shearing states are heavily susceptible to hysteresis, especially in stratified domains. I don't know of anywhere this is explicitly said in the literature.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{3}
\item It is true that direct numerical simulation of turbulent thermal convection is expensive. However, the highest Ra simulation run by Stevens et al. reaches a stationary state in a few hundreds of free-fall times. Hence, what is the necessity of running simulations for ``thousands or millions of free-fall times''?
\end{enumerate}
\end{myquotation}
Yeah, this is mostly only a problem in stratified cases. Actually, in general, I think this isn't a huge problem for constant temperature BCs, but it is for other types of BCs in RBC.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{4}
\item Presumably, the most important step in the “Accelerated convergence method” involves decreasing the heat flux through the top boundary so as to match it with the heat flux at the bottom boundary. This is achieved by introducing a function $\xi(z) \equiv  F_B/F_{tot}$. The following questions arise:
\begin{enumerate}
\item What is the functional form of $\xi(z)$? And where does the z-dependence come from?
\item Here, $F_{tot}$ is not really a constant, but depends on time. Hence, $\xi(z)$ should also be a function of time.
\item The “evolved” quantities are obtained by multiplying $\langle \bm{u} \times \bm{\omega} \rangle$ and $F_E$ by $\xi(z)$. Can this construction be rigorously justified? I would like the authors to provide more details on how they arrived at this step.
\end{enumerate}
\end{enumerate}
\end{myquotation}
We need to make all of this clearer, apparently. The fact that it's a function of $t$ is an important change.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{5}
\item The assumption that convection at early times occupies roughly the same volume as convection in the stationary state is acceptable. However, there is also the possibility that instead of decreasing the heat flux at the top one could increase it at the bottom? The boundary condition for T1 at the bottom surface is
$$
\frac{\partial T_1}{\partial z} = 0
$$
So, the imposed heat flux at the bottom is 0.
\end{enumerate}
\end{myquotation}
I think there's a fundamental misunderstanding of what's happening with the boundary conditions here. I need to type up a clear response to the referee, and also make sure that I make this clear in the paper.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{6}
\item Could the authors construct plots of Nu vs. t (like in figure 2) for both AE and SE starting from t = 0? I would like to understand how Nu(t) evolves with time in the AE cases.
\end{enumerate}
\end{myquotation}
Sure, we can do send the referee that plot. I don't think we should change the 
figure as is, though.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{7}
\item I diasgree with the authors’ statement that “Previous studies in 2D convection may have avoided these time-varying Nu states by using bootstrapping techniques...” If one were to measure Nu(t) in the interior, then the sign of Nu would fluctuate between positive and negative. However, the time average would be always be positive. (This I know from my own work.)
\end{enumerate}
\end{myquotation}
Hmm. Interesting point. Need to think about how to respond to this carefully.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{8}
\item Have the authors studied convection with fixed temperature and no-slip conditions at the top and bottom surfaces? Have they compared the AE and SE results for that case?
\end{enumerate}
\end{myquotation}
We have not. We've used no-slip at both surfaces, but only mixed thermal boundary conditions. We can do fixed T boundary conditions, but that would require a different treatment of the total flux.

\end{singlespace}

\bibliography{../../biblio.bib}
\end{document}

### 2018-05-31 referee_process/first_submission/referee_response.tex
ref response update from convos today

@@
 
+Don't bring in my special knowledge that other people don't get from
+reading the paper.
+
+Tone it down.
+
 \begin{myquotation}
@@
 How confident can one be that the BVP puts you closer to a nonlinear
-saturated state that where you were? For example, in highly nonlinear
+saturated state than where you were? For example, in highly nonlinear
 (turbulent) problems, there may be multiple states, maybe even
@@
 \end{myquotation}
+Questions: (1) how confident that it puts you closer? (2) are there multiple states?
+(1) Fairly confident. Gets you closer to the nonlinear saturated state that you are
+IN. Puts you closer to ONE. Not necessarily the one you would evolve towards. But
+initial conditions also mess with your final state.
+(2) No, it's not possible to guarantee. We have seen multiple states and
+slow evolution from one to another. When you're on a solution branch, doing AE
+generally keeps you on that same solution branch, but there's no guarantee that it's
+the same solution as you would achieve through a fully thermal evolution. We should
+say this in the discussion section, this will also help temper usefulness claims.
+
 Yeah, this is a good question. I don't know the answer to this immediately.
@@
 this problem. We should say that, and perhaps we should report Pe if we
-ever report one or the other.
+ever report one or the other. Ultimate goal of systems we're aiming for is
+high Pe than we can achieve through SE.
 
@@
 
-The sentence “ Our choice of the thermal boundary conditions in Eqn.
+The sentence ``Our choice of the thermal boundary conditions in Eqn.
 (9 ) was motivated by the fact that accelerated evolution is simpler
 when both the thermal profile and the flux through the domain are
-fixed at a boundary” is never revisited or explained, unless I missed
+fixed at a boundary'' is never revisited or explained, unless I missed
 it?
@@
 \end{myquotation}
+While writing up $\xi$ bit, write a little bit saying that the defintion of
+$\xi$ needs to be modified for non-constant dT/dz.
 Yeah, this should work for non-constant DT/Dz. I designed the layout of the
@@
 \end{myquotation}
-I think that's a typo from a previous draft.
+We take 3 equal steps in log space. We have changed it to 3.67 for easier reading.
 
@@
 \end{myquotation}
+The wording around figs 2-3 is hindering both referees' understanding of the paper.
 Fair. It's sort of off-topic. The purpose of that figure is to show that
@@
 \end{myquotation}
-Fair, let's figure out how to consolidate this and present it in a meaningful way.
+This is a good idea. We should make a section of this info.
+``Computational benefits of AE.''
 
@@
 \end{myquotation}
+We're explaining simple ideas, so we should remove jargon / clarify as much as
+possible. Make it as readable and simple to understand as possible.
 We need to define these
@@
 \end{enumerate}
-\end{myquotation}
+\end{myquotation}a
+We've seen this in polytropes, but we haven't seen HYSTERESIS. There are different
+stable states and bootstrapping keeps you in the evolved state from lower Ra.
+But we don't see hysteresis, word this CAREFULLY, and what we say in response to
+referee in private comments is important.
 I know this from my own work. Shearing states are heavily susceptible to hysteresis, especially in stratified domains. I don't know of anywhere this is explicitly said in the literature.
@@
 \end{myquotation}
+(1) Steady state vs. thermal convergence (and maybe this will be shown with Nu vs. energy time traces). Are we measuring nu or are we measuring temperature profiles.
 Yeah, this is mostly only a problem in stratified cases. Actually, in general, I think this isn't a huge problem for constant temperature BCs, but it is for other types of BCs in RBC.
@@
 \end{enumerate}
-\end{myquotation}
+\end{myquotation}a
+The question is: why are we rescaling these things by this flux ratio? Answer: ``th
+is what we do in order to do X." We're not going to rigorously derive this. They
+may be concerned that we're sneaking in a nonlinearity or something like that
+because we have this new function that we're sneaking in. Convince them that it's
+not a function. It's simple. It's funkiness is not what gives us our solutions.
+It's useful. Explain why it's useful, because the referee can't see why it's useful. This is a voodoo step of this in some ways.
+*** This is very important.
 We need to make all of this clearer, apparently. The fact that it's a function of $t$ is an important change.
@@
 \end{myquotation}
+Referee is latching onto positive/negativeness of Nu, rather than high/low transport.
+We went into a speculative state. We need to figure out what we're saying, how the ref got confused by what we said, and remove speculative nonsense.
 Hmm. Interesting point. Need to think about how to respond to this carefully.
@@
 We have not. We've used no-slip at both surfaces, but only mixed thermal boundary conditions. We can do fixed T boundary conditions, but that would require a different treatment of the total flux.
+We don't forsee major difficulties in this being done, but it was different enough
+from the mainline approach of the paper that we didn't do it.
 

### 2018-06-07 referee_process/first_submission/referee_response.tex
big commit of referee work

--- 2018-05-30 referee_process/first_submission/referee_response.tex
@@
 \end{myquotation}
-
-Yeah, that's fair. Peclet number is actually what matters, not Re, for
-this problem. We should say that, and perhaps we should report Pe if we
-ever report one or the other.
+We have reworked some text in the second paragraph of the introduction section
+in order to clarify that we are discussing high Pe convection.
 
@@
 
-After (4): The expression for delta T\_0 assumes that the background
+After (4): The expression for $\Delta T_0$ assumes that the background
 temperature gradient is constant, which has not been introduced yet.
+\end{myquotation}
+We have added a sentence before the description of our nondimensionalization
+stating that the initial temperature profile is linear.
 
-The sentence “ Our choice of the thermal boundary conditions in Eqn.
+\begin{myquotation}
+The sentence ``Our choice of the thermal boundary conditions in Eqn.
 (9 ) was motivated by the fact that accelerated evolution is simpler
 when both the thermal profile and the flux through the domain are
-fixed at a boundary” is never revisited or explained, unless I missed
+fixed at a boundary'' is never revisited or explained, unless I missed
 it?
 \end{myquotation}
-Two small fixes.
+We have clarified this in the second to last pargraph of section III 
+(and added a forward reference to this part of the text).
 
@@
 work. In a situation where nonlinearities affect the extent of the
-convective region (e.g. penetrative convection), our anywhere else
+convective region (e.g. penetrative convection), or anywhere else
 where the active region varies (e.g. an instability), this technique
@@
 simple background temperature gradient. Would this work for more
-complicated problems, for example, with a non-constant DT\_0/dz? What
+complicated problems, for example, with a non-constant $\partial T_0/\partial z$? What
 about the cases that are NOT symmetric (i.e. periodic in the
@@
 \end{myquotation}
-Yeah, this should work for non-constant DT/Dz. I designed the layout of the
-paper with internally heated systems in mind, where the background temperature
-gradient is linear. This is the reason for the generality of the $\xi$
-and $F_{tot}$ construction. Should say so explicitly, maybe?
+We are fairly confident that this prescription will work for more complex
+initial temperature profiles ($\text{F}_{\text{B}}$ will need to pick up some
+height dependence in the defintion of $\chi$, for simple internally heated
+systems, for example). It would be useful to test AE in such a case, but such
+studies are beyond the scope of this work, and we leave it to future work
+to determine if this method is valid in such cases.
+
+We are uncertain of 
+how AE will work for non-symmetric, horizontally variant cases. As it fundamentally
+adjusts the mean profile of the whole domain in a uniform manner, it may not be
+ideal for such cases.
+
+Refer to the revised final section of the paper for some discussion on these
+issues.
 
@@
 \end{myquotation}
-Proper probably isn't the right word.
+We have replaced ``proper'' with more appropriate descriptors.
 
@@
 \end{myquotation}
-I think that's a typo from a previous draft.
+To determine the Ra of our simulations, we take even sized steps in log space
+(3 per decade). We have changed 3 + 2/3 to 3.67 for easier reading.
 
@@
 \end{myquotation}
-Fair. It's sort of off-topic. The purpose of that figure is to show that
-AE works across Ra, not to show that we get correct scaling laws. We
-should address this.
+We feel that it is important to show that AE works across some swath of parameter
+space, in order to demonstrate its robustness for the problem presented here.
+We have trimmed the text of the scaling laws section and reduced speculation in
+order to keep the paper on topic. We have also replaced Re with Pe in this
+section in order to reinforce the point that we are interested in high Pe
+convection (since Pr = 1, Re = Pe numerically, so only labels have changed).
 
 \begin{myquotation}
-When discussing the PDFs, the author refer to the “modes” of the PDF?
+When discussing the PDFs, the author refer to the ``modes" of the PDF?
 This sounds a bit odd to me. Do they mean the peaks? The phrase
-“temperature fluctuations off of the modes” is particularly baffling!
+``temperature fluctuations off of the modes'' is particularly baffling!
 \end{myquotation}
-Yeah, I mean mode as in ``the mode of the PDF'', so the max. I can say max
-or peak.
+We have replaced ``modes'' with ``maxima'' for clarity.
 
@@
 \end{myquotation}
-This is the second biggest point in this referee report. We need to talk about this
-and figure out how to address it.
+We have added some discussion of our stopping criterion to appendix describing
+the AE method, and we have discussed this problem in our new conclusion section.
 
@@
 \end{myquotation}
-Fair, let's figure out how to consolidate this and present it in a meaningful way.
+We have added a new section V., ``Computational Benefits of AE'', to explicitly
+
+state speed increases of AE vs. SE. This section contains a small table which
+explicitly compares computational cost of select AE and SE runs in 2D and 3D.
 
@@
 \end{myquotation}
-We either need to back off on some of these claims, show that AE works
-in a more complex situation, or temper these claims with warnings of
-possible complications.
+We agree that our intial conclusion section was over-eager. We have removed
+our hopeful speculation and leave future work to
+prove if AE is useful in more complex situations (fully compressible,
+penetrative convection, etc.). The discussion section now includes a discussion
+of difficulties that the AE method faces, and future work.
 
@@
 Also, are these terms related to statistically steady state?
+\end{enumerate}
+\end{myquotation}
+All three of these phrases are equivalent, and we have replaced all mentions of
+thermal equilibration, relaxation, and thermal convergence with ``thermal
+equilibration'' or ``thermally equilibrated'' throughout the paper. This term
+is explained in pargraph 2 of the introduction.
+\begin{myquotation}
+$\,$\\\vspace{-1.25cm}
+\begin{enumerate}
+\setcounter{enumi}{1}
 \item What is the ``Kelvin-Helmholtz timescale''?
@@
 \end{myquotation}
-We need to define these
+The Kelvin-Helmholtz timescale is 
+$$
+t_{\text{KH}} = \frac{E_g}{L},
+$$
+where $E_g$ is the gravitational energy in a system, and $L$ is the luminosity
+(energy output / time). Basically it is a timescale that astronomers and
+astrophysicists use to estimate the timescale thermal evolution of a system 
+(e.g., a star). Since the point we were trying to make is that ``the mean 
+thermodynamic structure of the Sun evolves \emph{really} slowly,''
+we have removed this jargon and said this more clearly in paragraph 2 of the intro.
+
 \begin{myquotation}
@@
 \end{myquotation}
-I know this from my own work. Shearing states are heavily susceptible to hysteresis, especially in stratified domains. I don't know of anywhere this is explicitly said in the literature.
+We misspoke. We have not specifically seen hysteresis effects (nor have we seen
+this in the literature).  We meant to say that in simulations where there are
+multiple solution branches (e.g., a convective roll and a shearing solution),
+bootstrapping to different parameters will likely ensure that you stay on the 
+same solution branch, even at the higher parameters. Particularly, in our own
+work in stratified atmospheres, atmospheres trend toward shearing states, and then
+stay stuck in those states as we bootstrap to higher Ra.
+
+We have corrected our error, and made our meaning clearer.
+
 \begin{myquotation}
@@
 \end{myquotation}
-Yeah, this is mostly only a problem in stratified cases. Actually, in general, I think this isn't a huge problem for constant temperature BCs, but it is for other types of BCs in RBC.
+The convective flows reach a statistically stationary state quickly, particularly
+in Boussinesq systems, but here we are discussing the thermal equilibration
+of systems which have some sort of thermal stratification. Even if the convective 
+flows reach a state that is relatively statistically stationary quickly, the
+temperature (and/or density) stratification of the convecting atmosphere can take
+much longer to equilibrate, especially in the high Pe regime.
+
 \begin{myquotation}
@@
 \item Here, $F_{tot}$ is not really a constant, but depends on time. Hence, $\xi(z)$ should also be a function of time.
-\item The “evolved” quantities are obtained by multiplying $\langle \bm{u} \times \bm{\omega} \rangle$ and $F_E$ by $\xi(z)$.
+\item The ``evolved'' quantities are obtained by multiplying $\langle u \times \omega \rangle$ and $F_E$ by $\xi(z)$.
 Can this construction be rigorously justified?
@@
 \end{myquotation}
-We need to make all of this clearer, apparently. The fact that it's a function of $t$ is an important change.
+(a) In the simple case studied in this problem, where $F_B$ is constant in time
+and space, the functional form of $\xi \propto F_{tot}^{-1}$, and depnds only
+on the fluxes of the convective system. Since $F_{tot}$ can
+have a large z-dependence (e.g., Fig. 1b), $\xi$, too, has a z-dependence. 
+$\xi$ is simply a height-dependent scaling that we use to appropriately
+adjust our velocity, temperature, etc.
+
+(b) We have changed $\xi(z) \rightarrow \xi(z, t)$.
+
+(c) Physically, $\xi$ is a scaling factor that tells us how much larger the flux
+is in the interior than it should be. 
+We assume that $F_{tot} \sim F_{conv} \sim w (T - \langle T \rangle )$.
+As such, we assume that $\xi \propto (w^{-1/2}, (T - \langle T \rangle )^{-1/2})$,
+and that scaling both the temperature fields and the temperature fluctuations 
+around the mean profile will reduce the convective flux in the proper way.
+We scale $\langle \bm{u}\times\bm{\omega}\rangle$ by $\xi$, as it is
+nondimensionally of order $u^2 / L$, and so if the velocities must be multiplied
+by $\sqrt{\xi}$, this term must be multiplied by $\xi$.
+
+We cannot rigorously derive $\xi$ from first principles. Its form, and the use of
+it here, are the result of our experience and familiarity with convection.
+
 \begin{myquotation}
@@
 \end{myquotation}
-I think there's a fundamental misunderstanding of what's happening with the boundary conditions here.
-I need to type up a clear response to the referee, and also make sure that I make this clear in the paper.
+Our boundary condition is that fluctuations in the temperature derivative at the
+bottom of the domain are zero. Which is to say that 
+$\partial T_0 / \partial z = -1 =$ constant. We could increase the heat flux at
+the bottom to match the heat flux at the top, but in that case we would be solving
+a different system with a different set of boundary conditions than the ones
+studied here.
+
 \begin{myquotation}
@@
 \end{myquotation}
-Hmm. Interesting point. Need to think about how to respond to this carefully.
+We have tightened up the discussion around the scaling laws, as requested by the
+other referee report. We have removed speculative statements which aimed to
+compare the scaling law of Nu found here with Nu elsewhere in order to keep
+the focus of our paper on AE rather than Nu scaling for our system setup.
+
+Fig. 2 is not aiming to point out the sign of Nu (positive vs. negative), but
+rather aiming to show the flow morphology at times of high heat transport and
+low heat transport.
+
 \begin{myquotation}
@@
 \end{myquotation}
-We have not. We've used no-slip at both surfaces, but only mixed thermal boundary conditions. We can do fixed T boundary conditions, but that would require a different treatment of the total flux.
+We have not. We've used no-slip at both surfaces, 
+but only mixed thermal boundary conditions. 
+We don't forsee major difficulties in AE being applied to fixed T boundary 
+conditions, but felt that such a study was outside the scope of this work.
 

### 2018-06-07 tex/bvp_paper.tex
big commit of referee work

@@
 
-Unfortunately, convective systems are stiff in more than one timescale and
-generally evolve over the course of thermal
-timescales, which are often much larger than all relevant
-dynamical timescales. Transport by convection is a highly nonlinear process,
+Unfortunately, astrophysical convective systems are stiff in more than one 
+timescale. Specifically, the Peclet number (Pe), the ratio of the thermal
+diffusion timescale to the advective velocity timescale, is large.
+This further stiffness arises as a result of the thermodynamic structure 
+evolving over the course of thermal timescales, not the short dynamical advective
+timescales. In order to reach thermal equilibration, a steady state in which
+the thermal structure of the atmosphere is no longer evolving over time,
+many dynamical timescales must be simulated.
+Transport by convection is a highly nonlinear process,
 and this makes addressing the stiffness much more challenging; even fully
@@
 Resolving dynamics in atmospheres which are sufficiently
-thermally relaxed remains a challenging problem.
+thermally equilibrated remains a challenging problem.
 Solar convection is a prime example of this phenomenon, as
@@
 (convection overturns every $\sim 5$ minutes at the solar surface)
-compared to the Sun's Kelvin-Helmholtz timescale of
-$3 \cdot 10^7$ years \cite{stix2003}.  
+compared to the Sun's thermal evolution timescale, which is O($10^7$) years
+\cite{stix2003}.  
 In such a system, it is impossible to resolve the convective dynamics while also
@@
 traditional timestepping techniques alone.
-As modern simulations aim to model natural convection
+As modern simulations aim to model natural, high-Pe convection
 in the high-Rayleigh-number (Ra) regime,
@@
 numericists studying convection, and an abundance of approaches has been employed to
-study thermally converged solutions. One popular method for accelerating the convergence
+study thermally equilibrated solutions. One popular method for accelerating the convergence
 of high-Ra solutions is by ``bootstrapping'' -- the process of using the flow
@@
 Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
-but it is not without its faults.  Bootstrapped solutions are susceptible to hysteresis
-effects, in which large-scale convective structures present in the
+but it is not without its faults.  In systems in which there are multiple
+stable solutions, such as a roll state and a shearing state of convection,
+the large-scale convective structures present in the
 low Ra solution imprint onto the dynamics of the new, high Ra solution. 
+It is possible that this puts the high Ra solution into a different stable state
+than it would naturally reach from an initial, hydrostatically stable configuration.
 Another commonly-used tactic in
@@
 Despite the numerous methods that have been used,
-the most straightforward way to achieve a thermally converged solution
+the most straightforward way to achieve a thermally equilibrated solution
 is to evolve a convective simulation through a thermal timescale. Some modern
@@
 for hundreds of freefall timescales \cite{stevens&all2011}, much less the
-thousands or millions of freefall times required for thermal convergence.
+thousands or millions of freefall times required for thermal equilibration.
 
@@
 $T = T_0(z) + T_1(x, y, z, t)$ are the initial and fluctuating components of temperature, 
-and $P$ is the kinematic pressure.
+and $P$ is the kinematic pressure. The initial temperature profile decreases
+linearly with height.
 We non-dimensionalize these equations such that
@@
 was motivated by the fact that accelerated evolution is simpler when both the
-thermal profile and the flux through the domain are fixed at a boundary.
+thermal profile and the flux through the domain are fixed at a boundary 
+(see section \ref{sec:ae}).
 
@@
 \emph{the mean thermodynamic structure of the system is fully specified}. 
+Our choice of fixing the temperature at the top boundary and the flux at the bottom
+boundary ensures that there is a unique solution for $T_1$ given the evolved
+fluxes. If flux were fixed at both boundaries, there would be infinitely many
+temperature solutions. If temperature were fixed at both boundaries, 
+$\text{F}_{\text{B}}$ would not be precisely known \emph{a priori}.
 
@@
 Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
-to obtain the proper evolved thermodynamic profile, and proper conductive flux.
-To obtain the proper convective enthalpy flux, we multiply both the velocity field,
+to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
+To consistently modify the convective enthalpy flux, we multiply both the velocity field,
 $\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
@@
 where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
-When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
+When $S < 10^{3.67}$ in 2D and for all runs in 3D, 
 the evolved system is characterized by a time-stationary value of Nu, and is thus
@@
 The time- and volume-averaged values of Nu, the RMS
-Reynolds number (Re), and the mean temperature 
+Peclet number (Pe), and the mean temperature 
 are shown for AE solutions in Fig.~\ref{fig:parameter_space_comparison}a-c.
@@
 the vertical lines represent the standard deviation of the measurement over time.
-Nu is shown as a function of Ra and $S$ in Fig.~\ref{fig:parameter_space_comparison}a.
-The dynamic nature of the plume structures (e.g., Fig.~\ref{fig:oscillating_plumes})
-diminishes the mean
-scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
-which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
-Previous studies in 2D convection may have avoided these time-varying Nu states by using
-bootstrapping techniques as initial conditions for high $S$ runs.
-In Fig.~\ref{fig:parameter_space_comparison}b, we report 
-$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$ as a function of Ra and $S$.  
-Re measures the degree of
-turbulence in the solution, and scales roughly as
-$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
-the value of Re over time.
-Fig.~\ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$,
-the mean value of the temperature minus its value at the upper (fixed temperature) boundary.
-The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
-so this measurements serves as a probe of the temperature jump across the boundary
-layers. As a result, we expect this measure to
-scale inversely with Nu in converged solutions
-where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
-that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
-scaling of Nu.
+Nu is shown as a function of Ra and $S$ in 
+Fig.~\ref{fig:parameter_space_comparison}a, while 
+$\text{Pe} = \angles{|\bm{u}|} / \mathcal{P}$ is shown in 
+Fig.~\ref{fig:parameter_space_comparison}b, and $\angles{T} - T_{\text{top}}$ 
+(the mean temperature value minus its value at the upper, 
+fixed temperature boundary) is shown in Fig.~\ref{fig:parameter_space_comparison}c.
+We report $\text{Nu} \propto \text{Ra}^{1/5}$,
+$\text{Pe} \propto \text{Ra}^{0.45}$, and 
+$(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$.
+The average temperature, $\angles{T}$, 
+is dominated by its value in the isothermal interior,
+so this measurement serves as a probe of the temperature jump across the boundary
+layers. Thus, the inverse scaling of average temperature and Nu that we
+find here is expected for thermally equilibrated solutions \cite{otero&all2002}.
 
@@
 measured in AE are accurate to SE values to within $\sim 1$\%.
-Re measurements show marginally greater error, with AE measurements being 
+Pe measurements show marginally greater error, with AE measurements being 
 $\leq 2$\% different from SE measurements.
@@
 results in a large difference between the two temperature distributions near the values
-of the temperature modes.  The spread of temperature around the modes, which includes the 
+of the temperature maxima.  The spread of temperature around the maxima, which includes the 
 fluctuations that drive convection, are nearly identical between the two runs.
@@
 distribution such that its integral is unity.  The two PDFs have noticeably
-different modes, as is expected from Fig.~\ref{fig:temp_comparison}a. 
+different maxima, as is expected from Fig.~\ref{fig:temp_comparison}a. 
 Over long timescales, the 0.5\% difference between the two profiles would
 disappear, as the AE solution evolves to be exactly the SE solution; this
-is evident in the asymmetry of the AE PDF near the mode
+is evident in the asymmetry of the AE PDF near the maxima
 in Fig.~\ref{fig:temp_comparison}b and also
@@
 CDFs used to construct it overlay the PDFs in Fig.~\ref{fig:temp_comparison}b.
-Near the modes of the temperature PDFs, $\KSstat{T} = 0.495$, 
+Near the maxima of the temperature PDFs, $\KSstat{T} = 0.495$, 
 which is very large and implies that roughly half of all
@@
 While this difference is significant, it is also expected from Fig.~\ref{fig:temp_comparison}a.
-Fortunately, $\KS{T}$ is very small away from the modes, 
-indicating that the temperature fluctuations off of the modes, which are the primary
+Fortunately, $\KS{T}$ is very small away from the maxima, 
+indicating that the temperature fluctuations off of the maxima, which are the primary
 drivers of convective transport, are nearly identical.
@@
 
+%%%%%%%%%%%%
+%%%%%%%%%%%
+% SPEEDINESS OF AE vs SE
+%%%%%%%%%%%
+%%%%%%%%%%%%
+
+\section{Computational Benefits of AE}
+\label{sec:speedups}
 The small differences between the SE and AE solutions for the case studied in 
@@
 
-\section{Extensions \& Conclusions}
+\section{Discussion \& Conclusions}
 \label{sec:extensions}
 In this work we have studied a method of Accelerated Evolution (AE) which can
-be employed to achieve rapid thermal convergence of convective simulations.  We compared
+be employed to achieve rapid thermal equilibration of convective simulations.  We compared
 this technique to the Standard Evolution (SE) of convection through a full thermal diffusion timescale,
@@
 
-Here we studied \RB convection as a test case for the AE method, but we argue that
-the true power of this technique is in its extensions to more complicated studies.
+Here we studied \RB convection with mixed thermal boundary
+conditions as a test case for the AE method. There are many axes of complexity
+which are beyond the scope of this work, but into which future work should explore
+the correctness of AE. For example, the efficacy of AE at higher aspect ratios
+where multiple stable solution branches exist at a given value of Ra should be
+examined in order to determine if AE and SE obtain the same solution.
+
+Some assumptions which inform the AE solution, for example that the convection
+intially occupies the same space as the evolved convection, are large. It is
+unclear if such an assumption would hold in more complex studies, such as those
+of penetrative convection. However, techniques similar to AE have long been used
+in such studies \cite{hurlburt&all1986}, so the careful testing of such a 
+technique in domains with paired stable-unstable layers is key.
+
+While over short timescales the AE method does not perfectly achieve the same
+thermodynamic profile as the SE method (see e.g., the offset between the PDFs
+in Fig.~\ref{fig:temp_comparison}b), the AE solution is \emph{close} to the SE
+solution, and is achievable on dynamical timescales, which are computationally
+tractable at high Ra, while thermal timescales (SE) are intractable. Thus,
+while the AE solution is still evolving towards the SE solution over long thermal
+timescales, the change in the structure over time is small 
+(O(0.5\%), Fig.~\ref{fig:temp_comparison}c), and the dynamics of the AE solution 
+and SE solution, which are often the most interesting part of a 
+convective simulation to measure, are not massively different (e.g., 
+Fig.~\ref{fig:parameter_space_comparison}d-f).
+
+We anticipate that
+this technique will be powerful in its extensions to more complicated studies.
 To achieve AE in more complicated systems, one need only derive 
@@
 the astrophysically-interesting, high-Ra regime.
-
-Convection in natural systems is often driven by internal heating processes
-rather than imposed, fixed boundary conditions. The AE procedure can be straightforwardly
-applied to Boussinesq studies of internally heated convection \cite{goluskin2016},
-where a constant source term in the energy equation causes 
-the vertical flux through the system to increase with height.
-In these systems, the thermal evolution is very slow compared to convective
-dynamical timescales, just as it is in classic \RB convection.
-These systems can be
-studied using exactly the methods that we examined here, but 
-multiplying the flux profiles derived
-in Eqn.~(\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
-convection in natural systems often employ height-dependent conductivities
-\cite{brandenburg2016, kapyla&all2017}, leading
-to natural flux divergences that act as internal heating terms.
-The study
-of AE in the context of simple internal heating simulations will be an important step
-towards achieving AE in simulations with astrophysically realistic conductivities.
-As such studies (e.g., \cite{kapyla&all2017}) are currently very limited in the
-span of Ra that can be examined, AE could be key in studying the scaling of convective
-properties in such systems, and gaining knowledge about the eventual, very-high-Ra,
-ultimate regime of such systems.
-
-A further area which could benefit from AE is overshooting convection, in which
-studies examine adjacent stable and convecting regions
-\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
-When the interface between the stable region
-and the convecting region is stiff,
-convective motions cannot accelerate the restratification of the stable region.
-In fully-convective domains, such as those studied in this work, the thermodynamics evolve
-at a more rapid rate than the thermal diffusion time across the domain due to
-convective mixing.  For example, in Fig.~\ref{fig:time_trace}a,
-the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
-which is roughly 35\% of a thermal timescale. However, in 
-studies where there is a stable region which is not mixed by convection, the experimentalist
-must either wait through a thermal diffusion time 
-or otherwise manually adjust the initial profile to study converged dynamics \cite{couston&all2017}.
-In these systems, AE can instantaneously adjust the thermal profile in the
-stable region from a far-disequilibrium state to the properly converged solution,
-skipping the slow thermal evolution.
-
-Studies of stratified, compressible convection have much to gain through
-developing and employing AE.
-In many studies of stratified convection, the thermal diffusivity
-is a non-constant coefficient and varies
-inversely with density \cite{anders&brown2017}. Thus, the
-thermal timescale increases with depth in the atmosphere, and
-the difficulty of achieving thermal convergence grows as simulators study more highly
-stratified domains. For example, in a modestly stratified atmosphere which spans three
-density scale heights, the density at the bottom, and thus the thermal timescale, is a
-factor of 20 greater than at the top of the domain.
-In order to extend AE into this regime, two additional pieces of information must be considered.
-First, rather than constructing the profiles in Eqn.~(\ref{eqn:bvp_ratios})
-with the total flux through the domain, only the superadiabatic portion of
-the flux should be considered \cite{anders&brown2017}.
-Second, in addition to solving for
-hydrostatic balance and thermal equilibrium, as in Eqns.~(\ref{eqn:bouss_BVP_momentum})
-\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
-profile in a manner which conserves mass.  In a 1D boundary value problem, such as
-is solved to achieve AE here, this implies the inclusion of an equation which tracks
-the vertically integrated mass, and sets boundary conditions on that mass to ensure
-that no mass enters or leaves the domain.
-
-AE techniques can contribute to improving the description of convection
-in stellar evolution codes. Current state of the art stellar structure
-models are solutions of 1D simulations which parameterize convection 
-using Mixing Length Theory and its variants
-\cite{paxton&all2011, paxton&all2013, paxton&all2015, paxton&all2018}. 
-Recent studies \cite{viallet&all2011, viallet&all2013, viallet&all2016, arnett&all2015, cristini&all2016}
-have tried
-to understand how to simultaneously resolve convective motions and evolve
-systems through many thermal timescales, as is required when determining the
-interior structure of stars over their evolving lifetimes.
-We now know that implicit timestepping methods
-must resolve convective motions in order to timestep with stability
-\cite{viallet&all2011, viallet&all2013, viallet&all2016}, and thus
-cannot achieve fast, meaningful system evolution.
-Other efforts have begun to project the results of 3D simulations into 1D
-models to more properly parameterize convection for stellar evolution
-\cite{arnett&all2015, cristini&all2016}, but the validity of these 321D techniques
-has not been hitherto thoroughly tested. This is precisely the technology
-employed in the tested AE method we present here. Through the careful expansion
-of AE from \RB convection to fully stratified, compressible convection with realistic
-opacities, it is possible that carefully evolved stellar structure models which
-use statistics from resolved convective motions are well within reach of modern computing resources.
 

### 2018-06-11 tex/bvp_paper.tex
adds new fig 2 file

@@
 We study 2D and 3D convection in which the domain is a cartesian box, 
-whose dimensionless vertical extent is $z \in [-1/2, 1/2]$, 
+whose dimensionless vertical extent is $z \in [0, 1]$, 
 and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$,
@@
 \begin{equation}
-u = v = w = 0 \, \, \text{at}\,\,z = \pm 1/2,
+u = v = w = 0 \, \, \text{at}\,\,z = \pm 0,1,
 \label{eqn:vel_bcs}
@@
 \begin{equation}
-T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
-\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=-1/2.
+T_1 = 0 \,\,\text{at}\,\, z=1, \qquad
+\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=0.
 \label{eqn:temp_bcs}
@@
 The initial temperature profile is linearly unstable,
-$T_0(z) = -z$. On top of this profile, we fill $T_1$ with
+$T_0(z) = 0.5 - z$. On top of this profile, we fill $T_1$ with
 random white noise whose magnitude is $10^{-6}\mathcal{P}$, and which is
@@
 \label{sec:speedups}
+
+\begin{table}
+\caption{
+}
+\label{table:speed}
+\begin{center}
+\begin{tabularx}{\textwidth}{ X X X X }
+\hline																	
+$S$	&	nz, nx, ny	&	$t_{\text{sim,AE}}/t_{\text{sim,SE}}$	&	
+$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$		\\
+\hline \hline \multicolumn{4}{c}{\vspace{-0.2cm}}\\
+\multicolumn{4}{c}{\vspace{0.1cm}2D Runs} \\
+\hline
+$10^1$	&	32,	64	&	2.32    & \\
+$10^2$	&	64,	128	&	0.905   & 2.03  & 4.369 &  2.152    \\
+$10^3$	&	128,256	&	0.24    & 0.387 & 20.63 &  53.25    \\
+$10^4$	&	256,512	&	0.084   & 0.15  & 180.82&  1205.25  \\
+$10^5$	&	512,1024&	0.036   & 0.115 & 2757.73& 24061.75 \\
+\\ \hline \hline \multicolumn{4}{c}{\vspace{-0.2cm}}\\
+\multicolumn{4}{c}{\vspace{0.1cm}3D Runs} \\
+\hline
+$10^1$	&	32,	64$\times$64	& 2.29	& 106.15/61.5\\
+$10^2$	&	64,	128$\times$128	& 0.69	& 111.92/185.35\\
+$10^3$	&	128,256$\times$256	& 0.21	& 1426.39/6985.18\\
+$10^4$	&	256,512$\times$512	& 0.068	& 23063.77/331,717\\
+\hline																	
+\end{tabularx}
+\end{center}
+\end{table}
+
 The small differences between the SE and AE solutions for the case studied in 

### 2018-06-11 code/plotting/nu_comp.py

@@ -1,0 +1,182 @@
+import matplotlib.style
+import matplotlib
+#matplotlib.use('Agg')
+matplotlib.style.use('classic')
+matplotlib.rcParams.update({'font.size': 11})
+import matplotlib.pyplot as plt
+plt.rc('font',family='Times New Roman')
+from matplotlib.colors import ColorConverter
+import os
+import numpy as np
+import glob
+from docopt import docopt
+from mpi4py import MPI
+comm_world = MPI.COMM_WORLD
+from collections import OrderedDict
+import h5py
+import matplotlib.gridspec as gridspec
+
+
+import dedalus.public as de
+from scipy.interpolate import interp1d
+
+
+import pandas as pd
+
+
+
+base_dir = '/home/evanhanders/research/papers/accelerated_evolution/code/runs/'
+subdir = 'bvp_pre/rayleigh_benard_2D_mixed_noSlip_Ra1.30e8_Pr1_a2/'
+subdir2 = 'base_pre/rayleigh_benard_2D_mixed_noSlip_Ra1.30e8_Pr1_a2/'
+subdir3 = 'bvp_post/rayleigh_benard_2D_mixed_noSlip_Ra1.30e8_Pr1_a2/'
+full_dir = base_dir + '/' + subdir
+full_dir2 = base_dir + '/' + subdir2
+full_dir3 = base_dir + '/' + subdir3
+
+
+fig = plt.figure(figsize=(8, 6))
+gs     = gridspec.GridSpec(*(1000,1000))
+gs_info = (((30,0), 450, 1000), ((550, 0), 420, 660), ((550, 680), 420, 320) )
+axs = []
+for i in range(len(gs_info)):
+    axs.append(plt.subplot(gs.new_subplotspec(*gs_info[i])))
+
+ax1 = axs[0]
+ax2 = axs[1]
+ax3 = axs[2]
+
+
+scalars = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir), 'r')
+scalars2 = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir2), 'r')
+scalars3 = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir3), 'r')
+
[…]

### 2018-06-11 code/plotting/oscillating_plumes.py

@@ -24,7 +24,7 @@ from scipy.interpolate import interp1d
 
 
 
-base_dir = '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+base_dir = '/home/evanhanders/research/papers/accelerated_evolution/code/runs/bvp_post'
 subdir = 'rayleigh_benard_2D_mixed_noSlip_Ra1.30e8_Pr1_a2/'
 subdir2 = 'rayleigh_benard_2D_mixed_noSlip_Ra1.30e10_Pr1_a2/'
 full_dir = base_dir + '/' + subdir

### 2018-06-12 tex/bvp_paper.tex
updates conclusion and appendix text

@@
 where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
+The time evolution of Nu in AE and SE is compared to the mean temperature evolution
+in Fig.~\ref{fig:nu_v_time}. The mean value of Nu evolves towards its final value
+rapidly compared to the mean temperature. Thus, if Nu is the primary metric of 
+the evolved flows being measured, it is unnecessary to run for a full thermal
+time, and previous authors have taken advantage of this (CITE).
 When $S < 10^{3.67}$ in 2D and for all runs in 3D, 
@@
 where warm fluid is pulled down by the downflow
-lane, and cool fluid is drawn up by the upflow lane). The plumes in these
+lane, and cool fluid is drawn up by the upflow lane). High-transport and 
+low-transport states exhibit smaller Nu fluctuations away from the 
+mean once the system reaches thermal equilibrium (Fig. \ref{fig:nu_v_time}).
+The plumes in these
 systems naturally oscillate horizontally over time, switching between transport being dominated
@@
 
-\begin{figure}[t!]
+\begin{figure}[b]
+\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
+\caption{Here we compare the time evolution of the mean temperature and the
+Nusselt number for the 2D SE and AE run shown in Fig.~\ref{fig:time_trace}.
+\label{fig:nu_v_time} }
+\end{figure}
+
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
@@
 
-\begin{figure}[b!]
+\begin{figure}[t!]
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
@@
 
-\begin{figure}[t]
+\begin{figure}[b!]
 \includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
@@
 %%%%%%%%%%%%
-
+\newpage$\,$\newpage
 \section{Computational Benefits of AE}
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X }
+\begin{tabularx}{\textwidth}{ X X X X X X}
 \hline																	
 $S$	&	nz, nx, ny	&	$t_{\text{sim,AE}}/t_{\text{sim,SE}}$	&	
-$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$		\\
-\hline \hline \multicolumn{4}{c}{\vspace{-0.2cm}}\\
-\multicolumn{4}{c}{\vspace{0.1cm}2D Runs} \\
+$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$ & $t_{\text{CPU,AE}}$ & $t_{\text{CPU, SE}}$		\\
+\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
+\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
 \hline
-$10^1$	&	32,	64	&	2.32    & \\
 $10^2$	&	64,	128	&	0.905   & 2.03  & 4.369 &  2.152    \\
@@
 $10^5$	&	512,1024&	0.036   & 0.115 & 2757.73& 24061.75 \\
-\\ \hline \hline \multicolumn{4}{c}{\vspace{-0.2cm}}\\
-\multicolumn{4}{c}{\vspace{0.1cm}3D Runs} \\
+\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
+\multicolumn{6}{c}{\vspace{0.1cm}3D Runs} \\
 \hline
-$10^1$	&	32,	64$\times$64	& 2.29	& 106.15/61.5\\
-$10^2$	&	64,	128$\times$128	& 0.69	& 111.92/185.35\\
-$10^3$	&	128,256$\times$256	& 0.21	& 1426.39/6985.18\\
-$10^4$	&	256,512$\times$512	& 0.068	& 23063.77/331,717\\
+$10^1$	&	32,	64$\times$64	& 2.29	& 1.73  &   106.15      &   61.5\\
+$10^2$	&	64,	128$\times$128	& 0.69	& 0.6   &   111.92      &   185.35\\
+$10^3$	&	128,256$\times$256	& 0.21	& 0.2   &   1426.39     &   6985.18\\
+$10^4$	&	256,512$\times$512	& 0.068	& 0.07  &   23063.77    &   331,717\\
 \hline																	
@@
 
-The small differences between the SE and AE solutions for the case studied in 
-Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
-show the extreme power of AE.  In addition to the fact that AE runs require much
-less total simulation time (see e.g., Fig.~\ref{fig:time_trace}a\&c and the time
-values in the green highlighted regions), the first application of AE in a given
+The primary reason to use AE, rather than evolving all solutions through SE,
+is because of the computational timesaving of such an approach. In table 
+\ref{table:speed}, we compare simulation time and cpu-hour cost for select
+2D and 3D runs in which AE and SE solutions were compared. Times reported
+for AE and SE runs do not include the time over which measurements were taken
+in the equilibrated state, but rather represent the time required to reach a
+fully equilibrated state under the AE or SE formalism. All simulations
+were performed on Broadwell nodes on NASA's Pleiades supercomputer 
+(Intel Xeon E5-2680v4 processors). The key metric which highlights the usefulness
+of AE is the number of cpu-hours used for the AE run in units of cpu-hours used
+for the SE run ($t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$). We see that at low
+resolution and low supercriticality, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}} > 1$,
+and AE is not useful. However, as $S$ grows, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$
+shrinks. At the highest supercriticalities for which AE and SE were compared
+in this work, AE runs cost roughly an order of magnitude less computing time 
+than SE runs.
+ The additional computational expense of 3D runs compared
+to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.
+
+While storing information about the mean state for the AE solve marginally
+decreases the rate at which our solver timesteps, the first application of AE in a given
 simulation (Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
@@
 by nearly a factor of 4.
-Thus, AE achieves converged solutions in few simulation time units,
-while also taking less real world time per simulation time unit, when compared
-to the slowly converging SE state at the same simulation time.
 
@@
 time savings of nearly an order of magnitude.
-For example, in 2D and at $S = 10^5$, the
-AE run took 10.78 wall hours on 256 cores ($2.8\cdot 10^3$ cpu-hours) while the 
-SE run took 94 wall hours ($2.4\cdot 10^4$ cpu-hours). In 3D and at $S = 10^4$,
-the AE run took 2.81 wall hours on 8192 cores ($2.3 \cdot 10^4$ cpu-hours),
-while the SE run took 37.9 wall hours, or ($3.1 \cdot 10^5$ cpu-hours). As $S$ increases,
-and the thermal time, $t_{\kappa}$, simultaneously increases, we anticipate the 
-computational and wall hour time
-savings to further increase.  The additional computational expense of 3D runs compared
-to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.
 
-Here we studied \RB convection with mixed thermal boundary
-conditions as a test case for the AE method. There are many axes of complexity
-which are beyond the scope of this work, but into which future work should explore
-the correctness of AE. For example, the efficacy of AE at higher aspect ratios
-where multiple stable solution branches exist at a given value of Ra should be
-examined in order to determine if AE and SE obtain the same solution.
-
-Some assumptions which inform the AE solution, for example that the convection
-intially occupies the same space as the evolved convection, are large. It is
-unclear if such an assumption would hold in more complex studies, such as those
-of penetrative convection. However, techniques similar to AE have long been used
-in such studies \cite{hurlburt&all1986}, so the careful testing of such a 
-technique in domains with paired stable-unstable layers is key.
-
-While over short timescales the AE method does not perfectly achieve the same
-thermodynamic profile as the SE method (see e.g., the offset between the PDFs
-in Fig.~\ref{fig:temp_comparison}b), the AE solution is \emph{close} to the SE
-solution, and is achievable on dynamical timescales, which are computationally
-tractable at high Ra, while thermal timescales (SE) are intractable. Thus,
-while the AE solution is still evolving towards the SE solution over long thermal
-timescales, the change in the structure over time is small 
-(O(0.5\%), Fig.~\ref{fig:temp_comparison}c), and the dynamics of the AE solution 
-and SE solution, which are often the most interesting part of a 
-convective simulation to measure, are not massively different (e.g., 
-Fig.~\ref{fig:parameter_space_comparison}d-f).
-
+Here we studied the simplest possible case for the application of AE:
+\RB convection at low aspect ratio with mixed thermal boundary. 
 We anticipate that
@@
 section \ref{sec:ae} and appendix \ref{appendix:recipe}.
-While in-depth studies of AE extensions are beyond the 
-scope of this paper, we will briefly discuss
-avenues in which AE should be explored and tested in order
-to push interesting studies of various convective phenomena into
-the astrophysically-interesting, high-Ra regime.
+In general, AE should be useful in studies where there are two disparate
+timescales which must both be resolved and which cannot be overcome through
+clever timestepping techniques.  Some avenues in which extensions of AE could
+be beneficial for expanding the available parameter space of exploration
+include studies of internally heated convection \cite{goluskin2016},
+convection with height-dependent conductivities \cite{kapyla&all2017},
+penetrative convection \cite{hurlburt&all1986,brandenburg&all2005,couston&all2017},
+or fully compressible, stratified convection \cite{anders&brown2017}.
+
+We conclude by noting that AE should be extended to these more complicated
+studies with care. 
+While AE was extremely effective in this simple case studied here
+(where the aspect ratio was low, 
+the bounds of the convective domain were pre-defined,
+and the solutions were simple rolls),
+this may not be the case for more complicated systems. For example, at
+higher aspect ratios, multiple stable solution branches of various numbers of
+convective rolls may exist, and there is no guarantee that AE and SE will
+arrive at the same solution. 
+Some assumptions which inform the AE solution, such as the assumption
+that the convection
+intially occupies the same space as the evolved convection, may not hold in
+studies of penetrative convection, despite the fact that similar methods have
+long been used in those studies \cite{hurlburt&all1986}.
+Our work here should serve as a basis for determining if AE techniques are
+valid and effective in more complex studies of convection.
 
 \begin{acknowledgments}
+We thank the two anonymous referees whose careful comments greatly 
+improved the clarity and scientific content of this paper.
 EHA acknowledges the support of the University of Colorado's George 
@@
 Computations were conducted 
-with support by the NASA High End Computing (HEC) Program through the NASA 
+with the support of the NASA High End Computing (HEC) Program through the NASA 
 Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
-with allocations GID s1647 and GID g26133.
+with allocation GID s1647.
 \end{acknowledgments}
@@
 
+In general, the user of the AE method should choose some threshold
+fractional change of the mean temperature profile, $f$, such that once
+an AE solution differs from the DNS mean profile by less than $f$, the simulation
+is considered converged and the iterative AE adjustments may be stopped. In
+other words, once
+\begin{equation}
+\frac{|\angles{T}_{\text{DNS}} - \angles{T}_{\text{AE}}|}{|\angles{T}_{\text{DNS}}|} < f,
+\end{equation}
+the solution is converged. In this work, we chose our number of AE iterations
+such that $f \approx 10^{-2}$, except at $S = 10^7$, where we stopped after one AE
+iteration due to higher computational expense. In general, the user of AE could
+set $f$ smaller, and in doing so reduce the separation between the AE and SE
+solutions, which can be seen in e.g., Fig.~\ref{fig:temp_comparison}.
+
 \bibliography{biblio.bib}

### 2018-06-12 code/plotting/nu_comp.py

@@ -34,7 +34,7 @@ full_dir2 = base_dir + '/' + subdir2
 full_dir3 = base_dir + '/' + subdir3
 
 
-fig = plt.figure(figsize=(8, 6))
+fig = plt.figure(figsize=(8, 4))
 gs     = gridspec.GridSpec(*(1000,1000))
 gs_info = (((30,0), 450, 1000), ((550, 0), 420, 660), ((550, 680), 420, 320) )
 axs = []
@@ -103,10 +103,10 @@ ax2.set_xticks([200, 400, 600])
 
 #ax3.set_xscale('log')
 ax3.set_yscale('log')
-ax3.set_xlim(11115, 1.1435e4)
+ax3.set_xlim(11400-320, 11400)
 ax3.set_ylim(9e-1, 1e3)
-ax3.set_xticks([11235, 11435])
-ax3.set_xticklabels(("11235", "11435"))
+ax3.set_xticks([11200, 11400])
+ax3.set_xticklabels(("11200", "11400"))
 
 ax1.annotate("AE", xy=(950, 5e2))
 ax3.annotate("SE", xy=(11385, 5e2))
@@ -141,22 +141,33 @@ for ax in [ax1_2, ax3_2]:
     ax.tick_params(axis='y', colors='b')
 
 
-axs_share = [ax1_2, ax2_2, ax3_2]
-for ax in axs_share:
-    ax.set_ylim(2e-2, 1e0)
+axs_share = [(ax1_2, time1[-1] + 100), (ax2_2, time2[-1]+10), (ax3_2, time2[-1]+20)]
+for ax, t in axs_share:
+    ax.set_ylim(2e-2, 5e-1)
+#    plt.axes(ax)
+#    y_ticks = np.array([2e-2, 1e-1, 5e-1])
+#    plt.yticks(y_ticks, (r'$2\cdot 10^{-2}$', r'$10^{-2}$', r'$5\cdot 10^{-1}$'))
+    if ax == ax2_2:
+        continue
+    plt.axes(ax)
+    ax.set_yticks((1e-1,))
+    ax.set_yticklabels((r'$10^{-1}$',))
+    trans = ax.get_xaxis_transform() # x in data untis, y in axes fraction
+    ax.annotate(r'$2\cdot 10^{-2}$', xy=(t, 0.03), xycoords=trans, color='blue')
+    ax.annotate(r'$5\cdot 10^{-1}$', xy=(t, 0.94), xycoords=trans, color='blue')
 
 axs[1].spines['right'].set_visible(False)
[…]

### 2018-06-12 referee_process/first_submission/referee_response.tex
so many changes

@@
 \begin{document}
-%----------------------------------------------------------------------------------------
-%	LETTER CONTENT
-%----------------------------------------------------------------------------------------
-\noindent
-Dear Editor,
-$\,$\newline
-
 \newenvironment{myquotation}{
@@
 }
+%----------------------------------------------------------------------------------------
+%	LETTER CONTENT
+%----------------------------------------------------------------------------------------
+\noindent
+Dear Eckart, other PRFluids editors, and anonymous referees,
+$\,$\newline
 
 \begin{singlespace}
-Short cover letter blah blah.
+We return a new draft of our manuscript, ``Accelerated evolution in
+convective simulations,'' addressing the concerns of the referee reports.
+We would like to point out a few major changes in this version of the manuscript.
+A new section, ``Computational time-savings of AE'' has been added after the
+results section and before the conclusion section. In this section, we directly
+compare the computational cost of AE and SE for select simulations and we discuss
+the computational benefits of AE.  Furthermore, the final section of our paper
+is now titled ``Discussion \& Conclusions;'' we have removed a vast amount
+of speculation regarding extensions of AE from this section and have added
+a paragraph containing some caveats regarding challenges that users will face in
+extending AE to more difficult systems.  In addition to these changes in the text,
+we have added a new Fig. 2 which compares the evolution of Nu and the
+mean temperature in AE and SE, and we have added some accompanying text for this
+figure to the results section.  Small changes in the text throughout the paper have
+been made for clarity where these changes were requested by the reports.
+
+We feel that the clarity and scientific content of the paper have been greatly
+improved by the referee reports, and we thank the referees for their honest 
+critiques and attention to detail. We hope that the changes made have clarified
+and cleaned up the areas of concern raised in both referee reports.  Below we
+include our responses to the reports. The original text of the reports is included
+in italics, and our responses follow inline in unitalicized blocks.
 
@@
 
-$\,$
-\newline
-$\,$
-\newline
+\newpage
 \noindent
@@
 naive. I would suggest they temper these assertions substantially.
-\end{myquotation}
-So this is the summary / takeaway paragraph. I think we need to
-in some way \emph{prove} that such a prescription can be useful in
-more complex situations. This is one of the biggest points we need to
-address from this referee report: either temper our claims or prove them.
 
-Don't bring in my special knowledge that other people don't get from
-reading the paper.
-
-Tone it down.
-
-\begin{myquotation}
 Basic questions:
@@
 \end{myquotation}
-Questions: (1) how confident that it puts you closer? (2) are there multiple states?
-(1) Fairly confident. Gets you closer to the nonlinear saturated state that you are
-IN. Puts you closer to ONE. Not necessarily the one you would evolve towards. But
-initial conditions also mess with your final state.
-(2) No, it's not possible to guarantee. We have seen multiple states and
-slow evolution from one to another. When you're on a solution branch, doing AE
-generally keeps you on that same solution branch, but there's no guarantee that it's
-the same solution as you would achieve through a fully thermal evolution. We should
-say this in the discussion section, this will also help temper usefulness claims.
-
-Yeah, this is a good question. I don't know the answer to this immediately.
-I think we need to make some sort of clear distinction between ``AE works
-perfectly always'' and ``AE is better than running from initial conditions.''
+We are confident that the BVP puts us closer to a nonlinear saturated state
+than we were before. It is true that there may be multiple stable states, and there
+is no guarantee that the BVP puts the solution into the same stable state as
+SE. We have mentioned this in our conclusion.
 
@@
 \end{myquotation}
-We have added some discussion of our stopping criterion to appendix describing
-the AE method, and we have discussed this problem in our new conclusion section.
+We have added a paragraph to the ``accelerated evolution recipe'' appendix.
+In it, we discuss the fact that AE can be iteratively solved until you converge
+to a desired fractional percentage, and that we were only aiming for O(1\%) in this
+paper.  It is true that it will likely take a thermal relaxation time to evolve 
+from the 1\% off state to the true state, but that slow evolution does not
+appreciably change the dynamics.
 
@@
 \end{myquotation}
-We have added a new section V., ``Computational Benefits of AE'', to explicitly
-
-state speed increases of AE vs. SE. This section contains a small table which
-explicitly compares computational cost of select AE and SE runs in 2D and 3D.
+We have added a new section V., ``Computational Time-savings of AE.''
+We have combined the relevant information from the results section and the 
+conclusion section previously here, and we have added some information on a few
+additional runs in a new table.
 
@@
 \end{myquotation}
-We agree that our intial conclusion section was over-eager. We have removed
-our hopeful speculation and leave future work to
-prove if AE is useful in more complex situations (fully compressible,
-penetrative convection, etc.). The discussion section now includes a discussion
-of difficulties that the AE method faces, and future work.
+We agree that our intial conclusion section was over-eager. We have 
+greatly reduced the amount of text spent on speculation surrounding
+extensions of the AE method, and have added a paragraph warning the
+reader that not all extensions will be as simple (or guaranteed to work)
+as the case studied here.
 
+\newpage
 \noindent
@@
 (energy output / time). Basically it is a timescale that astronomers and
-astrophysicists use to estimate the timescale thermal evolution of a system 
+astrophysicists use to estimate the timescale of thermal evolution of a system 
 (e.g., a star). Since the point we were trying to make is that ``the mean 
@@
 multiple solution branches (e.g., a convective roll and a shearing solution),
-bootstrapping to different parameters will likely ensure that you stay on the 
-same solution branch, even at the higher parameters. Particularly, in our own
+bootstrapping a solution on one branch to different parameters with the same
+solution branches will result in a solution on the 
+same solution branch. Particularly, in our own
 work in stratified atmospheres, atmospheres trend toward shearing states, and then
@@
 
-We have corrected our error, and made our meaning clearer.
+We have corrected our error and made our meaning clearer.
 
@@
 \end{myquotation}
-The convective flows reach a statistically stationary state quickly, particularly
-in Boussinesq systems, but here we are discussing the thermal equilibration
-of systems which have some sort of thermal stratification. Even if the convective 
-flows reach a state that is relatively statistically stationary quickly, the
-temperature (and/or density) stratification of the convecting atmosphere can take
-much longer to equilibrate, especially in the high Pe regime.
+We have added a new Fig. 2 to address this question. In general, the convective
+flows and heat transport (e.g., Nu) reach their final, time-stationary mean
+value very quickly (see panels (a) and (b) of Fig. 2). However, the thermal 
+structure of the system can still be slowly evolving for long timescales
+despite the flows being relatively statistically stationary. The purpose of
+running for many, many free-fall times is to converge the thermal profile of
+the domain to ensure that the full system is in a steady state.
 
@@
 \end{myquotation}
+
 (a) In the simple case studied in this problem, where $F_B$ is constant in time
-and space, the functional form of $\xi \propto F_{tot}^{-1}$, and depnds only
+and space, the functional form of $\xi \propto F_{tot}^{-1}$, and depends only
 on the fluxes of the convective system. Since $F_{tot}$ can
@@
 around the mean profile will reduce the convective flux in the proper way.
-We scale $\langle \bm{u}\times\bm{\omega}\rangle$ by $\xi$, as it is
+We scale $\langle u\times \omega\rangle$ by $\xi$, as it is
 nondimensionally of order $u^2 / L$, and so if the velocities must be multiplied
@@
 \end{myquotation}
-Our boundary condition is that fluctuations in the temperature derivative at the
+Our boundary condition is that \emph{fluctuations} in the temperature derivative at the
 bottom of the domain are zero. Which is to say that 
@@
 \end{myquotation}
-Sure, we can do send the referee that plot. I don't think we should change the 
-figure as is, though.
+We have created this plot as part of a reponse to point 4. Please refer to the
+new Fig. 2 in the text.
+
 \begin{myquotation}
@@
 \end{myquotation}
-We have tightened up the discussion around the scaling laws, as requested by the
+The purpose of the previous Fig. 2 (now Fig. 3) was merely to show why we have
+such large error bars on Nu in our Nu v. Ra plot (Fig. 4). Our aim is to show
+the nature of the flow morphologies at times of high and low heat transport;
+the instantaneous sign of Nu (positive or negative) is not what we are trying
+to point out.
+
+We have clarified the discussion around the scaling laws, as requested by the
 other referee report. We have removed speculative statements which aimed to
@@
 the focus of our paper on AE rather than Nu scaling for our system setup.
-
-Fig. 2 is not aiming to point out the sign of Nu (positive vs. negative), but
-rather aiming to show the flow morphology at times of high heat transport and
-low heat transport.
 

### 2018-06-12 code/plotting/nu_comp.py

@@ -108,17 +108,17 @@ ax3.set_ylim(9e-1, 1e3)
 ax3.set_xticks([11200, 11400])
 ax3.set_xticklabels(("11200", "11400"))
 
-ax1.annotate("AE", xy=(950, 5e2))
-ax3.annotate("SE", xy=(11385, 5e2))
+ax1.annotate("AE", xy=(955, 5e2))
+ax3.annotate("SE", xy=(11360, 5e2))
 
 ax2.set_xlabel("Time (freefall units)")
-ax2.xaxis.set_label_coords(0.8, -0.125)
-ax2.set_ylabel("Nu")
-ax1.set_ylabel("Nu")
+ax2.xaxis.set_label_coords(0.76, -0.2)
+ax1.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
+ax2.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
 
-ax1.axvline(77 , c='k', ls='--')
-ax1.axvline(278, c='k', ls='--')
-ax1.axvline(360.6, c='k', ls='--')
+#ax1.axvline(77 , c='k', ls='--')
+#ax1.axvline(278, c='k', ls='--')
+#ax1.axvline(360.6, c='k', ls='--')
 
 
 ax1_2 = ax1.twinx()
@@ -134,14 +134,14 @@ ax1_2.set_yscale('log')
 ax2_2.set_yscale('log')
 ax3_2.set_yscale('log')
 
-ax3_2.set_ylabel(r'$\langle T \rangle - T_{top}$', color='b')
-ax1_2.set_ylabel(r'$\langle T \rangle - T_{top}$', color='b')
+ax3_2.set_ylabel(r'$\langle T \rangle - T_{top}$', color='b', rotation=270, labelpad=20)
+ax1_2.set_ylabel(r'$\langle T \rangle - T_{top}$', color='b', rotation=270, labelpad=20)
 for ax in [ax1_2, ax3_2]:
     ax.spines['right'].set_color('b')
     ax.tick_params(axis='y', colors='b')
 
 
-axs_share = [(ax1_2, time1[-1] + 100), (ax2_2, time2[-1]+10), (ax3_2, time2[-1]+20)]
+axs_share = [(ax1_2, time1[-1] + 100), (ax2_2, 11410), (ax3_2, 11410)]
 for ax, t in axs_share:
     ax.set_ylim(2e-2, 5e-1)
[…]

### 2018-06-12 code/plotting/oscillating_plumes.py

@@ -106,8 +106,8 @@ axes[1].annotate('IIb', xy=(330, -15), fontsize=10)
 axes[0].set_xlim(np.min(time[good]), np.max(time[good]))
 axes[1].set_xlim(np.min(time2[good2]), np.max(time2[good2]))
 axes[1].set_xlabel(r'$t/t_{\mathrm{ff}}$')
-axes[1].set_ylabel('Nu')
-axes[0].set_ylabel('Nu')
+axes[1].set_ylabel(r'$\langle$'+'Nu'+r'$\rangle$', labelpad=0)
+axes[0].set_ylabel(r'$\langle$'+'Nu'+r'$\rangle$')
 axes[0].set_yticks((6, 10, 14, 18, 22))
 axes[1].set_yticks((0, 40, 80, 120))
 axes[2].pcolormesh(xx, zz, temp1, cmap='RdBu_r', vmin=-0.5, vmax=-0.432)
@@ -174,4 +174,4 @@ axes[0].annotate(r'$S = 10^5$', xy=(425, 21), fontsize=10)
 axes[1].annotate(r'$S = 10^7$', xy=(215, 100), fontsize=10)
 
 
-plt.savefig('oscillating_plumes.png', bbox_inches='tight', dpi=300)
+plt.savefig('oscillating_plumes.png', bbox_inches='tight', dpi=400)

### 2018-06-12 code/plotting/parameter_space_comparison.py

@@ -37,10 +37,10 @@ MARKERSIZE=[5,4,5,7]
 
 fields = ['Nu', 'Re', 'IE']
 base_dirs = [
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/3d/base_post',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/3d/bvp_post'
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/base_post',
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/bvp_post',
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/3d/base_post',
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/3d/bvp_post'
             ]
 
 info = OrderedDict()
@@ -198,7 +198,7 @@ for i,k in enumerate(fields):
     elif k == 'Re':
         ax.annotate(r'$\mathrm{(b)}$', (2e3, 5e3), fontsize=10)
         label_end = '-{:.3g}'.format(pRe)
-        label_end = '$\\langle\\mathrm{Re}\\rangle$'#\\mathrm{ Ra}^{' + label_end + '}$'
+        label_end = '$\\langle\\mathrm{Pe}\\rangle$'#\\mathrm{ Ra}^{' + label_end + '}$'
         ax.set_ylabel(r'{}'.format(label_end))
         ax.set_ylim(1, 2e4)
 #        ax.set_title(r'$\langle\mathrm{Re}\rangle \mathrm{Ra}^{-1/2}$', fontsize=10)
@@ -297,4 +297,4 @@ for i,k in enumerate(fields):
     [t.set_fontsize(10) for t in ax.get_xticklabels()]
     [t.set_fontsize(10) for t in ax.get_yticklabels()]
 
-plt.savefig('parameter_space_comparison.png'.format(k), dpi=200, bbox_inches='tight')
+plt.savefig('parameter_space_comparison.png'.format(k), dpi=400, bbox_inches='tight')

### 2018-06-12 tex/bvp_paper.tex
so many changes
rough second draft of paper

@@
 This further stiffness arises as a result of the thermodynamic structure 
-evolving over the course of thermal timescales, not the short dynamical advective
+evolving over the course of thermal timescales which are much larger than
+the relevant dynamical advective
 timescales. In order to reach thermal equilibration, a steady state in which
@@
 \begin{equation}
-\xi(z) \equiv \frac{\text{F}_{\text{B}}}{\text{F}_{\text{tot}}},
+\xi(z,t) \equiv \frac{\text{F}_{\text{B}}}{\text{F}_{\text{tot}}},
 \label{eqn:xi}
@@
 where $\text{F}_{\text{B}} = \mathcal{P}$ is the amount of flux that enters the
-bottom of the atmosphere.
+bottom of the atmosphere. $\xi$ is a general depth-dependent scaling factor which
+tells us roughly how much larger F$_\text{E}$ is in the interior than it should
+be in the thermally equilibrated state.
 
@@
 by $\sqrt{\xi}$; this diminishes the magnitude of these perturbations, and the
-flux they carry, appropriately.
+flux they carry, appropriately. This scaling of variables with $\sqrt{\xi}$ is also
+the reason that we multiply $\angles{\bm{u}\times\bm{\omega}}_{x, y}$ by $\xi$
+before solving for the evolved temperature profile.
 After adjusing the fields of a simulation in this manner, we continue timestepping forward.
@@
 \label{sec:results}
+
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
+\caption{Here we compare the time evolution of the mean temperature and the
+Nusselt number in SE (a) and AE (b) for the simulations shown in 
+Fig.~\ref{fig:time_trace}. The mean value of Nu (black) is shown vs. time in both
+panels, and a centered boxcar moving average with a span of 50 freefall time
+units is overplotted as a thick, dashed line.  The mean value of the temperature
+(blue) is overplotted. We see that the mean value of Nu rapidly approaches its
+mean equilibrium value (plotted as a dashed horizontal black line), signifying
+that the convective motions roughly reach a statistically stationary state quickly
+compared to the temperature profile, which takes much longer to trend towards its
+equilibrium value. Regardless, we see that the fluctuations of Nu about the mean
+value are much smaller in the final equilibrated state than in the early state
+which is not in thermal equilibrium, and that the post-AE flows capture this
+proper Nu amplitude variation.
+The times at which AE solves occur are denoted by arrows in (b),
+and the grey boxed region is examined in more detail in Fig. \ref{fig:oscillating_plumes}.
+\label{fig:nu_v_time} }
+\end{figure}
+
 We study evolved standard evolution (SE) solutions whose supercriticalities ($S$) are 
@@
 in Fig.~\ref{fig:nu_v_time}. The mean value of Nu evolves towards its final value
-rapidly compared to the mean temperature. Thus, if Nu is the primary metric of 
-the evolved flows being measured, it is unnecessary to run for a full thermal
-time, and previous authors have taken advantage of this (CITE).
+rapidly compared to the mean temperature, as shown by the thick, dashed moving
+average.  As a result, if one is primarily measuring the mean value of Nu in
+a convective system, a full SE run through $t_\kappa$ or the AE procedure may not
+be necessary (e.g., \cite{stevens&all2010}). 
+Regardless, the variations around the mean value in Nu do change significantly
+over the course of thermal equilibration (Fig.~\ref{fig:nu_v_time}a). At early
+times, variations in Nu about the mean are much larger than they are at later times,
+and the use of AE seems to progress the fluctuations in Nu about the mean to
+a state which is consistent with the equilibrated SE fluctuations.
+
 When $S < 10^{3.67}$ in 2D and for all runs in 3D, 
@@
 in a state of constant convective heat transport.
-At larger $S$ in 2D, the value of Nu varies significantly over time,
+At larger $S$ in 2D, the value of Nu varies significantly over time even in the
+equilibrated state,
 as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
@@
 
-\begin{figure}[b]
-\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
-\caption{Here we compare the time evolution of the mean temperature and the
-Nusselt number for the 2D SE and AE run shown in Fig.~\ref{fig:time_trace}.
-\label{fig:nu_v_time} }
-\end{figure}
-
 \begin{figure}[t]
@@
 \end{figure}
-
-\begin{figure}[t!]
+\begin{figure}[t]
+\vspace{-1.5cm}
 \includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
@@
 We calculate the KS statistic for a PDF of some value, $q$, as
+\vspace{-0.5cm}
 \begin{equation}
@@
 %%%%%%%%%%%
-% SPEEDINESS OF AE vs SE
+% Computational time-savings
 %%%%%%%%%%%
@@
 \newpage$\,$\newpage
-\section{Computational Benefits of AE}
+\section{Computational Time-savings of AE}
 \label{sec:speedups}
@@
 \begin{table}
-\caption{
+\caption{We provide details regarding the computational cost of select
+AE and SE runs in 2D and 3D. For each run, we quote the supercriticality
+($S$), the coefficient resolution (nz, nx, ny), the number of CPUs used
+to perform the calculation ($N_{\text{CPU}}$), the number of CPU-hours
+used to perform the run ($t_{\text{CPU,AE/SE}}$), and the ratio of CPU-hours
+used in the AE run compared to the SE run.
 }
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X X X}
+\begin{tabularx}{\textwidth}{ X X X X X X }
 \hline																	
-$S$	&	nz, nx, ny	&	$t_{\text{sim,AE}}/t_{\text{sim,SE}}$	&	
-$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$ & $t_{\text{CPU,AE}}$ & $t_{\text{CPU, SE}}$		\\
+$S$	&	nz, nx$\times$ny	&	$N_{\text{CPU}}$	&	
+$t_{\text{CPU,AE}}$ & $t_{\text{CPU, SE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
@@
 \hline
-$10^2$	&	64,	128	&	0.905   & 2.03  & 4.369 &  2.152    \\
-$10^3$	&	128,256	&	0.24    & 0.387 & 20.63 &  53.25    \\
-$10^4$	&	256,512	&	0.084   & 0.15  & 180.82&  1205.25  \\
-$10^5$	&	512,1024&	0.036   & 0.115 & 2757.73& 24061.75 \\
+$10^2$	&	64,	128	&	32    & 4.369 &  2.152    & 2.03  \\
+$10^3$	&	128,256	&	64    & 20.63 &  53.25    & 0.387 \\
+$10^4$	&	256,512	&	128   & 180.82&  1205.25  & 0.15  \\
+$10^5$	&	512,1024&	256   & 2757.73& 24061.75 & 0.115 \\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
@@
 \hline
-$10^1$	&	32,	64$\times$64	& 2.29	& 1.73  &   106.15      &   61.5\\
-$10^2$	&	64,	128$\times$128	& 0.69	& 0.6   &   111.92      &   185.35\\
-$10^3$	&	128,256$\times$256	& 0.21	& 0.2   &   1426.39     &   6985.18\\
-$10^4$	&	256,512$\times$512	& 0.068	& 0.07  &   23063.77    &   331,717\\
+$10^1$	&	32,	64$\times$64	& 512    &   106.15      &   61.5    & 1.73\\
+$10^2$	&	64,	128$\times$128	& 512    &   111.92      &   185.35  & 0.6 \\
+$10^3$	&	128,256$\times$256	& 2048   &   1426.39     &   6985.18 & 0.2 \\
+$10^4$	&	256,512$\times$512	& 8192   &   23063.77    &   331,717 & 0.07\\
 \hline																	
@@
 is because of the computational timesaving of such an approach. In table 
-\ref{table:speed}, we compare simulation time and cpu-hour cost for select
+\ref{table:speed}, we compare cpu-hour cost for select
 2D and 3D runs in which AE and SE solutions were compared. Times reported
@@
 or fully compressible, stratified convection \cite{anders&brown2017}.
+As AE is fundamentally a horizontally uniform adjustment to the thermodynamic
+structure of the convective domain, it is unlikely that these techniques
+should be applied straightforwardly to nonperiodic convective domains.
 

### 2018-06-12 code/plotting/nu_comp.py

@@ -36,7 +36,7 @@ full_dir3 = base_dir + '/' + subdir3
 
 fig = plt.figure(figsize=(8, 4))
 gs     = gridspec.GridSpec(*(1000,1000))
-gs_info = (((30,0), 450, 1000), ((550, 0), 420, 660), ((550, 680), 420, 320) )
+gs_info = (((550,0), 420, 1000), ((30, 0), 420, 660), ((30, 680), 420, 320) )
 axs = []
 for i in range(len(gs_info)):
     axs.append(plt.subplot(gs.new_subplotspec(*gs_info[i])))
@@ -108,11 +108,11 @@ ax3.set_ylim(9e-1, 1e3)
 ax3.set_xticks([11200, 11400])
 ax3.set_xticklabels(("11200", "11400"))
 
-ax1.annotate("AE", xy=(955, 5e2))
-ax3.annotate("SE", xy=(11360, 5e2))
+ax3.annotate("(a) SE", xy=(11330, 5e2))
+ax1.annotate("(b) AE", xy=(925, 5e2))
 
-ax2.set_xlabel("Time (freefall units)")
-ax2.xaxis.set_label_coords(0.76, -0.2)
+ax1.set_xlabel("Time (freefall units)")
+#ax2.xaxis.set_label_coords(0.76, -0.2)
 ax1.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
 ax2.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
 
@@ -124,8 +124,13 @@ ax2.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
 ax1_2 = ax1.twinx()
 ax2_2 = ax2.twinx()
 ax3_2 = ax3.twinx()
-
-ax1_2.plot(time,  T+0.5,   c='b', lw=2)
+t1=76.8
+t2=278.3
+t3=360.6
+ax1_2.plot(time[time<t1],  T[time<t1]+0.5,   c='b', lw=2)
+ax1_2.plot(time[(time>=t1)*(time<t2)],  T[(time>=t1)*(time<t2)]+0.5,   c='b', lw=2)
+ax1_2.plot(time[(time>=t2)*(time<t3)],  T[(time>=t2)*(time<t3)]+0.5,   c='b', lw=2)
+ax1_2.plot(time[time>=t3],  T[time>=t3]+0.5,   c='b', lw=2)
[…]

### 2018-06-13 tex/bvp_paper.tex
readthrough of sections 1 and 2 complete

@@
 timescale. Specifically, the Peclet number (Pe), the ratio of the thermal
-diffusion timescale to the advective velocity timescale, is large.
-This further stiffness arises as a result of the thermodynamic structure 
-evolving over the course of thermal timescales which are much larger than
-the relevant dynamical advective
-timescales. In order to reach thermal equilibration, a steady state in which
-the thermal structure of the atmosphere is no longer evolving over time,
-many dynamical timescales must be simulated.
-Transport by convection is a highly nonlinear process,
-and this makes addressing the stiffness much more challenging; even fully
-implicit  methods remain bound by the nonlinear flow timescales
+diffusion timescale to the convective velocity timescale, is large.
+In a high Pe system, many convective dynamical timescales must pass before 
+the domain reaches thermal equilibrium, a steady state in which
+evolution of the thermal structure of the convective region has ceased.
+Fully implicit methods cannot be used to address the stiffness resulting from
+the discrepancy between convective and thermal timescales; convective flows are
+highly nonlinear, and implicit methods are bound by the nonlinear flow timescales
 \cite{viallet&all2011, viallet&all2013, viallet&all2016}.
+
 Resolving dynamics in atmospheres which are sufficiently
@@
 section \ref{sec:results}, we compare accelerated evolution solutions
-to solutions obtained from standard evolution through a full thermal diffusion timescale. Finally,
+to solutions obtained from standard evolution through a full thermal diffusion timescale. 
+In section \ref{sec:speedups}, we compare the numerical cost of accelerated
+solutions to solutions that are evolved through a thermal diffusion timescale.
+Finally,
 in section \ref{sec:extensions}, we offer concluding remarks and
@@
 \begin{equation}
-u = v = w = 0 \, \, \text{at}\,\,z = \pm 0,1,
+u = v = w = 0 \, \, \text{at}\,\,z = 0,1.
 \label{eqn:vel_bcs}
 \end{equation}
-and we use mixed thermal boundary conditions, such that
+The temperature is fixed at the top boundary, and the flux is fixed at the
+bottom boundary, such that
 \begin{equation}
@@
 the atmosphere three times, as denoted by the three labeled
-arrows in the graph numbered 1-3.  After the third profile adjustment, we find that
-the atmosphere is nearly in its converged state and we begin to sample the evolved
+arrows in the graph numbered 1-3.  The third profile adjustment associated with
+arrow 3 is small enough (see appendix \ref{appendix:recipe}) that we assume
+the atmosphere is sufficiently converged, and we begin to sample the evolved
 convective dynamics.
@@
 this final state both boundaries conduct the same amount of flux.
-The converged state achieved through AE is at most 5\% different from the SE solution, 
+The converged fluxes achieved through AE is at most 5\% different from the SE solution, 
 as shown in Fig.~\ref{fig:time_trace}e. 
@@
 
-In order to adjust the temperature profle to achieve AE, we calculate the total flux,
+In order to adjust the temperature profile to achieve AE, we calculate the total flux,
 F$_{\text{tot}} =$ F$_{\text{E}}$ + F$_{\kappa}$, and then derive the profiles
+\vspace{-0.5cm}
 \begin{equation}
@@
 the flux through the atmosphere must be decreased by some amount,
+\vspace{-0.5cm}
 \begin{equation}
@@
 where $\text{F}_{\text{B}} = \mathcal{P}$ is the amount of flux that enters the
-bottom of the atmosphere. $\xi$ is a general depth-dependent scaling factor which
+atmosphere at the bottom, fixed-flux boundary.
+$\xi$ is a general depth-dependent scaling factor which
 tells us roughly how much larger F$_\text{E}$ is in the interior than it should
-be in the thermally equilibrated state.
+be in the thermally equilibrated state (e.g., in Fig.~\ref{fig:time_trace}b,
+F$_{\text{tot}} \sim$ F$_{\text{E}} \sim 15\mathcal{P}$ just below the upper boundary layer, 
+but in the equilibrated state 
+it should just be $\mathcal{P}$, so $\xi \sim 1/15$ at that depth).
 
@@
 vanish due to symmetry, are
+\vspace{-0.5cm}
 \begin{gather}
@@
 construct $\xi(z)$ from measured flux profiles in the convective domain.
-We solve a 1D boundary value problem consisting of
+We solve a 1D boundary value problem (BVP) consisting of
 Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
 to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
+As the AE BVP solve only adjusts $\angles{T}$ and $\angles{\varpi}$, we must
+also appropriately adjust the temperature perturbations around the mean and the
+convective velocity flows, or else F$_{\text{E}}$ would be left unchanged, and
+would still be in a strongly disequilibrium state (e.g., Fig.~\ref{fig:time_trace}b).
 To consistently modify the convective enthalpy flux, we multiply both the velocity field,
@@
 the reason that we multiply $\angles{\bm{u}\times\bm{\omega}}_{x, y}$ by $\xi$
-before solving for the evolved temperature profile.
+to construct $\angles{\bm{u}\times\bm{\omega}}_{x, y\text{, ev}}$.
 After adjusing the fields of a simulation in this manner, we continue timestepping forward.

### 2018-06-13 tex/bvp_paper.tex
sections 3-4 improved.

@@
 
-\begin{figure}[t]
+\begin{figure}[b]
 \includegraphics[width=\textwidth]{./figs/nu_v_time.png}
-\caption{Here we compare the time evolution of the mean temperature and the
-Nusselt number in SE (a) and AE (b) for the simulations shown in 
-Fig.~\ref{fig:time_trace}. The mean value of Nu (black) is shown vs. time in both
-panels, and a centered boxcar moving average with a span of 50 freefall time
-units is overplotted as a thick, dashed line.  The mean value of the temperature
-(blue) is overplotted. We see that the mean value of Nu rapidly approaches its
-mean equilibrium value (plotted as a dashed horizontal black line), signifying
-that the convective motions roughly reach a statistically stationary state quickly
-compared to the temperature profile, which takes much longer to trend towards its
-equilibrium value. Regardless, we see that the fluctuations of Nu about the mean
-value are much smaller in the final equilibrated state than in the early state
-which is not in thermal equilibrium, and that the post-AE flows capture this
-proper Nu amplitude variation.
+\caption{The time evolution of Nu (black) and $\angles{T} - T_{\text{top}}$ (blue)
+are shown for simulations at $S = 10^5$ in SE (a) and AE (b).
+A moving average of Nu, using a centered boxcar with a span of 50 freefall time
+units, is overplotted as a thick, dashed line. 
+We see that the mean value of Nu reaches its equilibrium value quickly
+compared to $\angles{T}$.
+Regardless, fluctuations of Nu about the mean
+value are much smaller in the thermally equilibrated state.
 The times at which AE solves occur are denoted by arrows in (b),
@@
 The time evolution of Nu in AE and SE is compared to the mean temperature evolution
-in Fig.~\ref{fig:nu_v_time}. The mean value of Nu evolves towards its final value
-rapidly compared to the mean temperature, as shown by the thick, dashed moving
-average.  As a result, if one is primarily measuring the mean value of Nu in
-a convective system, a full SE run through $t_\kappa$ or the AE procedure may not
-be necessary (e.g., \cite{stevens&all2010}). 
-Regardless, the variations around the mean value in Nu do change significantly
-over the course of thermal equilibration (Fig.~\ref{fig:nu_v_time}a). At early
-times, variations in Nu about the mean are much larger than they are at later times,
-and the use of AE seems to progress the fluctuations in Nu about the mean to
-a state which is consistent with the equilibrated SE fluctuations.
+in Fig.~\ref{fig:nu_v_time}. In Fig.~\ref{fig:nu_v_time}a, we show the evolution
+of the SE run at $S = 10^5$. The black trace shows the instantaneous value of
+Nu, and the overplotted thick dashed line shows a moving time average of Nu. The
+time average is taken using a center boxcar window whose width is 50 $t_{\text{ff}}$.
+The mean value of Nu evolves towards its final value (shown in the horizontal
+dashed black line) rapidly compared to the mean system temperature (shown in
+blue), which approaches its evolved state (horizontal dashed blue line) slowly.
+As such, it is possible to measure the statistically stationary mean value of
+Nu after a few hundred freefall times, 
+as has been done previously \cite{stevens&all2010}. However, the fluctuations
+around the mean value are larger at early times when the system is not thermally
+equilibrated. In Fig.~\ref{fig:nu_v_time}b, we show the AE traces of Nu and mean
+temperature at $S = 10^5$. The times at which AE solves are completed are marked
+by arrows. Nu reaches its evolved mean value slightly more rapidly than in the SE case,
+but the early, large fluctuations away from the mean that we see in the SE
+case are not observed after the AE solves.
 
@@
 At larger $S$ in 2D, the value of Nu varies significantly over time even in the
-equilibrated state,
-as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
-AE runs in Fig.~\ref{fig:oscillating_plumes}. We find that these systems exhibit
+equilibrated state (as seen in Fig.~\ref{fig:nu_v_time}). We examine the shaded
+region of Fig.~\ref{fig:nu_v_time}b in more detail in the top left
+panel of Fig.~\ref{fig:oscillating_plumes}, as well as a comparable time trace
+at $S = 10^7$ (bottom, left). We find that these systems exhibit
 large Nu during
@@
 where warm fluid is pulled down by the downflow
-lane, and cool fluid is drawn up by the upflow lane). High-transport and 
-low-transport states exhibit smaller Nu fluctuations away from the 
-mean once the system reaches thermal equilibrium (Fig. \ref{fig:nu_v_time}).
+lane, and cool fluid is drawn up by the upflow lane).
 The plumes in these
@@
 equally effective in both 2D and 3D, and we restrict much of our study to 2D here
-in order to more thoroughly sample paramtere space.
+in order to more thoroughly sample parameter space.
 
@@
 our examination to a more direct comparison of AE and SE for 2D convection at
-$S = 10^5$, the time and flux evolution of which was shown in Fig.~\ref{fig:time_trace}.
+$S = 10^5$, the time, flux, and Nu evolution of which was shown in 
+Figs.~\ref{fig:time_trace}, \ref{fig:nu_v_time}, \& \ref{fig:oscillating_plumes}.
 All comparisons that follow for these two runs occur over the times shaded in
@@
 
-One means of comparing two
+One method of comparing two
 PDFs to determine if they are drawn from the same underlying
@@
 
-In addition to comparing the thermodynamic state achieved by the SE and AE methods,
+In addition to adjusting the 1D thermal profile, the AE method also scales the
+simulations velocities and temperature fluctuations by $\sqrt{\xi}$. 
+In Fig.~\ref{fig:pdf_comparison}
 we examine the velocities and heat transport found in the evolved states.
@@
 the Nu measurements of Fig.~\ref{fig:parameter_space_comparison}a\&d.
-this also confirms that the large $\KSstat{T}$ in Fig.~\ref{fig:temp_comparison}d is
+This also confirms that the large $\KSstat{T}$ in Fig.~\ref{fig:temp_comparison}d is
 not of concern, and that the AE run achieves the proper convective solution.
@@
 \begin{table}
-\caption{We provide details regarding the computational cost of select
-AE and SE runs in 2D and 3D. For each run, we quote the supercriticality
-($S$), the coefficient resolution (nz, nx, ny), the number of CPUs used
-to perform the calculation ($N_{\text{CPU}}$), the number of CPU-hours
-used to perform the run ($t_{\text{CPU,AE/SE}}$), and the ratio of CPU-hours
-used in the AE run compared to the SE run.
+\caption{Shown are details regarding the computational cost of select
+AE and SE runs in 2D and 3D. The supercriticality
+($S$), coefficient resolution (nz, nx, ny), number of CPUs used
+to perform the calculation ($N_{\text{CPU}}$), number of CPU-hours
+used to perform the run ($t_{\text{CPU,AE/SE}}$), and ratio of CPU-hours
+used in the AE run compared to the SE run are provided.
 }

### 2018-06-13 code/plotting/nu_comp.py

@@ -113,8 +113,10 @@ ax1.annotate("(b) AE", xy=(925, 5e2))
 
 ax1.set_xlabel("Time (freefall units)")
 #ax2.xaxis.set_label_coords(0.76, -0.2)
-ax1.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
-ax2.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
+#ax1.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
+#ax2.set_ylabel(r"$\langle$"+"Nu"+r"$\rangle$")
+ax1.set_ylabel("Nu")
+ax2.set_ylabel("Nu")
 
 #ax1.axvline(77 , c='k', ls='--')
 #ax1.axvline(278, c='k', ls='--')

### 2018-06-13 code/plotting/oscillating_plumes.py

@@ -106,8 +106,10 @@ axes[1].annotate('IIb', xy=(330, -15), fontsize=10)
 axes[0].set_xlim(np.min(time[good]), np.max(time[good]))
 axes[1].set_xlim(np.min(time2[good2]), np.max(time2[good2]))
 axes[1].set_xlabel(r'$t/t_{\mathrm{ff}}$')
-axes[1].set_ylabel(r'$\langle$'+'Nu'+r'$\rangle$', labelpad=0)
-axes[0].set_ylabel(r'$\langle$'+'Nu'+r'$\rangle$')
+#axes[1].set_ylabel(r'$\langle$'+'Nu'+r'$\rangle$', labelpad=0)
+#axes[0].set_ylabel(r'$\langle$'+'Nu'+r'$\rangle$')
+axes[1].set_ylabel('Nu', labelpad=0)
+axes[0].set_ylabel('Nu')
 axes[0].set_yticks((6, 10, 14, 18, 22))
 axes[1].set_yticks((0, 40, 80, 120))
 axes[2].pcolormesh(xx, zz, temp1, cmap='RdBu_r', vmin=-0.5, vmax=-0.432)

### 2018-06-14 referee_process/first_submission/referee_response.tex
some updates to paper draft

@@
 \begin{singlespace}
-We return a new draft of our manuscript, ``Accelerated evolution in
+We return our revised manuscript, ``Accelerated evolution in
 convective simulations,'' addressing the concerns of the referee reports.
@@
 \end{myquotation}
-We are confident that the BVP puts us closer to a nonlinear saturated state
-than we were before. It is true that there may be multiple stable states, and there
+All of the statistical tests that we have performed in this work point towards
+the evolved AE solution and SE solution being consistent.
+It is true that there may be multiple stable states, and there
 is no guarantee that the BVP puts the solution into the same stable state as
-SE. We have mentioned this in our conclusion.
+SE. We have included this caveat in our final discussion section.
 
@@
 \end{myquotation}
-We have replaced ``modes'' with ``maxima'' for clarity.
+We have replaced ``modes'' with ``maxima.''
 
@@
 In it, we discuss the fact that AE can be iteratively solved until you converge
-to a desired fractional percentage, and that we were only aiming for O(1\%) in this
-paper.  It is true that it will likely take a thermal relaxation time to evolve 
-from the 1\% off state to the true state, but that slow evolution does not
-appreciably change the dynamics.
+to a desired criterion, and that we were only aiming for O(1\%) in this
+paper. With a smaller convergence criterion, the user
+could get closer to the evolved SE solution, decreasing the separation
+between the temperature PDFs seen in what is now Fig. 5. 
+However, smaller convergence criteria
+come with significant computational cost (the horizontal averages must be
+better converged, and likely more iterative solves must be performed).
 
@@
 \end{myquotation}
+%contained too much speculation.
 We agree that our intial conclusion section was over-eager. We have 
@@
 $$
-t_{\text{KH}} = \frac{E_g}{L},
+t_{\text{KH}} = \frac{E}{L},
 $$
-where $E_g$ is the gravitational energy in a system, and $L$ is the luminosity
-(energy output / time). Basically it is a timescale that astronomers and
-astrophysicists use to estimate the timescale of thermal evolution of a system 
+where $E$ is the thermal energy in a system, and $L$ is the luminosity
+(energy output / time). It is an estimate of the timescale
+of thermal evolution of a system 
 (e.g., a star). Since the point we were trying to make is that ``the mean 
 thermodynamic structure of the Sun evolves \emph{really} slowly,''
-we have removed this jargon and said this more clearly in paragraph 2 of the intro.
+we have removed this jargon and said this more clearly in paragraph 3 of the intro.
 
@@
 bootstrapping a solution on one branch to different parameters with the same
-solution branches will result in a solution on the 
-same solution branch. Particularly, in our own
-work in stratified atmospheres, atmospheres trend toward shearing states, and then
-stay stuck in those states as we bootstrap to higher Ra.
+solution branches tends to result in a solution on the 
+same solution branch.
 
@@
 \end{myquotation}
-We have added a new Fig. 2 to address this question. In general, the convective
-flows and heat transport (e.g., Nu) reach their final, time-stationary mean
+We have added a new Fig. 2 to address this question. In general, we find that
+the heat transport reaches its final, time-stationary mean
 value very quickly (see panels (a) and (b) of Fig. 2). However, the thermal 
-structure of the system can still be slowly evolving for long timescales
+structure, kinetic energy, and fluctuations of heat transport away from the mean
+can still slowly evolve for long timescales
 despite the flows being relatively statistically stationary. The purpose of
@@
 
-We have clarified the discussion around the scaling laws, as requested by the
-other referee report. We have removed speculative statements which aimed to
-compare the scaling law of Nu found here with Nu elsewhere in order to keep
-the focus of our paper on AE rather than Nu scaling for our system setup.
+We have clarified the discussion in this portion of the paper.
 
@@
 We don't forsee major difficulties in AE being applied to fixed T boundary 
-conditions, but felt that such a study was outside the scope of this work.
+conditions, and have added a brief discussion in section III challenges that
+fixed flux or fixed temperature boundary conditions pose.
 

### 2018-06-14 tex/bvp_paper.tex
some updates to paper draft

@@
 }
+\setlength{\tabcolsep}{12pt}
 \label{table:speed}
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X X X }
+\begin{tabularx}{0.72\textwidth}{ c r r c c c }
 \hline																	
-$S$	&	nz, nx$\times$ny	&	$N_{\text{CPU}}$	&	
-$t_{\text{CPU,AE}}$ & $t_{\text{CPU, SE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
+$S$	&	nz$\times$nx$\times$ny	&	$N_{\text{CPU}}$	&	
+$t_{\text{CPU, SE}}$ & $t_{\text{CPU, AE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
@@
 \hline
-$10^2$	&	64,	128	&	32    & 4.369 &  2.152    & 2.03  \\
-$10^3$	&	128,256	&	64    & 20.63 &  53.25    & 0.387 \\
-$10^4$	&	256,512	&	128   & 180.82&  1205.25  & 0.15  \\
-$10^5$	&	512,1024&	256   & 2757.73& 24061.75 & 0.115 \\
+%2 sig figs, scientific notation, swap SE and AE, right justify Ncpu, 2 sig figs ratio, right justify communicates biggerness. 
+$10^2$	&	64$\times$128	&	32    &  2.2              & 4.4               &     2.0  \\
+$10^3$	&	128$\times$256	&	64    &  53               & 21                &     0.39 \\
+$10^4$	&	256$\times$512	&	128   &  1.2$\times 10^3$ & 1.8$\times 10^2$  &     0.15  \\
+$10^5$	&	512$\times$1024&	256   &  2.4$\times 10^4$ & 2.8$\times 10^3$  &     0.12 \\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
@@
 \hline
-$10^1$	&	32,	64$\times$64	& 512    &   106.15      &   61.5    & 1.73\\
-$10^2$	&	64,	128$\times$128	& 512    &   111.92      &   185.35  & 0.6 \\
-$10^3$	&	128,256$\times$256	& 2048   &   1426.39     &   6985.18 & 0.2 \\
-$10^4$	&	256,512$\times$512	& 8192   &   23063.77    &   331,717 & 0.07\\
+$10^1$	&	32$\times$64$\times$64	    & 512       &   62                 &        1.1$\times 10^2$   & 1.7\\
+$10^2$	&	64$\times$128$\times$128	& 512       &   1.9$\times 10^2$   &        1.1$\times 10^2$   & 0.60 \\
+$10^3$	&	128$\times$256$\times$256	& 2048      &   7.0$\times 10^3$   &        1.4$\times 10^3$   & 0.20 \\
+$10^4$	&	256$\times$512$\times$512	& 8192      &   3.3$\times 10^5$   &        2.3$\times 10^4$   & 0.070\\
 \hline																	
@@
 
-The primary reason to use AE, rather than evolving all solutions through SE,
-is because of the computational timesaving of such an approach. In table 
+Computational timesaving is the primary reason to use AE rather than 
+evolving all solutions through SE.
+In table 
 \ref{table:speed}, we compare cpu-hour cost for select
 2D and 3D runs in which AE and SE solutions were compared. Times reported
-for AE and SE runs do not include the time over which measurements were taken
-in the equilibrated state, but rather represent the time required to reach a
-fully equilibrated state under the AE or SE formalism. All simulations
+for AE and SE runs only include the time required to reach an equilibrated
+state, and do not include the time over which measurements were taken
+in the equilibrated state (e.g., the green shaded regions of
+Fig.~\ref{fig:time_trace}a\&c are not included in the $S = 10^5$ times).
+All simulations
 were performed on Broadwell nodes on NASA's Pleiades supercomputer 
@@
  The additional computational expense of 3D runs compared
-to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.
-
-While storing information about the mean state for the AE solve marginally
-decreases the rate at which our solver timesteps, the first application of AE in a given
-simulation (Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
-increases the average timestep by immediately progressing the simulation into
-a more converged state. For the $S = 10^5$ case we examined in detail, the
-average time step grew by a factor of 2-3 due to the decreased convective
-velocities from the transient state to the evolved state. 
+to 2D runs implies that 3D studies can greatly benefit from AE.
+
+Storing information about the mean state for the AE solve marginally
+decreases the rate at which our solver timesteps. However, 
+the first application of AE in a given simulation 
+(e.g., Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
+increases the average timestep by fastforwarding the simulation into
+a more stable state with lower convective velocities. 
+For the $S = 10^5$ case we examined in detail, the
+average time step grew by a factor of 2-3.
 At $S = 10^7$, the AE solve immediately improved the timestep size 
@@
 Here we studied the simplest possible case for the application of AE:
-\RB convection at low aspect ratio with mixed thermal boundary. 
+\RB convection at low aspect ratio with mixed thermal boundary conditions. 
 We anticipate that
@@
 this may not be the case for more complicated systems. For example, at
-higher aspect ratios, multiple stable solution branches of various numbers of
-convective rolls may exist, and there is no guarantee that AE and SE will
+higher aspect ratios, multiple stable solution branches 
+may exist, and there is no guarantee that AE and SE will
 arrive at the same solution. 
@@
 long been used in those studies \cite{hurlburt&all1986}.
-Our work here should serve as a basis for determining if AE techniques are
-valid and effective in more complex studies of convection.
+Our work here serves as a basis for determining if AE techniques are
+effective in more complex studies of convection.
 
@@
 Simulation run times required to reach convergence
-are reported for the SE solutions ($t_{\text{therm}}$) and the AE solutions ($t_{\text{AE}}$).
+are reported for the SE solutions ($t_{\text{SE}}$) and the AE solutions ($t_{\text{AE}}$).
 The amount of time over which simulations measurements were taken in the evolved
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{ X X X X | X X X | X X }
+\begin{tabularx}{\textwidth}{ X X r | X X X | X X }
 \hline																	
-$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{AE}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
-\hline \hline \multicolumn{9}{c}{\vspace{-0.2cm}}\\
-\multicolumn{9}{c}{\vspace{0.1cm}2D Runs} \\
+$S$	&	Ra	&	nz$\times$nx$\times$ny$\,\,\,\,\,\,\,$	&	$t_{\text{SE}}$	&	$t_{\text{AE}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
+\hline \hline \multicolumn{8}{c}{\vspace{-0.2cm}}\\
+\multicolumn{8}{c}{\vspace{0.1cm}2D Runs} \\
 \hline
-$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	$340$	&	100	&	1.46	&	1.46	\\
-$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	$282$	&	100	&	1.95	&	1.95	\\
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	$265$	&	100	&	2.43	&	2.42	\\
-$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	$251$	&	100	&	2.54	&	2.54	\\
-$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	$245$	&	100	&	3.14	&	3.14	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
-$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	$528$	&	$248$	&	100	&	4.71	&	4.71	\\
-$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	$776$	&	$251$	&	100	&	5.5	&	5.5	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	$1.14 \cdot 10^3$	&	$268$	&	200	&	6.4	&	6.33	\\
-$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	$1.67 \cdot 10^3$	&	$247$	&	500	&	6.87	&	6.95	\\
-$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	$2.45 \cdot 10^3$	&	$275$	&	500	&	7.54	&	7.59	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	$3.60 \cdot 10^3$	&	$301$	&	500	&	8.83	&	8.83	\\
-$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	$5.28 \cdot 10^3$	&	$317$	&	500	&	10.13	&	10.14	\\
-$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	$7.76 \cdot 10^3$	&	$326$	&	500	&	11.65	&	11.69	\\
-$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	$411$	&	500	&	14.02	&	14.18	\\
-$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	$391$	&	500	&	---	&	16.21	\\
-$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	$453$	&	500	&	---	&	18.58	\\
-$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
-$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	38.29	\\
-\\ \hline \hline \multicolumn{9}{c}{\vspace{-0.2cm}}\\
-\multicolumn{9}{c}{\vspace{0.1cm}3D Runs} \\
+$10^{1/3}$	    &	$2.79 \cdot 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$52.8$	&	$340$	&	100	&	1.46	&	1.46	\\
+$10^{2/3}$	    &	$6.01 \cdot 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$77.6$	&	$282$	&	100	&	1.95	&	1.95	\\
+$10^1$	        &	$1.30 \cdot 10^4$       &  	32$\times$64$\,\,\,\,\,\,\,$&	$114$	&	$265$	&	100	&	2.43	&	2.42	\\
+$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$167$	&	$251$	&	100	&	2.54	&	2.54	\\
+$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$245$	&	$245$	&	100	&	3.14	&	3.14	\\
+$10^2$	        &	$1.30 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
+$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$528$	&	$248$	&	100	&	4.71	&	4.71	\\
+$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$776$	&	$251$	&	100	&	5.5	&	5.5	\\
+$10^3$	        &	$1.30 \cdot 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.14 \cdot 10^3$	&	$268$	&	200	&	6.4	&	6.33	\\
+$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.67 \cdot 10^3$	&	$247$	&	500	&	6.87	&	6.95	\\
+$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$       &	256$\times$512$\,\,\,\,\,\,\,$&	$2.45 \cdot 10^3$	&	$275$	&	500	&	7.54	&	7.59	\\
+$10^4$	        &	$1.30 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$3.60 \cdot 10^3$	&	$301$	&	500	&	8.83	&	8.83	\\
+$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$5.28 \cdot 10^3$	&	$317$	&	500	&	10.13	&	10.14	\\
+$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$7.76 \cdot 10^3$	&	$326$	&	500	&	11.65	&	11.69	\\
+$10^5$	        &	$1.30 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.14 \cdot 10^4$	&	$411$	&	500	&	14.02	&	14.18	\\
+$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.67 \cdot 10^4$	&	$391$	&	500	&	---	&	16.21	\\
+$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$2.45 \cdot 10^4$	&	$453$	&	500	&	---	&	18.58	\\
+$10^6$	        &	$1.30 \cdot 10^9$       &	1024$\times$2048$\,\,\,\,\,\,\,$	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
+$10^7$	        &	$1.30 \cdot 10^{10}$	&	2048$\times$4096$\,\,\,\,\,\,\,$	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	38.29	\\
+\\ \hline \hline \multicolumn{8}{c}{\vspace{-0.2cm}}\\
+\multicolumn{8}{c}{\vspace{0.1cm}3D Runs} \\
 \hline
-$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	$261$	&	100	&	2.42	&	2.42	\\
-$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128$\times$128	&	$360$	&	$249$	&	100	&	3.97	&	4	\\
-$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256$\times$256	&	$1.14 \cdot 10^3$	&	$243$	&	500	&	6.27	&	6.27	\\
-$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512$\times$512	&	$3.60 \cdot 10^3$	&	$244$	&	500	&	9.92	&	9.88	\\
+$10^1$          &	$1.30 \cdot 10^4$	&	32$\times$64$\times$64$\,\,\,\,\,\,\,$   &	$114$	&	$261$	&	100	&	2.42	&	2.42	\\
+$10^2$          &	$1.30 \cdot 10^5$	&	64$\times$128$\times$128$\,\,\,\,\,\,\,$   &	$360$	&	$249$	&	100	&	3.97	&	4	\\
+$10^3$          &	$1.30 \cdot 10^6$	&	128$\times$256$\times$256$\,\,\,\,\,\,\,$	&	$1.14 \cdot 10^3$	&	$243$	&	500	&	6.27	&	6.27	\\
+$10^4$          &	$1.30 \cdot 10^7$	&	256$\times$512$\times$512$\,\,\,\,\,\,\,$	&	$3.60 \cdot 10^3$	&	$244$	&	500	&	9.92	&	9.88	\\
 \hline																	
@@
 
-In general, the user of the AE method should choose some threshold
-fractional change of the mean temperature profile, $f$, such that once
-an AE solution differs from the DNS mean profile by less than $f$, the simulation
-is considered converged and the iterative AE adjustments may be stopped. In
-other words, once
+In general, to use AE, a threshold, $f$, should be chosen. When the fractional
+change of the mean temperature profile from an AE BVP solve becomes less than $f$,
+the solution can be considered converged on its chosen solution branch.
+In other words, once
 \begin{equation}
@@
 the solution is converged. In this work, we chose our number of AE iterations
-such that $f \approx 10^{-2}$, except at $S = 10^7$, where we stopped after one AE
-iteration due to higher computational expense. In general, the user of AE could
+such that $f \approx 10^{-2}$.  In general, the user of AE could
 set $f$ smaller, and in doing so reduce the separation between the AE and SE
-solutions, which can be seen in e.g., Fig.~\ref{fig:temp_comparison}.
+solutions, which can be seen in e.g., Fig.~\ref{fig:temp_comparison}a\&b. However,
+smaller values of $f$ require additional AE BVP solves, and likely require smaller values
+of $P$, resulting in longer wait times while the horizontal averages are computed.
 

### 2018-06-14 code/plotting/nu_comp.py

@@ -45,6 +45,12 @@ ax1 = axs[0]
 ax2 = axs[1]
 ax3 = axs[2]
 
+ax1_2 = ax1.twinx()
+ax2_2 = ax2.twinx()
+ax3_2 = ax3.twinx()
+
+
+
 
 scalars = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir), 'r')
 scalars2 = h5py.File('{:s}/scalar_plots/scalar_values.h5'.format(full_dir2), 'r')
@@ -68,27 +74,36 @@ T3  = scalars3['IE'].value
 T_final = np.mean(T2[-1000:])
 Nu_final = np.mean(nu2[-1000:])
 
+
+#Add horizontal final values
+ax1_2.axhline(T_final + 0.5,  c='blue')
+ax2_2.axhline(T_final + 0.5,  c='blue')
+ax1.axhline(Nu_final, c='dimgrey')
+ax2.axhline(Nu_final, c='dimgrey')
+
+
+
 time1 = np.concatenate((time, time3))
 nu1 = np.concatenate((nu, nu3))
-run_df = pd.DataFrame({'t':    time1[np.argmax(nu1)+50:],
-                        'nu':   nu1[np.argmax(nu1)+50:]})
+run_df = pd.DataFrame({'t':    time1[np.argmax(nu1)+5:],
+                        'nu':   nu1[np.argmax(nu1)+5:]})
 print(run_df)
-avg_nu1 = run_df.rolling(window=500, min_periods=50).mean()
+avg_nu1 = run_df.rolling(window=500, min_periods=50, axis=0, center=True).mean()
 avg_nu1 = np.array(avg_nu1)[:,1]
-ax1.plot(time1[nu1 > 0], nu1[nu1 > 0],   c='k')
-ax1.plot(run_df['t'], avg_nu1,   c='k', ls='--', lw=3, dashes=(5,1))
+ax1.plot(time1[nu1 > 0], nu1[nu1 > 0],   c='k', lw=2)
+ax1.plot(run_df['t'], avg_nu1,   c='dimgrey', lw=2)#, dashes=(5,1))
 #ax1.plot(time3, nu3, c='k')
 
-run2_df = pd.DataFrame({'t':    time2[np.argmax(nu2)+5:],
-                        'nu':   nu2[np.argmax(nu2)+5:]})
[…]

### 2018-06-14 referee_process/first_submission/referee_response.tex
referee response letter looking pretty good

@@
 of speculation regarding extensions of AE from this section and have added
-a paragraph containing some caveats regarding challenges that users will face in
-extending AE to more difficult systems.  In addition to these changes in the text,
-we have added a new Fig. 2 which compares the evolution of Nu and the
-mean temperature in AE and SE, and we have added some accompanying text for this
-figure to the results section.  Small changes in the text throughout the paper have
-been made for clarity where these changes were requested by the reports.
+a brief paragraph containing some caveats regarding challenges that users will face in
+extending AE to more complex systems.  In addition to these changes in the text,
+we have added a new Fig. 2 which compares the evolution of Nu vs time to the
+evolution of the
+mean temperature vs. time in AE and SE, 
+and we have added some accompanying text to the results section for this
+figure.  Small changes in the text throughout the paper have
+been made where these changes were requested by the reports.
 
@@
 improved by the referee reports, and we thank the referees for their honest 
-critiques and attention to detail. We hope that the changes made have clarified
-and cleaned up the areas of concern raised in both referee reports.  Below we
-include our responses to the reports. The original text of the reports is included
+critiques and attention to detail. We hope that the changes made have
+cleaned up the areas of concern raised in both referee reports.  Below we
+include our responses to the reports; the original text of the reports is included
 in italics, and our responses follow inline in unitalicized blocks.
@@
 
-Evan H. Anders, Benjamin P. Brown, \& Jeffrey S. Oishi
+Evan H. Anders, Benjamin P. Brown, and Jeffrey S. Oishi
 
@@
 All of the statistical tests that we have performed in this work point towards
-the evolved AE solution and SE solution being consistent.
-It is true that there may be multiple stable states, and there
-is no guarantee that the BVP puts the solution into the same stable state as
-SE. We have included this caveat in our final discussion section.
+the evolved AE solution and SE solution being consistent for the simple problem
+studied here.
+It is true that convective systems may have multiple stable states, and there
+is no guarantee that the AE BVP puts the solution into the same stable state as an
+SE evolution. We have included this caveat in the final paragraph of the paper's
+Discussions \& Conclusions section.
 
@@
 \end{myquotation}
-We have clarified this in the second to last pargraph of section III 
-(and added a forward reference to this part of the text).
+We have clarified this in the second to last pargraph of section III,
+and added a forward reference to section III by this quoted sentence.
 
@@
 initial temperature profiles ($\text{F}_{\text{B}}$ will need to pick up some
-height dependence in the defintion of $\chi$, for simple internally heated
+height dependence in the defintion of $\xi$ for simple internally heated
 systems, for example). It would be useful to test AE in such a case, but such
@@
 space, in order to demonstrate its robustness for the problem presented here.
-We have trimmed the text of the scaling laws section and reduced speculation in
+We have trimmed the text of the scaling laws section in
 order to keep the paper on topic. We have also replaced Re with Pe in this
@@
 could get closer to the evolved SE solution, decreasing the separation
-between the temperature PDFs seen in what is now Fig. 5. 
+between the temperature PDFs seen in Fig. 5 (previously Fig. 4). 
 However, smaller convergence criteria
@@
 \end{myquotation}
-%contained too much speculation.
-We agree that our intial conclusion section was over-eager. We have 
+We agree that our intial conclusion section contained too much speculation.
+We have 
 greatly reduced the amount of text spent on speculation surrounding
@@
 structure, kinetic energy, and fluctuations of heat transport away from the mean
-can still slowly evolve for long timescales
+can still slowly evolve over long timescales
 despite the flows being relatively statistically stationary. The purpose of
@@
 We assume that $F_{tot} \sim F_{conv} \sim w (T - \langle T \rangle )$.
-As such, we assume that $\xi \propto (w^{-1/2}, (T - \langle T \rangle )^{-1/2})$,
-and that scaling both the temperature fields and the temperature fluctuations 
-around the mean profile will reduce the convective flux in the proper way.
+As such, if we must scale $F_{tot}$ by a factor of $\xi$, we are equivalently
+scaling
+$\bm{u}$ and $T - \langle T\rangle$ by $\sqrt{\xi}$ to reduce the convective flux.
 We scale $\langle u\times \omega\rangle$ by $\xi$, as it is
 nondimensionally of order $u^2 / L$, and so if the velocities must be multiplied
-by $\sqrt{\xi}$, this term must be multiplied by $\xi$.
+by $\sqrt{\xi}$, this term must be multiplied by $\xi$. We have added a short
+paragraph before Eqns (12) and (13), as well as some text shortly after those
+equations, containing this information.
 
@@
 We don't forsee major difficulties in AE being applied to fixed T boundary 
-conditions, and have added a brief discussion in section III challenges that
+conditions, and have added a brief discussion shortly after Eqns (12) and (13)
+in section III of challenges that
 fixed flux or fixed temperature boundary conditions pose.

### 2018-06-14 tex/bvp_paper.tex
referee response letter looking pretty good

@@
 
-In a time-stationary state, the horizontal- and time-average of
-Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
-vanish due to symmetry, are
-\vspace{-0.5cm}
+In order to properly reduce F$_\text{E}$, we note that, upon removing 
+terms which vanish due to symmetry, the convective enthalpy flux is carried
+solely by the velocity field coupling to perturbations in temperature around
+the mean temperature profile, or F$_\text{E} \propto \{w, T-\angles{T}_{x,y}\}$.
+As the evolved enthalpy flux should be roughly $\xi$F$_\text{E}$, we reduce 
+the velocity, $\bm{u}$,
+and temperature perturbations about the mean state, $T-\angles{T}_{x,y}$,
+ by $\sqrt{\xi}$.
+
+To properly reduce the conductive flux, we examine the 
+time-stationary state, horizontally- and time-averaged
+Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}); after 
+neglecting terms which vanish due to symmetry, these equations become
+\vspace{-0.2cm}
 \begin{gather}
@@
 \end{gather}
-Here, we construct $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
-\xi(z) \angles{\bm{u}\times\bm{\omega}}_{x, y}$ and $\text{F}_{\text{E, ev}} = \xi(z) \text{F}_{\text{E}}$
-from our unevolved state, and solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
+Here, we construct  $\text{F}_{\text{E, ev}} = \xi \text{F}_{\text{E}}$ 
+and $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
+\xi \angles{\bm{u}\times\bm{\omega}}_{x, y}$, where we scale 
+$\angles{\bm{u}\times\bm{\omega}}_{x, y} \propto \bm{u}^2$, by $\xi$ because we
+scaled $\bm{u}$ by $\sqrt{\xi}$ in order to reduce the convective enthalpy flux.
+With these profiles, we solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
 Convective flows
 are perturbations around a thermal profile defined by these equations in the proper evolved, 
-statistically stationary state. Furthermore, under the proper specification of
+statistically stationary state, so the proper specification of
 F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
-\emph{the mean thermodynamic structure of the system is fully specified}. 
+fully specifies the mean thermodynamic structure of the system. 
 Our choice of fixing the temperature at the top boundary and the flux at the bottom
-boundary ensures that there is a unique solution for $T_1$ given the evolved
+boundary ensures that there is a unique solution for $\angles{T_1}$ given the evolved
 fluxes. If flux were fixed at both boundaries, there would be infinitely many
@@
 also appropriately adjust the temperature perturbations around the mean and the
-convective velocity flows, or else F$_{\text{E}}$ would be left unchanged, and
-would still be in a strongly disequilibrium state (e.g., Fig.~\ref{fig:time_trace}b).
-To consistently modify the convective enthalpy flux, we multiply both the velocity field,
-$\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
-by $\sqrt{\xi}$; this diminishes the magnitude of these perturbations, and the
-flux they carry, appropriately. This scaling of variables with $\sqrt{\xi}$ is also
-the reason that we multiply $\angles{\bm{u}\times\bm{\omega}}_{x, y}$ by $\xi$
-to construct $\angles{\bm{u}\times\bm{\omega}}_{x, y\text{, ev}}$.
+convective velocity flows.
 After adjusing the fields of a simulation in this manner, we continue timestepping forward.
@@
 may exist, and there is no guarantee that AE and SE will
-arrive at the same solution. 
+arrive at the same solution. Studies whose horizontal boundaries are not periodic may need
+a much more careful treatment of the adjustment of the mean temperature profile,
+especially near the side walls.
 Some assumptions which inform the AE solution, such as the assumption

### 2018-06-14 code/plotting/nu_comp.py

@@ -76,10 +76,10 @@ Nu_final = np.mean(nu2[-1000:])
 
 
 #Add horizontal final values
-ax1_2.axhline(T_final + 0.5,  c='blue')
-ax2_2.axhline(T_final + 0.5,  c='blue')
-ax1.axhline(Nu_final, c='dimgrey')
-ax2.axhline(Nu_final, c='dimgrey')
+ax1_2.axhline(T_final + 0.5,  c='blue', dashes=(2,2))
+ax2_2.axhline(T_final + 0.5,  c='blue', dashes=(2,2))
+ax1.axhline(Nu_final, c='dimgrey', dashes=(5,1))
+ax2.axhline(Nu_final, c='dimgrey', dashes=(5,1))
 
 
 

### 2018-06-14 tex/bvp_paper.tex
almost ready for resubmission

@@
 diffusion timescale to the convective velocity timescale, is large.
-In a high Pe system, many convective dynamical timescales must pass before 
+In a high Pe system, many convective timescales must pass before 
 the domain reaches thermal equilibrium, a steady state in which
 evolution of the thermal structure of the convective region has ceased.
-Fully implicit methods cannot be used to address the stiffness resulting from
-the discrepancy between convective and thermal timescales; convective flows are
-highly nonlinear, and implicit methods are bound by the nonlinear flow timescales
+As the timestep size of implicit methods is bound to the fastest nonlinear flows,
+(convection) fully implicit methods cannot be used to address this form of stiffness
 \cite{viallet&all2011, viallet&all2013, viallet&all2016}.
@@
 Resolving dynamics in atmospheres which are sufficiently
-thermally equilibrated remains a challenging problem.
+thermally equilibrated therefore remains a challenging problem.
 Solar convection is a prime example of this phenomenon, as
@@
 through a single convective overturn time becomes more computationally expensive
-and the number of overturn times required for systems to reach thermal equilibration
+and the number of overturn times required for systems to reach thermal equilibrium
 grows.
@@
 In section \ref{sec:speedups}, we compare the numerical cost of accelerated
-solutions to solutions that are evolved through a thermal diffusion timescale.
+solutions to standard solutions.
 Finally,
@@
 $T = T_0(z) + T_1(x, y, z, t)$ are the initial and fluctuating components of temperature, 
-and $P$ is the kinematic pressure. The initial temperature profile decreases
+and $P$ is the kinematic pressure. The initial temperature profile, $T_0$, decreases
 linearly with height.
@@
 using an implicit-explicit (IMEX), third-order, four-stage 
-Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.
+Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}. The code used to run the simulations
+in this work is included in the supplemental materials as a zip file.
 
@@
 this final state both boundaries conduct the same amount of flux.
-The converged fluxes achieved through AE is at most 5\% different from the SE solution, 
+The converged fluxes achieved through AE are at most 5\% different from the SE solution, 
 as shown in Fig.~\ref{fig:time_trace}e. 
@@
 Convective flows
-are perturbations around a thermal profile defined by these equations in the proper evolved, 
-statistically stationary state, so the proper specification of
-F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
+are perturbations around a thermal profile defined by these equations in the evolved, 
+statistically stationary state. Thus, the specification of
+F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$
 fully specifies the mean thermodynamic structure of the system. 
@@
 Thus, the AE method occurs in the following steps. First, we pause a convective simulation and
-construct $\xi(z)$ from measured flux profiles in the convective domain.
+construct $\xi(z,t)$ from measured flux profiles in the convective domain.
 We solve a 1D boundary value problem (BVP) consisting of
@@
 to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
-As the AE BVP solve only adjusts $\angles{T}$ and $\angles{\varpi}$, we must
-also appropriately adjust the temperature perturbations around the mean and the
-convective velocity flows.
+We multiply both the temperature perturbations around the mean and the
+convective velocity flows by $\sqrt{\xi}$.
 After adjusing the fields of a simulation in this manner, we continue timestepping forward.
@@
 A moving average of Nu, using a centered boxcar with a span of 50 freefall time
-units, is overplotted as a thick, dashed line. 
+units, is overplotted as a grey line. 
 We see that the mean value of Nu reaches its equilibrium value quickly
@@
 of the SE run at $S = 10^5$. The black trace shows the instantaneous value of
-Nu, and the overplotted thick dashed line shows a moving time average of Nu. The
-time average is taken using a center boxcar window whose width is 50 $t_{\text{ff}}$.
-The mean value of Nu evolves towards its final value (shown in the horizontal
-dashed black line) rapidly compared to the mean system temperature (shown in
-blue), which approaches its evolved state (horizontal dashed blue line) slowly.
+Nu, and the overplotted grey line shows a moving time average of Nu. The
+time average is taken using a centered boxcar window whose width is 50 $t_{\text{ff}}$.
+The mean value of Nu evolves towards its final value (dashed horizontal
+grey line) rapidly compared to $\angles{T}-T_{\text{top}}$ (blue), 
+which approaches its evolved state (dashed horizontal blue line) slowly.
 As such, it is possible to measure the statistically stationary mean value of
-Nu after a few hundred freefall times, 
-as has been done previously \cite{stevens&all2010}. However, the fluctuations
-around the mean value are larger at early times when the system is not thermally
-equilibrated. In Fig.~\ref{fig:nu_v_time}b, we show the AE traces of Nu and mean
-temperature at $S = 10^5$. The times at which AE solves are completed are marked
+Nu after only a few hundred simulated freefall times, 
+as has been done previously \cite{stevens&all2010}. However, fluctuations in
+Nu around the mean value at early times have both a larger magnitude and higher
+frequency than the fluctuations in the equilibrated state.
+In Fig.~\ref{fig:nu_v_time}b, we show the AE traces of Nu and
+$\angles{T}-T_{\text{top}}$ at $S = 10^5$. The times at which AE solves occur are marked
 by arrows. Nu reaches its evolved mean value slightly more rapidly than in the SE case,
-but the early, large fluctuations away from the mean that we see in the SE
-case are not observed after the AE solves.
+and the frequency and magnitude of fluctuations in Nu away from the mean resemble the
+final equilibrated state of SE.
 
@@
 panel of Fig.~\ref{fig:oscillating_plumes}, as well as a comparable time trace
-at $S = 10^7$ (bottom, left). We find that these systems exhibit
+at $S = 10^7$ (bottom, left panel). We find that these systems exhibit
 large Nu during
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \includegraphics[width=\textwidth]{./figs/temp_comparison.png}
@@
 We calculate the KS statistic for a PDF of some value, $q$, as
-\vspace{-0.5cm}
 \begin{equation}
@@
 drivers of convective transport, are nearly identical.
+
+\begin{figure}[b!]
+\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
+\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
+convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
+at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
+(d-f) The KS profiles, as defined in Eqn.~(\ref{eqn:ks_profile}),
+are shown for the related distributions; solid lines indicate positive values
+while dashed lines are negative values. Unlike the temperature distributions in
+Fig.~\ref{fig:temp_comparison}, these distributions
+show very good agreement and small values of the KS statistic.
+\label{fig:pdf_comparison} }
+\end{figure}
+
+\newpage$\,$\newpage
 
@@
 
-\begin{figure}[b!]
-\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
-convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
-at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
-(d-f) The KS profiles, as defined in Eqn.~(\ref{eqn:ks_profile}),
-are shown for the related distributions; solid lines indicate positive values
-while dashed lines are negative values. Unlike the temperature distributions in
-Fig.~\ref{fig:temp_comparison}, these distributions
-show very good agreement and small values of the KS statistic.
-\label{fig:pdf_comparison} }
-\end{figure}
-
 %%%%%%%%%%%%
@@
 %%%%%%%%%%%%
-\newpage$\,$\newpage
 \section{Computational Time-savings of AE}
@@
 
-\begin{table}
+\begin{table}[b!]
 \caption{Shown are details regarding the computational cost of select
@@
 
-Computational timesaving is the primary reason to use AE rather than 
+Computational time-saving is the primary reason to use AE rather than 
 evolving all solutions through SE.
@@
 (Intel Xeon E5-2680v4 processors). The key metric which highlights the usefulness
-of AE is the number of cpu-hours used for the AE run in units of cpu-hours used
+of AE is the number of cpu-hours used for the AE run divided by cpu-hours used
 for the SE run ($t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$). We see that at low
@@
 than SE runs.
- The additional computational expense of 3D runs compared
-to 2D runs implies that 3D studies can greatly benefit from AE.
-
-Storing information about the mean state for the AE solve marginally
-decreases the rate at which our solver timesteps. However, 
+
+Integrating information about the mean state in time (fluxes, etc.)
+decreases the rate at which our solver timesteps early in the AE cases. 
+However, 
 the first application of AE in a given simulation 
@@
 
+\newpage
 \section{Discussion \& Conclusions}
@@
 We conclude by noting that AE should be extended to these more complicated
-studies with care. 
+studies with caution. 
 While AE was extremely effective in this simple case studied here
@@
 may exist, and there is no guarantee that AE and SE will
-arrive at the same solution. Studies whose horizontal boundaries are not periodic may need
-a much more careful treatment of the adjustment of the mean temperature profile,
-especially near the side walls.
+arrive at the same solution. 
 Some assumptions which inform the AE solution, such as the assumption

### 2018-06-14 code/boussinesq_dynamics/equations.py
removes unnecessary code comments

@@ -378,7 +378,7 @@ class BoussinesqEquations(Equations):
             self.problem.add_bc("right(p) = 0", condition="(nx == 0) and (ny == 0)")
             self.problem.add_bc("right(w) = 0", condition="(nx != 0) or  (ny != 0)")
         else:
-            self.problem.add_bc("right(p) = 0")
+            self.problem.add_bc("right(w) = 0")
         self.dirichlet_set.append('w')
         
     def set_IC(self, solver, A0=1e-6, **kwargs):
@@ -595,7 +595,6 @@ class BoussinesqEquations3D(BoussinesqEquations):
             w_z  - z-derivative of w
         """
         super(BoussinesqEquations3D, self).__init__(*args, dimensions=dimensions, **kwargs)
-#        self.variables=['T1','T1_z','p','u','v', 'w','u_z', 'v_z', 'w_z']
         self.variables=['T1','T1_z','p','u','v', 'w','Ox', 'Oy', 'Oz']
 
 
@@ -624,7 +623,6 @@ class BoussinesqEquations3D(BoussinesqEquations):
         self.problem.substitutions['UdotGrad(A, A_z)'] = '(u * dx(A) + v * dy(A) + w * A_z)'
         self.problem.substitutions['Lap(A, A_z)'] = '(dx(dx(A)) + dy(dy(A)) + dz(A_z))'
 
-#        self.problem.substitutions['Oy']          = '(dz(u) - dx(w))'
         self.problem.substitutions['v_fluc'] = '(v - plane_avg(v))'
         super(BoussinesqEquations3D, self)._set_subs()
 
@@ -681,26 +679,6 @@ class BoussinesqEquations3D(BoussinesqEquations):
         self._set_parameters(Rayleigh, Prandtl)
         self._set_subs()
 
-
-        # 3D Boussinesq hydrodynamics
-#        logger.debug('Adding Eqn: Incompressibility constraint')
-#        self.problem.add_equation("dx(u) + dy(v) + w_z = 0")
-#        logger.debug('Adding Eqn: Energy')
-#        self.problem.add_equation("dt(T1) - P*Lap(T1, T1_z) + w*T0_z   = -UdotGrad(T1, T1_z)")
-#        logger.debug('Adding Eqn: Momentum, x')
-#        self.problem.add_equation("dt(u)  - R*Lap(u, u_z) + dx(p)       =  -UdotGrad(u, u_z) ")
[…]

### 2018-06-15 tex/bvp_paper.tex
finishes iteration of paper

@@
 \begin{abstract}
-High Rayleigh number, turbulent convection is a classic system with a large timescale
+High Peclet number, turbulent convection is a classic system with a large timescale
 separation between flow speeds and equilibration time.
@@
 Evolved flow properties of AE solutions are measured to be within a few percent
-of solutions which are reached through standard evolution over a full thermal timescale. 
-We conclude with a discussion of useful extensions of AE, including 
-stratified, compressible convection or stellar structure models.
+of solutions which are reached through Standard Evolution (SE) over a full thermal timescale.
+At the highest values of the Rayleigh number at which we compare SE and AE,
+we find that AE solutions require roughly an order of magnitude fewer cpu-hours
+to compute than SE solutions.
 \end{abstract}
@@
 evolution of the thermal structure of the convective region has ceased.
-As the timestep size of implicit methods is bound to the fastest nonlinear flows,
-(convection) fully implicit methods cannot be used to address this form of stiffness
+As the timestep size of implicit methods is bound to the fastest nonlinear flows
+(convection), fully implicit methods cannot be used to address this form of stiffness
 \cite{viallet&all2011, viallet&all2013, viallet&all2016}.
@@
 atmosphere at the bottom, fixed-flux boundary.
-$\xi$ is a general depth-dependent scaling factor which
-tells us roughly how much larger F$_\text{E}$ is in the interior than it should
-be in the thermally equilibrated state (e.g., in Fig.~\ref{fig:time_trace}b,
-F$_{\text{tot}} \sim$ F$_{\text{E}} \sim 15\mathcal{P}$ just below the upper boundary layer, 
+For example, in Fig.~\ref{fig:time_trace}b,
+F$_{\text{tot}} \approx 19\mathcal{P}$ at the upper boundary,
 but in the equilibrated state 
-it should just be $\mathcal{P}$, so $\xi \sim 1/15$ at that depth).
-
-In order to properly reduce F$_\text{E}$, we note that, upon removing 
-terms which vanish due to symmetry, the convective enthalpy flux is carried
-solely by the velocity field coupling to perturbations in temperature around
-the mean temperature profile, or F$_\text{E} \propto \{w, T-\angles{T}_{x,y}\}$.
-As the evolved enthalpy flux should be roughly $\xi$F$_\text{E}$, we reduce 
-the velocity, $\bm{u}$,
-and temperature perturbations about the mean state, $T-\angles{T}_{x,y}$,
- by $\sqrt{\xi}$.
-
-To properly reduce the conductive flux, we examine the 
+it should just be $\mathcal{P}$, so $\xi \approx 1/19$ at that depth.
+
+To reduce the conductive flux by $\xi$, we examine the 
 time-stationary state, horizontally- and time-averaged
@@
 Here, we construct  $\text{F}_{\text{E, ev}} = \xi \text{F}_{\text{E}}$ 
-and $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
-\xi \angles{\bm{u}\times\bm{\omega}}_{x, y}$, where we scale 
-$\angles{\bm{u}\times\bm{\omega}}_{x, y} \propto \bm{u}^2$, by $\xi$ because we
-scaled $\bm{u}$ by $\sqrt{\xi}$ in order to reduce the convective enthalpy flux.
-With these profiles, we solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
-Convective flows
-are perturbations around a thermal profile defined by these equations in the evolved, 
-statistically stationary state. Thus, the specification of
-F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$
-fully specifies the mean thermodynamic structure of the system. 
+and $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}}
+= \xi\angles{\bm{u}\times\bm{\omega}}_{x, y}$.
+Using these profiles and 
+Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}),
+we solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
 Our choice of fixing the temperature at the top boundary and the flux at the bottom
-boundary ensures that there is a unique solution for $\angles{T_1}$ given the evolved
+boundary ensures that there is a unique solution for $\angles{T_1}_{x,y}$ given the evolved
 fluxes. If flux were fixed at both boundaries, there would be infinitely many
@@
 
-Thus, the AE method occurs in the following steps. First, we pause a convective simulation and
+Solving the above equations adjusts the mean thermal state and 
+$\text{F}_{\kappa}$ of the atmosphere while leaving $\text{F}_{\text{E}}$
+unchanged. In the  
+bulk of the domain, convective enthalpy flux dominates transport, and so there we
+assume that $\text{F}_{\text{tot}} \approx \text{F}_{\text{E}}$. Upon 
+removing terms which vanish due to symmetry, we note that the convective
+enthalpy flux is carried solely by the velocity field and perturbations in
+temperature away from the mean state, $\text{F}_{\text{E}} = 
+\angles{w(T - \angles{T})}$.
+In order to instantaneously decrease the convective enthalpy flux in a manner
+which is consistent with the conductive flux, 
+we multiply both the velocity, $\bm{u}$,
+and temperature perturbations about the mean state, $T-\angles{T}_{x,y}$,
+ by $\sqrt{\xi}$. This scaling of the velocity field is the reason that we
+multiply $\angles{\bm{u}\times\bm{\omega}}_{x, y}$, which is nondimensionally
+of order $u^2/L$, by $\xi$ while constructing
+$\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}}$.
+
+In general, the AE method occurs in the following steps. First, we pause a convective simulation and
 construct $\xi(z,t)$ from measured flux profiles in the convective domain.
@@
 The difference between the mean profiles is very small, O(0.5\%).
-(d) $\KS{T}$, as defined in Eqn.~\ref{eqnks_profile}, is shown. The small
+(d) $\KS{T}$, as defined in Eqn.~\ref{eqn:ks_profile}, is shown. The small
 difference in the mean interior temperature between AE and SE
@@
 \ref{table:speed}, we compare cpu-hour cost for select
-2D and 3D runs in which AE and SE solutions were compared. Times reported
+2D and 3D runs in which both AE and SE solutions were computed. Times reported
 for AE and SE runs only include the time required to reach an equilibrated

### 2018-06-15 referee_process/first_submission/referee_response.tex
finishes referee response

@@
 We would like to point out a few major changes in this version of the manuscript.
-A new section, ``Computational time-savings of AE'' has been added after the
+A brief new section, ``Computational time-savings of AE'' has been added after the
 results section and before the conclusion section. In this section, we directly
@@
 \end{myquotation}
-We have clarified this in the second to last pargraph of section III,
+We have clarified this in the third to last pargraph of section III,
 and added a forward reference to section III by this quoted sentence.
@@
 We have added a new section V., ``Computational Time-savings of AE.''
-We have combined the relevant information from the results section and the 
-conclusion section previously here, and we have added some information on a few
+We have combined the relevant information which was previously in the results 
+section and the conclusion section here, 
+and we have added some information on a few
 additional runs in a new table.
@@
 equilibration'' or ``thermally equilibrated'' throughout the paper. This term
-is explained in pargraph 2 of the introduction.
+is explained in paragraph 2 of the introduction.
 \begin{myquotation}
@@
 $\xi$ is simply a height-dependent scaling that we use to appropriately
-adjust our velocity, temperature, etc.
+adjust our velocity, temperature, etc. We have added a sentence after the 
+definition of $\xi$ giving an example of its value for the case presented in
+Fig. 1.
 
@@
 scaling
-$\bm{u}$ and $T - \langle T\rangle$ by $\sqrt{\xi}$ to reduce the convective flux.
+$u$ and $T - \langle T\rangle$ by $\sqrt{\xi}$ to reduce the convective flux.
 We scale $\langle u\times \omega\rangle$ by $\xi$, as it is
@@
 by $\sqrt{\xi}$, this term must be multiplied by $\xi$. We have added a short
-paragraph before Eqns (12) and (13), as well as some text shortly after those
-equations, containing this information.
+paragraph after Eqns (12) and (13) containing this information.
 

### 2018-07-19 referee_process/second_submission/referee_response.tex
referee round 2

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Eckart, other PRFluids editors, and anonymous referees,
$\,$\newline

\begin{singlespace}
We return our revised manuscript, ``Accelerated evolution in convective simulations,''
clarifying the paper where requested by the report of referee 1. 
Aside from these changes, the 
final pargaraph of the introductory section of the 
manuscript now contains references to the works of
Julien et al 1998 (ref 16) and Sprague et al 2006 (ref 17), whose studies of
rapidly rotating, asymptotically reduced convection 
we felt should be mentioned in this work.

We appreciate the very careful work of the referees in improving the clarity of
this manuscript. Below ew include our responses to the report; the original
text of the report is included in italics, and our response follows inline in
unitalicized blocks.

$\,$\newline
\noindent
Sincerely,

Evan H. Anders, Benjamin P. Brown, and Jeffrey S. Oishi

%\end{singlespace}

\newpage
\noindent
\Large{\textbf{Response to first referee:}}\newline$\,$\newline\indent

\begin{myquotation}
I am ok with the paper being published now.   There are a small number of things
that could be done that would still help the clarity of the paper:

Intro:  This is perhaps a bit nit-picky, but the authors talk about
“equilibration times” whereas perhaps they should be more precise and refer to
what they really mean, i.e. the thermal relaxation time.   There is no natural
timescale that is the equilibration time, since this depends on where you start
from.  One of the points made in the intro is that one way around the thermal
relaxation problem is to start near the true solution by “bootstrapping”, but
this requires a guess at the nonlinear solution which is hard in a turbulent
system.  So the problem really arises because, without such a guess, the
simulation follows the full evolution from unstable equilibrium to stable
equilibrium which have very different thermal profiles.  The equilibration time
is therefore just the thermal relaxation time, which is one of the many
timescales that the authors refer too.  I think it is better to just talk in
terms of widely separated timescales (a stiff problem) and be specific that the
one they are interested in is the stiffness between convective and thermal
relaxation, i.e. high Pe problems.
\end{myquotation}
This is a good (and subtle) point. Where appropriate, we have changed the text
to refer to thermal relaxation rather than thermal equilibration throughout.

\begin{myquotation}
In referring to reference [16], I think it is more accurate to say that this is
one EXAMPLE of where this technique has been used MANY times before.
\end{myquotation}
Ref. 16 (which is now ref. [18], due to the addition of the sentence before it
which calls out new refs [16, 17]) is now appropriately called out as an example
of where a similar technique has been used before.

\begin{myquotation}
Sect III para 2:  ``proper'' -- I think you mean ``nonlinear'' or ``saturated''
\end{myquotation}
Correct! ``proper'' $\rightarrow$ ``saturated''.

\begin{myquotation}
Sect IV para 2: ``oscillatory nature is stable''  -- I am not sure what this means!
\end{myquotation}
The plumes oscillate for long timescales (the oscillatory motions do not
eventually give way to stationary plumes). We have modified this sentence to
better explain our meaning.

\begin{myquotation}
My personal opinion is that I still think the section about the scaling laws is
weird to have here, in the sense that it interrupts the flow of the paper.  But
it is not wrong, so I guess it can stay!

Sect VI:  I think this section has improved in the more cautionary and less
speculative way as suggested.  I would add a comment to the penultimate line
that says that there could be issues with sound waves in compressible
calculations which are very sensitive to pressure mismatches.
\end{myquotation}
A sentence explaining this point has been added where suggested.

\end{singlespace}

\bibliography{../../biblio.bib}
\end{document}

### 2018-07-19 tex/bvp_paper.tex
referee round 2

@@
 High Peclet number, turbulent convection is a classic system with a large timescale
-separation between flow speeds and equilibration time.
+separation between flow speeds and the thermal relaxation time.
 In this paper, we present a method of achieving Accelerated Evolution (AE) of convective simulations which
@@
 simulations is infeasible due to the
-large separation between various flow timescales and equilibration times.
+large separation between various flow timescales and relaxation times.
 Stiffness in astrophysical systems can manifest in multiple ways, some of which can
@@
 In a high Pe system, many convective timescales must pass before 
-the domain reaches thermal equilibrium, a steady state in which
+the domain thermally relaxes into a steady state in which
 evolution of the thermal structure of the convective region has ceased.
@@
 Resolving dynamics in atmospheres which are sufficiently
-thermally equilibrated therefore remains a challenging problem.
+thermally relaxed therefore remains a challenging problem.
 Solar convection is a prime example of this phenomenon, as
@@
 (convection overturns every $\sim 5$ minutes at the solar surface)
-compared to the Sun's thermal evolution timescale, which is O($10^7$) years
+compared to the Sun's thermal relaxation timescale, which is O($10^7$) years
 \cite{stix2003}.  
@@
 through a single convective overturn time becomes more computationally expensive
-and the number of overturn times required for systems to reach thermal equilibrium
+and the number of overturn times required for systems to thermally relax
 grows.
@@
 numericists studying convection, and an abundance of approaches has been employed to
-study thermally equilibrated solutions. One popular method for accelerating the convergence
+study thermally relaxed solutions. One popular method for accelerating the convergence
 of high-Ra solutions is by ``bootstrapping'' -- the process of using the flow
@@
 \cite{brandenburg&all2005}, initial conditions can be adjusted such that the stratification
-within the convective domain is closer to an equilibrium state than the largely
+within the convective domain is closer to a relaxed state than the largely
 unstable hydrostatic state.
@@
 Despite the numerous methods that have been used,
-the most straightforward way to achieve a thermally equilibrated solution
+the most straightforward way to achieve a thermally relaxed solution
 is to evolve a convective simulation through a thermal timescale. Some modern
@@
 for hundreds of freefall timescales \cite{stevens&all2011}, much less the
-thousands or millions of freefall times required for thermal equilibration.
+thousands or millions of freefall times required for thermal relaxation.
 
 In this work, we study a method of achieving accelerated evolution of
-convective simulations. We couple measurements of the dynamics of unequilibrated
+convective simulations. 
+Our technique is similar in essence to the approach used in asymptotically 
+reduced models of rapidly rotating convection, in which the
+slowly evolving mean temperature profile is timestepped separately from the
+fast convective dynamics \cite{julien&all1998, sprague&all2006}. 
+We couple measurements of the dynamics of unstable, evolving
 convective simulations with knowledge about energy balances in the desired solution
-to self-consistently adjust the mean vertical thermodynamic profile towards its evolved state. 
-While a technique of this kind has been used previously \cite{hurlburt&all1986},
+to instantaneously and self-consistently adjust the mean vertical thermodynamic 
+profile toward its relaxed state. 
+While a technique of this kind has been used by many studies previously 
+(e.g., \cite{hurlburt&all1986}),
 the details of implementation, the convergence properties, and whether or not the
-accelerated evolution state corresponds to a standard evolution state are not documented.
+thermally relaxed state achieved from 
+accelerated evolution corresponds to the relaxed state in standard evolution 
+are not documented.
 In section \ref{sec:experiment}, we describe our convective simulations and
@@
 first $\sim 25$ $t_{\text{ff}}$. The solution then saturates and begins to slowly
-equilibrate towards the proper isothermal profile in the interior of the domain.
-This slow equilibration is evident in the behavior of the blue line, which measures
+relax toward the saturated isothermal profile in the interior of the domain.
+This slow relaxation is evident in the behavior of the blue line, which measures
 $\angles{T} - T_{\text{top}}$, where \angles{T} is the volume-average of $T$, and
@@
 F$_{\text{tot}} \approx 19\mathcal{P}$ at the upper boundary,
-but in the equilibrated state 
+but in the relaxed state 
 it should just be $\mathcal{P}$, so $\xi \approx 1/19$ at that depth.
@@
 units, is overplotted as a grey line. 
-We see that the mean value of Nu reaches its equilibrium value quickly
+We see that the mean value of Nu reaches its relaxed value quickly
 compared to $\angles{T}$.
 Regardless, fluctuations of Nu about the mean
-value are much smaller in the thermally equilibrated state.
+value are much smaller in the thermally relaxed state.
 The times at which AE solves occur are denoted by arrows in (b),
@@
 Nu around the mean value at early times have both a larger magnitude and higher
-frequency than the fluctuations in the equilibrated state.
+frequency than the fluctuations in the relaxed state.
 In Fig.~\ref{fig:nu_v_time}b, we show the AE traces of Nu and
@@
 and the frequency and magnitude of fluctuations in Nu away from the mean resemble the
-final equilibrated state of SE.
+final relaxed state of SE.
 
@@
 At larger $S$ in 2D, the value of Nu varies significantly over time even in the
-equilibrated state (as seen in Fig.~\ref{fig:nu_v_time}). We examine the shaded
+relaxed state (as seen in Fig.~\ref{fig:nu_v_time}). We examine the shaded
 region of Fig.~\ref{fig:nu_v_time}b in more detail in the top left
@@
 \cite{goluskin&all2014}, and the
-oscillatory nature of the plumes is stable. However, thanks to our choice of periodic
+oscillatory motions of the plumes are a long-lived, stable phenomenon. 
+However, thanks to our choice of periodic
 boundary conditions and despite the no-slip conditions, the full system of the
@@
 2D and 3D runs in which both AE and SE solutions were computed. Times reported
-for AE and SE runs only include the time required to reach an equilibrated
+for AE and SE runs only include the time required to reach a relaxed
 state, and do not include the time over which measurements were taken
-in the equilibrated state (e.g., the green shaded regions of
+in that state (e.g., the green shaded regions of
 Fig.~\ref{fig:time_trace}a\&c are not included in the $S = 10^5$ times).
@@
 In this work we have studied a method of Accelerated Evolution (AE) which can
-be employed to achieve rapid thermal equilibration of convective simulations.  We compared
+be employed to achieve rapid thermal relaxation of convective simulations.  We compared
 this technique to the Standard Evolution (SE) of convection through a full thermal diffusion timescale,
@@
 studies of penetrative convection, despite the fact that similar methods have
-long been used in those studies \cite{hurlburt&all1986}.
+long been used in those studies \cite{hurlburt&all1986}. Extensions to 
+fully compressible convection in which there are two true thermodynamic
+variables \cite{anders&brown2017} must contain a very careful treatment of
+AE pressure adjustments, so as to avoid wave-launching pressure mismatches.
 Our work here serves as a basis for determining if AE techniques are

### 2018-07-30 referee_process/second_submission/referee_response.tex
editorial stuff

@@
 manuscript now contains references to the works of
-Julien et al 1998 (ref 16) and Sprague et al 2006 (ref 17), whose studies of
+Julien et al 1998 (ref 16) and Sprague et al 2006 (ref 17), whose techniques in
 rapidly rotating, asymptotically reduced convection 
-we felt should be mentioned in this work.
+we felt should be mentioned in this work. A few grammatical and mechanical
+corrections have been made throughout the manuscript.
 
 We appreciate the very careful work of the referees in improving the clarity of
-this manuscript. Below ew include our responses to the report; the original
+this manuscript. Below we include our responses to the report; the original
 text of the report is included in italics, and our response follows inline in

### 2018-07-30 tex/bvp_paper.tex
editorial stuff

@@
 separation between flow speeds and the thermal relaxation time.
-In this paper, we present a method of achieving Accelerated Evolution (AE) of convective simulations which
-fast-forwards through the long thermal evolution of these systems, and we test the
-validity of this method. The AE procedure involves measuring the dynamics of convection
+In this paper, we present a method of
+fast-forwarding through the long thermal relaxation of convective simulations, and we test the
+validity of this method. This Accelerated Evolution (AE) method involves measuring the dynamics of convection
 early in a simulation and using its characteristics to adjust the mean thermodynamic
@@
 Evolved flow properties of AE solutions are measured to be within a few percent
-of solutions which are reached through Standard Evolution (SE) over a full thermal timescale.
+of solutions which are reached through Standard Evolution (SE) over a full thermal diffusion timescale.
 At the highest values of the Rayleigh number at which we compare SE and AE,
@@
 study thermally relaxed solutions. One popular method for accelerating the convergence
-of high-Ra solutions is by ``bootstrapping'' -- the process of using the flow
-fields in a converged solution at low Ra as initial conditions for a simulation at high
+of high-Ra solutions is by ``bootstrapping'' -- the process of using the relaxed flow
+fields and thermal structure of a low Ra solution as initial conditions for a simulation at high
 Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
@@
 reduced models of rapidly rotating convection, in which the
-slowly evolving mean temperature profile is timestepped separately from the
+mean temperature profile evolves separately from the
 fast convective dynamics \cite{julien&all1998, sprague&all2006}. 
 We couple measurements of the dynamics of unstable, evolving
-convective simulations with knowledge about energy balances in the desired solution
+convective simulations with knowledge about energy balances in the relaxed solution
 to instantaneously and self-consistently adjust the mean vertical thermodynamic 
@@
 \\
-\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
+\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 (T_0 + T_1),
 	\label{eqn:dim_bouss_energy}
@@
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}. The code used to run the simulations
-in this work is included in the supplemental materials as a zip file.
+in this work is included in the supplemental materials as a zip file \cite{supp}.
 
@@
 Here we describe a method of Accelerated Evolution (AE), which we use 
-to rapidly evolve the thermodynamic state of convective simulations.  
+to rapidly relax the thermodynamic state of convective simulations.  
 We compare this AE method to Standard Evolution
@@
 The mean atmospheric temperature and
-kinetic energies are fully converged when $t = 4000$ $t_{\text{ff}}$ $= 0.35$ $t_{\kappa}$.
+kinetic energies are fully converged when $t = 4000t_{\text{ff}} = 0.35t_{\kappa}$.
 We show roughly the first thousand freefall time
@@
 The horizontally averaged profiles of the vertical conductive flux, 
-F$_{\kappa} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective enthalpy flux,
-F$_{\text{E}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method.
+F$_{\kappa} = \angles{-\kappa\partial_z T}_{x,y}$, and the vertical convective enthalpy flux,
+F$_{\text{E}} = \angles{wT}_{x,y}$, are the basis of the AE method.
 Here we use $\angles{}_{x,y}$ to represent a horizontal average. We measure
@@
 those shown in Fig.~\ref{fig:time_trace}b.
-As the atmosphere evolves towards
+As the atmosphere relaxes towards
 the isothermal profile specified by the upper (cold) boundary condition, excess
@@
 To reduce the conductive flux by $\xi$, we examine the 
-time-stationary state, horizontally- and time-averaged
-Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}); after 
+horizontally- and time-averaged
+Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}) in the time-stationary state; after 
 neglecting terms which vanish due to symmetry, these equations become
@@
 temperature away from the mean state, $\text{F}_{\text{E}} = 
-\angles{w(T - \angles{T})}$.
+\angles{w(T_1 - \angles{T_1})}$.
 In order to instantaneously decrease the convective enthalpy flux in a manner
@@
 we multiply both the velocity, $\bm{u}$,
-and temperature perturbations about the mean state, $T-\angles{T}_{x,y}$,
+and temperature perturbations about the mean state, $T_1-\angles{T_1}_{x,y}$,
  by $\sqrt{\xi}$. This scaling of the velocity field is the reason that we
@@
 time average is taken using a centered boxcar window whose width is 50 $t_{\text{ff}}$.
-The mean value of Nu evolves towards its final value (dashed horizontal
+The mean value of Nu evolves towards its relaxed value (dashed horizontal
 grey line) rapidly compared to $\angles{T}-T_{\text{top}}$ (blue), 
@@
 In addition to adjusting the 1D thermal profile, the AE method also scales the
-simulations velocities and temperature fluctuations by $\sqrt{\xi}$. 
+simulation velocities and temperature fluctuations by $\sqrt{\xi}$. 
 In Fig.~\ref{fig:pdf_comparison}
@@
 vertical velocity ($w$, Fig.~\ref{fig:pdf_comparison}a), horizontal velocity ($u$, Fig. \ref{fig:pdf_comparison}b),
-and the nonlinear vertical convective flux ($w(T - \angles{T}_{x,y})$, Fig.~\ref{fig:pdf_comparison}c). 
+and the nonlinear vertical convective flux ($w(T_1 - \angles{T_1}_{x,y})$, Fig.~\ref{fig:pdf_comparison}c). 
 Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
@@
 $\KSstat{w} = 0.00615$, $\KSstat{u} = 0.0349$,
-and $\KSstat{w(T - \angles{T}_{x,y})} = 0.0263$.
+and $\KSstat{w(T_1 - \angles{T_1}_{x,y})} = 0.0263$.
 The difference in vertical velocity
@@
 This also confirms that the large $\KSstat{T}$ in Fig.~\ref{fig:temp_comparison}d is
-not of concern, and that the AE run achieves the proper convective solution.
-The horizontal velocity shows some small deviation between the two simulations, and this
-likely relates to the precise configuration of the convective plumes (e.g., Fig.~\ref{fig:oscillating_plumes}).
+not of concern, and that the AE run achieves the same relaxed convective solution
+as the SE run.
 We find that the difference in $\KS{u}$, which consistently has more probability
@@
 \begin{acknowledgments}
-We thank the two anonymous referees whose careful comments greatly 
+We thank Geoff Vasil, Daniel Lecoanet, 
+and the two anonymous referees whose careful comments greatly 
 improved the clarity and scientific content of this paper.
@@
 \hline
-$10^{1/3}$	    &	$2.79 \cdot 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$52.8$	&	$340$	&	100	&	1.46	&	1.46	\\
-$10^{2/3}$	    &	$6.01 \cdot 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$77.6$	&	$282$	&	100	&	1.95	&	1.95	\\
-$10^1$	        &	$1.30 \cdot 10^4$       &  	32$\times$64$\,\,\,\,\,\,\,$&	$114$	&	$265$	&	100	&	2.43	&	2.42	\\
-$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$167$	&	$251$	&	100	&	2.54	&	2.54	\\
-$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$245$	&	$245$	&	100	&	3.14	&	3.14	\\
-$10^2$	        &	$1.30 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
-$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$528$	&	$248$	&	100	&	4.71	&	4.71	\\
-$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$776$	&	$251$	&	100	&	5.5	&	5.5	\\
-$10^3$	        &	$1.30 \cdot 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.14 \cdot 10^3$	&	$268$	&	200	&	6.4	&	6.33	\\
-$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.67 \cdot 10^3$	&	$247$	&	500	&	6.87	&	6.95	\\
-$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$       &	256$\times$512$\,\,\,\,\,\,\,$&	$2.45 \cdot 10^3$	&	$275$	&	500	&	7.54	&	7.59	\\
-$10^4$	        &	$1.30 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$3.60 \cdot 10^3$	&	$301$	&	500	&	8.83	&	8.83	\\
-$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$5.28 \cdot 10^3$	&	$317$	&	500	&	10.13	&	10.14	\\
-$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$7.76 \cdot 10^3$	&	$326$	&	500	&	11.65	&	11.69	\\
-$10^5$	        &	$1.30 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.14 \cdot 10^4$	&	$411$	&	500	&	14.02	&	14.18	\\
-$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.67 \cdot 10^4$	&	$391$	&	500	&	---	&	16.21	\\
-$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$2.45 \cdot 10^4$	&	$453$	&	500	&	---	&	18.58	\\
-$10^6$	        &	$1.30 \cdot 10^9$       &	1024$\times$2048$\,\,\,\,\,\,\,$	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
-$10^7$	        &	$1.30 \cdot 10^{10}$	&	2048$\times$4096$\,\,\,\,\,\,\,$	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	38.29	\\
+$10^{1/3}$	    &	$2.79 \times 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$52.8$	&	$340$	&	100	&	1.46	&	1.46	\\
+$10^{2/3}$	    &	$6.01 \times 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$77.6$	&	$282$	&	100	&	1.95	&	1.95	\\
+$10^1$	        &	$1.30 \times 10^4$       &  	32$\times$64$\,\,\,\,\,\,\,$&	$114$	&	$265$	&	100	&	2.43	&	2.42	\\
+$10^{1 + 1/3}$	&	$2.79 \times 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$167$	&	$251$	&	100	&	2.54	&	2.54	\\
+$10^{1 + 2/3}$	&	$6.01 \times 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$245$	&	$245$	&	100	&	3.14	&	3.14	\\
+$10^2$	        &	$1.30 \times 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
+$10^{2 + 1/3}$	&	$2.79 \times 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$528$	&	$248$	&	100	&	4.71	&	4.71	\\
+$10^{2 + 2/3}$	&	$6.01 \times 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$776$	&	$251$	&	100	&	5.5	&	5.5	\\
+$10^3$	        &	$1.30 \times 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.14 \times 10^3$	&	$268$	&	200	&	6.4	&	6.33	\\
+$10^{3 + 1/3}$	&	$2.79 \times 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.67 \times 10^3$	&	$247$	&	500	&	6.87	&	6.95	\\
+$10^{3 + 2/3}$	&	$6.01 \times 10^6$       &	256$\times$512$\,\,\,\,\,\,\,$&	$2.45 \times 10^3$	&	$275$	&	500	&	7.54	&	7.59	\\
+$10^4$	        &	$1.30 \times 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$3.60 \times 10^3$	&	$301$	&	500	&	8.83	&	8.83	\\
+$10^{4 + 1/3}$	&	$2.79 \times 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$5.28 \times 10^3$	&	$317$	&	500	&	10.13	&	10.14	\\
+$10^{4 + 2/3}$	&	$6.01 \times 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$7.76 \times 10^3$	&	$326$	&	500	&	11.65	&	11.69	\\
+$10^5$	        &	$1.30 \times 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.14 \times 10^4$	&	$411$	&	500	&	14.02	&	14.18	\\
+$10^{5 + 1/3}$	&	$2.79 \times 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.67 \times 10^4$	&	$391$	&	500	&	---	&	16.21	\\
+$10^{5 + 2/3}$	&	$6.01 \times 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$2.45 \times 10^4$	&	$453$	&	500	&	---	&	18.58	\\
+$10^6$	        &	$1.30 \times 10^9$       &	1024$\times$2048$\,\,\,\,\,\,\,$	&	$3.60 \times 10^4$	&	$436$	&	500	&	---	&	22.13	\\
+$10^7$	        &	$1.30 \times 10^{10}$	&	2048$\times$4096$\,\,\,\,\,\,\,$	&	$1.14 \times 10^5$	&	$183$	&	170	&	---	&	38.29	\\
 \\ \hline \hline \multicolumn{8}{c}{\vspace{-0.2cm}}\\
@@
 \hline
-$10^1$          &	$1.30 \cdot 10^4$	&	32$\times$64$\times$64$\,\,\,\,\,\,\,$   &	$114$	&	$261$	&	100	&	2.42	&	2.42	\\
-$10^2$          &	$1.30 \cdot 10^5$	&	64$\times$128$\times$128$\,\,\,\,\,\,\,$   &	$360$	&	$249$	&	100	&	3.97	&	4	\\
-$10^3$          &	$1.30 \cdot 10^6$	&	128$\times$256$\times$256$\,\,\,\,\,\,\,$	&	$1.14 \cdot 10^3$	&	$243$	&	500	&	6.27	&	6.27	\\
-$10^4$          &	$1.30 \cdot 10^7$	&	256$\times$512$\times$512$\,\,\,\,\,\,\,$	&	$3.60 \cdot 10^3$	&	$244$	&	500	&	9.92	&	9.88	\\
+$10^1$          &	$1.30 \times 10^4$	&	32$\times$64$\times$64$\,\,\,\,\,\,\,$   &	$114$	&	$261$	&	100	&	2.42	&	2.42	\\
+$10^2$          &	$1.30 \times 10^5$	&	64$\times$128$\times$128$\,\,\,\,\,\,\,$   &	$360$	&	$249$	&	100	&	3.97	&	4	\\
+$10^3$          &	$1.30 \times 10^6$	&	128$\times$256$\times$256$\,\,\,\,\,\,\,$	&	$1.14 \times 10^3$	&	$243$	&	500	&	6.27	&	6.27	\\
+$10^4$          &	$1.30 \times 10^7$	&	256$\times$512$\times$512$\,\,\,\,\,\,\,$	&	$3.60 \times 10^3$	&	$244$	&	500	&	9.92	&	9.88	\\
 \hline																	
@@
 While the use of a single AE BVP solve rapidly advances the convecting state to
-one that is closer to the evolved state, we find that repeating this method 
+one that is closer to the relaxed state, we find that repeating this method 
 multiple times is the best way to

### 2018-07-30 code/plotting/nu_comp.py

@@ -166,15 +166,15 @@ for ax, t in axs_share:
     ax.set_ylim(2e-2, 5e-1)
 #    plt.axes(ax)
 #    y_ticks = np.array([2e-2, 1e-1, 5e-1])
-#    plt.yticks(y_ticks, (r'$2\cdot 10^{-2}$', r'$10^{-2}$', r'$5\cdot 10^{-1}$'))
+#    plt.yticks(y_ticks, (r'$2\times 10^{-2}$', r'$10^{-2}$', r'$5\cdot 10^{-1}$'))
     if ax == ax2_2:
         continue
     plt.axes(ax)
     ax.set_yticks((1e-1,))
     ax.set_yticklabels((r'$10^{-1}$',))
     trans = ax.get_xaxis_transform() # x in data untis, y in axes fraction
-    ax.annotate(r'$2\cdot 10^{-2}$', xy=(t, 0.03), xycoords=trans, color='blue')
-    ax.annotate(r'$5\cdot 10^{-1}$', xy=(t, 0.94), xycoords=trans, color='blue')
+    ax.annotate(r'$2\times 10^{-2}$', xy=(t, 0.03), xycoords=trans, color='blue')
+    ax.annotate(r'$5\times 10^{-1}$', xy=(t, 0.94), xycoords=trans, color='blue')
 
 axs[1].spines['right'].set_visible(False)
 ax2_2.spines['right'].set_visible(False)

### 2018-07-30 code/plotting/pdf_comparison.py

@@ -76,8 +76,8 @@ COLORS_2=['peru', 'gold', 'teal']
 MARKERSIZE_2=[5,5,5]
 
 base_dirs_post = [
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/base_post',
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/bvp_post'
             ]
 ra_runs = '1.30e8'
 #ra_runs = '6.01e7'
@@ -266,7 +266,7 @@ axes[-1].plot(diff_x[(diff_y < 0)*(diff_x > 0.001)], -diff_y[(diff_y < 0)*(diff_
 axes[-1].set_xlim(-0.0013, 0.004)
 axes[-1].set_yscale('log')
 axes[-1].set_ylim(1e-4, 1e-1)
-axes[-1].set_xlabel(r'$w(T - \langle T\,\rangle_{x,y})$', labelpad=-4)
+axes[-1].set_xlabel(r'$w(T_1 - \langle T_1\rangle_{x,y})$', labelpad=-4)
 axes[-1].annotate(r'$\mathrm{(f)}$', (-1e-3, 1e-2), fontsize=10)
 for tick in axes[-1].get_xticklabels():
     tick.set_rotation(45)
@@ -275,4 +275,4 @@ for tick in axes[-1].get_xticklabels():
 
 
 
-plt.savefig('pdf_comparison.png'.format(k), bbox_inches='tight', dpi=200)
+plt.savefig('pdf_comparison.png'.format(k), bbox_inches='tight', dpi=400)

### 2018-07-30 code/plotting/temp_comparison.py

@@ -87,8 +87,8 @@ COLORS_2=['peru', 'gold', 'teal']
 MARKERSIZE_2=[5,5,5]
 
 base_dirs_post = [
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/base_post',
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/bvp_post'
             ]
 ra_runs = '1.30e8'
 #ra_runs = '6.01e7'
@@ -220,4 +220,4 @@ axes[-1].annotate(r'$\mathrm{(d)}$', (-0.497, 1.5e-1), fontsize=10)
 print('for {}, max diff is {}'.format('T', max_diff))
 
 
-plt.savefig('temp_comparison.png'.format(k), bbox_inches='tight', dpi=200)
+plt.savefig('temp_comparison.png'.format(k), bbox_inches='tight', dpi=400)

### 2018-07-30 code/plotting/time_trace.py

@@ -11,7 +11,9 @@ Options:
 
 
 import matplotlib   
+import matplotlib.style
 matplotlib.rcParams.update({'font.size': 11})
+matplotlib.style.use('classic')
 import matplotlib.pyplot as plt
 plt.rc('font',family='Times New Roman')
 from matplotlib.colors import ColorConverter
@@ -30,13 +32,13 @@ import dedalus.public as de
 
 
 base_dirs_pre = [
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_pre',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_pre'
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/base_pre',
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/bvp_pre'
             ]
 
 base_dirs_post = [
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/base_post',
-            '/home/evan/research/my_papers/bvp_initial_conditions_paper/code/runs/bvp_post'
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/base_post',
+            '/home/evanhanders/research/papers/accelerated_evolution/code/runs/bvp_post'
             ]
 fields = ['Nu', 'Re', 'IE', 'KE', 'TE']
 
@@ -180,7 +182,8 @@ axes[2].set_xlim(0, 910.6)
 x_ticks = [250, 500, 750, 1000]
 axes[0].set_xticks(x_ticks)
 x_ticks = [1.133e4, 1.133e4+250, 1.183e4]
-axes[1].set_xticks(x_ticks)
+plt.axes(axes[1])
+plt.xticks(x_ticks, ('11330', '11580', '11830'))
 x_ticks = [250, 500, 750]
 axes[2].set_xticks(x_ticks)
 axes[0].set_ylabel(r'$\mathrm{Kinetic\,\, Energy}$', labelpad=-10)
@@ -190,8 +193,8 @@ axes[0].xaxis.set_label_coords(0.24, -0.125)
 x, y = axes[0].xaxis.get_label().get_position()
 print(x, y)
[…]

### 2018-08-17 tex/bvp_paper.tex
publication-like quality

@@
 \newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
-\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
-\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
+\newcommand{\KS}[1]{\ensuremath{D_{\text{KS}}(#1)}}
+\newcommand{\KSstat}[1]{\ensuremath{\overline{D_\text{KS}(#1)}}}
 \newcommand{\grad}{\ensuremath{\nabla}}
@@
 At the highest values of the Rayleigh number at which we compare SE and AE,
-we find that AE solutions require roughly an order of magnitude fewer cpu-hours
-to compute than SE solutions.
+we find that AE solutions require roughly an order of magnitude fewer computing
+to evolve than SE solutions.
 \end{abstract}
@@
 Studying realistic models of natural systems through direct numerical
-simulations is infeasible due to the
+simulations is infeasible because of the
 large separation between various flow timescales and relaxation times.
@@
 dynamical timescales in the solar convective zone are relatively short 
-(convection overturns every $\sim 5$ minutes at the solar surface)
+(convection overturns every $\sim 5$ min at the solar surface)
 compared to the Sun's thermal relaxation timescale, which is O($10^7$) years
@@
 in the high-Rayleigh-number (Ra) regime,
-the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
+the thermal diffusion timescale ($t_{\kappa}$, defined in Sec. \ref{sec:ae}) 
 becomes intractably large compared to dynamical timescales 
-such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
+such as the freefall time ($t_{\text{ff}}$, defined in Sec. \ref{sec:experiment})
 \cite{anders&brown2017}, 
@@
 a linear eigenvalue solve \cite{hurlburt&all1984} in plane-parallel studies, or
-axisymmetric solutions in studies of convection in 3D cylinders \cite{verzicco&camussi1997}. 
+axisymmetric solutions in studies of convection in three-dimensional (3D)
+ cylinders \cite{verzicco&camussi1997}. 
 In other systems, particularly when convective zones are adjacent to stable regions,
@@
 are not documented.
-In section \ref{sec:experiment}, we describe our convective simulations and
-numerical methods. In section \ref{sec:ae}, we describe the procedure for 
+In Sec. \ref{sec:experiment}, we describe our convective simulations and
+numerical methods. In Sec. \ref{sec:ae}, we describe the procedure for 
 achieving accelerated evolution. In
-section \ref{sec:results}, we compare accelerated evolution solutions
+Sec. \ref{sec:results}, we compare accelerated evolution solutions
 to solutions obtained from standard evolution through a full thermal diffusion timescale. 
-In section \ref{sec:speedups}, we compare the numerical cost of accelerated
+In Sec. \ref{sec:speedups}, we compare the numerical cost of accelerated
 solutions to standard solutions.
 Finally,
-in section \ref{sec:extensions}, we offer concluding remarks and
+in Sec. \ref{sec:extensions}, we offer concluding remarks and
 discuss extensions of the methods presented here.
@@
 $\bm{u}\cdot\grad\bm{u} = \grad(|\bm{u}|^2/2) - \bm{u}\times(\grad\times\bm{u})$
-and $\grad^2\bm{u} = -\grad\times(\grad\times\bm{u})$, Eqns.~\ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
+and $\grad^2\bm{u} = -\grad\times(\grad\times\bm{u})$, Eqs.~(\ref{eqn:dim_bouss_momentum}) and (\ref{eqn:dim_bouss_energy})
 become
@@
 
-In Eqns.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}),
+In Eqs.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), and (\ref{eqn:bouss_energy}),
 linear terms are grouped on the left-hand side of the equations, while nonlinear terms
@@
 pseudospectral framework \cite{burns&all2016} to evolve  
-Eqns.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}) 
+Eqs.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), and (\ref{eqn:bouss_energy}) 
 forward in time
@@
 physical grid dimensions are 3/2 the size of the coefficient grid.  
-We study 2D and 3D convection in which the domain is a cartesian box, 
+We study two- (2D) and three-dimensional (3D) convection in which the domain is a cartesian box, 
 whose dimensionless vertical extent is $z \in [0, 1]$, 
@@
 We specify no-slip, impenetrable boundary conditions at both the top and
-bottom boundary,
+bottom boundaries,
 \begin{equation}
@@
 thermal profile and the flux through the domain are fixed at a boundary 
-(see section \ref{sec:ae}).
+(see Sec. \ref{sec:ae}).
 
@@
 $t_\kappa = \mathcal{P}^{-1}$. Both AE and SE simulations begin with identical
-initial conditions, as described in section \ref{sec:experiment}.
+initial conditions, as described in Sec. \ref{sec:experiment}.
 As Ra increases, and $\mathcal{P}$ decreases, SE solutions become intractable, 
@@
 We compare kinetic energy (KE, black line) and mean temperature (blue line)
-traces from a SE run in Fig.~\ref{fig:time_trace}a to an AE run
-in Fig.~\ref{fig:time_trace}c.
-In Fig.~\ref{fig:time_trace}a, the time evolution of the SE simulation is shown.
+traces from a SE run in Fig.~\ref{fig:time_trace}(a) to an AE run
+in Fig.~\ref{fig:time_trace}(c).
+In Fig.~\ref{fig:time_trace}(a), the time evolution of the SE simulation is shown.
 The KE grows exponentially from white noise during the
@@
 units of evolution, as well as the evolved thermodynamic state reached after a full
-thermal time of evolution.  In Fig.~\ref{fig:time_trace}c, similar traces are
+thermal time of evolution.  In Fig.~\ref{fig:time_trace}(c), similar traces are
 shown for the corresponding AE solution
@@
 both of these fluxes early in a simulation, retrieving profiles such as
-those shown in Fig.~\ref{fig:time_trace}b.
+those shown in Fig.~\ref{fig:time_trace}(b).
 As the atmosphere relaxes towards
@@
 energy leaves through the upper boundary, as seen in 
-Fig.~\ref{fig:time_trace}b, where the amount of flux exiting at the top of the domain
+Fig.~\ref{fig:time_trace}(b), where the amount of flux exiting at the top of the domain
 is nearly 20 times larger the flux entering the bottom of the domain. Once the atmospheric
@@
 is equal to the flux exiting through the upper boundary.  In general, this 
-evolution is slow in SE (Fig.~\ref{fig:time_trace}a), but AE (Fig.~\ref{fig:time_trace}c)
-can rapidly advance a system whose fluxes are in a strongly disequilibrium state (Fig.~\ref{fig:time_trace}b),
-into a near-equilibrium state, as shown in Fig.~\ref{fig:time_trace}d. In
+evolution is slow in SE [Fig.~\ref{fig:time_trace}(a)], but AE [Fig.~\ref{fig:time_trace}(c)]
+can rapidly advance a system whose fluxes are in a strongly disequilibrium state [Fig.~\ref{fig:time_trace}(b)],
+into a near-equilibrium state, as shown in Fig.~\ref{fig:time_trace}(d). In
 this final state both boundaries conduct the same amount of flux.
 The converged fluxes achieved through AE are at most 5\% different from the SE solution, 
-as shown in Fig.~\ref{fig:time_trace}e. 
+as shown in Fig.~\ref{fig:time_trace}(e). 
 This is a very small difference considering the short timescales on which convergence
@@
 \end{equation}
-which have the systematic asymmetries (Fig.~\ref{fig:time_trace}b) removed. These profiles describe which
+which have the systematic asymmetries [Fig.~\ref{fig:time_trace}(b)] removed. These profiles describe which
 parts of the atmosphere depend on convection to carry flux (where $f_{\text{E}}(z) = 1$
@@
 horizontally- and time-averaged
-Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}) in the time-stationary state; after 
+Eqs.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}) in the time-stationary state; after 
 neglecting terms which vanish due to symmetry, these equations become
@@
 Using these profiles and 
-Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}),
+Eqs. (\ref{eqn:bouss_BVP_momentum}) and (\ref{eqn:bouss_BVP_energy}),
 we solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
@@
 We solve a 1D boundary value problem (BVP) consisting of
-Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
+Eqs.~(\ref{eqn:bouss_BVP_momentum}) and (\ref{eqn:bouss_BVP_energy})
 to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
@@
 A moving average of Nu, using a centered boxcar with a span of 50 freefall time
-units, is overplotted as a grey line. 
+units, is overplotted as a gray line. 
 We see that the mean value of Nu reaches its relaxed value quickly
@@
 The times at which AE solves occur are denoted by arrows in (b),
-and the grey boxed region is examined in more detail in Fig. \ref{fig:oscillating_plumes}.
+and the gray boxed region is examined in more detail in Fig. \ref{fig:oscillating_plumes}.
 \label{fig:nu_v_time} }
@@
 The time evolution of Nu in AE and SE is compared to the mean temperature evolution
-in Fig.~\ref{fig:nu_v_time}. In Fig.~\ref{fig:nu_v_time}a, we show the evolution
+in Fig.~\ref{fig:nu_v_time}. In Fig.~\ref{fig:nu_v_time}(a), we show the evolution
 of the SE run at $S = 10^5$. The black trace shows the instantaneous value of
-Nu, and the overplotted grey line shows a moving time average of Nu. The
+Nu, and the overplotted gray line shows a moving time average of Nu. The
 time average is taken using a centered boxcar window whose width is 50 $t_{\text{ff}}$.
 The mean value of Nu evolves towards its relaxed value (dashed horizontal
-grey line) rapidly compared to $\angles{T}-T_{\text{top}}$ (blue), 
+gray line) rapidly compared to $\angles{T}-T_{\text{top}}$ (blue), 
 which approaches its evolved state (dashed horizontal blue line) slowly.
@@
 frequency than the fluctuations in the relaxed state.
-In Fig.~\ref{fig:nu_v_time}b, we show the AE traces of Nu and
+In Fig.~\ref{fig:nu_v_time}(b), we show the AE traces of Nu and
 $\angles{T}-T_{\text{top}}$ at $S = 10^5$. The times at which AE solves occur are marked
@@
 relaxed state (as seen in Fig.~\ref{fig:nu_v_time}). We examine the shaded
-region of Fig.~\ref{fig:nu_v_time}b in more detail in the top left
+region of Fig.~\ref{fig:nu_v_time}(b) in more detail in the top left
 panel of Fig.~\ref{fig:oscillating_plumes}, as well as a comparable time trace
@@
 states in which temperature fluctuations travel in their natural buoyant
-direction (Fig.~\ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
+direction (Fig.~\ref{fig:oscillating_plumes}, Ia and IIa, where cold elements fall and hot elements rise).
 However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
@@
 is shown as a function of time. On the right, temperature snapshots are shown for
-Nu maxima (Ia \& IIa) and minima (Ib \& IIb). The suppressed value of Nu at the
+Nu maxima (Ia and IIa) and minima (Ib and IIb). The suppressed value of Nu at the
 minma arises from entrainment of fluid elements whose temperature perturbations
 are wrongly signed (e.g., hot material going downwards and cold material going
-upwards in Ib \& IIb). The colorbar scaling of panels Ia\&b are the same, as
+upwards in Ib and IIb). The colorbar scaling of panels Ia\&b are the same, as
 are the scalings of panels IIa\&b. 
@@
 \caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
-RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
+RMS Peclet number ($\angles{\text{Pe}}$), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
 Symbols are located at the mean value of
@@
 The run at $S = 10^5$ marked as a
-black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
-\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
+black square is examined in more detail in Figs. \ref{fig:time_trace}-\ref{fig:oscillating_plumes},
+\ref{fig:temp_comparison}, and \ref{fig:pdf_comparison}.
 Vertical lines represent the standard deviation of the measurement,
@@
 (see Fig.~\ref{fig:oscillating_plumes}).  
-(b) Re, which measures turbulence in the solution, scales as
+(b) Pe, which measures turbulence in the solution, scales as
 Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at the fixed-temperature
 top boundary is shown; this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
-Relative error for measurements of (d) Nu, (e) Re, and (f) $\angles{T} - T_{\text{top}}$ between 
+Relative error for measurements of (d) Nu, (e) Pe, and (f) $\angles{T} - T_{\text{top}}$ between 
 AE solutions and SE solutions are shown.
@@
 Peclet number (Pe), and the mean temperature 
-are shown for AE solutions in Fig.~\ref{fig:parameter_space_comparison}a-c.
+are shown for AE solutions in Figs.~\ref{fig:parameter_space_comparison}(a)-\ref{fig:parameter_space_comparison}(c).
 Mean values are shown by the symbols (purple circles and red stars), and 
@@
 $\text{Pe} = \angles{|\bm{u}|} / \mathcal{P}$ is shown in 
-Fig.~\ref{fig:parameter_space_comparison}b, and $\angles{T} - T_{\text{top}}$ 
+Fig.~\ref{fig:parameter_space_comparison}(b), and $\angles{T} - T_{\text{top}}$ 
 (the mean temperature value minus its value at the upper, 
-fixed temperature boundary) is shown in Fig.~\ref{fig:parameter_space_comparison}c.
+fixed temperature boundary) is shown in Fig.~\ref{fig:parameter_space_comparison}(c).
 We report $\text{Nu} \propto \text{Ra}^{1/5}$,
@@
 
-In Fig.~\ref{fig:parameter_space_comparison}d-f, we report the fractional difference
+In Figs.~\ref{fig:parameter_space_comparison}(d)-\ref{fig:parameter_space_comparison}(f), we report the fractional difference
 between measurements in the AE and SE solutions.
@@
 
-For the select 3D runs conducted in this study, the scaling of Nu, Re, and $\angles{T} - T_{\text{top}}$
-reported in Fig.~\ref{fig:parameter_space_comparison}a-c is nearly identical to the
+For the select 3D runs conducted in this study, the scaling of Nu, Pe, and $\angles{T} - T_{\text{top}}$
+reported in Figs.~\ref{fig:parameter_space_comparison}(a)-\ref{fig:parameter_space_comparison}(c) is nearly identical to the
 2D simulations. Errors between AE and SE solutions in 3D fall within the same range as
-errors in 2D in Fig.~\ref{fig:parameter_space_comparison}d-f. AE is therefore
+errors in 2D in Figs.~\ref{fig:parameter_space_comparison}(d)-\ref{fig:parameter_space_comparison}(f). AE is therefore
 equally effective in both 2D and 3D, and we restrict much of our study to 2D here
@@
 our examination to a more direct comparison of AE and SE for 2D convection at
-$S = 10^5$, the time, flux, and Nu evolution of which was shown in 
-Figs.~\ref{fig:time_trace}, \ref{fig:nu_v_time}, \& \ref{fig:oscillating_plumes}.
+$S = 10^5$, the time, flux, and Nu evolution of which are shown in 
+Figs.~\ref{fig:time_trace}, \ref{fig:nu_v_time}, and \ref{fig:oscillating_plumes}.
 All comparisons that follow for these two runs occur over the times shaded in
-green in Fig.~\ref{fig:time_trace}a\&c. Measurements are sampled every
+green in Figs.~\ref{fig:time_trace}(a) and \ref{fig:time_trace}(c). Measurements are sampled every
 0.1 freefall time units for 500 total freefall time units.
@@
 solution, we compare the horizontally- and time-averaged temperature profiles 
-attained by AE and SE in Fig.~\ref{fig:temp_comparison}a.  
+attained by AE and SE in Fig.~\ref{fig:temp_comparison}(a).  
 The boundary layer width and structure are  
@@
 the mean temperature in the isothermal interior differs by roughly 0.5\%
-(Fig.~\ref{fig:temp_comparison}c).
+[Fig.~\ref{fig:temp_comparison}(c)].
 
@@
 temperature profiles, as a function of height.
-(b) Probability Distribution Functions (PDFs) and their integrated
-Cumulative Distribution Functions (CDFs)
+(b) Probability Distribution Functions (PDFs, $P(T)$) and their integrated
+Cumulative Distribution Functions (CDFs, $F(T)$)
 of point-by-point measurements of the temperature field.
@@
 of point-by-point temperature measurements are compared for the two runs
-in Fig.~\ref{fig:temp_comparison}b. To construct these PDFs, 
+in Fig.~\ref{fig:temp_comparison}(b). To construct these PDFs, 
 we interpolate the full temperature field
@@
 distribution such that its integral is unity.  The two PDFs have noticeably
-different maxima, as is expected from Fig.~\ref{fig:temp_comparison}a. 
+different maxima, as is expected from Fig.~\ref{fig:temp_comparison}(a). 
 Over long timescales, the 0.5\% difference between the two profiles would
@@
 is evident in the asymmetry of the AE PDF near the maxima
-in Fig.~\ref{fig:temp_comparison}b and also
-the trend of the mean temperature over time in Fig.~\ref{fig:time_trace}c.
+in Fig.~\ref{fig:temp_comparison}(b) and also
+the trend of the mean temperature over time in Fig.~\ref{fig:time_trace}(c).
 
@@
 PDFs to determine if they are drawn from the same underlying
-sample distribution is through the use of a Kolmogorov-Smirnov (KS) test \cite{wall&jenkins2012}.
-We calculate the KS statistic for a PDF of some value, $q$, as
+sample distribution is through the use of a Kolmogorov-Smirnov ($D_{\text{KS}}$) test \cite{wall&jenkins2012}.
+We calculate the $D_{\text{KS}}$ statistic for a PDF of some value, $q$, as
 \begin{equation}
-\KS{q} = \text{CDF}_{\text{AE}}(q) - \text{CDF}_{\text{SE}}(q),
+\KS{q} = F_{\text{AE}}(q) - F_{\text{SE}}(q),
 \label{eqn:ks_profile}
 \end{equation}
-where CDF stands for cumulative distribution function, the integral of the PDF.
+where $F$ stands for cumulative distribution function (CDF), the integral of the PDF.
 A traditional Kolmogorov-Smirnov statistic is just a single value,
@@
 $\KSstat{q}$ to gain insight into the likeness of two PDFs. 
-We show $\KS{T}$ in Fig.~\ref{fig:temp_comparison}d, and the
-CDFs used to construct it overlay the PDFs in Fig.~\ref{fig:temp_comparison}b.
+We show $\KS{T}$ in Fig.~\ref{fig:temp_comparison}(d), and the
+CDFs used to construct it overlay the PDFs in Fig.~\ref{fig:temp_comparison}(b).
 Near the maxima of the temperature PDFs, $\KSstat{T} = 0.495$, 
@@
 measurements in the AE case are at a lower $T$ than those in the SE case.
-While this difference is significant, it is also expected from Fig.~\ref{fig:temp_comparison}a.
+While this difference is significant, it is also expected from Fig.~\ref{fig:temp_comparison}(a).
 Fortunately, $\KS{T}$ is very small away from the maxima, 
@@
 \includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
-\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
-convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
+\caption{Probability distribution functions (PDFs, $P(q)$) of (a) the vertical velocity ($q = w$), (b) the horizontal velocity ($q = u$), and (c) nonlinear
+convective transport [$q = w(T_1 - \angles{T_1}_{x,y})$] are shown for 2D runs achieved through SE (blue) and AE (red)
 at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
-(d-f) The KS profiles, as defined in Eqn.~(\ref{eqn:ks_profile}),
+(d-f) The $D_{\text{KS}}$ profiles, as defined in Eq.~(\ref{eqn:ks_profile}),
 are shown for the related distributions; solid lines indicate positive values
@@
 Fig.~\ref{fig:temp_comparison}, these distributions
-show very good agreement and small values of the KS statistic.
+show very good agreement and small values of the $D_{\text{KS}}$ statistic.
 \label{fig:pdf_comparison} }
@@
 Shown are the PDFs of 
-vertical velocity ($w$, Fig.~\ref{fig:pdf_comparison}a), horizontal velocity ($u$, Fig. \ref{fig:pdf_comparison}b),
-and the nonlinear vertical convective flux ($w(T_1 - \angles{T_1}_{x,y})$, Fig.~\ref{fig:pdf_comparison}c). 
+vertical velocity [$w$, Fig.~\ref{fig:pdf_comparison}(a)], horizontal velocity [$u$, Fig. \ref{fig:pdf_comparison}(b)],
+and the nonlinear vertical convective flux [$w(T_1 - \angles{T_1}_{x,y})$, Fig.~\ref{fig:pdf_comparison}(c)]. 
 Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
-velocity boundary conditions (Eqn.~(\ref{eqn:vel_bcs})).
+velocity boundary conditions (Eq.~(\ref{eqn:vel_bcs})).
 The CDFs of each profile are overplotted, and corresponding KS profiles are
-shown in Fig.~\ref{fig:pdf_comparison}d-f.  We report
+shown in Figs.~\ref{fig:pdf_comparison}(d)-\ref{fig:pdf_comparison}(f).  We report
 $\KSstat{w} = 0.00615$, $\KSstat{u} = 0.0349$,
@@
 and heat transport between AE and SE is negligible, which is unsurprising in light of
-the Nu measurements of Fig.~\ref{fig:parameter_space_comparison}a\&d.
-This also confirms that the large $\KSstat{T}$ in Fig.~\ref{fig:temp_comparison}d is
+the Nu measurements of Figs.~\ref{fig:parameter_space_comparison}(a) and \ref{fig:parameter_space_comparison}(d).
+This also confirms that the large $\KSstat{T}$ in Fig.~\ref{fig:temp_comparison}(d) is
 not of concern, and that the AE run achieves the same relaxed convective solution
@@
 in that state (e.g., the green shaded regions of
-Fig.~\ref{fig:time_trace}a\&c are not included in the $S = 10^5$ times).
+Figs.~\ref{fig:time_trace}(a) and \ref{fig:time_trace}(c) are not included in the $S = 10^5$ times).
 All simulations
@@
 the first application of AE in a given simulation 
-(e.g., Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
+[e.g., Fig.~\ref{fig:time_trace}(c), at the arrow labeled ``1''] drastically
 increases the average timestep by fastforwarding the simulation into
@@
 the convective dynamics
-(e.g., the analogs to Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
+[e.g., the analogs to Eqs.~(\ref{eqn:bouss_BVP_momentum}) and (\ref{eqn:bouss_BVP_energy})]
 and couple those equations with knowledge of the boundary conditions
 and current dynamics as described in
-section \ref{sec:ae} and appendix \ref{appendix:recipe}.
+Sec. \ref{sec:ae} and appendix \ref{appendix:recipe}.
 In general, AE should be useful in studies where there are two disparate
@@
 \item Construct $\xi$, F$_{\text{E, ev}}$, and $\angles{\bm{u} \times \bm{\omega}}_{x,y\text{, ev}}$,
-as specified in section \ref{sec:ae}
+as specified in Sec. \ref{sec:ae}
 from the averaged profiles.

### 2018-08-17 code/plotting/pdf_comparison.py

@@ -178,7 +178,7 @@ axes[-1].set_xlim(-0.165, 0.165)
 axes[-1].set_yscale('log')
 axes[-1].set_ylim(1e-4, 1e-1)
 axes[-1].set_ylabel(r'$D_{\mathrm{KS}}(q)$')
-axes[-1].set_xlabel('Vertical Velocity', labelpad=-2)
+axes[-1].set_xlabel(r'$w$', labelpad=-2)
 axes[-1].annotate(r'$\mathrm{(d)}$', (-0.15, 1e-2), fontsize=10)
 for tick in axes[-1].get_xticklabels():
     tick.set_rotation(45)
@@ -221,7 +221,7 @@ axes[-1].plot(diff_x[diff_y < 0], -diff_y[diff_y < 0], c='k', dashes=(3,1), lw=1
 axes[-1].set_xlim(-0.165, 0.165)
 axes[-1].set_yscale('log')
 axes[-1].set_ylim(1e-4, 1e-1)
-axes[-1].set_xlabel('Horizontal Velocity', labelpad=-1)
+axes[-1].set_xlabel(r'$u$', labelpad=-1)
 axes[-1].annotate(r'$\mathrm{(e)}$', (-0.15, 1e-2), fontsize=10)
 for tick in axes[-1].get_xticklabels():
     tick.set_rotation(45)
